### 2019-01-25 notes/notes.tex
theory code in likelihood, power spectrum pipeline in analysis, power spectrum and N(z) data in analysis/data, notes in notes

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[left=2.5cm, right=2.5cm, top=2.5cm]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}
\newcommand{\nv}{\hat{\bf n}}
\title{tSZ $\times$ galaxies}
\date{\today}
\newcommand{\aj}    {{\em Astron.\ J.}}
\newcommand{\aap}{{\em Astron.\ Astrophys.}}
\newcommand{\apj}{{\em Astrophys.\ J.}}
\newcommand{\apjl}{{\em Astrophys.\ J.\ Lett.}}
\newcommand{\apjs}{{\em Astrophys.\ J.\ Suppl.}}
\newcommand{\mnras}{{\em Mon.\ Not.\ R.\ Astron.\ Soc.}}
\newcommand{\npb}{{\em Nucl.\ Phys.\ B}}
\newcommand{\nat}{{\em Nature}}
\newcommand{\physrep}{{\em Phys.\ Rep.}}
\newcommand{\pasj}{{\em Publ.\ Astron.\ Soc.\ Japan}}
\newcommand{\pasp}{{\em Publ.\ ASP}}
\newcommand{\jcap}{{\em J.\ Cosmol.\ Astropart.\ Phys.}}
\newcommand{\prd}{{\em Phys.\ Rev.\ D}}
\newcommand{\prl}{{\em Phys.\ Rev.\ Lett.}}
\newcommand{\procspie}{Proceedings of the SPIE}

\begin{document}
\maketitle

\section{Introduction}
The aim of the project is to model and measure the cross power spectrum of galaxy density and the received thermal Sunyaev-Zel'dovich effect (tSZ) signal in the universe. This is defined as the covariance of the harmonic coefficients of the projected fields:
\begin{equation}
  \langle a^g_{\ell m} a^{y*}_{\ell' m'} \rangle=C^{gY}_\ell\,\delta_{\ell\ell'}
\end{equation}

The tSZ signal emitted from a given structure is related to the projected gas pressure, $P_e(\hat{n} \chi)$, along our line of sight. For convenience, we work in units of comoving distance $\chi$, in which the Compton $y$ parameter is given by
\begin{equation}
  y(\nv) = \frac{\sigma_T}{m_e c^2} \int \frac{d\chi}{1+z}\,P_e(\chi\nv),
\end{equation}
where $\sigma_T$ is the Thomson scattering cross section.

The projected overdensities of galaxy number counts are related to the 3D number density fluctuations through a Kernel given by the redshift distribution of those galaxies
\begin{equation}
  \delta_g(\nv) = \int \frac{dN_g}{d\chi} \Delta_g(\chi\nv) d\chi.
\end{equation}

\section{Angular power spectra}
In general, let's consider two projected quantities $u(\nv)$ and $v(\nv)$, related to three-dimensional fields $U({\bf r})$ $V({\bf r})$:
\begin{equation}
  u(\nv)=\int d\chi\,W_u(\chi)\,U(\chi\nv),\hspace{12pt} v(\nv)=\int d\chi\,W_v(\chi)\,V(\chi\nv),
\end{equation}
where $W_{u,v}$ are their corresponding radial window functions.

The angular power spectrum of the projected quantities can be related to the 3D power spectrum of the non-projected ones $P_{UV}$ as:
\begin{equation}
  C_\ell^{uv} = \int \frac{dz}{H(z)} \frac{W_u(z)W_v(z)}{\chi^2(z)}\,P_{UV}\left( z, k=\frac{\ell+1/2}{\chi(z)} \right).
\end{equation}
Here, the 3D power spectrum is analogously defined as the variance of the Fourier-space 3D quantities:
\begin{equation}
  \left\langle U({\bf k})V^*({\bf k}')\right\rangle = P_{UV}(k)\,\delta({\bf k}-{\bf k}').
\end{equation}

Note that the expression above for $C_\ell^{uv}$ only holds in the \emph{Limber approximation}, and the exact expression would be
\begin{equation}
  C^{uv}_\ell=\frac{2}{\pi}\int dk\,k^2 \int d\chi_1\,W_u(\chi_1)j_\ell(k\chi_1)\int d\chi_2\,W_u(\chi_2)j_\ell(k\chi_2)\,P_{UV}(\chi_1,\chi_2,k),
\end{equation}
where we $j_\ell$ are the spherical Bessel functions. The Limber approximation is appropriate for our purposes.

Using this notation, the window functions associated with the galaxy number overdensity and the tSZ anisotropy are simply:
\begin{equation}
  W_g(\chi)=\frac{dN_g}{d\chi}=H(z)\,\frac{dN_g}{dz},\hspace{12pt}W_y(\chi)=\frac{\sigma_T}{m_ec^2}\frac{1}{1+z},
\end{equation}
where $H(z)$ is the expansion rate (in units of inverse distance).

\section{Halo model}
We will use the halo model prescription for the 3D power spectrum. Let $U(r|M)$ and $V(r|M)$ be the profile of the two fields described above as a function of the comoving distance $r$ to the centre of a halo of mass $M$, and let us define the Fourier-space profiles simply as the Fourier transform of these:
\begin{equation}
  U(k|M)\equiv4\pi \int_0^\infty dr\,r^2\,\frac{\sin(kr)}{kr}U(r|M)
\end{equation}
(and analogously for $V$).

All the profiles we will use take the form:
\begin{equation}
  U(r|M)=U_0(M,z,\vec{\theta})\,f_u(r/r_\Delta(M,z)),
\end{equation}
where $U_0$ is an overall scale-independent normalization that depends on mass, redshift and additional parameters $\vec{\theta}$, and $f_u$ is a form factor that only depends on the ratio of the comoving distance to the centre of the halo $r$ and the comoving halo size $r_\Delta$. The halo size $r_\Delta$ is commonly defined as the radius enclosing an average overdensity $\Delta$ of the critical density:
\begin{equation}
  \frac{4\pi}{3}\rho_c(z)\,\Delta\left(\frac{r_\Delta}{1+z}\right)^3=M_\Delta
  \hspace{12pt}\Longrightarrow\hspace{12pt}
  \frac{r_\Delta}{1\,{\rm Mpc}}=(1+z)\left(\frac{M_\Delta}{1.1622\times10^{12}\,M_\odot}\frac{1}{\Delta\,h^2\,E^2(z)}\right)^{1/3},
\end{equation}
where $E(z)\equiv H(z)/H(z=0)$. Another common choice is to define this radius in terms of the matter density (i.e. replacing $\Delta$ by $\Delta\Omega_M(z)$). To distinguish both cases we will write $r_{\Delta c}$ and $r_{\Delta m}$ respectively. In terms of the normalization and form factors, the Fourier-space profile can be written as:
\begin{equation}
  U(k|M)=4\pi\,r_\Delta^3\,U_0(M,z,\vec{\theta})\,\tilde{f}_u(kr_\Delta),
\end{equation}
where we have defined
\begin{equation}
  \tilde{f}(q)\equiv\int_0^\infty dx\,x^2\frac{\sin(q x)}{q x}\,f_u(x)
\end{equation}

The halo model prediction for the cross-power spectrum $P_{UV}$ then consists of two contributions, from the so-called 1-halo term and 2-halo term:
\begin{equation}
  P_{UV}(k)=P^{1h}_{UV}(k)+P^{2h}_{UV}(k).
\end{equation}
Each of these can be estimated in terms of the Fourier-space profiles as:
\begin{align}
  &P^{1h}_{UV}(k)=\int dM\,\frac{dn}{dM}\,U(k|M)\,V(k|M)\\
  &P^{2h}_{UV}(k)=P_L(k)\,\left[\int dM\frac{dn}{dM}\,b_h(M)\,U(k|M)\right]\,\left[\int dM\frac{dn}{dM}\,b_h(M)\,V(k|M)\right].
\end{align}
Here, $P_L(k)$ is the linear matter power spectrum, $dn/dM$ is the halo mass function and $b_h(M)$ is the halo bias.

\section{Specific models}
\subsection{Cosmological quantities}
We will use the linear power spectrum computed from CLASS (as provided by the Core Cosmology Library - CCL). We will use the Tinker 2010 mass function and halo bias \cite{2010ApJ...724..878T}, also provided by CCL. Distance-redshift relations etc. will also be produced by CCL

\subsection{Halo profiles}
We will use prescriptions for the halo profiles from the following references:
\begin{itemize}
\item Pressure profiles: we will try two possible prescriptions:
  \begin{enumerate}
  \item The Arnaud GNFW profile \cite{2010A&A...517A..92A}, with the mass-observable relation used by Planck \cite{2016A&A...594A..24P}. This profile takes the form:
    \begin{equation}
      P_e(r)=P_*\,p(r/r_{500c}),
    \end{equation}
    where $r_{500c}$ is the cluster radius enclosing an overdensity of 500 times the critical density (see next section). The normalization $P_*$ is given by
    \begin{equation}
      P_*=6.41\,\left(1.65 {\rm eV}\,{\rm cm}^{-3}\right)\left(\frac{h}{0.7}\right)^{8/3}\left(\frac{(h/0.7)(1-b)M_{500c}}{3\times10^{14}M_\odot}\right)^{2/3+0.12}
    \end{equation}
    and the form factor is
    \begin{equation}
      p(x)=(c_{500}x)^{-\gamma}\left[1+(c_{500}x)^\alpha\right]^{(\gamma-\beta)/\alpha},\hspace{12pt}(\alpha,\beta,\gamma,c_{500})=(1.33,4.13,0.31,1.81).
    \end{equation}

  \item The Battaglia et al. profile \cite{2012ApJ...758...75B}.
  \end{enumerate}
\item Density profile (useful for CMB lensing): we will use a truncated Navarro-Frenk and White (NFW) profile \cite{1997ApJ...490..493N}. See \cite{2017MNRAS.470.2100K} for further details on implementation.

  For a given mass definition $M_\Delta$ (see next section), the profile can be written as:
  \begin{equation}
    \rho(r)=M_\Delta u_m(r/r_\Delta),
  \end{equation}
  where
  \begin{equation}
    u_m(x)=\frac{c_\Delta^3}{4\pi\,r_\Delta^3\,[\log(1+c_\Delta)-c_\Delta/(1+c_\Delta)]}\,\frac{1}{c_\Delta x\,(1+c_\Delta x)^2}.
  \end{equation}
  The Fourier-space profile can be computed analytically (under the assumption that the profile is truncated at $r=r_\Delta$):
  \begin{align}\nonumber
    u_m(k)=\left[\log(1+c_\Delta)-\frac{c_\Delta}{(1+c_\Delta)}\right]^{-1}&\left[\cos(q)\left({\rm Ci}((1+c_\Delta)q)-{\rm Ci}(q)\right)\right.\\\nonumber
      &\left.+\sin(q)\left({\rm Si}((1+c_\Delta)q)-{\rm Si}(q)\right)\right.\\&\left.-\sin(c_\Delta q)/(1+c_\Delta q)\right]
  \end{align}
  where $q\equiv kr_\Delta/c_\Delta$.

\item Galaxy density profiles: we will use a Halo Occupation Distribution as prescribed by \cite{2005ApJ...633..791Z,2011ApJ...736...59Z}. See implementation details in \cite{2017MNRAS.470.2100K}.

  We will model the galaxy content of dark matter halos as being made up of central and satellite galaxies. Centrals lie at the center of the halo, while satellites are distributed according to a profile $u_s(r)$. Halos can have zero or one central, and the mean number of centrals for a halo of mass $M$ is modelled as a smoothed step function
  \begin{equation}
    \langle N_c(M)\rangle=\frac{1}{2}\left[1+{\rm erf}\left(\frac{\log(M/M_{\rm min})}{\sigma_{\rm lnM}}\right)\right].
  \end{equation}
  We then assume that satellites can only be formed if a halo has a central and has a mass larger than some threshold $M_0$. In that case, average number of satellites is a power law of the form:
  \begin{equation}
    \langle N_s(M)\rangle=\Theta(M-M_0)\,\left(\frac{M-M_0}{M_1'}\right)^{\alpha_s}.
  \end{equation}
  Furthermore, we may assume that only a fraction $f_c$ of centrals make it into our selection.

  Putting everything together, the galaxy overdensity profile is given by:
  \begin{equation}
    u_g(k|M)=\bar{n_g}^{-1}\langle N_c(M)\rangle\left[f_c+\langle N_s(M)\rangle\,u_s(k|M)\right],
  \end{equation}
  where the number density of galaxies is
  \begin{equation}
    \bar{n_g}\equiv\int dM\,\frac{dn}{dM}\langle N_c(M)\rangle\left[f_c+\langle N_s(M)\rangle\right].
  \end{equation}

  Finally, for simplicity we will assume that the satellites follow the matter distribution: $u_s(k|M)=u_m(k|M)$.

\end{itemize}
We will start by implementing these as defined in the papers, and then decide which parameters of them to free up (an obvious one is $1-b$, but we may want to be more general than that).

\subsection{Translating between mass definitions}
We may need to translate between masses defined with different prescriptions. All of them can be described by the following equation, describing the relation between the mass and the size of a halo:
\begin{equation}
  M_{\Delta_x}=\frac{4\pi}{3}\rho_c(z)\Delta_x\,R_{\Delta_x}^3,
\end{equation}
here $\Delta_x=\Delta\,f_x$, where $\Delta$ is a number (e.g. 200, 500 etc.) and $x$ is either $c$ or $m$, to distinguish between masses defined with respect to the critical density or the matter density. In either case:
\begin{equation}
  f_c=1,\hspace{12pt} f_m=\Omega_M(z).
\end{equation}

Now, under the assumption that halos have an NFW density profile, it's easy to calculate the mass enclosed within a given radius:
\begin{equation}
  M(<R)=4\pi\rho_0\,r_s^3\left[\ln\left(1+\frac{R}{r_s}\right)-\frac{R/r_s}{1+R/r_s}\right]
\end{equation}
Now, writing $M_{\Delta_x}=M(<R_{\Delta_x})$ and defining the concentration parameter $c_{\Delta_x}=R_{\Delta_x}/r_s$, we have, for two different mass definitions $\Delta_x$ and $\Delta'_y$:
\begin{align}
  M_{\Delta_x}=\frac{4\pi}{3}\rho_c(z)\Delta_x\,R_{\Delta_x}^3=4\pi\rho_0\,\left(\frac{R_{\Delta_x}}{c_{\Delta_x}}\right)^3\left[\ln\left(1+c_{\Delta_x}\right)-\frac{c_{\Delta_x}}{1+c_{\Delta_x}}\right]\\
  M_{\Delta'_y}=\frac{4\pi}{3}\rho_c(z)\Delta'_y\,R_{\Delta'_y}^3=4\pi\rho_0\,\left(\frac{R_{\Delta'_y}}{c_{\Delta'_y}}\right)^3\left[\ln\left(1+c_{\Delta'_y}\right)-\frac{c_{\Delta'_y}}{1+c_{\Delta'_y}}\right].
\end{align}
Taking the ratio of both equations, we obtain a relation between the concentration parameters for both mass definitions:
\begin{equation}
  \frac{c_{\Delta_x}^3\Delta_x}{c_{\Delta'_y}^3\Delta'_y}=\frac{\ln\left(1+c_{\Delta_x}\right)-\frac{c_{\Delta_x}}{1+c_{\Delta_x}}}{\ln\left(1+c_{\Delta'_y}\right)-\frac{c_{\Delta'_y}}{1+c_{\Delta'_y}}}.
\end{equation}

So, in order to translate between $M_{\Delta_x}$ and $M_{\Delta'_y}$:
\begin{enumerate}
\item Get a concentration-mass relation for $M_{\Delta_x}$ and compute both $c_{\Delta_x}$ and $R_{\Delta_x}$.
\item Obtain $c_{\Delta'_y}$ by solving the equation above numerically.
\item From $c_{\Delta'_y}$ obtain $R_{\Delta'_y}$ and then $M_{\Delta'_y}$.
\end{enumerate}

\subsection{Halo profile statistics}
To fully account for the statistics of any halo observable, let's rederive the halo model power spectrum carefully. A given quantity $U$ at a position ${\bf x}$ is given by the cumulative effect of all halos in the universe:
\begin{equation}
  U({\bf x})=\sum_h u_h({\bf x}-{\bf r}_h)N_h
\end{equation}
where the sum goes over a set of voxels covering all of space, which have been chosen to be sufficiently small so that the number of halos in each voxel, $N_h$ is either 0 or 1. ${\bf r}_h$ is the position of the halo in voxel $h$, and $u_h({\bf r})$ is the profile of $U$ around that halo.

The Fourier transform of $U({\bf x})$ is
\begin{align}\nonumber
  U_{\bf k}=\int dx^3\,U({\bf x})\,e^{-i{\bf k}{\bf x}}=\sum_h N_h u_h({\bf k}) e^{-{\bf r}_i{\bf k}},
\end{align}
where $u_h({\bf k})$ is the Fourier transform of $u_h({\bf r})$.

Now, let's take the two-point correlator of two such fields, $U$ and $V$, in Fourier space:
\begin{align}
  \left\langle U_{\bf k}V^*_{\bf q}\right\rangle_{p,H,\delta}&=\left\langle\sum_{h_1h_2}N_{h_1}N_{h_2}\,\left\langle u_{h_1}({\bf k})v^*_{h_2}({\bf q})\right\rangle_p\,e^{-i({\bf r}_{h_1}{\bf k}-{\bf r}_{h_2}{\bf q})}\right\rangle_{H,\delta}
\end{align}
Here, the subscripts $p,H,\delta$ under each ensemble average denote averaging over realizations of the profile for a given halo ($p$), over the realizations of the halo distribution ($H$) and over the realizations of the underlying dark matter distribution.

The expression above can be rewritten as:
\begin{align}\\
  \left\langle U_{\bf k}V^*_{\bf q}\right\rangle_{p,H,\delta}=&\left\langle\sum_h N_h\,\left\langle u_h({\bf k})v^*_h({\bf q})\right\rangle_p\,e^{-ir_h\,({\bf k}-{\bf q})}\right\rangle_{H,\delta}\\
  &+\left\langle\sum_{h_1\neq h_2}N_{h_1}N_{h_2}\,\left\langle u_{h_1}({\bf k})\right\rangle_p\left\langle v^*_{h_2}({\bf q})\right\rangle_p\,e^{-i({\bf r}_{h_1}{\bf k}-{\bf r}_{h_2}{\bf q})}\right\rangle_{H,\delta}\\
  &+\left\langle\sum_{h_1\neq h_2}N_{h_1}N_{h_2}\,{\rm Cov}\left(u_{h_1}({\bf k})v^*_{h_2}({\bf q})\right)_p\,e^{-i({\bf r}_{h_1}{\bf k}-{\bf r}_{h_2}{\bf q})}\right\rangle_{H,\delta}
\end{align}
Under the {\bf assumption} that the profiles for two different halos are uncorrelated, we can discard the last term, and the remaining ones are the so-called ``1-halo'' and ``2-halo'' terms.

Let's first concentrate on the 2-halo term. Assuming that halos of mass $M$ are Poisson-distributed over the underlying halo density distribution $\delta_M({\bf x})$, the average over $H$ is equivalent to replacing $N_h$ with $\int dM\,n(M)\,dr^3_h(1+\delta_M({\bf r}_h))$, where $n(M)$ is the halo mass function. In that case we obtain:
\begin{align}
  \left\langle U_{\bf k}V^*_{\bf q}\right\rangle_{p,H,\delta}^{2h}=&\int dM_1\,n(M_1) \langle u(k|M_1)\rangle_p\int dM_2\,n(M_2) \langle v^*(q|M_2)\rangle_p\\&\left\langle\sum_{h_1\neq h_2}dr_{h_1}^3dr_{h_2}^3(1+\delta_{M_1}({\bf r}_{h_1}))(1+\delta_{M_2}({\bf r}_{h_2}))e^{-i{\bf r}_{h_1}{\bf k}}e^{i{\bf r}_{h_2}{\bf q}}\right\rangle_{\delta},
\end{align}
where  we have {\bf assumed} that the only quantity that determines the statistics of halo profiles is the halo mass. Under the {\bf assumption} that the halo overdensities are deterministically related to the linear matter overdensity through a simple bias function $b(M)$ (i.e. $\delta_M({\bf x})=b(M)\delta({\bf x})$), and ignoring the unobservable ${\bf k}=0$ mode we obtain:
\begin{align}
  \left\langle U_{\bf k}V^*_{\bf q}\right\rangle_{p,H,\delta}^{2h}=\left\langle\delta_{\bf k}\delta^*_{\bf q}\right\rangle_\delta\int dM\,n(M)\,b(M)\,\langle u(k|M)\rangle_p\,\int dM\,n(M)\,b(M) \langle v^*(q|M)\rangle_p.
\end{align}
Using the definition of the linear matter power spectrum ($\langle\delta_{\bf k}\delta_{\bf q}^*\rangle=(2\pi)^3\delta^{\cal D}({\bf k}-{\bf q})P_L(k)$), we obtain the final result:
\begin{align}
  \left\langle U_{\bf k}V^*_{\bf q}\right\rangle_{p,H,\delta}^{2h}=(2\pi)^3\delta^{\cal D}({\bf k}-{\bf q})\,b_U(k)\,b_V(k)\,P_L(k),
\end{align}
where we have defined
\begin{align}
  b_U(k)\equiv\int dM n(M) b(M) \left\langle u(k|M)\right\rangle_p.
\end{align}

Using the same approximation, the 1-halo term reads:
\begin{align}
  \left\langle U_{\bf k}V^*_{\bf q}\right\rangle_{p,H,\delta}^{1h}&=(2\pi)^3\delta^{\cal D}({\bf k}-{\bf q})\int dM\,n(M)\,\left\langle u(k|M) v^*(k|M)\right\rangle_p\\
  &=(2\pi)^3\delta^{\cal D}({\bf k}-{\bf q})\int dM\,n(M)\,\left[\left\langle u(k|M)\right\rangle_p\left\langle v^*(k|M)\right\rangle_p+{\rm Cov}_p\left(u(k|M),v(k|M)\right)\right]
\end{align}

\bibliography{notes}
\bibliographystyle{habbrv}
\end{document}

### 2019-01-25 analysis/analysis.py

@@ -1,0 +1,322 @@
+from __future__ import print_function
+from optparse import OptionParser
+import healpy as hp
+import numpy as np
+import matplotlib.pyplot as plt
+import pymaster as nmt
+import os
+from scipy.interpolate import interp1d
+
+def opt_callback(option, opt, value, parser):
+  setattr(parser.values, option.dest, value.split(','))
+
+parser=OptionParser()
+parser.add_option("--nside",dest='nside',default=512,type=int,help="HEALPix Nside resolution parameter")
+parser.add_option("--recreate",dest='recreate',default=False,action='store_true',
+                  help="Recompute power spectra and covariances?")
+parser.add_option("--linlog_binning",dest='use_linlog',default=False,action='store_true',
+                  help="Use hybrid lin-log binning for bandpowers")
+parser.add_option("--nlb",dest='nlb',default=20,type=int,
+                  help="If using linear bandpowers, this is the bandpowers width")
+(o, args) = parser.parse_args()
+
+#TODO: y beam
+nside_use=o.nside
+recreate=o.recreate
+use_linlog=o.use_linlog
+nlb_use=o.nlb
+
+predir_out='out'
+predir_out+="_ns%d"%nside_use
+if use_linlog :
+    predir_out+='_linlog'
+else :
+    predir_out='_nb%d'%nlb_use
+os.system("mkdir -p "+predir_out)
+    
+def read_map(name,fname,nside_out,field=0) :
+    print("  Reading "+name)
+    return hp.ud_grade(hp.read_map(fname,verbose=False),nside_out=nside_out)
+
+def get_field(name,fname,nside,mask,is_ndens=False) :
+    mask_bn=np.ones_like(mask); mask_bn[mask<=0]=0; #Get binary mask
+    mp=read_map(name,fname,nside) # Read map
+    mp*=mask_bn #Remove masked pixels
+    ndens=0
+    if is_ndens : #Get overdensity if needed
[…]

### 2019-01-25 analysis/analysis.py
added linear binning files

@@ -31,7 +31,7 @@ predir_out+="_ns%d"%nside_use
 if use_linlog :
     predir_out+='_linlog'
 else :
-    predir_out='_nb%d'%nlb_use
+    predir_out+='_nb%d'%nlb_use
 os.system("mkdir -p "+predir_out)
     
 def read_map(name,fname,nside_out,field=0) :

### 2019-01-30 notes/notes.tex
added section on HOD variance

@@
 
+\subsection{The HOD example}
+In the case of HOD modelling of the galaxy overdensity, the galaxy density profile is modelled as:
+\begin{equation}
+  u({\bf r})=N_c\,\delta^{\cal D}({\bf r})+n_s({\bf r}),
+\end{equation}
+where $N_c$ is the number of central galaxies in the halo and $n_s$ is the density profile of satellite galaxies.
+Most commonly, $N_c$ is assumed to be either 0 or 1, and therefore has a Bernoulli distribution with probability $P(N_c=1|M)=1-P(N_c=0|M)\equiv \bar{N}_c(M)$.
+The satellite galaxies are usually assumed to be Poisson-distributed around a profile that is proportional to the NFW profile ($u_{\rm NFW}({\bf r}|M)$), as long as the halo already has a central galaxy.
+The last statement means that the number of satellite galaxies found in a differential volume element $d{\bf r}^3$ around ${\bf r}$ has a conditional distribution
+\begin{equation}
+ P(n_s({\bf r})\,d{\bf r}^3=N_s|N_c,M)=
+ \left\{\begin{array}{lll}
+          1 & {\rm if} & N_c=0\,{\rm and}\,N_s=0\\
+          0 & {\rm if} & N_c=0\,{\rm and}\,N_s>0\\
+          e^{-\lambda}\frac{\lambda^{N_s}}{N_s!} & {\rm if} & N_c=1
+        \end{array}\right.
+\end{equation}
+where $\lambda\equiv d{\bf r}^3\bar{N_s}(M)\,u_{\rm NFW}({\bf r}|M)$.
+Furthermore, the number of galaxies found in different volume elements are independent.
+The mean and variance of this distribution are:
+\begin{equation}
+ {\rm E}(n_s({\bf r})\,d{\bf r}^3|M)={\rm Var}(n_s({\bf r})\,d{\bf r}^3|M)=d{\bf r}^3 \bar{N}_s(M)\,u_{\rm NFW}({\bf r}|M).
+\end{equation}
+
+Using this model, the mean Fourier profile becomes
+\begin{align}
+ \langle u({\bf k})\rangle
+ &=\left\langle \sum_{\bf r} d{\bf r}^3 \left[N_c\,\delta^{\cal D}({\bf r})+n_s({\bf r})\right]e^{-i{\bf k}{\bf r}}\right\rangle\\
+ &=\bar{N_c}\left[1+\bar{N}_s\,u_{\rm NFW}(k|M)\right]\\
+\end{align}
+and its variance is
+\begin{align}
+\langle |u({\bf k})|^2\rangle
+ &=\left\langle \sum_{\bf x} d{\bf x}^3\sum_{\bf y} d{\bf y}^3 \left[N_c\,\delta^{\cal D}({\bf x})+n_s({\bf x})\right]\,\left[N_c\,\delta^{\cal D}({\bf y})+n_s({\bf y})\right]e^{i{\bf k}({\bf y}-{\bf x})}\right\rangle\\
+ &=\bar{N}_c\left(\left[1+\bar{N}_s\,u_{\rm NFW}({\bf k})\right]^2+\bar{N}_s\right)
+\end{align}
+
 \bibliography{notes}

### 2019-01-30 likelihood.py
working likelihood (no corrections)

@@ -66,15 +66,7 @@ def callbackf(X):
 
 
 p0 = [12, 12.2, 13.65, 0.5, 1.0, 0.8]
-bds = [(6, 17),     # Mmin
-       (6, 17),     # M0
-       (6, 17),     # M1
-       (0.1, 1),    # sigma_lnM
-       (0.5, 1.5),  # alpha
-       (0.1, 1.0)]  # fc
-res = minimize(func, p0, method="Powell",
-               bounds=bds, callback=callbackf,
-               options={"maxiter" : 6000})
+res = minimize(func, p0, method="Powell", callback=callbackf, options={"maxiter" : 6000})
 
 
 ### PLOTS ##

### 2019-01-30 profile2D.py

@@ -195,7 +195,7 @@ class HOD(object):
 
     def kernel(self, cosmo, a):
         """The galaxy number overdensity window function."""
-        unit_norm = 3.3356409519815205e-04  # 1/c
+        unit_norm = 3.3356409519815204e-04  # 1/c
         Hz = ccl.h_over_h0(cosmo, a)*cosmo["h"]
         return Hz*unit_norm * self.nzf(1/a-1)
 
@@ -204,12 +204,13 @@ class HOD(object):
         """Computes the overall profile normalisation for the angular cross-
         correlation calculation."""
         # extract parameters
-        Mmin = 10**kwargs["Mmin"]
-        M0 = 10**kwargs["M0"]
-        M1 = 10**kwargs["M1"]
-        sigma_lnM = kwargs["sigma_lnM"]
-        alpha = kwargs["alpha"]
-        fc = kwargs["fc"]
+        Mmin = 10**kwargs["Mmin"] if (6 <= kwargs["Mmin"] <= 17) else -np.inf
+        M0 = 10**kwargs["M0"] if (6 <= kwargs["M0"] <= 17) else -np.inf
+        M1 = 10**kwargs["M1"] if (6 <= kwargs["M1"] <= 17) else -np.inf
+        sigma_lnM = 10**kwargs["sigma_lnM"] if (0.1 <= kwargs["sigma_lnM"] <= 1.0) else -np.inf
+        alpha = 10**kwargs["alpha"] if (0.5 <= kwargs["alpha"] <= 1.5) else -np.inf
+        fc = 10**kwargs["fc"] if (0.1 <= kwargs["fc"] <= 1.0) else -np.inf
+
 
         logMmin, logMmax = (6, 17) # log of min and max halo mass [Msun]
         mpoints = int(256)         # number of integration points
@@ -231,12 +232,12 @@ class HOD(object):
         Default parameter values from Krause & Eifler (2014).
         """
         # extract parameters
-        Mmin = 10**kwargs["Mmin"]
-        M0 = 10**kwargs["M0"]
-        M1 = 10**kwargs["M1"]
-        sigma_lnM = kwargs["sigma_lnM"]
-        alpha = kwargs["alpha"]
-        fc = kwargs["fc"]
+        Mmin = 10**kwargs["Mmin"] if (6 <= kwargs["Mmin"] <= 17) else -np.inf
[…]

### 2019-02-02 notes/notes.tex
removed shot noise from HOD

@@
 \begin{equation}
-  u({\bf r})=N_c\,\delta^{\cal D}({\bf r})+n_s({\bf r}),
+  u({\bf r})=n_g^{-1}\left[N_c\,\delta^{\cal D}({\bf r})+n_s({\bf r})\right],
 \end{equation}
-where $N_c$ is the number of central galaxies in the halo and $n_s$ is the density profile of satellite galaxies.
+where $n_g$ is the total mean density of galaxies, $N_c$ is the number of central galaxies in the halo and $n_s$ is the density profile of satellite galaxies.
 Most commonly, $N_c$ is assumed to be either 0 or 1, and therefore has a Bernoulli distribution with probability $P(N_c=1|M)=1-P(N_c=0|M)\equiv \bar{N}_c(M)$.
@@
  \langle u({\bf k})\rangle
- &=\left\langle \sum_{\bf r} d{\bf r}^3 \left[N_c\,\delta^{\cal D}({\bf r})+n_s({\bf r})\right]e^{-i{\bf k}{\bf r}}\right\rangle\\
- &=\bar{N_c}\left[1+\bar{N}_s\,u_{\rm NFW}(k|M)\right]\\
+ &=\left\langle n_g^{-1}\sum_{\bf r} d{\bf r}^3 \left[N_c\,\delta^{\cal D}({\bf r})+n_s({\bf r})\right]e^{-i{\bf k}{\bf r}}\right\rangle\\
+ &=n_g^{-1}\bar{N_c}\left[1+\bar{N}_s\,u_{\rm NFW}(k|M)\right]\\
 \end{align}
@@
   \langle |u({\bf k})|^2\rangle
- &=\left\langle \sum_{\bf x} d{\bf x}^3\sum_{\bf y} d{\bf y}^3 \left[N_c\,\delta^{\cal D}({\bf x})+n_s({\bf x})\right]\,\left[N_c\,\delta^{\cal D}({\bf y})+n_s({\bf y})\right]e^{i{\bf k}({\bf y}-{\bf x})}\right\rangle\\
- &=\bar{N}_c\left(\left[1+\bar{N}_s\,u_{\rm NFW}({\bf k})\right]^2+\bar{N}_s\right)
+  &=n_g^{-2}\left\langle \sum_{\bf x} d{\bf x}^3\sum_{\bf y} d{\bf y}^3 \left[N_c\,\delta^{\cal D}({\bf x})+n_s({\bf x})\right]\,\left[N_c\,\delta^{\cal D}({\bf y})+n_s({\bf y})\right]e^{i{\bf k}({\bf y}-{\bf x})}\right\rangle\\
+  &=n_g^{-2}\bar{N}_c\left(\left[1+\bar{N}_s\,u_{\rm NFW}({\bf k})\right]^2+\bar{N}_s\right)
+\end{align}
+
+So far we have ignored the total galaxy density $n_g$. This is simply given by 
+\begin{equation}
+  n_g=\int dM\,n(M)\,\bar{N}_c(M)\left(1+\bar{N}_s(M)\right).
+\end{equation}
+We have also ignored the fact that we need to subtract the shot-noise contribution from the total galaxy power spectrum.
+This is given by $1/n_g$, which is equivalent to modifying the variance of the galaxy profile as:
+\begin{align}
+  \langle |u({\bf k})|^2\rangle
+  &=n_g^{-2}\left[\bar{N}_c\left(\left[1+\bar{N}_s\,u_{\rm NFW}({\bf k})\right]^2+\bar{N}_s\right)-\bar{N}_c(1+\bar{N}_s)\right]\\
+  &=n_g^{-2}\bar{N}_c\left[2\bar{N}_s\,u_{\rm NFW}({\bf k})+\bar{N}_s^2u_{\rm NFW}^2({\bf k})\right]
 \end{align}

### 2019-02-05 likelihood/MCMC.py
likelihood works w/o 1h-term correction

@@ -1,9 +1,9 @@
 import numpy as np
-from scipy.optimize import minimize
+import emcee
 import pyccl as ccl
 
-import pspec
 import profile2D
+import pspec
 
 
 
@@ -23,7 +23,7 @@ def func(args):
     if not prior_test:  # deal with priors
         lnprob = -np.inf
     else:
-        Cl = pspec.ang_power_spectrum(cosmo, ells, prof, prof, is_zlog=False, **kwargs)
+        Cl = pspec.ang_power_spectrum(cosmo, ells, prof, prof, **kwargs)
         if Cl is None:  # deal with zero division (unphysical)
             lnprob = -np.inf
         else :
@@ -31,17 +31,6 @@ def func(args):
 
 #    print(args)  # output trial parameter values
     return -lnprob
-
-
-
-Neval = 1  # display number of evaluations
-def callbackf(X):
-    global Neval
-    print("{0:4d}   {1: 3.6f}   {2: 3.6f}   {3: 3.6f}   \
-          {4: 3.6f}   {5: 3.6f}   {6: 3.6f}".format(Neval, X[0], X[1], X[2],
-                                                           X[3], X[4], X[5]))
-    Neval += 1
-
 
 
 ## DATA ##
@@ -61,7 +50,7 @@ cells = cells[mask]
 covar=dcov['cov']
 covar = covar[mask, :][:, mask]
 err_ell = np.sqrt(np.diag(covar))
-
+I = np.linalg.inv(covar)  # inverse covariance
 
 
 ## MODEL ##
@@ -70,35 +59,9 @@ cosmo = ccl.Cosmology(Omega_c=0.27, Omega_b=0.045, h=0.67, sigma8=0.8, n_s=0.96)
 nz = "../analysis/data/dndz/2MPZ_bin1.txt"
 prof = profile2D.HOD(nz_file=nz)
 
+ndim, nwalkers = 6, 100
+ivar = 1 / np.random.rand(ndim)
+p0 = [12.061706, 12.881403, 13.567549, 0.632100, 1.238674, 0.644111]
 
-kwargs = {"Mmin"      : 12.012471,
-          "M0"        : 12.5394811,
-          "M1"        : 13.56884228,
-          "sigma_lnM" : 0.68020429,
-          "alpha"     : 1.26862144,
-          "fc"        : 0.53721529}
[…]

### 2019-02-05 likelihood/cosmotools.py

@@ -3,7 +3,7 @@ This script contains definitions of useful cosmological functions for quick
 retrieval and data analysis.
 """
 
-
+import numpy as np
 import pyccl as ccl
 
 

### 2019-02-05 likelihood/profile2D.py

@@ -219,7 +219,11 @@ class HOD(object):
         delta_matter = self.Delta/ccl.omega_x(cosmo, a, "matter")  # CCL uses Dm
         mfunc = ccl.massfunc(cosmo, M_arr, a, delta_matter)        # mass function
         Nc = 0.5 * (1 + erf((np.log10(M_arr/Mmin))/sigma_lnM))     # centrals
-        Ns = np.heaviside(M_arr-M0, 0.5) * ((M_arr-M0)/M1)**alpha  # satellites
+        # Satellites (modified heaviside)
+        diff = M_arr-M0            # mass difference (no negative mass!)
+        pos = np.argmax(diff > 0)  # first positive (physical) value
+        Ns = np.heaviside(diff[pos:], 0.5) * (diff[pos:]/M1)**alpha
+        Ns = np.append(np.zeros(pos), Ns)  # for M < M0, no satellites
 
         dng = mfunc*Nc*(fc+Ns)  # integrand
 
@@ -241,7 +245,8 @@ class HOD(object):
 
         # HOD Model
         Nc = 0.5 * (1 + erf((np.log10(M/Mmin))/sigma_lnM))  # centrals
-        Ns = np.heaviside(M-M0, 0.5) * ((M-M0)/M1)**alpha   # satellites
+        # satellites
+        Ns = np.heaviside((M-M0)/M1, 0.5) * ((M-M0)/M1)**alpha if M > M0 else 0
 
         H = NFW().fourier_profile(cosmo, k, M, a)
 

### 2019-02-05 likelihood/pspec.py

@@ -43,7 +43,7 @@ def power_spectrum(cosmo, k_arr, a, p1, p2,
     # Profile normalisations
     Unorm = p1.profnorm(cosmo, a, **kwargs)
     Vnorm = p2.profnorm(cosmo, a, **kwargs)
-    if (Unorm < 1E-16) or (Vnorm < 1E-16):
+    if (Unorm < 1E-16) or (Vnorm < 1E-16):  # deal with zero division
         return None
 
     # Set up integration boundaries
@@ -152,7 +152,7 @@ def ang_power_spectrum(cosmo, l_arr, p1, p2,
                              logMrange=logMrange, mpoints=mpoints,
                              include_1h=include_1h, include_2h=include_2h,
                              **kwargs)
-        if Puv is None:
+        if Puv is None:  # deal with zero division
             return None
 
         I[:, x] = N[x] * Puv

### 2019-02-05 likelihood/likelihood.py
added correct HOD profile variance

@@ -21,22 +21,19 @@ def func(args):
                  (0.1 <= kwargs["fc"] <= 1.0)
 
     # Piecewise probability handling
-#    if not prior_test:
-#        lnprob = -np.inf
-#    else:
-#        Cl = pspec.ang_power_spectrum(cosmo, ells, prof, prof, is_zlog=False, **kwargs)
-#        if Cl is None:
-#            lnprob = -np.inf
-#        else :
-#            lnprob = -0.5*np.dot(cells-Cl, np.dot(I, cells-Cl))
+    if not prior_test:
+        lnprob = -np.inf
+    else:
+        Cl = pspec.ang_power_spectrum(cosmo, ells, prof, prof,
+                                      zrange=(0.001,0.3),zpoints=64, is_zlog=False,
+                                      **kwargs)
+        if Cl is None:
+            lnprob = -np.inf
+        else :
+            lnprob = -0.5*np.dot(cells-Cl, np.dot(I, cells-Cl))
 
-    Cl = pspec.ang_power_spectrum(cosmo, ells, prof, prof, is_zlog=False, **kwargs)
-    lnprob = -0.5*np.dot(cells-Cl, np.dot(I, cells-Cl))
-
-#    print(args)  # output trial parameter values
+    print(args,-2*lnprob,len(ells))  # output trial parameter values
     return -lnprob
-
-
 
 Neval = 1  # display number of evaluations
 def callbackf(X):
@@ -45,8 +42,6 @@ def callbackf(X):
           {4: 3.6f}   {5: 3.6f}   {6: 3.6f}".format(Neval, X[0], X[1], X[2],
                                                            X[3], X[4], X[5]))
     Neval += 1
-
-
 
 ## DATA ##
 dcl = np.load("../analysis/out_ns512_linlog/cl_2mpz_2mpz.npz")
@@ -74,32 +69,28 @@ cosmo = ccl.Cosmology(Omega_c=0.27, Omega_b=0.045, h=0.67, sigma8=0.8, n_s=0.96)
 nz = "../analysis/data/dndz/2MPZ_bin1.txt"
 prof = profile2D.HOD(nz_file=nz)
 
-kwargs = {"Mmin"      : 12,
-          "M0"        : 12.2,
-          "M1"        : 13.65,
[…]

### 2019-02-05 likelihood/profile2D.py

@@ -48,22 +48,22 @@ class Arnaud(object):
         return 1
 
 
-#    def norm(self, cosmo, M, a, b=0.4):
-#        """Computes the normalisation factor of the Arnaud profile.
-#
-#        .. note:: Normalisation factor is given in units of ``eV/cm^3``. \
-#        (Arnaud et al., 2009)
-#        """
-#        aP = 0.12  # Arnaud et al.
-#        h70 = cosmo["h"]/0.7
-#        P0 = 6.41 # reference pressure
-#
-#        K = 1.65*h70**2*P0 * (h70/3e14)**(2/3+aP)  # prefactor
-#
-#        Pz = ccl.h_over_h0(cosmo, a)**(8/3)  # scale factor (z) dependence
-#        PM = (M*(1-b))**(2/3+aP)             # mass dependence
-#        P = K*Pz*PM
-#        return P
+    def norm(self, cosmo, M, a, b=0.4):
+        """Computes the normalisation factor of the Arnaud profile.
+
+        .. note:: Normalisation factor is given in units of ``eV/cm^3``. \
+        (Arnaud et al., 2009)
+        """
+        aP = 0.12  # Arnaud et al.
+        h70 = cosmo["h"]/0.7
+        P0 = 6.41 # reference pressure
+
+        K = 1.65*h70**2*P0 * (h70/3e14)**(2/3+aP)  # prefactor
+
+        Pz = ccl.h_over_h0(cosmo, a)**(8/3)  # scale factor (z) dependence
+        PM = (M*(1-b))**(2/3+aP)             # mass dependence
+        P = K*Pz*PM
+        return P
 
 
     def form_factor(self, x):
@@ -119,7 +119,7 @@ class Arnaud(object):
         return F
 
 
-    def fourier_profile(self, cosmo, k, M, a, **kwargs):
+    def fourier_profiles(self, cosmo, k, M, a, **kwargs):
         """Computes the Fourier transform of the Arnaud profile.
 
         .. note:: Output units are ``[norm] Mpc^3``
@@ -127,8 +127,8 @@ class Arnaud(object):
         b = kwargs["b_hydro"]  # hydrostatic bias
         R = ct.R_Delta(cosmo, M, a, self.Delta) / a  # R_Delta*(1+z) [Mpc]
         F = self.norm(cosmo, M, a, b) * self._fourier_interp(np.log10(k*R))
[…]

### 2019-02-05 likelihood/pspec.py

@@ -60,10 +60,14 @@ def power_spectrum(cosmo, k_arr, a, p1, p2,
     # initialise integrands
     I1h, I2h_1, I2h_2 = [np.zeros((len(k_arr), len(M_arr)))  for i in range(3)]
     for m, M in enumerate(M_arr):
-        U = p1.fourier_profile(cosmo, k_arr, M, a, **kwargs)
-        V = p2.fourier_profile(cosmo, k_arr, M, a, **kwargs)
+        U,UU = p1.fourier_profiles(cosmo, k_arr, M, a, **kwargs)
+        if p1==p2 :
+            V=U; UV=UU
+        else :
+            V,VV = p2.fourier_profiles(cosmo, k_arr, M, a, **kwargs)
+            UV=U*V
 
-        I1h[:, m] = mfunc[m]*U*V
+        I1h[:, m] = mfunc[m]*UV
         I2h_1[:, m] = bh[m]*mfunc[m]*U
         I2h_2[:, m] = bh[m]*mfunc[m]*V
 
@@ -79,12 +83,17 @@ def power_spectrum(cosmo, k_arr, a, p1, p2,
     n0_1h = (rhoM - np.sum(mfunc*M_arr) * dlM) / M_arr[0]
     n0_2h = (rhoM - np.sum(mfunc*bh*M_arr) * dlM) / M_arr[0]
 
-    prof1_0 = p1.fourier_profile(cosmo, k_arr, M_arr[0], a, **kwargs)
-    prof2_0 = p2.fourier_profile(cosmo, k_arr, M_arr[0], a, **kwargs)
+    prof1_0,prof1_02 = p1.fourier_profiles(cosmo, k_arr, M_arr[0], a, **kwargs)
+    if p1==p2 :
+        prof2_0=prof1_0
+        prof12_0=prof1_02
+    else :
+        prof2_0,prof2_02 = p2.fourier_profiles(cosmo, k_arr, M_arr[0], a, **kwargs)
+        prof12_0=prof1_0*prof2_0
 
     b2h_1 += n0_2h*prof1_0
     b2h_2 += n0_2h*prof2_0
-    P1h += n0_1h*prof1_0*prof2_0
+    P1h += n0_1h*prof12_0
 
     F = (include_1h*P1h + include_2h*(Pl*b2h_1*b2h_2)) / (Unorm*Vnorm)
     return F

### 2019-04-01 notes/notes.tex
updated notes, added 1h-2h split when plotting

@@
 \begin{align}
-  &P^{1h}_{UV}(k)=\int dM\,\frac{dn}{dM}\,U(k|M)\,V(k|M)\\
-  &P^{2h}_{UV}(k)=P_L(k)\,\left[\int dM\frac{dn}{dM}\,b_h(M)\,U(k|M)\right]\,\left[\int dM\frac{dn}{dM}\,b_h(M)\,V(k|M)\right].
+  &P^{1h}_{UV}(k)=\int dM\,\frac{dn}{dM}\,\langle U(k|M)\,V(k|M)\rangle\\
+  &P^{2h}_{UV}(k)=P_L(k)\,\left[\int dM\frac{dn}{dM}\,b_h(M)\,\langle U(k|M)\rangle\right]\,\left[\int dM\frac{dn}{dM}\,b_h(M)\,\langle V(k|M)\rangle\right].
 \end{align}
@@
 
+\item 1-halo covariance: note that different halo properties are not perfectly correlated due to e.g. hidden variables (age, merger history, environment etc.). I.e. in almost all cases
+  \begin{equation}
+    \langle U(k|M) V(k|M)\rangle\neq\langle U(k|M)\rangle\langle V(k|M)\rangle.
+  \end{equation}
+  In the particular case of the cross-correlation between tSZ flux and galaxy overdensity, we will model the scatter between both quantities by introducing one additional parameter $\rho_{yg}$:
+  \begin{equation}
+    \langle u_g(k) u_y(k)\rangle = (1+\rho_{yg})\langle u_g(k)\rangle \langle u_y(k)\rangle.
+  \end{equation}
 \end{itemize}
@@
 
+Finally, it is easy to incorporate the fact that we may only be able to observe a fraction $f_c$ of the centrals, in which case the two profile moments read:
+\begin{align}
+ \langle u({\bf k})\rangle
+ &=n_g^{-1}\bar{N_c}\left[f_c+\bar{N}_s\,u_{\rm NFW}(k|M)\right]\\
+  \langle |u({\bf k})|^2\rangle
+  &=n_g^{-2}\bar{N}_c\left[2f_c\bar{N}_s\,u_{\rm NFW}({\bf k})+\bar{N}_s^2u_{\rm NFW}^2({\bf k})\right]
+\end{align}
+
 \bibliography{notes}

### 2019-04-01 likelihood/like.py

@@ -151,7 +151,8 @@ class Likelihood(object):
 
         return -2 * pr
 
-    def plot_data(self, par, dvec, save_figures=False, prefix=None):
+    def plot_data(self, par, dvec, save_figures=False, prefix=None,
+                  get_theory_1h=None, get_theory_2h=None):
         """
         Produces a plot of the different data power spectra with
         error bars and the theory prediction corresponding to a set
@@ -168,6 +169,10 @@ class Likelihood(object):
                 where tracer1 and tracer2 are the names of the two
                 tracers contributing to a given power spectrum.
             prefix (str): output prefix.
+            get_theory_1h (function): function returning the 1-halo
+                contribution.
+            get_theory_2h (function): function returning the 2-halo
+                contribution.
 
         Returns:
             array of figure objects.
@@ -184,6 +189,15 @@ class Likelihood(object):
         # Compute theory prediction and reshape to
         # [n_correlations,n_ells]
         tv = self.get_theory(params)[indices]
+        # Compute 1-h and 2-h if needed:
+        if get_theory_1h is not None:
+            tv1h = get_theory_1h(params)[indices]
+        else:
+            tv1h = None
+        if get_theory_2h is not None:
+            tv2h = get_theory_2h(params)[indices]
+        else:
+            tv2h = None
         # Reshape data vector
         dv = self.dv[indices]
         # Compute error bars and reshape
@@ -195,8 +209,8 @@ class Likelihood(object):
         # Loop through each correlation and produce a figure
         figs = []
         ax = []
-        for ll, tt, dd, ee, tr in zip(ls, tv, dv, ev,
-                                      dvec.tracers):
+        for ic, (ll, tt, dd, ee, tr) in enumerate(zip(ls, tv, dv, ev,
+                                                      dvec.tracers)):
             typ_str = ''
             for t in tr:
                 typ_str += t.type
@@ -213,6 +227,10 @@ class Likelihood(object):
             ax1.set_xscale('log')
             ax1.set_yscale('log')
             ax1.set_xlim([ll[0]/1.1, ll[-1]*1.1])
+            if tv1h is not None:
+                ax1.plot(ll, tv1h[ic], 'k-.')
+            if tv2h is not None:
+                ax1.plot(ll, tv2h[ic], 'k--')
             ax2 = fig.add_axes((.1, .1, .8, .2))
             ax2.set_xlim([ll[0]/1.1, ll[-1]*1.1])
             # Normalized residuals

### 2019-04-01 model/theory.py

@@ -3,6 +3,7 @@ from .power_spectrum import hm_ang_power_spectrum
 
 
 def get_theory(p, dm, cosmo, return_separated=False,
+               include_1h=True, include_2h=True,
                hm_correction=None, **kwargs):
     """Computes the theory prediction used in the MCMC.
 
@@ -50,6 +51,8 @@ def get_theory(p, dm, cosmo, return_separated=False,
         cl = hm_ang_power_spectrum(cosmo, ls, profiles,
                                    zrange=zrange, zpoints=zpoints,
                                    zlog=use_zlog, hm_correction=hm_correction,
+                                   include_1h=include_1h,
+                                   include_2h=include_2h,
                                    **kwargs)
         if cl is None:
             return None

### 2019-04-01 plot_stuff.py

@@ -36,6 +36,18 @@ for v in p.get('data_vectors'):
                           hm_correction=hm_correction,
                           **pars)
 
+    def th1h(pars):
+        return get_theory(p, d, cosmo, return_separated=False,
+                          hm_correction=hm_correction,
+                          include_2h=False, include_1h=True,
+                          **pars)
+
+    def th2h(pars):
+        return get_theory(p, d, cosmo, return_separated=False,
+                          hm_correction=hm_correction,
+                          include_2h=True, include_1h=False,
+                          **pars)
+
     # Set up likelihood
     lik = Likelihood(p.get('params'), d.data_vector, d.covar, th,
                      debug=p.get('mcmc')['debug'])
@@ -51,7 +63,8 @@ for v in p.get('data_vectors'):
 
     # Plot power spectra
     figs_cl = lik.plot_data(sam.p0, d, save_figures=True,
-                            prefix=p.get_sampler_prefix(v['name']))
+                            prefix=p.get_sampler_prefix(v['name']),
+                            get_theory_1h=th1h, get_theory_2h=th2h)
 
     # Plot likelihood
     figs_ch = lik.plot_chain(sam.chain, save_figure=True,

### 2019-04-02 notes/notes.tex
updated notes

@@
 \usepackage{hyperref}
+\usepackage{graphicx}
 \newcommand{\nv}{\hat{\bf n}}
@@
 \section{Introduction}
-The aim of the project is to model and measure the cross power spectrum of galaxy density and the received thermal Sunyaev-Zel'dovich effect (tSZ) signal in the universe.
-This is defined as the covariance of the harmonic coefficients of the projected fields:
+  The aim of the project is to model and measure the cross power spectrum of the galaxy overdensity and the thermal Sunyaev-Zel'dovich effect.
   \begin{equation}
-  \langle a^g_{\ell m} a^{y*}_{\ell' m'} \rangle=C^{gY}_\ell\,\delta_{\ell\ell'}
+    \langle a^g_{\ell m} a^{y*}_{\ell' m'} \rangle=C^{gy}_\ell\,\delta_{\ell\ell'}\delta_{mm'}
   \end{equation}
 
-The tSZ signal emitted from a given structure is related to the projected gas pressure, $P_e(\hat{n} \chi)$, along our line of sight.
+  The kind of science we expect to extract from this is:
+  \begin{enumerate}
+    \item A tomographic measurement of the hydrostatic bias affecting tSZ cluster studies.
+    \item More in general, we may be able to phrase that as a tomographic measurement of the different contributions to the total tSZ signal from different redshifts.
+    \item From the 1-halo term we may be able to extract information about scatter between galaxy content and pressure in clusters (?).
+  \end{enumerate}
+
+\section{Theory modelling}
+  The tSZ signal caused by a given structure is related to the projected gas pressure, $P_e(\hat{n} \chi)$, along our line of sight.
 For convenience, we work in units of comoving distance $\chi$, in which the Compton $y$ parameter is given by
@@
   \begin{equation}
-  \delta_g(\nv) = \int \frac{dN_g}{d\chi} \Delta_g(\chi\nv) d\chi.
+    \delta_g(\nv) = \int d\chi\frac{dN_g}{d\chi} \Delta_g(\chi\nv).
   \end{equation}
 
-\section{Angular power spectra}
+  \subsection{Angular power spectra}
     In general, let's consider two projected quantities $u(\nv)$ and $v(\nv)$, related to three-dimensional fields $U({\bf r})$ $V({\bf r})$:
@@
 
-The angular power spectrum of the projected quantities can be related to the 3D power spectrum of the non-projected ones $P_{UV}$ as:
+    The angular power spectrum of the projected quantities can be related to the 3D power spectrum of the non-projected ones $P_{UV}$ as\footnote{Note that the expression above for $C_\ell^{uv}$ only holds in the \emph{Limber approximation}, and the exact expression would be
+    \begin{equation}
+      C^{uv}_\ell=\frac{2}{\pi}\int dk\,k^2 \int d\chi_1\,W_u(\chi_1)j_\ell(k\chi_1)\int d\chi_2\,W_u(\chi_2)j_\ell(k\chi_2)\,P_{UV}(\chi_1,\chi_2,k),
+    \end{equation}
+    where we $j_\ell$ are the spherical Bessel functions. The Limber approximation is appropriate for our purposes.}:
     \begin{equation}
@@
     \begin{equation}
-  \left\langle U({\bf k})V^*({\bf k}')\right\rangle = P_{UV}(k)\,\delta({\bf k}-{\bf k}').
+      \left\langle U({\bf k})V^*({\bf k}')\right\rangle = (2\pi)^3\,\delta({\bf k}-{\bf k}')\,P_{UV}(k).
     \end{equation}
-
-Note that the expression above for $C_\ell^{uv}$ only holds in the \emph{Limber approximation}, and the exact expression would be
-\begin{equation}
-  C^{uv}_\ell=\frac{2}{\pi}\int dk\,k^2 \int d\chi_1\,W_u(\chi_1)j_\ell(k\chi_1)\int d\chi_2\,W_u(\chi_2)j_\ell(k\chi_2)\,P_{UV}(\chi_1,\chi_2,k),
-\end{equation}
-where we $j_\ell$ are the spherical Bessel functions. The Limber approximation is appropriate for our purposes.
 
@@
     \begin{equation}
-  W_g(\chi)=\frac{dN_g}{d\chi}=H(z)\,\frac{dN_g}{dz},\hspace{12pt}W_y(\chi)=\frac{\sigma_T}{m_ec^2}\frac{1}{1+z},
+      W_g(\chi)=\frac{dN_g}{d\chi}=\frac{H(z)}{c}\,\frac{dN_g}{dz},\hspace{12pt}W_y(\chi)=\frac{\sigma_T}{m_ec^2}\frac{1}{1+z},
     \end{equation}
-where $H(z)$ is the expansion rate (in units of inverse distance).
+    where $H(z)$ is the expansion rate.
 
-\section{Halo model}
+  \subsection{Halo model}
     We will use the halo model prescription for the 3D power spectrum.
@@
     (and analogously for $V$).
-
-All the profiles we will use take the form:
-\begin{equation}
-  U(r|M)=U_0(M,z,\vec{\theta})\,f_u(r/r_\Delta(M,z)),
-\end{equation}
-where $U_0$ is an overall scale-independent normalization that depends on mass, redshift and additional parameters $\vec{\theta}$, and $f_u$ is a form factor that only depends on the ratio of the comoving distance to the centre of the halo $r$ and the comoving halo size $r_\Delta$.
-The halo size $r_\Delta$ is commonly defined as the radius enclosing an average overdensity $\Delta$ of the critical density:
-\begin{equation}
-  \frac{4\pi}{3}\rho_c(z)\,\Delta\left(\frac{r_\Delta}{1+z}\right)^3=M_\Delta
-  \hspace{12pt}\Longrightarrow\hspace{12pt}
-  \frac{r_\Delta}{1\,{\rm Mpc}}=(1+z)\left(\frac{M_\Delta}{1.1622\times10^{12}\,M_\odot}\frac{1}{\Delta\,h^2\,E^2(z)}\right)^{1/3},
-\end{equation}
-where $E(z)\equiv H(z)/H(z=0)$.
-Another common choice is to define this radius in terms of the matter density (i.e.
-replacing $\Delta$ by $\Delta\Omega_M(z)$).
-To distinguish both cases we will write $r_{\Delta c}$ and $r_{\Delta m}$ respectively.
-In terms of the normalization and form factors, the Fourier-space profile can be written as:
-\begin{equation}
-  U(k|M)=4\pi\,r_\Delta^3\,U_0(M,z,\vec{\theta})\,\tilde{f}_u(kr_\Delta),
-\end{equation}
-where we have defined
-\begin{equation}
-  \tilde{f}(q)\equiv\int_0^\infty dx\,x^2\frac{\sin(q x)}{q x}\,f_u(x)
-\end{equation}
 
@@
     \end{align}
-Here, $P_L(k)$ is the linear matter power spectrum, $dn/dM$ is the halo mass function and $b_h(M)$ is the halo bias.
+    Here, $P_L(k)$ is the linear matter power spectrum, $dn/dM$ is the halo mass function and $b_h(M)$ is the halo bias. Further details are discussed in Appendix \ref{app:hm}.
 
-\section{Specific models}
-\subsection{Cosmological quantities}
+  \subsection{Model specifics}
+    \subsubsection{Cosmological quantities}
       We will use the linear power spectrum computed from CLASS (as provided by the Core Cosmology Library - CCL).
@@
 
-\subsection{Halo profiles}
+    \subsubsection{Halo profiles}
       We will use prescriptions for the halo profiles from the following references:
       \begin{itemize}
-\item Pressure profiles: we will try two possible prescriptions:
-  \begin{enumerate}
-  \item The Arnaud GNFW profile \cite{2010A&A...517A..92A}, with the mass-observable relation used by Planck \cite{2016A&A...594A..24P}. This profile takes the form:
+        \item {\bf Pressure.} For the time being we will stick to the choice of profile used by Planck (the GNFW ``Arnaud'' profile \cite{2010A&A...517A..92A,2016A&A...594A..24P}.
+This profile takes the form:
               \begin{equation}
-      P_e(r)=P_*\,p(r/r_{500c}),
+                P_e(r)=P_*\,p(r/R_{500c}),
               \end{equation}
-    where $r_{500c}$ is the cluster radius enclosing an overdensity of 500 times the critical density (see next section). The normalization $P_*$ is given by
+              where $r_{R00c}$ is the cluster radius enclosing an overdensity of 500 times the critical density (see Appendix \ref{app:massdef}). The normalization $P_*$ is given by
               \begin{equation}
@@
 
-  \item The Battaglia et al. profile \cite{2012ApJ...758...75B}.
-  \end{enumerate}
-\item Density profile (useful for CMB lensing): we will use a truncated Navarro-Frenk and White (NFW) profile \cite{1997ApJ...490..493N}.
+              We may also want to give the Battaglia et al. profile a go \cite{2012ApJ...758...75B}.
+        \item {\bf Matter density} (useful for CMB lensing).
+We will use a truncated Navarro-Frenk and White (NFW) profile \cite{1997ApJ...490..493N}.
 See \cite{2017MNRAS.470.2100K} for further details on implementation.
-
-  For a given mass definition $M_\Delta$ (see next section), the profile can be written as:
+              For a given mass definition $M_\Delta$ (see Appendix \ref{app:massdef}), the profile can be written as:
               \begin{equation}
@@
               where $q\equiv kr_\Delta/c_\Delta$.
-
-\item Galaxy density profiles: we will use a Halo Occupation Distribution as prescribed by \cite{2005ApJ...633..791Z,2011ApJ...736...59Z}. See implementation details in \cite{2017MNRAS.470.2100K}.
-
+        \item {\bf Galaxy overdensity}.
+We will use a Halo Occupation Distribution as prescribed by \cite{2005ApJ...633..791Z,2011ApJ...736...59Z}.
+See implementation details in \cite{2017MNRAS.470.2100K}.
               We will model the galaxy content of dark matter halos as being made up of central and satellite galaxies.
@@
               \end{equation}
-  We then assume that satellites can only be formed if a halo has a central and has a mass larger than some threshold $M_0$. In that case, average number of satellites is a power law of the form:
+              We then assume that satellites can only be formed if a halo has a central and has a mass larger than some threshold $M_0$.
+In that case, average number of satellites is a power law of the form:
               \begin{equation}
@@
               \begin{equation}
-    \bar{n_g}\equiv\int dM\,\frac{dn}{dM}\langle N_c(M)\rangle\left[f_c+\langle N_s(M)\rangle\right].
+                \bar{n}_g\equiv\int dM\,\frac{dn}{dM}\langle N_c(M)\rangle\left[f_c+\langle N_s(M)\rangle\right].
               \end{equation}
-
-  Finally, for simplicity we will assume that the satellites follow the matter distribution: $u_s(k|M)=u_m(k|M)$.
-
+              Finally, for simplicity we will assume that the satellites follow the matter distribution: $u_s(k|M)=u_m(k|M)$ (i.e. an NFW profile).
         \item 1-halo covariance: note that different halo properties are not perfectly correlated due to e.g. hidden variables (age, merger history, environment etc.). I.e. in almost all cases
@@
       \end{itemize}
-We will start by implementing these as defined in the papers, and then decide which parameters of them to free up (an obvious one is $1-b$, but we may want to be more general than that).
+      For the moment we will only consider the following four free parameters: $M_{\rm min}$, $M_1$, $1-b$, $\rho_{yg}$.
+We will fix all other parameters to the following values: $M_0=M_{\rm min}$, $\sigma_{{\rm ln}M}=0.15$, $\alpha=1$, $f_c=1$.
+We will fix cosmological parameters to the latest Planck values.
 
-\subsection{Translating between mass definitions}
-We may need to translate between masses defined with different prescriptions. All of them can be described by the following equation, describing the relation between the mass and the size of a halo:
-\begin{equation}
-  M_{\Delta_x}=\frac{4\pi}{3}\rho_c(z)\Delta_x\,R_{\Delta_x}^3,
+\section{Measurement}
+  \subsection{Data}
+    \begin{itemize}
+      \item {\bf Galaxies:} For the moment we've used only maps of the galaxy overdensity field for the 2MPZ sample and the 5 WISC redshift bins.
+We'll see what we do with SDSS later on.
+We're also using the redshift distribution for these samples that were estimated in the CMB lensing cross-correlation paper.
+We use the masks provided.
+      \item {\bf tSZ:} We've downloaded the tSZ MILCA and NILC maps. For these we use the Planck 60\% foreground mask.      
+    \end{itemize}
+
+  \subsection{Power spectra}
+    We compute unbiased angular power spectra using {\tt NaMaster}, a well-tested pseudo-$C_\ell$ code \cite{2019MNRAS.484.4127A}.
+We have computed all auto- and cross-spectra between maps, but so far we have only analyzed the auto-correlation of the galaxy overdensities from 2MPZ and MILCA, and their cross-correlation with the MILCA $y$ map.
+
+  \subsection{Covariance matrix}
+    We compute three versions of the covariance matrix:
+    \begin{enumerate}
+      \item {\bf Theoretical covariance.} We estimate this covariance as a sum of two terms: the Gaussian disconnected part and the 1-halo connected trispectrum.
+            \begin{itemize}
+              \item Gaussian disconnected covariance: we use the approach of \cite{2004MNRAS.349..603E}, which fully accounts for the effects of mode coupling from survey geometry.
+              \item 1-halo trispectrum: this is computed as
+                    \begin{equation}\nonumber
+                       {\rm Cov}(C^{uv}_\ell,C^{xy}_{\ell'})=\frac{1}{4\pi f_{\rm sky}}\int {d\chi}{\chi^2}\frac{W^u(\chi)W^v(\chi)W^x(\chi)W^y(\chi)}{\chi^4}\left\langle U(k|M)V(k|M)X(k'|M)Y(k'|M)\right\rangle,
                     \end{equation}
-here $\Delta_x=\Delta\,f_x$, where $\Delta$ is a number (e.g.
-200, 500 etc.) and $x$ is either $c$ or $m$, to distinguish between masses defined with respect to the critical density or the matter density.
-In either case:
-\begin{equation}
-  f_c=1,\hspace{12pt} f_m=\Omega_M(z).
-\end{equation}
-
-Now, under the assumption that halos have an NFW density profile, it's easy to calculate the mass enclosed within a given radius:
-\begin{equation}
-  M(<R)=4\pi\rho_0\,r_s^3\left[\ln\left(1+\frac{R}{r_s}\right)-\frac{R/r_s}{1+R/r_s}\right]
-\end{equation}
-Now, writing $M_{\Delta_x}=M(<R_{\Delta_x})$ and defining the concentration parameter $c_{\Delta_x}=R_{\Delta_x}/r_s$, we have, for two different mass definitions $\Delta_x$ and $\Delta'_y$:
-\begin{align}
-  M_{\Delta_x}=\frac{4\pi}{3}\rho_c(z)\Delta_x\,R_{\Delta_x}^3=4\pi\rho_0\,\left(\frac{R_{\Delta_x}}{c_{\Delta_x}}\right)^3\left[\ln\left(1+c_{\Delta_x}\right)-\frac{c_{\Delta_x}}{1+c_{\Delta_x}}\right]\\
-  M_{\Delta'_y}=\frac{4\pi}{3}\rho_c(z)\Delta'_y\,R_{\Delta'_y}^3=4\pi\rho_0\,\left(\frac{R_{\Delta'_y}}{c_{\Delta'_y}}\right)^3\left[\ln\left(1+c_{\Delta'_y}\right)-\frac{c_{\Delta'_y}}{1+c_{\Delta'_y}}\right].
-\end{align}
-Taking the ratio of both equations, we obtain a relation between the concentration parameters for both mass definitions:
-\begin{equation}
-  \frac{c_{\Delta_x}^3\Delta_x}{c_{\Delta'_y}^3\Delta'_y}=\frac{\ln\left(1+c_{\Delta_x}\right)-\frac{c_{\Delta_x}}{1+c_{\Delta_x}}}{\ln\left(1+c_{\Delta'_y}\right)-\frac{c_{\Delta'_y}}{1+c_{\Delta'_y}}}.
-\end{equation}
-
-So, in order to translate between $M_{\Delta_x}$ and $M_{\Delta'_y}$:
-\begin{enumerate}
-\item Get a concentration-mass relation for $M_{\Delta_x}$ and compute both $c_{\Delta_x}$ and $R_{\Delta_x}$.
-\item Obtain $c_{\Delta'_y}$ by solving the equation above numerically.
-\item From $c_{\Delta'_y}$ obtain $R_{\Delta'_y}$ and then $M_{\Delta'_y}$.
+                    where $k=(\ell+1/2)/\chi$ and $k'=(\ell'+1/2)/\chi$.
+            \end{itemize}
+            Note that this covariance requires a model for the power spectra and halo profiles.
+We obtain these from the best-fit model found using a purely Gaussian covariance for which we use, as a model, an interpolated version of the power spectra measured from the data.
+      \item {\bf Jackknife covariance.} We produce a set of 460 jackknife maps produced by removing patches corresponding to $N_{\rm side}=8$ HEALPix pixels.
+We only take pixels that are more than half unmasked.
+      \item {\bf Combined covariance.} The reduced number of jackknife regions makes the jackknife noisy, and its inverse a bit unstable.
+To remedy this we combine the two covariances above as follows:
+            \begin{itemize}
+              \item We take the diagonal of the combined covariance to be the maximum of the jackknife and theory covariances.
+Note that this only matters at low $\ell$, where the jackknife covariance underestimates the uncertainties.
+              \item We estimate the correlation matrix (i.e.
+$r_{ij}\equiv{\rm Cov}_{ij}/\sqrt{{\rm Cov}_{ii}{\rm Cov}_{jj}}$) from the theoretical covariance.
+This is to ensure that we have a smooth correlation structure, which we know should be well captured by the theoretical approach used here.
+              \item We combine diagonals and correlation matrix into the final covariance matrix.
+            \end{itemize}
     \end{enumerate}
 
-\subsection{Halo profile statistics}
+  \subsection{Likelihood}
+    We assume a Gaussian likelihood $-2\log{\cal L}=({\bf d}-{\bf t})^T{\sf C}^{-1}({\bf b}-{\bf t})$, where ${\bf d}$ is a data vector formed by stacking a series of power spectrum measurements, ${\bf t}$ is the corresponding vector of theory predictions and ${\sf C}$ is the covariance matrix described above.
+
+    We analyse each redshift bin independently in order to limit the size of the data vector and the corresponding covariance.
+Thus, in each case the data vector is constructed by stacking two power spectrum measurements ${\bf d}=(\vec{C}^{gg}_\ell,\vec{C}^{gy}_\ell)$.
+
+    We impose scale cuts to avoid having to model very non-linear scales.
+We limit ourselves to a maximum wavenumber $k_{\rm max}=1\,{\rm Mpc}^{-1}$, which we map into a maximum multipole $\ell_{\rm max}=k_{\rm max}\chi(\bar{z})-1/2$, where $\bar{z}$ is the mean redshift of each redshift bin.
+
+\section{Results}
+  Results for 2MPZ and the 5 WISC redshift bins in Figures \ref{fig:res_2mpz}, \ref{fig:res_wisc1}, \ref{fig:res_wisc2}, \ref{fig:res_wisc3}, \ref{fig:res_wisc4} and \ref{fig:res_wisc5} respectively.
+Results are summarized in Fig.
+\ref{fig:oneminusb}.
+  \begin{figure*}
+    \centering
+    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_2mpz_cls_2mpz_2mpz}
+    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_2mpz_cls_2mpz_y_milca}
+    \includegraphics[width = 0.90\textwidth]{../output_test/sampler_minimal_hmc_2mpz_triangle}
+    \caption{{\sl Upper left:} galaxy-galaxy power spectrum. {\sl Upper right:} galaxy-tSZ power spectrum. {\sl Lower:} parameter constraints. All for the 2MPZ sample.}\label{fig:res_2mpz}
+  \end{figure*}
+  \begin{figure*}
+    \centering
+    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_wisc1_cls_wisc1_wisc1}
+    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_wisc1_cls_wisc1_y_milca}
+    \includegraphics[width = 0.90\textwidth]{../output_test/sampler_minimal_hmc_wisc1_triangle}
+    \caption{Same as Fig. \ref{fig:res_2mpz} for the first WISC bin.}\label{fig:res_wisc1}
+  \end{figure*}
+  \begin{figure*}
+    \centering
+    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_wisc2_cls_wisc2_wisc2}
+    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_wisc2_cls_wisc2_y_milca}
+    \includegraphics[width = 0.90\textwidth]{../output_test/sampler_minimal_hmc_wisc2_triangle}
+    \caption{Same as Fig. \ref{fig:res_2mpz} for the second WISC bin.}\label{fig:res_wisc2}
+  \end{figure*}
+  \begin{figure*}
+    \centering
+    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_wisc3_cls_wisc3_wisc3}
+    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_wisc3_cls_wisc3_y_milca}
+    \includegraphics[width = 0.90\textwidth]{../output_test/sampler_minimal_hmc_wisc3_triangle}
+    \caption{Same as Fig. \ref{fig:res_2mpz} for the third WISC bin.}\label{fig:res_wisc3}
+  \end{figure*}
+  \begin{figure*}
+    \centering
+    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_wisc4_cls_wisc4_wisc4}
+    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_wisc4_cls_wisc4_y_milca}
+    \includegraphics[width = 0.90\textwidth]{../output_test/sampler_minimal_hmc_wisc4_triangle}
+    \caption{Same as Fig. \ref{fig:res_2mpz} for the fourth WISC bin.}\label{fig:res_wisc4}
+  \end{figure*}
+  \begin{figure*}
+    \centering
+    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_wisc5_cls_wisc5_wisc5}
+    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_wisc5_cls_wisc5_y_milca}
+    \includegraphics[width = 0.90\textwidth]{../output_test/sampler_minimal_hmc_wisc5_triangle}
+    \caption{Same as Fig. \ref{fig:res_2mpz} for the fifth WISC bin.}\label{fig:res_wisc5}
+  \end{figure*}
+
+  \begin{figure}
+   \centering
+   \includegraphics[width = 0.7\textwidth]{../output_test/sampler_minimal_hmc_b_hydro_all}
+   \caption{Summary plot.}\label{fig:oneminusb}
+  \end{figure}
+
+\bibliography{notes}
+\bibliographystyle{habbrv}
+
+\appendix
+\section{Halo profile statistics}\label{app:hm}
   To fully account for the statistics of any halo observable, let's rederive the halo model power spectrum carefully.
@@
   \begin{align}\nonumber
-  U_{\bf k}=\int dx^3\,U({\bf x})\,e^{-i{\bf k}{\bf x}}=\sum_h N_h u_h({\bf k}) e^{-{\bf r}_i{\bf k}},
+    U_{\bf k}=\int dx^3\,U({\bf x})\,e^{-i{\bf k}{\bf x}}=\sum_h N_h u_h({\bf k}) e^{-{\bf r}_h{\bf k}},
   \end{align}
@@
 
-\bibliography{notes}
-\bibliographystyle{habbrv}
+\section{Translating between mass definitions}\label{app:massdef}
+  We may need to translate between masses defined with different prescriptions. All of them can be described by the following equation, describing the relation between the mass and the size of a halo:
+  \begin{equation}
+    M_{\Delta_x}=\frac{4\pi}{3}\rho_c(z)\Delta_x\,R_{\Delta_x}^3,
+  \end{equation}
+  here $\Delta_x=\Delta\,f_x$, where $\Delta$ is a number (e.g.
+200, 500 etc.) and $x$ is either $c$ or $m$, to distinguish between masses defined with respect to the critical density or the matter density.
+In either case:
+  \begin{equation}
+    f_c=1,\hspace{12pt} f_m=\Omega_M(z).
+  \end{equation}
+
+  Now, under the assumption that halos have an NFW density profile, it's easy to calculate the mass enclosed within a given radius:
+  \begin{equation}
+    M(<R)=4\pi\rho_0\,r_s^3\left[\ln\left(1+\frac{R}{r_s}\right)-\frac{R/r_s}{1+R/r_s}\right]
+  \end{equation}
+  Now, writing $M_{\Delta_x}=M(<R_{\Delta_x})$ and defining the concentration parameter $c_{\Delta_x}=R_{\Delta_x}/r_s$, we have, for two different mass definitions $\Delta_x$ and $\Delta'_y$:
+  \begin{align}
+    M_{\Delta_x}=\frac{4\pi}{3}\rho_c(z)\Delta_x\,R_{\Delta_x}^3=4\pi\rho_0\,\left(\frac{R_{\Delta_x}}{c_{\Delta_x}}\right)^3\left[\ln\left(1+c_{\Delta_x}\right)-\frac{c_{\Delta_x}}{1+c_{\Delta_x}}\right]\\
+    M_{\Delta'_y}=\frac{4\pi}{3}\rho_c(z)\Delta'_y\,R_{\Delta'_y}^3=4\pi\rho_0\,\left(\frac{R_{\Delta'_y}}{c_{\Delta'_y}}\right)^3\left[\ln\left(1+c_{\Delta'_y}\right)-\frac{c_{\Delta'_y}}{1+c_{\Delta'_y}}\right].
+  \end{align}
+  Taking the ratio of both equations, we obtain a relation between the concentration parameters for both mass definitions:
+  \begin{equation}
+    \frac{c_{\Delta_x}^3\Delta_x}{c_{\Delta'_y}^3\Delta'_y}=\frac{\ln\left(1+c_{\Delta_x}\right)-\frac{c_{\Delta_x}}{1+c_{\Delta_x}}}{\ln\left(1+c_{\Delta'_y}\right)-\frac{c_{\Delta'_y}}{1+c_{\Delta'_y}}}.
+  \end{equation}
+
+  So, in order to translate between $M_{\Delta_x}$ and $M_{\Delta'_y}$:
+  \begin{enumerate}
+    \item Get a concentration-mass relation for $M_{\Delta_x}$ and compute both $c_{\Delta_x}$ and $R_{\Delta_x}$.
+    \item Obtain $c_{\Delta'_y}$ by solving the equation above numerically.
+    \item From $c_{\Delta'_y}$ obtain $R_{\Delta'_y}$ and then $M_{\Delta'_y}$.
+  \end{enumerate}
+
 \end{document}

### 2019-04-02 likelihood/like.py

@@ -152,7 +152,7 @@ class Likelihood(object):
         return -2 * pr
 
     def plot_data(self, par, dvec, save_figures=False, prefix=None,
-                  get_theory_1h=None, get_theory_2h=None):
+                  get_theory_1h=None, get_theory_2h=None, extension='pdf'):
         """
         Produces a plot of the different data power spectra with
         error bars and the theory prediction corresponding to a set
@@ -165,7 +165,7 @@ class Likelihood(object):
                 the data vector.
             save_figures (bool): if true, figures will be saved to
                 file. File names will take the form:
-                <`prefix`>cls_<tracer1>_<tracer2>.png
+                <`prefix`>cls_<tracer1>_<tracer2>.<`extension`>
                 where tracer1 and tracer2 are the names of the two
                 tracers contributing to a given power spectrum.
             prefix (str): output prefix.
@@ -173,6 +173,7 @@ class Likelihood(object):
                 contribution.
             get_theory_2h (function): function returning the 2-halo
                 contribution.
+            extension (str): plot extension (pdf, pdf etc.).
 
         Returns:
             array of figure objects.
@@ -251,11 +252,12 @@ class Likelihood(object):
             if prefix is None:
                 raise ValueError("Need a file prefix to save stuff")
             for fig, tr in zip(figs, dvec.tracers):
-                fname = prefix+'cls_'+tr[0].name+'_'+tr[1].name+'.png'
+                fname = prefix+'cls_'+tr[0].name+'_'+tr[1].name+'.'+extension
                 fig.savefig(fname, bbox_inches='tight')
         return figs
 
-    def plot_chain(self, chain, save_figure=False, prefix=None):
+    def plot_chain(self, chain, save_figure=False, prefix=None,
+                   extension='pdf'):
         """
         Produces a triangle plot from a chain, which can be
         saved to file automatically.
@@ -267,8 +269,9 @@ class Likelihood(object):
                 for this likelihood run.
             save_figures (bool): if true, figures will be saved to
                 file. File names will take the form:
-                <`prefix`>triangle.png
+                <`prefix`>triangle.<`extension`>
             prefix (str): output prefix.
+            extension (str): plot extension (pdf, pdf etc.).
 
         Returns:
             figure object
@@ -288,7 +291,6 @@ class Likelihood(object):
         if save_figure:
             if prefix is None:
                 raise ValueError("Need a file prefix to save stuff")
-            fname = prefix+'triangle.png'
[…]

### 2019-04-02 plot_stuff.py

@@ -24,11 +24,20 @@ if p.get('mcmc').get('hm_correct'):
 else:
     hm_correction = None
 
+zmeans=[]
+szmeans=[]
+bmeans=[]
+sbmeans=[]
 for v in p.get('data_vectors'):
     print(v['name'])
 
     # Construct data vector and covariance
     d = DataManager(p, v, cosmo)
+    z, nz = np.loadtxt(d.tracers[0][0].dndz, unpack=True)
+    zmean=np.sum(nz * z) / np.sum(nz)
+    sigz=np.sqrt(np.sum(nz * (z - zmean)**2) / np.sum(nz))
+    zmeans.append(zmean)
+    szmeans.append(sigz)
 
     # Theory predictor wrapper
     def th(pars):
@@ -73,6 +82,16 @@ for v in p.get('data_vectors'):
     print(" Best-fit parameters:")
     for nn,vv,ss in zip(sam.parnames, sam.p0, np.std(sam.chain,axis=0)):
         print("  " + nn + " : %.3lE +- %.3lE" %(vv,ss))
+        if nn == 'b_hydro':
+            bmeans.append(vv)
+            sbmeans.append(ss)
+        chain = sam.chain
     print(" chi^2 = %lf" % (lik.chi2(sam.p0)))
     print(" n_data = %d" % (len(d.data_vector)))
+
+plt.figure()
+plt.errorbar(zmeans,1-np.array(bmeans),xerr=szmeans,yerr=sbmeans,fmt='ro')
+plt.xlabel('$z$',fontsize=15)
+plt.ylabel('$1-b$',fontsize=15)
+plt.savefig(p.get_sampler_prefix('b_hydro')+'all.pdf',bbox_inches='tight')
 plt.show()

### 2019-04-02 model/power_spectrum.py
added bias prediction

@@ -45,6 +45,59 @@ class HalomodCorrection(object):
         return self.rk_func(np.log10(k), a)
 
 
+def hm_bias(cosmo, a, profile,
+            logMrange=(6, 17), mpoints=128,
+            **kwargs):
+    """Computes the halo model prediction for the bias of a given
+    tracer.
+
+    Args:
+        cosmo (:obj:`ccl.Cosmology`): cosmology.
+        a (array): array of scale factor values
+        profile (`Profile`): a profile. Only Arnaud and HOD are
+            implemented.
+        logMrange (tuple): limits of integration in log10(M/Msun)
+        mpoints (int): number of mass samples
+        **kwargs: parameter used internally by the profiles.
+    """
+    # Input handling
+    a = np.atleast_1d(a)
+
+    # Profile normalisations
+    Unorm = profile.profnorm(cosmo, a, squeeze=False, **kwargs)
+    Unorm = Unorm[..., None]
+
+    # Set up integration boundaries
+    logMmin, logMmax = logMrange  # log of min and max halo mass [Msun]
+    mpoints = int(mpoints)        # number of integration points
+    M = np.logspace(logMmin, logMmax, mpoints)  # masses sampled
+
+    # Out-of-loop optimisations
+    Dm = profile.Delta/ccl.omega_x(cosmo, a, "matter")  # CCL uses Delta_m
+    mfunc = np.array([ccl.massfunc(cosmo, M, A1, A2) for A1, A2 in zip(a, Dm)])
+    bh = np.array([ccl.halo_bias(cosmo, M, A1, A2) for A1, A2 in zip(a, Dm)])
+    # shape transformations
+    mfunc, bh = mfunc.T[..., None], bh.T[..., None]
+
+    U, _ = profile.fourier_profiles(cosmo, np.array([0.001]), M, a,
+                                    squeeze=False, **kwargs)
+
+    # Tinker mass function is given in dn/dlog10M, so integrate over d(log10M)
+    b2h = simps(bh*mfunc*U, x=np.log10(M), axis=0).squeeze()
+
+    # Contribution from small masses (added in the beginning)
+    rhoM = ccl.rho_x(cosmo, a, "matter", is_comoving=True)
+    dlM = (logMmax-logMmin) / (mpoints-1)
+    mfunc, bh = mfunc.squeeze(), bh.squeeze()  # squeeze extra dimensions
+
[…]

### 2019-04-02 model/profile2D.py

@@ -254,7 +254,8 @@ class HOD(object):
         Ns = self.n_sat(M, **kwargs)    # satellites
         Nc, Ns = Nc[..., None, None], Ns[..., None, None]
 
-        H, _ = NFW().fourier_profiles(cosmo, k, M, a, **kwargs)
+        H, _ = NFW().fourier_profiles(cosmo, k, M, a, squeeze=False,
+                                      **kwargs)
 
         F, F2 = Nc*(fc + Ns*H), Nc*(2*fc*Ns*H + (Ns*H)**2)
         return (F.squeeze(), F2.squeeze()) if squeeze else F, F2

### 2019-04-02 plot_stuff.py

@@ -6,7 +6,7 @@ from likelihood.sampler import Sampler
 from model.data import DataManager
 from model.theory import get_theory
 import matplotlib.pyplot as plt
-from model.power_spectrum import HalomodCorrection
+from model.power_spectrum import HalomodCorrection, hm_bias
 
 try:
     fname_params = sys.argv[1]
@@ -24,18 +24,18 @@ if p.get('mcmc').get('hm_correct'):
 else:
     hm_correction = None
 
-zmeans=[]
-szmeans=[]
-bmeans=[]
-sbmeans=[]
+zmeans = []
+szmeans = []
+bmeans = []
+sbmeans = []
 for v in p.get('data_vectors'):
     print(v['name'])
 
     # Construct data vector and covariance
     d = DataManager(p, v, cosmo)
     z, nz = np.loadtxt(d.tracers[0][0].dndz, unpack=True)
-    zmean=np.sum(nz * z) / np.sum(nz)
-    sigz=np.sqrt(np.sum(nz * (z - zmean)**2) / np.sum(nz))
+    zmean = np.sum(nz * z) / np.sum(nz)
+    sigz = np.sqrt(np.sum(nz * (z - zmean)**2) / np.sum(nz))
     zmeans.append(zmean)
     szmeans.append(sigz)
 
@@ -70,6 +70,15 @@ for v in p.get('data_vectors'):
     sam.get_chain()
     sam.update_p0(sam.chain[np.argmax(sam.probs)])
 
+    # Compute galaxy bias
+    zarr = np.linspace(zmean - sigz, zmean + sigz, 10)
+    bg = np.mean(hm_bias(cosmo, 1./(1 + zarr),
+                         d.tracers[0][0].profile,
+                         **(lik.build_kwargs(sam.p0))))
+    by = np.mean(hm_bias(cosmo, 1./(1 + zarr),
+                         d.tracers[1][1].profile,
+                         **(lik.build_kwargs(sam.p0))))
+
     # Plot power spectra
     figs_cl = lik.plot_data(sam.p0, d, save_figures=True,
                             prefix=p.get_sampler_prefix(v['name']),
@@ -80,18 +89,22 @@ for v in p.get('data_vectors'):
                              prefix=p.get_sampler_prefix(v['name']))
 
     print(" Best-fit parameters:")
[…]

### 2019-04-04 legacy/likelihood/MCMC.py
adding legacy code

@@ -1,0 +1,63 @@
+import sys
+import numpy as np
+from pathos.multiprocessing import ProcessingPool as Pool
+import pyccl as ccl
+
+import fittingtools as ft
+
+
+
+# SURVEY PROPERTIES #
+dir1 = "../analysis/data/dndz/"
+wisc = ["wisc_b%d" % i for i in range(1, 6)]
+surveys = ["2mpz"] + wisc
+bins = np.append([1], np.arange(1, 6))
+sprops = ft.survey_properties(dir1, surveys, bins)
+
+cosmo = ccl.Cosmology(Omega_c=0.26066676,
+                      Omega_b=0.048974682,
+                      h=0.6766,
+                      sigma8=0.8102,
+                      n_s=0.9665)
+
+
+
+# PARAMETER : [VALUE, STATUS, CONSTRAINTS] #
+# (free : 0) ::: (fixed : 1) ::: (coupled : -N)
+priors = {"Mmin"       :  [12.0,   -1,   (10, 16)],
+          "M0"         :  [12.0,   -1,   (10, 16)],
+          "M1"         :  [13.5,    0,   (10, 16)],
+          "sigma_lnM"  :  [0.15,    1,   (0.1, 1.0)],
+          "alpha"      :  [1.0,     1,   (0.5, 1.5)],
+          "fc"         :  [1.0,     1,   (0.1, 1.0)],
+          "bg"         :  [1.0,     1,   (0, np.inf)],
+          "bmax"       :  [1.0,     1,   (0, np.inf)],
+          "r_corr"     :  [0.0,     0,   (-1, 1)],
+          "b_hydro"    :  [0.50,    0,   (0.1, 0.9)]}
+
+
+
+# INPUT HANDLING #
+if len(sys.argv) == 1:
+    y = input("Warning: Chains will start from the beginning!\nContinue? (y/n): ")
+    if y == "y":
+        c = False
+        # minimizer
+        minimizer = lambda sur: ft.param_fiducial(sur, sprops, cosmo, priors, v=True)
+        p0 = Pool().map(minimizer, list(sprops.keys()))
+        sys.argv.append(None)
+    elif y == "n":
+        y = input("Start chains from saved states? (y/n): ")
+        if y == "y":
+            sys.argv.append("continue")
+
+if sys.argv[1] == "continue":
+    c = True
+    p0 = [priors for sur in sprops]
+    print("Continuing from saved samplers...")
+
+
+# MCMC
[…]

### 2019-04-04 legacy/likelihood/archive/examples.py

@@ -1,0 +1,133 @@
+"""
+This script contains useful tests for the codes, as well as example figures
+illustrating the inner workings of some classes, functions, and methods.
+
+Sections/Tests are separated by description in triple quotations.
+Uncomment trailing code to run test.
+"""
+
+
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.cm import viridis as cmap
+from matplotlib.cm import viridis_r as cmap_r
+from matplotlib.colors import LogNorm
+from mpl_toolkits.mplot3d import Axes3D
+import pyccl as ccl
+
+import pspec
+from profiles import Arnaud
+from cosmotools import scale_factor
+
+savedir = "images/"  # output directory
+
+
+"""
+ARNAUD RATIO
+"""
+#def Arnaud_ratio(x, M, z):
+#    """Computes the ratio of two Arnaud profiles of a given mass and at a given
+#    redshift. The profiles are identical, except one uses the full Arnaud profile
+#    including a radial mass dependence.
+#    """
+#    r = Arnaud(x, M, z, aPP=False) / Arnaud(x, M, z, aPP=True)
+#    return r
+#
+#
+#
+#x = np.logspace(-3, np.log10(2), 1000)  # R/R_Delta
+#
+#M_array = np.logspace(np.log10(6.0e13), np.log10(1.3e15), 8)
+#M_dep = [Arnaud_ratio(x, M=M, z=0) for M in M_array]
+#
+#
+#fig, ax = plt.subplots(1, 1, figsize=(5,5))
+#ax.set_xlabel("$R \mathrm{ /R_{500} }$", fontsize=16)
+#lbl = r"$\frac{ P_{th}\left( x, M_{500}, z \right) }{ P_{th}\left( x, M_{500}, z, \alpha(x) \right) }$"
+#ax.set_ylabel(lbl, fontsize=16)
+#
+#ax.axhline(y=1, ls="--", c="k")
+#
+#colors = cmap(np.linspace(0, 1, len(M_array)))
+#for i, _ in enumerate(M_array):
+#    txt = r"$ %.1e\ \mathrm{M_{\odot}}$" % M_array[i]
[…]

### 2019-04-04 legacy/likelihood/archive/get_new_cm.py

@@ -1,0 +1,74 @@
+import cosmotools as ct
+import pyccl as ccl
+import numpy as np
+from scipy.optimize import brentq
+import matplotlib.pyplot as plt
+from matplotlib.pyplot import cm
+
+cosmo = ccl.Cosmology(Omega_c=0.27, Omega_b=0.05, h=0.67, sigma8=0.8, n_s=0.81)
+
+m200_arr=np.logspace(6,17,256)
+z_arr=np.array([0.,0.1,0.3,0.5,1.0,1.5,2.0])
+a_arr=1./(1+z_arr)
+
+m500_arr=np.zeros([len(a_arr),len(m200_arr)])
+c200_arr=np.zeros([len(a_arr),len(m200_arr)])
+c500_arr=np.zeros([len(a_arr),len(m200_arr)])
+
+def func_tobrent(c,d) :
+    return (np.log(1+c)-c/(1+c))/(d*c*c*c)
+
+print("Translating c200 into c500")
+plt.figure()
+for ia,a in enumerate(a_arr) :
+    ha2=(cosmo['h']*ccl.h_over_h0(cosmo,a))**2
+    for im,m200 in enumerate(m200_arr) :
+        #At each redshift and at each value of m200
+        r200=ct.R_Delta(cosmo,m200,a,Delta=200) #Compute r200
+        c200=ct.concentration_duffy(m200,a) #Compute c200
+        c200_arr[ia,im]=c200
+
+        #Get c500 from c200 by solving:
+        # [ ln(1+c500)-c500/(1+c500) ]/(500*c500**3) = [ ln(1+c200)-c200/(1+c200) ]/(200*c200**3)
+        func0=func_tobrent(c200,200)
+        def fzero(c) :
+            return func_tobrent(c,500)-func0
+        c500=brentq(fzero,c200/10.,c200*10,maxiter=1000)
+        c500_arr[ia,im]=c500
+
+        #That should be it, but we also want to see the translation between m200 and m500
+        #for our own education
+        r500=c500*r200/c200 #Compute r500
+        m500=500*1.16217766E12*ha2*r500**3 #Compute m500
+        m500_arr[ia,im]=m500
+
+    plt.plot(m500_arr[ia],c500_arr[ia],c=cm.spring(ia/(len(a_arr)-1.))) #Plot both c-M relations
+    plt.plot(m200_arr,c200_arr[ia],c=cm.winter(ia/(len(a_arr)-1.)))
[…]

### 2019-04-04 legacy/likelihood/archive/hod.py

@@ -1,0 +1,183 @@
+import numpy as np
+import pyccl as ccl
+from scipy.special import erf,sici
+import matplotlib.pyplot as plt
+from matplotlib.pyplot import cm
+
+
+def concentration_duffy(halo_mass,a,is_Dmatter=False,is_D500=False) :
+    """
+    Concentration-Mass relation from 0804.2486
+    Extended to Delta=500 (critical density)
+
+    .. note:: Returns A*(halo_mass/M_pivot)**B/a**C
+              where (A,B,C) depend on the mass definition
+              and M_pivot=1E12 M_sun/h
+
+    Arguments
+    ---------
+    halo_mass : float or array_like
+        Halo mass [Msun].
+    a : float
+        Scale factor
+    is_D500 : boolean
+        If `True`, return the extension of the original Duffy et al. relation for Delta=500.
+
+    Returns
+    -------
+    float or array_like : The halo concentration.
+    """
+    m_pivot=2.78164E12 #Pivot mass in M_sun
+
+    if is_D500 :
+        A_Delta=3.67; B_Delta=-0.0903; C_Delta=-0.51;
+    else : #2nd row in Table 1 of Duffy et al. 2008
+        if is_Dmatter :
+            A_Delta=10.14; B_Delta=-0.081; C_Delta=-1.01;
+        else :
+            A_Delta=5.71; B_Delta=-0.084; C_Delta=-0.47;
+
+    return A_Delta*(halo_mass/m_pivot)**B_Delta/a**C_Delta
+
+def r_Delta(cosmo, halo_mass, a, Delta=200, is_matter=False) :
+    """
+    Calculate the reference radius of a halo.
+
+    .. note:: this is R=(3M/(4*pi*rho_c(a)*Delta))^(1/3), where rho_c is the critical
+              matter density
+
+    Arguments
+    ---------
+    cosmo : ``pyccl.Cosmology`` object
+        Cosmological parameters.
+    halo_mass : float or array_like
+        Halo mass [Msun].
+    a : float
+        Scale factor
+    Delta : float
+        Overdensity parameter.
+
+    Returns
+    -------
+    float or array_like : The halo reference radius in `Mpc`.
+    """
+    omega_factor=1.
[…]

### 2019-04-04 legacy/likelihood/archive/likelihood_HOD.py

@@ -1,0 +1,111 @@
+import numpy as np
+from scipy.optimize import minimize
+import pyccl as ccl
+
+import pspec
+import profile2D
+
+
+def func(args):
+    """The function to be minimised."""
+    params = ["Mmin", "M0", "M1", "sigma_lnM", "alpha", "fc"]
+    kwargs = dict(zip(params, args))
+    global cosmo, prof, l, cl
+
+    prior_test = (6 <= kwargs["Mmin"] <= 17)*\
+                 (6 <= kwargs["M0"] <= 17)*\
+                 (6 <= kwargs["M1"] <= 17)*\
+                 (0.1 <= kwargs["sigma_lnM"] <= 1.0)*\
+                 (0.5 <= kwargs["alpha"] <= 1.5)*\
+                 (0.1 <= kwargs["fc"] <= 1.0)
+
+    # Piecewise probability handling
+    if not prior_test:
+        lnprob = -np.inf
+    else:
+        Cl = pspec.ang_power_spectrum(cosmo, l, (prof, prof),
+                                      zrange=(0.001, 0.3), **kwargs)
+
+        if Cl is None:  # treat zero division (unphysical)
+            lnprob = -np.inf
+        else:
+            lnprob = -0.5*np.dot(cl-Cl, np.dot(I, cl-Cl))
+
+    print(args, -2*lnprob, len(l))  # output trial parameter values
+    return -lnprob
+
+
+Neval = 1  # display number of evaluations
+def callbackf(X):
+    global Neval
+    print("{0:4d}   {1: 3.6f}   {2: 3.6f}   {3: 3.6f}   \
+          {4: 3.6f}   {5: 3.6f}   {6: 3.6f}".format(Neval, X[0], X[1], X[2],
+                                                           X[3], X[4], X[5]))
+    Neval += 1
+
+
+
+## DATA ##
+# science
+data = np.load("../analysis/out_ns512_linlog/cl_2mpz_2mpz.npz")            # clgg
+# covariances
+cov = np.load("../analysis/out_ns512_linlog/cov_2mpz_2mpz_2mpz_2mpz.npz")  # clgg
+
+# x-data
+l = data["leff"]
+mask = l < 260
+l = l[mask]
+# y-data
+cl = data["cell"] - data["nell"]
+cl = cl[mask]
+
[…]

### 2019-04-04 legacy/likelihood/archive/likelihood_b_hydro.py

@@ -1,0 +1,139 @@
+import numpy as np
+from scipy.optimize import minimize
+import pyccl as ccl
+
+import pspec
+import profile2D
+
+
+
+def func(p0, args=None):
+    """The function to be minimised."""
+    params = ["Mmin", "M0", "M1", "sigma_lnM", "alpha", "fc", "b_hydro"]
+    if args is not None: p0 = np.hstack((args, p0))
+    kwargs = dict(zip(params, p0))
+    global cosmo, prof1, prof2, l, cl
+
+    prior_test = (6 <= kwargs["Mmin"] <= 17)*\
+                 (6 <= kwargs["M0"] <= 17)*\
+                 (6 <= kwargs["M1"] <= 17)*\
+                 (0.1 <= kwargs["sigma_lnM"] <= 1.0)*\
+                 (0.5 <= kwargs["alpha"] <= 1.5)*\
+                 (0.1 <= kwargs["fc"] <= 1.0)*\
+                 (0.1 <= kwargs["b_hydro"] <= 1.0)
+
+    # Piecewise probability handling
+    if not prior_test:
+        lnprob = -np.inf
+    else:
+        Cl = pspec.ang_power_spectrum(cosmo, l, (prof1, prof2),
+                                      zrange=(0.001, 0.3), **kwargs)
+
+        if Cl is None:  # treat zero division (unphysical)
+            lnprob = -np.inf
+        else:
+            lnprob = -0.5*np.dot(cl-Cl, np.dot(I, cl-Cl))
+
+    print(p0, -2*lnprob, len(l))  # output trial parameter values
+    return -lnprob
+
+
+Neval = 1  # display number of evaluations
+def callbackf(X):
+    global Neval
+    print("{0:4d}".format(Neval), *X)
+    Neval += 1
+
+
+
+## DATA ##
+# science
+data = np.load("../../analysis/out_ns512_linlog/cl_2mpz_y_milca.npz")  # clyg
+# covariances
+cov = np.load("../../analysis/out_ns512_linlog/cov_2mpz_y_milca_2mpz_y_milca.npz")  # clyg
+
+# x-data
+l = data["leff"]
+mask = l < 260
+l = l[mask]
+# y-data
+cl = data["cell"] - data["nell"]
+cl = cl[mask]
+
+# error bars
+covar = cov["cov"]
+covar = covar[mask, :][:, mask]
[…]

### 2019-04-04 legacy/likelihood/archive/profs_test.py

@@ -1,0 +1,82 @@
+"""
+This script contains definitions of 3-dimensional profiles.
+"""
+
+
+from scipy import constants as const
+from astropy.constants import M_sun, G
+from astropy.cosmology import Planck15 as cosmo
+from pyccl.background import h_over_h0 as h
+
+from cosmotools import R_Delta
+
+from cosmotools import rho_cr_SI  # FIXME: replace with CCL
+
+
+
+def Arnaud(x, M500=3e14, z=0, aPP=True):
+    """Returns the Arnaud pressure profile of a halo of a given mass,
+    ``M500``, and at a given redshift, ``z``. Units are ``keV/cm^3``.
+
+    - Note: User should input the ``M500`` mass in solar masses.
+    - Note: Units of x are ``R500``.
+    """
+    h70 = cosmo.H(0).value/0.7
+
+    # Parameters
+    alpha_P = 0.12  # P
+    alpha_PP = 0.10 - (alpha_P+0.10) * (x/0.5)**3 / (1+x/0.5)**3  # P-primed
+    if not aPP: alpha_PP = 0
+    P0 = 6.41  # reference pressure
+
+    # Arnaud et al. best fit
+    c500 = 1.81
+    alpha = 1.33
+    beta = 4.13
+    gama = 0.31
+
+    p = P0 / ((c500*x)*gama*(1+c500*x*alpha)**((beta-gama)/alpha))
+    P1 = 1.65*h(z)**(8/3) * p*h70**2
+    P2 = (M500/(3e14/h70))**(2/3+alpha_P+alpha_PP)
+    P = P1*P2  # universal pressure profile  [eV/cm^3]
+
+    return P
+
+
+def Battaglia(x, M200=1e14, z=0):
+    """Returns the Battaglia pressure profile of a halo of a given mass,
+    ``M200``, and at a given redshift, ``z``. Units are ``keV/cm^3``.
+
+    - Note: User should input the ``M200`` mass in solar masses.
+    - Units of x are ``R200``.
+    """
+    # [J/m^3] >> [keV/cm^3]
+    eV = const.value("electron volt")
+    u = (1/eV)/(1e2)**3
+
+    power_law = lambda A0, am, az: A0 * (M200/1e14)**am * (1+z)**az  # power law
+
+    def P_Delta(M200, z):
+        """Computes the self-similar amplitude for pressure.
[…]

### 2019-04-04 legacy/likelihood/archive/temp.py

@@ -1,0 +1,26 @@
+"""
+temp file for calcs and unstable test code
+"""
+
+
+import numpy as np
+import pyccl as ccl
+
+import profile2D
+
+
+# Cosmology Definition
+cosmo = ccl.Cosmology(Omega_c=0.27, Omega_b=0.045, h=0.67, sigma8=0.8, n_s=0.96)
+
+a = 1
+Delta = 500
+
+rmin, rmax = 1e-4, 5  # [R_Delta]
+kmin, kmax = 2*np.pi/rmax, 2*np.pi/rmin
+# so, values of k probed, logarithmically span [kmin, kmax]
+k_arr = np.logspace(np.log10(kmin), np.log10(kmax), 100)
+M_arr = np.logspace(6, 17, 256)  # masses sampled
+
+p1 = profile2D.Arnaud()
+p2 = profile2D.Arnaud()
+p3 = profile2D.HOD()

### 2019-04-04 legacy/likelihood/best_fit.py

@@ -1,0 +1,185 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import pyccl as ccl
+import corner
+import emcee
+
+import fittingtools as ft
+import profile2D as p2D
+import pspec as pspec
+
+
+
+# PARAMETER : [VALUE, STATUS, CONSTRAINTS] #
+# (free : 0) ::: (fixed : 1) ::: (coupled : -N)
+priors = {"Mmin"       :  [12.0,   -1,   (10, 16)],
+          "M0"         :  [12.0,   -1,   (10, 16)],
+          "M1"         :  [13.5,    0,   (10, 16)],
+          "sigma_lnM"  :  [0.15,    1,   (0.1, 1.0)],
+          "alpha"      :  [1.0,     1,   (0.5, 1.5)],
+          "fc"         :  [1.0,     1,   (0.1, 1.0)],
+          "bg"         :  [1.0,     1,   (0, np.inf)],
+          "bmax"       :  [1.0,     1,   (0, np.inf)],
+          "r_corr"     :  [0.0,     0,   (-1, 1)],
+          "b_hydro"    :  [0.50,    0,   (0.1, 0.9)]}
+
+
+# SURVEY PROPERTIES #
+dir1 = "../analysis/data/dndz/"
+wisc = ["wisc_b%d" % i for i in range(1, 6)]
+surveys = ["2mpz"] + wisc
+bins = np.append([1], np.arange(1, 6))
+sprops = ft.survey_properties(dir1, surveys, bins)
+
+
+
+# INPUT #
+samplers = [emcee.backends.HDFBackend("samplers/%s" % sur) for sur in surveys]
+#tau = [np.max(sampler.get_autocorr_time()) for sampler in samplers]
+tau = [80, 30, 80, 30, 30, 30]  # manual input
+burnin = [int(np.ceil(2*np.max(t))) for t in tau]
+print(burnin)
+
+samples = [sampler.get_chain(discard=burn, flat=True) for sampler, burn in zip(samplers, burnin)]
+popt = [np.median(sample, axis=0) for sample in samples]
+
+free, fixed, coupled = ft.split_kwargs(**priors)
+
+# parameters
+cosmo = ccl.Cosmology(Omega_c=0.26066676,
+                      Omega_b=0.048974682,
+                      h=0.6766,
[…]

### 2019-04-04 legacy/likelihood/bhydro.py

@@ -1,0 +1,65 @@
+import numpy as np
+from scipy.integrate import simps
+import matplotlib.pyplot as plt
+from matplotlib.cm import copper
+
+
+
+dir1 = "../analysis/data/dndz/"
+
+# g-surveys
+wisc = ["wisc_b%d" % i for i in range(1, 6)]
+surveys = ["2mpz"] + wisc
+
+# MCMC results: 50, 16, 84 quantiles
+vals = [np.load("fit_vals/%s.npy" % sur) for sur in surveys]
+bh = np.array([[val[i, 1] for val in vals] for i in range(3)])
+
+z_avg = np.zeros((3, len(surveys)))
+z, N = [[[] for j in surveys] for i in range(2)]
+for i, s in enumerate(surveys):
+    # data manipulation
+    fname = dir1 + ("2MPZ_bin1.txt" if s is "2mpz" else  s[:4].upper() + "_bin%d.txt" % i)
+    zd, Nd = np.loadtxt(fname, unpack=True)
+    Nd /= simps(Nd, x=zd)  # normalise histogram
+    #surveys
+    z[i] = zd
+    N[i] = Nd
+    # average redshift & std
+    z_avg[0, i] = np.average(zd, weights=Nd)
+    perc = np.array([np.trapz(Nd[:j], zd[:j]) for j, _ in enumerate(zd)])
+    # redshifts at 16, 84 percentiles
+    z_avg[1, i], z_avg[2, i] = [np.abs(z_avg[0, i] - zd[np.abs(perc-p).argmin()]) for p in [0.16, 0.84]]
+
+z, N = map(lambda x: [np.array(y) for y in x], [z, N])
+
+
+
+# PLOT #
+col = [copper(i) for i in np.linspace(0, 1, len(surveys))]
+
+fig, (hist, ax) = plt.subplots(2, 1, sharex=True, figsize=(10, 10),
+                         gridspec_kw={"height_ratios":[1, 3], "hspace":0.05})
+
+
+ax.set_xlabel("$\mathrm{z}$", fontsize=15)
+ax.set_ylabel("$\mathrm{b_{hydro}}$", fontsize=15)
+hist.set_ylabel("$\mathrm{dN/dz}$", fontsize=15)
+
+hist.set_xlim(0, 0.4)
+[hist.fill_between((z_avg[0,i]-z_avg[1,i], z_avg[0,i]+z_avg[2,i]),
[…]

### 2019-04-04 legacy/likelihood/cosmotools.py

@@ -1,0 +1,86 @@
+"""
+This script contains definitions of useful cosmological functions for quick
+retrieval and data analysis.
+"""
+
+import numpy as np
+import pyccl as ccl
+
+
+
+def concentration_duffy(M, a, is_D500=False, squeeze=True):
+    """
+    Mass-Concentration relation from 0804.2486.
+    Extended to ``Delta=500`` (Delta definition uses critical density).
+
+    .. note:: Returns ``1A*(halo_mass/M_pivot)**B/a**C``,  where (A,B,C) depend
+              on the mass definition and ``M_pivot = 1e+12 M_sun/h``.
+
+    Arguments
+    ---------
+    M : float or array_like
+        Halo mass [Msun].
+    a : float or array_like
+        Scale factor.
+    is_D500 : bool
+        If `True`, extends of the original Duffy et al. relation to Delta=500.
+    squeeze : bool
+        Whether to squeeze extra dimensions.
+
+    Returns
+    -------
+    float or array_like : The halo concentration.
+    """
+    # Input handling
+    M, a = np.atleast_1d(M), np.atleast_1d(a)
+
+    m_pivot=2.78164e12  # Pivot mass [M_sun]
+
+    if is_D500:
+        A, B, C = 3.67, -0.0903, -0.51
+    else: # Duffy et al. 2008 (Table 1, row 2)
+        A, B, C = 5.71, -0.084, -0.47
+
+    c = A * (M[..., None]/m_pivot)**B / a**C
+    return c.squeeze() if squeeze else c
+
+
+
+def R_Delta(cosmo, M, a, Delta=500, is_matter=False, squeeze=True):
+    """
+    Calculate the reference radius of a halo.
+
+    .. note:: This is ``R = (3M/(4*pi*rho_c(a)*Delta))^(1/3)``, where rho_c is
+              the critical matter density at scale factor ``a``.
+
+    Arguments
+    ---------
+    cosmo : ``pyccl.Cosmology`` object
+        Cosmological parameters.
+    M : float or array_like
+        Halo mass [Msun].
+    a : float or array_like
+        Scale factor
+    Delta : float
+        Overdensity parameter.
+    is_matter : bool
+        True when R_Delta is calculated using the average matter density.
+        False when R_Delta is calculated using the critical density.
+    squeeze : bool
+        Whether to squeeze extra dimensions.
+
+    Returns
[…]

### 2019-04-04 legacy/likelihood/fittingtools.py

@@ -1,0 +1,286 @@
+"""
+This script contains definitions of useful fitting functions for quick
+retrieval and data analysis.
+"""
+
+from collections import ChainMap
+from itertools import product
+import numpy as np
+import pyccl as ccl
+import emcee
+from scipy.optimize import minimize
+
+import profile2D
+import pspec
+
+
+
+def max_multipole(fname, cosmo, kmax=1):
+    """Calculates the highest working multipole for HOD cross-correlation."""
+    z, N = np.loadtxt(fname, unpack=True)
+    z_avg = np.average(z, weights=N)
+    chi_avg = ccl.comoving_radial_distance(cosmo, 1/(1+z_avg))
+    lmax = kmax*chi_avg - 1/2
+    return lmax
+
+
+
+def survey_properties(directory, surveys, bins, cutoff=0.5):
+    """Returns a ``dict`` of the survey ``zrange`` and its bin."""
+    Z = [[] for i, _ in enumerate(surveys)]
+    for i, sur in enumerate(surveys):
+        fname = directory + sur.strip("_b%d" % i).upper() + "_bin%d.txt" % bins[i]
+        z, N = np.loadtxt(fname, unpack=True)
+        m = N.argmax()
+        imin = np.abs(N[:m] - cutoff*N.max()/100).argmin()
+        imax = np.abs(N[m:] - cutoff*N.max()/100).argmin()
+        Z[i] = (z[imin], z[m+imax])
+
+    sprops = dict(zip(surveys, zip(Z, bins)))
+    return sprops
+
+
+
+def dataman(cells, z_bin=None, cosmo=None):
+    """
+    Constructs data vectors from different data sets and computes their inverse
+    covariance matrix.
+
+    Arguments
+    ---------
+    data : tuple or str
+        The names of the surveys used to compute ``Cl``, in the form "s1, s2".
+    bins : int
+        The redshift bin used.
+    cosmo : `pyccl.Cosmology` object
+        Cosmological parameters.
+    """
+    def Beam(l, profile, arcmin=10):
+        """Calculates the beam of a data set."""
+        if profile == "y":
+            sigma = np.deg2rad(arcmin/2.355/60)
+            B = np.exp(-0.5*l*(l+1)*sigma**2)
+        else:
+            B = np.ones_like(l)
+        return B
+
+    # dictionary of surveys #
+    sdss = ["sdss_b%d" % i for i in range(1, 10)]
+    wisc = ["wisc_b%d" % i for i in range(1, 6)]
[…]

### 2019-04-04 legacy/likelihood/get_covariance.py

@@ -1,0 +1,175 @@
+import numpy as np
+import pyccl as ccl
+from pspec import ang_power_spectrum, power_spectrum
+from profile2D import Arnaud,HOD
+from scipy.integrate import simps
+import matplotlib.pyplot as plt
+import healpy as hp
+from covariance import ang_1halo_covariance
+import sys
+
+if len(sys.argv)!=3:
+    raise ValueError("Usage: get_covariance.py sample_name bin_number")
+
+g_sample=sys.argv[1]
+bin_no=int(sys.argv[2])
+y_sample='y_milca'
+prefix_cls='../analysis/out_ns512_linlog/'
+prefix_nz='../analysis/data/dndz/'
+kmax=1.
+zpoints=128
+
+#y-map beam
+nside=512
+fwhm_y_amin=10.
+fwhm_hp_amin=60*41.7/nside
+sigma_y_rad=np.radians(fwhm_y_amin/2.355/60)
+sigma_hp_rad=np.radians(fwhm_hp_amin/2.355/60)
+def beam_ymap(l):
+    return np.exp(-0.5*l*(l+1)*sigma_y_rad**2)
+def beam_hpix(l):
+    return np.exp(-0.5*l*(l+1)*sigma_hp_rad**2)
+
+#Fiducial cosmology
+cosmo = ccl.Cosmology(Omega_c=0.26066676,
+                      Omega_b=0.048974682,
+                      h=0.6766,
+                      sigma8=0.8102,
+                      n_s=0.9665)
+
+#Read data
+fname_dndz=prefix_nz+g_sample.upper()
+if bin_no<0:
+    ibin_string=''
+    fname_dndz+='_bin1.txt'
+else:
+    ibin_string='_b%d'%bin_no
+    fname_dndz+='_bin%d.txt'%bin_no
+fname_cl_gg=prefix_cls+'cl_'+g_sample+ibin_string+'_'+g_sample+ibin_string+'.npz'
+fname_cl_gy=prefix_cls+'cl_'+g_sample+ibin_string+'_'+y_sample+'.npz'
[…]

### 2019-04-04 legacy/likelihood/profile2D.py

@@ -1,0 +1,308 @@
+import numpy as np
+from numpy.linalg import lstsq
+from scipy.special import sici
+from scipy.special import erf
+from scipy.integrate import quad
+from scipy.integrate import simps
+from scipy.interpolate import interp1d
+import scipy.constants as u
+from scipy.constants import value as v
+import pyccl as ccl
+
+import cosmotools as ct
+
+
+
+class Arnaud(object):
+    """
+    Calculate an Arnaud profile quantity of a halo and its Fourier transform.
+
+
+    Parameters
+    ----------
+    rrange : tuple
+        Desired physical distance to probe (expressed in units of R_Delta).
+        Change only if necessary. For distances too much outside of the
+        default range the calculation might become unstable.
+    qpoints : int
+        Number of integration sampling points.
+    """
+    def __init__(self, name, rrange=(1e-3, 10), qpoints=1e2):
+
+        self.name = name
+        self.rrange = rrange         # range of probed distances [R_Delta]
+        self.qpoints = int(qpoints)  # no of sampling points
+        self.Delta = 500             # reference overdensity (Arnaud et al.)
+        self.name = "Arnaud"
+
+        self._fourier_interp = self._integ_interp()
+
+
+    def kernel(self, cosmo, a, **kwargs):
+        """The thermal Sunyaev-Zel'dovich anisotropy window function."""
+        prefac = 4.017100792437957e-06  # avoid recomputing every time
+        return prefac*a
+
+
+    def profnorm(self, cosmo, a, squeeze=True, **kwargs):
+        """Computes the overall profile normalisation for the angular cross-
+        correlation calculation."""
+        return np.ones_like(a)
+
+
+    def norm(self, cosmo, M, a, b, squeeze=True):
+        """Computes the normalisation factor of the Arnaud profile.
+
+        .. note:: Normalisation factor is given in units of ``eV/cm^3``. \
+        (Arnaud et al., 2009)
+        """
+        # Input handling
+        M, a = np.atleast_1d(M), np.atleast_1d(a)
+
+        aP = 0.12  # Arnaud et al.
[…]

### 2019-04-04 legacy/likelihood/pspec.py

@@ -1,0 +1,128 @@
+import numpy as np
+from scipy.integrate import simps
+import pyccl as ccl
+
+
+
+def power_spectrum(cosmo, k, a, profiles, logMrange=(6, 17), mpoints=128,
+                   include_1h=True, include_2h=True, squeeze=True, **kwargs):
+    """Computes the cross power spectrum of two halo profiles."""
+    # Input handling
+    a, k = np.atleast_1d(a), np.atleast_2d(k)
+
+    # Profile normalisations
+    p1, p2 = profiles
+    Unorm = p1.profnorm(cosmo, a, squeeze=False, **kwargs)
+    Vnorm = Unorm if p1.name == p2.name else p2.profnorm(cosmo, a, squeeze=False, **kwargs)
+    if (Vnorm < 1e-16).any() or (Unorm < 1e-16).any(): return None  # zero division
+    Unorm, Vnorm = Unorm[..., None], Vnorm[..., None]  # transform axes
+
+    # Set up integration boundaries
+    logMmin, logMmax = logMrange  # log of min and max halo mass [Msun]
+    mpoints = int(mpoints)        # number of integration points
+    M = np.logspace(logMmin, logMmax, mpoints)  # masses sampled
+
+    # Out-of-loop optimisations
+    Pl = np.array([ccl.linear_matter_power(cosmo, k[i], a) for i, a in enumerate(a)])
+    Dm = p1.Delta/ccl.omega_x(cosmo, a, "matter")  # CCL uses Delta_m
+    mfunc = np.array([ccl.massfunc(cosmo, M, A1, A2) for A1, A2 in zip(a, Dm)])
+    bh = np.array([ccl.halo_bias(cosmo, M, A1, A2) for A1, A2 in zip(a, Dm)])
+    # shape transformations
+    mfunc, bh = mfunc.T[..., None], bh.T[..., None]
+
+    U, UU = p1.fourier_profiles(cosmo, k, M, a, squeeze=False, **kwargs)
+    # optimise for autocorrelation (no need to recompute)
+    if p1.name == p2.name:
+        V = U; UV = UU
+    else :
+        V, VV = p2.fourier_profiles(cosmo, k, M, a, squeeze=False, **kwargs)
+        
+        r = kwargs["r_corr"] if "r_corr" in kwargs else 0
+        UV = U*V*(1+r)
+
+    # Tinker mass function is given in dn/dlog10M, so integrate over d(log10M)
+    P1h = simps(mfunc*UV, x=np.log10(M), axis=0)
[…]

### 2019-04-04 notes/notes.tex

@@
 
+\newpage
+\section{Next steps}
+\begin{itemize}
+  \item Systematics in $gg$. We could try deprojection and see if things improve. Otherwise just remove first point or two in WISC data.
+  \item Systematics in $gy$: quantify CIB contamination.
+  \item Do we want a different angle on the signal modelling? E.g.:
+        \begin{enumerate}
+          \item Our measurement could be transformed into a measurement of the mean electron pressure weighed by halo bias at a given redshift:
+                \begin{equation}
+                  \bar{P}_{e,b}(z) = \int dM\,\frac{dn}{dM}\,b_h(M) \bar{P}_e(M,z)
+                \end{equation}
+          \item We could quantify whether there's any statistical evidence for a redshift evolution of $1-b_H$.
+          \item $\rho_{gy}\simeq-0.5$. Is there anything we can say about that?
+        \end{enumerate}
+\end{itemize}
+
 \bibliography{notes}

### 2019-05-09 images/massfunc/massfunc.py
Tinker08/Tinker10 comparison

@@ -1,0 +1,52 @@
+import pyccl as ccl
+import numpy as np
+import matplotlib.pyplot as plt
+
+cosmo08 = ccl.Cosmology(Omega_c=0.26066676, Omega_b=0.048974682, h=0.6766, sigma8=0.8102, n_s=0.9665, mass_function="tinker")
+cosmo10 = ccl.Cosmology(Omega_c=0.26066676, Omega_b=0.048974682, h=0.6766, sigma8=0.8102, n_s=0.9665, mass_function="tinker10")
+
+M = np.logspace(11, 14, 7)
+z = np.linspace(0.001, 0.5, 1000)
+a = 1/(1+z)
+
+
+mfunc08, mfunc10 = [[[]]*len(a) for i in range(2)]
+for i, dist in enumerate(a):
+    mfunc08[i] = list(ccl.massfunc(cosmo08, M, dist))
+    mfunc10[i] = list(ccl.massfunc(cosmo10, M, dist))
+
+
+mfunc08 = np.array(mfunc08).T
+mfunc10 = np.array(mfunc10).T
+
+
+alphas = np.linspace(1, 0.2, len(M))
+
+fig, ax1 = plt.subplots()
+for i, _ in enumerate(M):
+    ax1.loglog(z, mfunc08[i], "r", lw=3, alpha=alphas[i])
+    ax1.loglog(z, mfunc10[i], "b", lw=3, alpha=alphas[i])
+
+plt.ylim(1e-5,)
+plt.legend(["Tinker10", "Tinker08"], ncol=2, loc="lower center", fontsize=12)
+plt.xlabel("z", fontsize=14)
+plt.ylabel("$dn/dM$", fontsize=14)
+plt.savefig("dndM.pdf")
+##############################################################################
+
+#from matplotlib.colors import Normalize
+
+fig, ax2 = plt.subplots()
+
+mdiff = np.abs(mfunc10 - mfunc08)
+for i, _ in enumerate(M):
+    ax2.loglog(z, mdiff[i], "k", lw=3, alpha=alphas[i])
+
+#cmap = plt.cm.Greys
+#norm = Normalize(vmin=11, vmax=14)
+#
+#
+#cb = plt.colorbar(ax, cmap=cmap, norm=norm)
+plt.xlabel("z", fontsize=14)
+plt.ylabel("|Tinker10 - Tinker08|", fontsize=14)
+plt.savefig("dndM_diff.pdf")

### 2019-05-09 plot_stuff.py

@@ -116,4 +116,4 @@ plt.ylabel('$1-b$', fontsize=15)
 plt.savefig(p.get_sampler_prefix('b_hydro')+'all.pdf',
             bbox_inches='tight')
 
-np.save("bH_%s" % p.get_outdir(), np.vstack((zmeans, 1-bmeans, szmeans, sbmeans)))
+np.save("%s/bH_%s" % p.get_outdir(), np.vstack((zmeans, 1-bmeans, szmeans, sbmeans)))

### 2019-05-10 images/massfunc/massfunc.py
more halo model

@@ -5,8 +5,8 @@ import matplotlib.pyplot as plt
 cosmo08 = ccl.Cosmology(Omega_c=0.26066676, Omega_b=0.048974682, h=0.6766, sigma8=0.8102, n_s=0.9665, mass_function="tinker")
 cosmo10 = ccl.Cosmology(Omega_c=0.26066676, Omega_b=0.048974682, h=0.6766, sigma8=0.8102, n_s=0.9665, mass_function="tinker10")
 
-M = np.logspace(11, 14, 7)
-z = np.linspace(0.001, 0.5, 1000)
+M = np.logspace(8, 16, 128)
+z = np.linspace(0.0, 2., 25)
 a = 1/(1+z)
 
 
@@ -16,22 +16,25 @@ for i, dist in enumerate(a):
     mfunc10[i] = list(ccl.massfunc(cosmo10, M, dist))
 
 
-mfunc08 = np.array(mfunc08).T
-mfunc10 = np.array(mfunc10).T
+mfunc08 = np.array(mfunc08)#.T
+mfunc10 = np.array(mfunc10)#.T
 
 
-alphas = np.linspace(1, 0.2, len(M))
+alphas = np.linspace(1, 0.2, len(z))
 
 fig, ax1 = plt.subplots()
-for i, _ in enumerate(M):
-    ax1.loglog(z, mfunc08[i], "r", lw=3, alpha=alphas[i])
-    ax1.loglog(z, mfunc10[i], "b", lw=3, alpha=alphas[i])
+for i, _ in enumerate(z):
+    ax1.plot(M, mfunc08[i]/mfunc10[i], "r", lw=3, alpha=alphas[i])
+    #ax1.loglog(M, mfunc10[i], "b", lw=3, alpha=alphas[i])
 
-plt.ylim(1e-5,)
-plt.legend(["Tinker10", "Tinker08"], ncol=2, loc="lower center", fontsize=12)
-plt.xlabel("z", fontsize=14)
-plt.ylabel("$dn/dM$", fontsize=14)
-plt.savefig("dndM.pdf")
+plt.xlim([10**11.5,10**15])
+plt.xscale('log')
+#plt.ylim(1e-5,)
+#plt.legend(["Tinker10", "Tinker08"], ncol=2, loc="lower center", fontsize=12)
+#plt.xlabel("z", fontsize=14)
+#plt.ylabel("$dn/dM$", fontsize=14)
+#plt.savefig("dndM.pdf")
+plt.show(); exit(1)
[…]

### 2019-05-10 plot_stuff.py
save b_hydro

@@ -116,4 +116,5 @@ plt.ylabel('$1-b$', fontsize=15)
 plt.savefig(p.get_sampler_prefix('b_hydro')+'all.pdf',
             bbox_inches='tight')
 
-np.save("%s/bH_%s" % p.get_outdir(), np.vstack((zmeans, 1-bmeans, szmeans, sbmeans)))
+D = np.vstack((zmeans, 1-bmeans, szmeans, sbmeans))
+np.save("%s/bH_%s" % (p.get_outdir(), p.get_outdir()), D)

### 2019-05-16 images/b_hydro/bhydro.py
combined bhydro plot

@@ -1,0 +1,40 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+ymilca = np.load("ymilca.npy")
+ynilc = np.load("ynilc.npy")
+masked_ymilca = np.load("masked_ymilca.npy")
+masked_nilc = np.load("masked_ynilc.npy")
+mfunc_ymilca = np.load("mfunc_ymilca.npy")
+mfunc_ynilc = np.load("mfunc_ynilc.npy")
+dndz_ymilca = np.load("dndz_ymilca.npy")
+dndz_ynilc = np.load("dndz_ynilc.npy")
+
+def plotfunc(a, xerr=False, fmt=None, color=None, label=None):
+    """Plots b_hydro data with error bars."""
+    x, y = a[0: 2]
+    if xerr: xerr = a[2]
+    yerr = a[3:]
+    plt.errorbar(x, y, xerr=xerr, yerr=yerr,
+                 fmt=fmt, c=color, label=label)
+
+
+data = [ymilca, ynilc,
+        masked_ymilca, masked_nilc,
+        mfunc_ymilca, mfunc_ynilc]
+colours = ["k", "k",
+           "salmon", "salmon",
+           "royalblue", "royalblue",
+           "forestgreen", "forestgreen"]
+fmts = ["o", "^"]*4
+lbls = ["ymilca", "ynilc",
+        "masked_ymilca", "masked_nilc",
+        "mfunc_ymilca", "mfunc_ynilc"
+        "dndz_ymilca", "dndz_ynilc"]
+
+for a, c, fmt, lbl in zip(data, colours, fmts, lbls):
+    plotfunc(a, True, fmt, c, lbl)
+
+plt.legend(loc="lower center", fontsize=10, ncol=int(len(data)/2))
+plt.xlabel("z", fontsize=14)
+plt.ylabel(r"$\mathrm{b_{hydro}}$", fontsize=14)

### 2019-05-16 plot_stuff.py
un-errored errorbar error :)

@@ -110,7 +110,7 @@ sbmeans = np.array(sbmeans)  # (2,N): min,max
 
 plt.figure()
 plt.errorbar(zmeans, 1-np.array(bmeans),
-             xerr=szmeans, yerr=np.flip(sbmeans), fmt='ro')
+             xerr=szmeans, yerr=np.flip(sbmeans, 0), fmt='ro')
 plt.xlabel('$z$', fontsize=15)
 plt.ylabel('$1-b$', fontsize=15)
 plt.savefig(p.get_sampler_prefix('b_hydro')+'all.pdf',

### 2019-05-16 images/b_hydro/bhydro.py
combined bhydro plot

@@ -38,3 +38,4 @@ for a, c, fmt, lbl in zip(data, colours, fmts, lbls):
 plt.legend(loc="lower center", fontsize=10, ncol=int(len(data)/2))
 plt.xlabel("z", fontsize=14)
 plt.ylabel(r"$\mathrm{b_{hydro}}$", fontsize=14)
+plt.savefig("bhydro.pdf")

### 2019-05-17 images/b_hydro/bhydro.py
new dndz, masked, mfunc for ymilca/nilc, combined bhydro plot

@@ -10,32 +10,34 @@ mfunc_ynilc = np.load("mfunc_ynilc.npy")
 dndz_ymilca = np.load("dndz_ymilca.npy")
 dndz_ynilc = np.load("dndz_ynilc.npy")
 
-def plotfunc(a, xerr=False, fmt=None, color=None, label=None):
+def plotfunc(a, xerr=None, fmt=None, color=None, alpha=0, label=None):
     """Plots b_hydro data with error bars."""
     x, y = a[0: 2]
     if xerr: xerr = a[2]
     yerr = a[3:]
     plt.errorbar(x, y, xerr=xerr, yerr=yerr,
-                 fmt=fmt, c=color, label=label)
+                 fmt=fmt, c=color, alpha=alpha, label=label)
 
 
 data = [ymilca, ynilc,
         masked_ymilca, masked_nilc,
-        mfunc_ymilca, mfunc_ynilc]
+        mfunc_ymilca, mfunc_ynilc,
+        dndz_ymilca, dndz_ynilc]
 colours = ["k", "k",
            "salmon", "salmon",
            "royalblue", "royalblue",
            "forestgreen", "forestgreen"]
 fmts = ["o", "^"]*4
+alphas = [1, 0.5]*4
 lbls = ["ymilca", "ynilc",
         "masked_ymilca", "masked_nilc",
-        "mfunc_ymilca", "mfunc_ynilc"
+        "mfunc_ymilca", "mfunc_ynilc",
         "dndz_ymilca", "dndz_ynilc"]
 
-for a, c, fmt, lbl in zip(data, colours, fmts, lbls):
-    plotfunc(a, True, fmt, c, lbl)
+for a, c, fmt, alpha, lbl in zip(data, colours, fmts, alphas, lbls):
+    plotfunc(a, xerr=None, fmt=fmt, color=c, alpha=alpha, label=lbl)
 
-plt.legend(loc="lower center", fontsize=10, ncol=int(len(data)/2))
+plt.legend(loc="lower right", fontsize=10, ncol=2)
 plt.xlabel("z", fontsize=14)
 plt.ylabel(r"$\mathrm{b_{hydro}}$", fontsize=14)
-plt.savefig("bhydro.pdf")
+#plt.savefig("bhydro.pdf")

### 2019-05-17 images/b_hydro/bhydro.py
combined bhydro

@@ -40,4 +40,4 @@ for a, c, fmt, alpha, lbl in zip(data, colours, fmts, alphas, lbls):
 plt.legend(loc="lower right", fontsize=10, ncol=2)
 plt.xlabel("z", fontsize=14)
 plt.ylabel(r"$\mathrm{b_{hydro}}$", fontsize=14)
-#plt.savefig("bhydro.pdf")
+plt.savefig("bhydro.pdf")

### 2019-05-29 mk_mask_y.py
fixed bug in mask

@@ -18,8 +18,8 @@ def rDelta(m,zz,Delta) :
 
 #Read catalog and remove all clusters above z=0.43
 data=(fits.open('data/maps/HFI_PCCS_SZ-union_R2.08.fits'))[1].data
-ids=np.where(data['REDSHIFT']>=0)[0]; data=data[ids]
-idsz=np.where(data['REDSHIFT']<0.43)[0]; data=data[idsz]
+mask = (data['REDSHIFT']>=0) & (data['SNR']>=6)
+data=data[mask]
 #Compute their angular extent
 r500=rDelta(data['MSZ']*HH*1E14,data['REDSHIFT'],500)
 chi=ccl.comoving_radial_distance(cosmo,1./(1+data['REDSHIFT']))*HH

### 2019-05-29 images/b_hydro/bhydro.py
temp

@@ -53,7 +53,7 @@ dir1 = "../../data/dndz/"
 wisc = ["wisc_b%d" % i for i in range(1, 6)]
 surveys = ["2mpz"] + wisc
 sci = [r"$\mathrm{2MPZ}$"] + \
-      [r"$\mathrm{WI \times SC - %d}$" % i for i in range(1, 6)]
+      [r"$\mathrm{WI \times SC}$ - $\mathrm{%d}$" % i for i in range(1, 6)]
 
 dz1, dN1 = get_z_Nz()
 dz2, dN2 = get_z_Nz(version="_v2")

### 2019-05-29 images/fits/fits_v2.py

@@ -85,8 +85,9 @@ for s, sur in enumerate(surveys):
         ax2.set_xlim([ll[ind2][0]/1.1, ll[ind2][-1]*1.1])
 
         if i == 0:
-            ax1.axvspan(ax1.get_xlim()[0], ll[ind0][0], color="grey", alpha=0.2)
-            ax2.axvspan(ax1.get_xlim()[0], ll[ind0][0], color="grey", alpha=0.2)
+            if lmin != 0:
+                ax1.axvspan(ax1.get_xlim()[0], ll[ind0][0], color="grey", alpha=0.2)
+                ax2.axvspan(ax1.get_xlim()[0], ll[ind0][0], color="grey", alpha=0.2)
             ax1.text(0.02, 0.05, sci[s]+"\n"+"$\\chi^2/{\\rm dof}=%.2lf/%d$" %
                      (chi2, dof), transform=ax1.transAxes)
 

### 2019-07-16 likelihood/like.py
more paper

@@ -329,9 +329,16 @@ class Likelihood(object):
 
         nsamples = len(chain)
         # Generate samples
+        ranges={}
+        for n,pr in zip(self.p_free_names,self.p_free_prior):
+            if pr['type']=='TopHat':
+                ranges[n]=pr['values']
         samples = MCSamples(samples=chain[nsamples//4:],
                             names=self.p_free_names,
-                            labels=self.p_free_labels)
+                            labels=self.p_free_labels,
+                            ranges=ranges)
+        samples.smooth_scale_2D=0.2
+
         # Triangle plot
         g = gplots.getSubplotPlotter()
         g.triangle_plot([samples], filled=True)

### 2019-07-17 likelihood/chanal.py
more plots

@@ -97,7 +97,8 @@ def sampler2kwargs(sam, lik, diff=False, error_type=None):
     return kwargs
 
 
-def chan(fname_params, diff=False, error_type=None, b_hydro=None, chains=True):
+def chan(fname_params, diff=False, error_type=None, b_hydro=None,
+         chains=True, by_subsample=100):
     """
     Given a parameter file, looks up corresponding sampler and calculates
     best-fit parameters, and min & max values.
@@ -129,13 +130,13 @@ def chan(fname_params, diff=False, error_type=None, b_hydro=None, chains=True):
     sel = selfunc(p)
     hm_correction = halmodcor(p, cosmo)
 
-    params, chi2, dof = [[] for i in range(3)]
+    params, chi2, dof, bf = [[] for i in range(4)]
     chains = [[],[]]
     for s, v in enumerate(p.get("data_vectors")):
 
         # Construct data vector and covariance
         d = DataManager(p, v, cosmo, all_data=False)
-        lik = Likelihood(p.get('params'), d.data_vector, d.covar, th)
+        lik = Likelihood(p.get('params'), d.data_vector, d.covar, th, template=d.templates)
         sam = Sampler(lik.lnprob, lik.p0, lik.p_free_names,
                       p.get_sampler_prefix(v['name']), p.get('mcmc'))
 
@@ -155,9 +156,10 @@ def chan(fname_params, diff=False, error_type=None, b_hydro=None, chains=True):
 
         # p0 or user-input b_hydro
         if b_hydro is None:
-            bys = np.array([hm_bias(cosmo, 1/(1 + zarr),
-                        d.tracers[1][1].profile,
-                        **(lik.build_kwargs(p0))) for p0 in sam.chain[::100]])
+            bys = np.mean(np.array([hm_bias(cosmo, 1/(1 + zarr),
+                                            d.tracers[1][1].profile,
+                                            **(lik.build_kwargs(p0)))
+                                    for p0 in sam.chain[::by_subsample]]),axis=1)
             bymin, by, bymax = np.percentile(bys, [16, 50, 84])
             if diff: bymin=by-bymin; bymax=bymax-by
             kwargs["by"] = [by, bymin, bymax]
@@ -172,8 +174,9 @@ def chan(fname_params, diff=False, error_type=None, b_hydro=None, chains=True):
         params.append(kwargs)
         chi2.append(lik.chi2(sam.p0))
         dof.append(len(lik.dv))
+        bf.append(sam.p0)
[…]

### 2019-08-21 analysis/params.py
re-run bhydro

@@ -117,9 +117,10 @@ class ParamRun(object):
             str: file prefix.
         """
         fname = self.get_prefix_cls(f1, f2)
-        if jk_region is not None:
+        if bool(jk_region):
             fname += "_jk%d" % jk_region
         fname += ".npz"
+        print(fname)
         return fname
 
     def get_fname_cmcm(self, f1, f2, f3, f4):

### 2019-08-21 images/b_hydro/bhydro.py

@@ -1,5 +1,7 @@
 import os
-#os.chdir("../../")
+import subprocess
+if "b_hydro" in str(subprocess.check_output(["pwd"])):
+    os.chdir("../../")
 import numpy as np
 from scipy.integrate import simps
 from scipy.interpolate import interp1d
@@ -54,14 +56,11 @@ param_yml = ["params_default.yml",
              "params_tinker.yml",
              "params_kmax.yml",
              "params_masked.yml"]
-#param_yml = ["params_wfixed.yml",
-#             "params_wnarrow.yml",
-#             "params_wbroad.yml"]
+
 
 sci = [r"$\mathrm{2MPZ}$"] + \
       [r"$\mathrm{WI \times SC}$ - $\mathrm{%d}$" % i for i in range(1, 6)]
 lbls = ["fiducial", "$y$-NILC", "Tinker10", r"$k_{max}$", "high mass mask"]
-#lbls = ["$w = 1$", r"$w \in [0.8, 1.2]$", r"$w \in [0.2, 2.0]$"]
 colours = ["k", "brown", "darkorange", "orangered", "y"]
 col = [copper(i) for i in np.linspace(0, 1, len(sci))]
 fmts = ["o"]*len(param_yml)

### 2019-08-21 images/covar/covar.py

@@ -1,5 +1,7 @@
 import os
-#os.chdir("../../")
+import subprocess
+if "covar" in str(subprocess.check_output(["pwd"])):
+    os.chdir("../../")
 import numpy as np
 from likelihood.chanal import chan
 import matplotlib.pyplot as plt
@@ -31,8 +33,8 @@ def covplot(cov, save=None):
         os.chdir("../../")
 
 
-bh = np.vstack([np.load("output_default/b_hydro_jackknife%d.npy" % jk)
-                 for jk in np.arange(1, 461)])
+bh = np.vstack([np.load("output_default/b_hydro_jackknife_%d.npy" % jk)
+                 for jk in np.arange(1, 3)])
 
 bh_cov = (len(bh)-1)*np.cov(bh.T, bias=True)
 np.save("output_default/bhydro_covar.npy", bh_cov)

### 2019-08-21 images/fits/fits_v3.py

@@ -1,5 +1,7 @@
 import os
-#os.chdir("../..")
+import subprocess
+if "fits" in str(subprocess.check_output(["pwd"])):
+    os.chdir("../../")
 import numpy as np
 import pyccl as ccl
 from analysis.params import ParamRun

### 2019-08-21 images/werrors/w_test.py

@@ -1,0 +1,84 @@
+import numpy as np
+from scipy.integrate import simps
+from scipy.interpolate import interp1d
+from scipy.optimize import curve_fit
+import matplotlib.pyplot as plt
+
+
+def gaus(x, mu, sigma):
+    """Returns a normalised gaussian with (mu, sigma) parameters."""
+    a = 1/(sigma*np.sqrt(2*np.pi))
+    p = a*np.exp(-0.5*((x-mu)/sigma)**2)
+    p /= simps(p, x)
+    return p
+
+
+def modgaus(z, nz, w):
+    """Modified Gaussian function."""
+    nzf = interp1d(z, nz, kind="cubic", bounds_error=False, fill_value=0)
+    z_avg = np.average(z, weights=nz)
+    nz_new = nzf(z_avg + (1/w)*(z-z_avg))
+    nz_new /= simps(nz_new, x=z)
+    return nz_new
+
+
+def convolve(z, a1, a2):
+    """Convolves and normalises two arrays."""
+    nz = np.convolve(a1, a2, "full")[::2]
+    nz /= simps(nz, x=z)
+    return nz
+
+
+def nz_maker(z, f1=(0.20, 0.25), f2=(0.00, 0.04), full_output=False):
+    """Makes fiducial N(z)'s for a top-hat + Gaussian combination."""
+    # tophat
+    top = np.zeros_like(z)
+    ones = np.where((z >= f1[0]) & (z <= f1[1]))[0]
+    top[ones] = 1
+    top /= simps(top, x=z)
+    # Gaussian
+    pr = gaus(z, f2[0], f2[1])
+    # convolve & normalise
+    nz = convolve(z, top, pr)
+    if full_output:
+        return top, pr, nz
+    else:
+        return nz
+
+
+
+# redshifts
+z = np.linspace(-0.3, 0.50, 1000)
+s_fid = 0.04
+s_ext = 1.50
+sigmas = np.append(np.linspace(0.99, 1.01, 100), s_ext)*s_fid
+
+top, pr, nz_fid = nz_maker(z, full_output=True)
+
+nz = np.array([nz_maker(z, f2=(0.00, s), full_output=False) for s in sigmas])
+
+p = [curve_fit(lambda z, w: modgaus(z, nz_fid, w), z, N) for N in nz]
[…]

### 2019-08-21 mcmc.py

@@ -86,5 +86,5 @@ for v in p.get('data_vectors'):
 if len(par) > 0:
     is_jk = str(jk_region) if bool(jk_region) else ""
     fname = p.get_outdir() + "/" + p.get("mcmc")["save_par"] + \
-            "_" + p.get("mcmc")["run_name"] + is_jk
+            "_" + p.get("mcmc")["run_name"] + "_" + is_jk
     np.save(fname, np.array(par))

### 2019-08-21 model/data.py

@@ -212,7 +212,6 @@ class DataManager(object):
                 tr2 = [tracers[n] for n in tp2['tracers']]
                 nd2_here = np.sum(m2)  # Number of points for vector 2
                 # Read covariance block
-                if jk_region: v["covar_type"] = "jk"  # jackknives
                 fname_cov, trans = choose_cov_file(p, tr1, tr2,
                                                    v['covar_type'])
                 with np.load(fname_cov) as f:

### 2019-08-21 plot_bhydro.py

@@ -48,12 +48,17 @@ def get_dndz(fname, width):
     return zd, Nd_new
 
 
-param_yml = ["params_dam_wnarrow.yml",
-             "params_dam_tinker10.yml",
-             "params_dam_wfixed.yml",
-             "params_dam_ynilc.yml",
-#             "params_dam_masked.yml"
-]
+#param_yml = ["params_dam_wnarrow.yml",
+#             "params_dam_tinker10.yml",
+#             "params_dam_wfixed.yml",
+#             "params_dam_ynilc.yml",
+##             "params_dam_masked.yml"
+#]
+
+param_yml = ["params_default.yml",
+             "params_tinker.yml",
+             "params_wfixed.yml",
+             "params_ynilc.yml"]
 
 sci = [r"$\mathrm{2MPZ}$"] + \
       [r"$\mathrm{WI \times SC}$ - $\mathrm{%d}$" % i for i in range(1, 6)]
@@ -125,7 +130,7 @@ hist.set_ylabel(r"$\mathrm{d} n \mathrm{/d} z$", fontsize=17)
 for i, (dd, cc, fmt, lbl) in enumerate(zip(data, colours, fmts, lbls)):
     plotfunc(ax, z, dd, fmt=fmt, color=cc, label=lbl, inverted=True, offset=i)
 ax.errorbar([0.37],[0.59],yerr=[0.03],fmt='D',c='r',label='Constant fit')
-    
+
 handles, labels = ax.get_legend_handles_labels()
 ax.legend([object]+handles, ["Planck15"]+labels,
           handler_map={object: AnyObjectHandler()},
@@ -139,6 +144,6 @@ ax.legend([object]+handles, ["Planck15"]+labels,
 hist.legend(loc="lower center", bbox_to_anchor=[0.5, -0.15],
             ncol=len(sci), fontsize=9.5, frameon=False)
 
-plt.savefig("notes/paper/bhydro.pdf", bbox_inches="tight")
+#plt.savefig("notes/paper/bhydro.pdf", bbox_inches="tight")
 plt.show()
 #os.chdir("images/b_hydro/")

### 2019-08-23 images/werrors/w_test.py
EN (gb) + some text here and there and everywhere

@@ -24,7 +24,7 @@ def modgaus(z, nz, w):
 
 def convolve(z, a1, a2):
     """Convolves and normalises two arrays."""
-    nz = np.convolve(a1, a2, "full")[::2]
+    nz = np.correlate(a1, a2, "full")[::2]
     nz /= simps(nz, x=z)
     return nz
 
@@ -72,7 +72,7 @@ plt.figure()
 plt.plot(soff[:-1], woff[:-1], "k", lw=3)
 plt.xlabel("percentage offset in $\sigma$")
 plt.ylabel("percentage offset in $w$")
-#plt.savefig("error_test1.pdf")
+plt.savefig("error_test1.pdf")
 
 plt.figure()
 plt.plot(z, top, "k:", label="$p(z_{photo})$")
@@ -81,4 +81,4 @@ plt.plot(z, nz_fid, "k-", lw=4, label="$p_{fid} = N(z|0, \sigma_{fid})$")
 plt.plot(z, nz[-1], "r-", lw=2, label="$N(z|0, %.1f\sigma_{fid})$" % s_ext)
 plt.plot(z, nz_fit, "b--", lw=1, label="best fit")
 plt.legend()
-#plt.savefig("error_test2.pdf")
+plt.savefig("error_test2.pdf")

### 2019-08-23 plot_fits.py

@@ -232,7 +232,7 @@ for s, v in enumerate(p.get("data_vectors")):
             if i == 1:
                 ax1.text(0.45, 1.1, r"$y \times g$", fontsize=15,
                          transform=ax1.transAxes)
-                ax1.legend(loc="lower right", ncol=4, fontsize=8)
+                ax1.legend(loc="lower center", ncol=4, fontsize=8)
 
         if s != len(surveys)-1:
             ax2.get_xaxis().set_visible(False)

### 2019-09-11 plot_mf.py
mf ratio plot

@@ -1,0 +1,68 @@
+import pyccl as ccl
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib import cm
+from matplotlib.ticker import FormatStrFormatter
+import matplotlib.colors as colors
+from matplotlib import rc
+rc("font", **{"family":"sans-serif", "sans-serif":["Helvetica"]})
+rc("text", usetex=True)
+
+
+
+def truncate_colormap(cmap, minval=0.0, maxval=1.0, n=100):
+    # https://matplotlib.org/api/colors_api.html
+    new_cmap = colors.LinearSegmentedColormap.from_list(
+        "trunc({n},{a:.2f},{b:.2f})".format(n=cmap.name, a=minval, b=maxval),
+        cmap(np.linspace(minval, maxval, n)))
+    return new_cmap
+
+
+z = np.linspace(0.01, 0.5, 20)
+a = 1/(1+z)
+
+
+cosmo = [ccl.Cosmology(Omega_c=0.26066676,
+                       Omega_b=0.048974682,
+                       h=0.6766,
+                       sigma8=0.8102,
+                       n_s=0.9665,
+                       mass_function=mf) for mf in ["tinker", "tinker10"]]
+
+M = np.logspace(10, 15, 100)
+
+mfr = [[]]*len(a)
+for i, sf in enumerate(a):
+    rho = [500/ccl.omega_x(c, sf, "matter") for c in cosmo]
+    mf = [ccl.massfunc(c, M, sf, overdensity=r) for c, r in zip(cosmo, rho)]
+    mfr[i] = mf[0]/mf[1]
+
+mfr = np.array(mfr)
+
+cmap = truncate_colormap(cm.Reds, 0.2, 1.0)
+col = [cmap(i) for i in np.linspace(0, 1, len(a))]
+
+fig, ax = plt.subplots(figsize=(9, 7))
+ax.set_xlim(M.min(), M.max())
+ax.axhline(y=1, ls="--", color="k")
+[ax.loglog(M, R, c=c, label="%s" % red) for R, c, red in zip(mfr, col, z)]
+
+ax.yaxis.set_major_formatter(FormatStrFormatter("$%.1f$"))
+ax.yaxis.set_minor_formatter(FormatStrFormatter("$%.1f$"))
+
+sm = plt.cm.ScalarMappable(cmap=cmap,
[…]

### 2019-09-11 notes/paper/paper.tex
updated paper to latest version

\documentclass[useAMS,usenatbib]{mn2e}
\bibliographystyle{mn2e}
\pdfoutput=1
\pdfminorversion=5

%\usepackage{widetext}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{amssymb,amsmath,bm}  
\usepackage{color}
\usepackage[colorlinks,linkcolor=red,citecolor=blue,urlcolor=blue ]{hyperref}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage{balance}
\usepackage{enumitem}
\usepackage{lipsum}
\usepackage{ulem}

\newcommand{\nv}{\hat{\boldsymbol{\theta}}}
\newcommand{\wisc}{WI$\times$SC}
\newcommand{\cites}{{\bf CITES}}
\newcommand{\todo}[1]{{\bf TODO:} #1}
\newcommand{\kalo}{Karhunen-Lo\`{e}ve\,}
\newcommand{\jcap}{JCAP}
\newcommand{\mnras}{MNRAS}
\newcommand{\aap}{A\&A}
\newcommand{\aaps}{A\&AS}
\newcommand{\apjs}{ApJS}
\newcommand{\apj}{ApJ}
\newcommand{\apjl}{ApJL}
\newcommand{\prd}{Phys.~Rev.~D}
\newcommand{\prl}{Phys.~Rev.~Lett.}
\newcommand{\aj}{Astron. Journal}
\newcommand{\pasp}{Publications of the ASP}
\newcommand{\nar}{New Astronomy Review}
\newcommand{\procspie}{Proceedings of the SPIE}
\newcommand{\physrep}{Physics Reports}
\newcommand{\baas}{Bulletin of the AAS}
\newcommand{\araa}{Annual Review of Astron and Astrophys}

\newcommand{\MB}[1]{\textcolor{red}{#1}}
\newcommand{\DA}[1]{\textcolor{green}{#1}}

\def\bH{b_{\scriptscriptstyle\rm H}}
\def\planck{{\it Planck\/}}
\def\citejap#1{\citeauthor{#1}\ \citeyear{#1}}

\title[Tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations]{Wide-angle tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations}
\author[David Alonso]{Nick Koukoufilippas$^1$, David Alonso$^1$, Maciej Bilicki$^2$, John A. Peacock$^3$\\
                      $^{1}$Department of Physics, University of Oxford, Keble Road, Oxford, OX1 3RH, UK\\
                      $^{2}$Center for Theoretical Physics, Polish Academy of Sciences, al. Lotnik\'ow 32/46, 02-668, Warsaw, Poland\\
                      $^{3}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ, United Kingdom
                      }

\begin{document}
  \date{\today}
  \pagerange{1--18} \pubyear{2018}
  \maketitle

\begin{abstract}
    We cross-correlate maps of the thermal Sunyaev-Zeldovich (tSZ)
    Compton-$y$ parameter published by \planck\ with the projected
    distribution of galaxies in a set of low-redshift tomographic
    bins. We use the nearly full-sky 2MASS Photometric Redshift and
    WISE $\times$ SuperCOSMOS public
    catalogues, covering the redshift range $z\lesssim0.4$. Our
    measurements allow us to place constraints on the redshift
    dependence of the mass-observable relation for tSZ cluster count
    analysis in terms of the so-called `hydrostatic bias' parameter
    $1-\bH$. These resultsts can also be interpreted as measurements
    of the bias-weighted average gas
    pressure $\langle bP_e\rangle$ as a function of redshift, a
    quantity that can be related to the thermodynamics of gas inside
    haloes and used to constrain energy injection processes. We
    measure $1-\bH$ with $\sim13\%$ precision in 6 equispaced
    redshift bins, and find no evidence for a redshift-dependent mass
    bias parameter, in agreement with previous analyses. Our mean value of
    $1-\bH = 0.59\pm0.03$ is also in good agreement with that estimated by
    the joint analysis of \planck\ cluster counts and CMB
    anisotropies. Our measurements of $\langle bP_e\rangle$, at the
    level of $\sim10\%$ in each bin, are the most stringent
    constraints on the redshift dependence of this parameter to date,
    and agree well both with previous measurements and with
    theoretical expectations from shock-heating
    models. \todo{Something we do not discuss at all, but should, is
      the fact that all our constraints assume (and depend on) the
      value of $\sigma_8$ found by Planck18 primary CMB. Our
      measurement of $1-\bH$ will depend on whatever prior on
      $\sigma_8$ we use, and therefore it shouldn't be completely
      surprising that we find something that agrees with \planck. It
      is however a good consistency check that we do, and what is
      definitely new is the measurement of the redshift
      dependence. I'd add words about this in Sections
      \ref{sec:results} and \ref{sec:conclusion}.}
\end{abstract}

\begin{keywords}
  cosmology: large-scale structure of the Universe, observations -- methods: data analysis
\end{keywords}

\section{Introduction}\label{sec:intro}
  Modern observational cosmology has reached a stage where constraints from most current and future datasets are limited by astrophysical systematic uncertainties, i.e. our lack of detailed understanding of the small-scale physics behind the luminous components of the Universe, galaxies and gas \citep[e.g.][]{2011MNRAS.415.3649V,2011MNRAS.417.2020S,2014JCAP...04..028F,2015MNRAS.454.2451E,2015MNRAS.454.1958M,2015JCAP...12..049S,2019MNRAS.488.1652H,2019JCAP...03..020S,2019OJAp....2E...4C}. The limiting factor for cosmological constraints from cluster number counts is the uncertainty in the mass-observable relation \citep{2009ApJ...692.1060V,2010ApJ...722.1180V,2011ApJ...732...44S,2013JCAP...07..008H,2014MNRAS.440.2077M,2014A&A...571A..20P,2015MNRAS.446.2205M,2016A&A...594A..24P,2016ApJ...832...95D,2019ApJ...878...55B}. \MB{[why is this relevant here?]} \DA{[It's another example of where gastrophysics limits cosmology.]} Cosmic shear measurements are strongly affected by sub-grid baryonic physics, and by uncertainties in the processes by which galaxies acquire correlated intrinsic alignments \citep[e.g.][]{2001MNRAS.320L...7C,2002MNRAS.332..788M,2004PhRvD..70f3526H,2017MNRAS.465.2033J,2018PhRvD..98d3528T,2018arXiv181206076H,2018ARA&A..56..393M,2018arXiv181106989S}. Finally, even though the clustering pattern of galaxies is one of the cosmological observables with the highest signal-to-noise ratio, the cosmological constraints that can be extracted from it are severely limited by our incomplete understanding of the galaxy-dark matter connection \citep[see e.g.][and references therein]{2018ARA&A..56..435W}. Even the analysis of the temperature anisotropies in the Cosmic Microwave Background (CMB), arguably the cleanest cosmological observable, are currently limited by the impact of astrophysical foregrounds on small scales \citep{2014ApJ...782...74H,2017JCAP...06..031L,2019arXiv190712875P}.

  The CMB secondary anisotropies, in particular the thermal and kinetic Sunyaev-Zeldovich effects \citep[tSZ and kSZ respectively,][]{1972CoASP...4..173S}, as well as the gravitational lensing of the CMB photons, have gained popularity as a means to address this issue \citep{2017JCAP...11..040B,2019BAAS...51c.297B}. These effects are relatively clean probes of some of the physical quantities that need to be understood in order to mitigate the impact of astrophysical uncertainties: the matter and gas densities, the gas pressure and the velocity field. Since these observables are also sensitive to cosmology, their combination with large-scale structure data can be extremely powerful at disentangling astrophysical and cosmological parameters. This has been explored by a large number of groups: CMB lensing data have been used to constrain the bias of different tracers of the matter distribution \citep[e.g.][]{2019MNRAS.485.1720H,2018JCAP...04..053A,2018arXiv181002322A,2018MNRAS.481.1133P}, as well as to calibrate the measurement of galaxy shapes in cosmic shear analyses \citep{2017PhRvD..95l3512S}. The tSZ effect has been used in cross-correlation with galaxy clustering and weak lensing data to determine the physical properties of the diffuse gas, as well as to potentially improve constraints on the amplitude of matter fluctuations \citep{2014PhRvD..89b3508V,2014JCAP...02..030H,2015JCAP...09..046M,2017MNRAS.471.1565H,2017ApJ...845...71A,2018PhRvD..97f3514A,2018MNRAS.480.3928M,2019A&A...624A..48D,2019MNRAS.483..223T,2019arXiv190306654T,2019arXiv190413347P,2019arXiv190707870M}. The kSZ has been used in cross-correlation with galaxy clustering to constrain the growth of structure and the gas density profile around haloes \citep{2016PhRvD..93h2002S,2016A&A...586A.140P,2016PhRvL.117e1301H,2016MNRAS.461.3172S,2017JCAP...03..008D}.

  In this work we will focus on the cross-correlation between galaxy clustering data and maps of the tSZ Compton-$y$ parameter, making use of existing data from the Planck collaboration \citep{2016A&A...594A..22P} and a set of photometric galaxy surveys \citep{2014ApJS..210....9B,2016ApJS..225....5B}. The availability of redshift information will allow us to place constraints on the cosmic evolution of the thermal gas pressure and the thermal energy in haloes, as well as to examine any redshift dependence of the mass bias for tSZ cluster studies. This is a relevant topic given the current mild tensions between SZ cluster number counts and CMB primary anisotropies \citep{2016A&A...594A..24P,2016ApJ...832...95D,2019ApJ...878...55B,2019arXiv190407887Z}, which could be caused by the assumptions made to model the $y$-mass relation. Conversely, under the assumption that the relation between mass and gas pressure is well understood, the tSZ effect can be thought of as a mass tracer, which can be used to break degeneracies with the galaxy bias parameter -- we will however leave this analysis for future work.

  This paper is structured as follows: Section \ref{sec:theory} presents the theoretical background used here to describe our two main observables, the projected overdensity of galaxies and the Compton-$y$ parameter, as well as their cross-correlation. Section \ref{sec:data} presents the datasets used for our analysis. The methods used to analyse these data are described in Section \ref{sec:methods}, and Section \ref{sec:results} presents the results. We summarise our conclusions in Section \ref{sec:conclusion}.

\section{Theory}\label{sec:theory}
  Our work focuses on the cross-correlation of the projected galaxy overdensity in consecutive redshift bins $\delta_g$ and maps of the tSZ Compton-$y$ parameter.

  Here $\delta_g$ is simply the overdensity in the number of galaxies integrated over a redshift bin:
  \begin{equation}
    \delta_g(\nv)=\int dz\,\phi_g(z)\,\Delta_g(\chi(z)\,\nv),
  \end{equation}
  where $\nv$ is a unit vector on the sphere, $\chi(z)$ is the comoving radial distance to redshift $z$ and $\phi_g(z)$ is the normalised galaxy redshift distribution in the bin. $\Delta_g({\bf x})=n_g({\bf x})/\bar{n}_g-1$ is the 3D galaxy overdensity, where $n_g$ is the galaxy number density.

  The Compton-$y$ parameter in turn is given by \citep{1972CoASP...4..173S}:
  \begin{equation}\label{eq:compty}
    y(\nv)=\frac{\sigma_{\scriptscriptstyle \rm T}}{m_ec^2}\int \frac{d\chi}{(1+z)} P_e(\chi\nv),
  \end{equation}
  where $P_e=n_e\,T_e$ is the electron pressure ($n_e$ and $T_e$ are the electron density and temperature respectively), $\sigma_{\scriptscriptstyle\rm T}$ is the Thomson scattering cross-section, and $m_e$ is the electron mass. For a fully ionised gas, the electron pressure is directly related to the total thermal gas pressure through $P_{\rm th}=P_e\,(8-5Y)/(4-2Y)$, where $Y$ is the helium mass fraction (with $Y\simeq0.24$).

  \subsection{Projected fields and angular power spectra}\label{ssec:theory.cls}    
    Both $\delta_g$ and $y$ can be described as a projected quantity $u(\nv)$ related to a three-dimensional field $U({\bf r})$ through some radial kernel $W_u(\chi)$:
    \begin{equation}
      u(\nv)=\int d\chi\,W_u(\chi)\,U(\chi\nv).
    \end{equation}
    Any projected quantity can be decomposed into its spherical harmonic coefficients $u_{\ell m}$, the covariance of which is the so-called angular power spectrum $\langle u_{\ell m}v^*_{\ell' m'}\rangle\equiv C^{uv}_\ell\delta_{\ell\ell'}\delta_{mm'}$.

    The angular power spectrum can be related to the 3D power spectrum of the associated 3D fields $P_{UV}$ as\footnote{Note that Eq.\!~\ref{eq:cllimber} is only valid in the {\sl Limber approximation} \citep{1953ApJ...117..134L,1992ApJ...388..272K}, which is accurate for broad radial kernels. This approximation is adequate for the redshift distributions and scales used here.}:
    \begin{equation}\label{eq:cllimber}
      C_\ell^{uv} = \int d\chi \frac{W_u(\chi)W_v(\chi)}{\chi^2}\,P_{UV}\left(k=\frac{\ell+1/2}{\chi},z(\chi) \right).
    \end{equation}
    Here, the 3D power spectrum is analogously defined as the variance of the Fourier-space 3D quantities:
    \begin{equation}
      \left\langle U({\bf k})V^*({\bf k}')\right\rangle = (2\pi)^3\,\delta({\bf k}-{\bf k}')\,P_{UV}(k).
    \end{equation}
    We model the 3D power spectrum using the halo model, which we describe in the next section.

    In this formalism, the 3D quantities associated with $\delta_g(\nv)$ and $y(\nv)$ are the 3D overdensity $\Delta_g({\bf x})$ and the electron pressure $P_e({\bf x})$ respectively. The associated radial kernels are:
    \begin{equation}
      W_g(\chi)=\frac{H(z)}{c}\,\phi_g(z),\hspace{12pt}W_y(\chi)=\frac{\sigma_{\scriptscriptstyle\rm T}}{m_ec^2}\frac{1}{1+z},
    \end{equation}
    where $H(z)$ is the expansion rate.

  \subsection{Halo model predictions}\label{ssec:theory.hm}
    The halo model describes the spatial fluctuations of any quantity in terms of the contributions of all dark matter haloes, under the assumption that all matter in the Universe is contained in those haloes. We only quote here the final results regarding the halo model prediction for power spectra, and refer the reader to \cite{2000MNRAS.318..203S,2000MNRAS.318.1144P,2002PhR...372....1C} for further details.

    Let $U(r|M)$ be the profile of a given quantity as a function of the comoving distance $r$ to the centre of a halo of mass $M$, and let $U(k|M)$ be its Fourier transform:
    \begin{equation}
      U(k|M)\equiv4\pi \int_0^\infty dr\,r^2\,\frac{\sin(kr)}{kr}U(r|M).
    \end{equation}
    The halo model prediction for the cross-power spectrum $P_{UV}$ then consists of two contributions, from the so-called 1-halo term and 2-halo term:
    \begin{equation}
      P_{UV}(k)=P^{1h}_{UV}(k)+P^{2h}_{UV}(k).
    \end{equation}
    Each of these can be estimated in terms of the Fourier-space profiles as:
    \begin{align}
      &P^{1h}_{UV}(k)=\int dM\,\frac{dn}{dM}\,\langle U(k|M)\,V(k|M)\rangle,\\
      &P^{2h}_{UV}(k)=\langle bU\rangle\,\langle bV\rangle\,P_L(k),\\
      &\langle bU\rangle(k)\equiv\int dM\frac{dn}{dM}\,b_h(M)\,\langle U(k|M)\rangle. \label{eq:hm_bias}
    \end{align}
    Here, $P_L(k)$ is the linear matter power spectrum, $dn/dM$ is the halo mass function (comoving density of haloes per unit halo mass) and $b_h(M)$ is the halo bias.
    %Further details are discussed in Appendix \ref{app:hm}.

    It is important to note that the halo model is inaccurate in the range of scales corresponding to the transition between the 1-halo and 2-halo-dominated regimes. This is a well-known effect \citep{2015MNRAS.454.1958M}, and we correct for it here simply by multiplying all halo-model power spectra by a universal scale-dependent factor, given by the ratio between the revised {\sl halofit} prediction for the matter power spectrum of \cite{2012ApJ...761..152T} and the pure halo-model prediction for the same quantity
    \begin{equation}
      R(k)\equiv\frac{P_{\rm Halofit}(k)}{P_{\rm halo\,model}(k)}.
    \end{equation}

    \subsubsection{Galaxies and the halo occupation distribution}\label{sssec:theory.hm.hod}
      To model the galaxy overdensity $\Delta_g$ we will use a Halo Occupation Distribution (HOD) model \citep{2002ApJ...575..587B,2005ApJ...633..791Z,2013MNRAS.430..725V}, as prescribed by \cite{2011ApJ...736...59Z}. The HOD models the galaxy content of dark matter haloes as being made up of central and satellite galaxies. Centrals lie at the centre of the halo, while satellites are distributed according to a profile $u_s(r|M)$. Haloes can have zero or one central, and the mean number of centrals for a halo of mass $M$ is modelled as a smoothed step function
      \begin{equation}
        \langle N_c(M)\rangle=\frac{1}{2}\left[1+{\rm erf}\left(\frac{\log(M/M_{\rm min})}{\sigma_{\rm lnM}}\right)\right].
      \end{equation}
      We then assume that satellites can only be formed if a halo has a central and has a mass larger than some threshold $M_0$. In that case, the average number of satellites follows a power law of the form:
      \begin{equation}
        \langle N_s(M)\rangle=\Theta(M-M_0)\,\left(\frac{M-M_0}{M_1'}\right)^{\alpha_s}.
      \end{equation}
      For simplicity, we will fix $M_0$ to $M_{\rm min}$, $\sigma_{\rm lnM}=0.15$ and $\alpha_s$=1, as in \cite{2018MNRAS.473.4318A}, leaving only two free parameters: $M_{\rm min}$ and $M_1'$.

      Besides their mean values, we also need to specify the statistics of $N_c$ and $N_s$. Following the standard practice \citep{2013MNRAS.430..725V}, we assume $N_c$ to have a binomial distribution with probability $p=\langle N_c\rangle$, and $N_s$ to be Poisson-distributed.

      Putting everything together, the moments of the galaxy overdensity Fourier profile are \citep{2013MNRAS.430..725V}:
      \begin{align}
        &\langle u_g(k)\rangle=\bar{n}_g^{-1}\langle N_c\rangle\left[1+\langle N_s\rangle\,u_s(k)\right],\\
        &\langle |u_g(k)|^2\rangle=\bar{n}_g^{-2}\langle N_c\rangle\left[\langle N_s\rangle^2u_s^2(k)+2\langle N_s\rangle u_s(k)\right],
      \end{align}
      where the mean number density $\bar{n}_g$ is
      \begin{equation}
        \bar{n}_g\equiv\int dM\,\frac{dn}{dM}\langle N_c\rangle\left[1+\langle N_s\rangle\right],
      \end{equation} 
      and we have suppressed the mass dependence of all quantities for simplicity.

      Finally, we assume that the satellites follow the matter distribution, and therefore $u_s(k|M)$ is given by a truncated Navarro, Frenk and White profile \citep{1996ApJ...462..563N}:
      \begin{align}
        u_s(k|M)=&\left[\log(1+c_\Delta)-\frac{c_\Delta}{(1+c_\Delta)}\right]^{-1}\\\nonumber
               &\left[\cos(q)\left({\rm Ci}((1+c_\Delta)q)-{\rm Ci}(q)\right)\right.\\\nonumber
               &\left.+\sin(q)\left({\rm Si}((1+c_\Delta)q)-{\rm Si}(q)\right)\right.\\\nonumber
               &\left.-\sin(c_\Delta q)/(1+c_\Delta q)\right],
      \end{align}
      where $q\equiv kr_\Delta/c_\Delta$, $r_\Delta$ and $c_\Delta$ are the halo radius and concentration defined in Section \ref{sssec:theory.hm.cm}, and $\{{\rm Ci}, {\rm Si}\}$ are the cosine and sine integrals.

    \subsubsection{tSZ and pressure profiles}\label{sssec:theory.hm.pe}
      In order to describe the electron pressure in a halo, we use the generalised NFW profile (GNFW) described in \cite{2010A&A...517A..92A} and used in the \planck\ tSZ cluster analysis \cite{2016A&A...594A..24P}. This profile takes the form:
      \begin{equation}
        P_e(r)=P_*\,p(r/r_{500c}),
      \end{equation}
      where $r_{500c}$ is the cluster radius enclosing an overdensity of 500 times the critical density (see Section \ref{sssec:theory.hm.cm}). The normalization $P_*$ is given by
      \begin{equation}\label{eq:arnaud_norm}
        P_*=6.41\,\left(1.65\,\, {\rm eV}\,{\rm cm}^{-3}\right)h_{70}^{8/3}
        \left(\frac{h_{70}(1-\bH)M_{500c}}{3\times10^{14}M_\odot}\right)^{0.79},
      \end{equation}
      where $h_{70}=H_0/(70\ {\rm km}\,{\rm s}^{-1}\,{\rm Mpc}^{-1})$, and $M_{500c}$ is the halo mass enclosed by $r_{500c}$. The GNFW form factor is
      \begin{equation}
        p(x)=(c_P x)^{-\gamma}\left[1+(c_P x)^\alpha\right]^{(\gamma-\beta)/\alpha},
      \end{equation}
      with $(\alpha,\beta,\gamma,c_P)=(1.33,4.13,0.31,1.81)$. We must note that other pressure profiles have been proposed in the literature (e.g. \citejap{2012ApJ...758...75B}), but we choose this parameterisation in order to be able to relate our measurement of $(1-\bH)$ to the results of \cite{2016A&A...594A..24P}.

      The quantity $1-\bH$ in Eq.\!~\ref{eq:arnaud_norm} parameterises our lack of knowledge about the precise relation between mass and pressure in clusters. This factor is also commonly referred to as the `hydrostatic bias', since it was originally defined to account for the fraction of halo mass not in hydrostatic equilibrium missed by X-ray observations. Since this parameter also encapsulates other sources of bias in the X-ray-based mass estimates, we will instead refer to it as the \emph{mass bias}. Numerical simulations have constrained the mass deficit to be around 20\% (i.e. $1-\bH\simeq0.8$: \citejap{2012ApJ...758...74B}; \citejap{2014ApJ...782..107N}), although it is known that a smaller value is needed in order to fully reconcile CMB primary constraints and SZ cluster counts \citep{2016A&A...594A..24P}. This will be a central point of our discussion in Sections \ref{sec:results} and \ref{sec:conclusion}.

      Within the halo model description, and assuming a log-normal $y$-mass relation, the pressure profile cumulants are given by:
      \begin{align}
        &\langle u_y(k|M)\rangle=P_e(k),\\
        &\langle u_y^2(k|M)\rangle=P_e^2(k)\,e^{\sigma_{\ln Y}^2},
      \end{align}
      where $P_e(k)$ is the Fourier transform of the GNFW profile and $\sigma_{\ln Y}=0.173\pm0.023$ is the intrinsic logarithmic scatter in the $y$-mass relation \cite{2016A&A...594A..24P}. Note that, since we do not make use of the tSZ auto-correlation, we will not use the second order cumulant of the pressure profile in our analysis. However, since we analyse the galaxy-tSZ correlation, we need to model the covariance between the galaxy overdensity and pressure profiles. For simplicity, we adopt a simple parameterisation:
      \begin{equation}
        \langle u_y(k|M) u_g(k|M)\rangle = (1+\rho_{yg})\langle u_g(k|M)\rangle \langle u_y(k|M)\rangle,
      \end{equation}
      where $\rho_{yg}$ is a free parameter that determines the sign of the correlation between galaxy abundance and pressure. Marginalising over this parameter has the added advantage of removing any sensitivity of our final constraints to $1-\bH$ on the details of the cross-spectrum model in the 1-halo regime, where both parameters are completely degenerate.

      It is also worth exploring the halo model bias (Eq.\!~\ref{eq:hm_bias}) for the Compton-$y$ parameter. At $k\rightarrow0$ it is given by:
      \begin{align}\nonumber
        \langle bP_e\rangle&=\int dM\,\frac{dn}{dM}\,b_h(M)\,\int_0^\infty dr\,4\pi r^2\,P_e(r|M)\\\label{eq:by}
               &=\int dM\,\frac{dn}{dM}\,b_h(M)\,E_T(M),
      \end{align}
      where $E_T(M)$ is the thermal energy in a halo of mass $M$ \citep{2017MNRAS.467.2315V,2019arXiv190413347P}. A measurement of $\langle bP_e\rangle$ can therefore be related to the thermodynamics of gas inside haloes \MB{[more about this relation? and, this is electron pressure - how it connects to gas pressure?]} \DA{[Eq. \ref{eq:by} is the equation linking to thermal energy. Note that electron and total pressure are just proportional to each other, I've now noted this below Eq. \ref{eq:compty}.]}. We will also express our measurements in terms of this parameter in Section \ref{sec:results}.

    \subsubsection{Concentration-mass relation and mass definitions}\label{sssec:theory.hm.cm}
      Halo radii $r_\Delta$ are usually defined as the size of the sphere containing a given mass $M_\Delta$:
      \begin{equation}
        M_\Delta = \frac{4\pi}{3}\rho_*(z) \; \Delta \; r^3_\Delta.
      \end{equation}
      Common choices for $\rho_*$ are the critical density $\rho_c=3H^2(z)/4\pi G$ or the matter density $\rho_M(z)$ \MB{[which one do we use?]}\DA{[We state this in the next paragraph.]}. The spherical overdensity parameter $\Delta$ is usually chosen within the range $\sim(200,500)$ and sometimes defined as the quantity yielding the virial radius in the spherical top-hat collapse model $\Delta_v$ \citep{1998ApJ...495...80B}.

      Ideally we would like to use the same mass definition (i.e. choice of $\Delta$ and $\rho_*$) for the mass function, the mass-concentration relation $c_\Delta(M)$ and the calibrated pressure profile. Unfortunately while the GNFW profile is calibrated to $\Delta_{500c}$ (where $c$ denotes critical density), the mass functions of \cite{2008ApJ...688..709T,2010ApJ...724..878T} are only provided for $\rho_M$-based mass definitions, and the concentration-mass relation of \cite{2008MNRAS.390L..64D} was only estimated for $\Delta=200$ (for critical and matter densities) and for $\Delta=\Delta_v$. To overcome this issue, we follow the procedure used by \cite{2016A&A...594A..24P} and \cite{2018MNRAS.477.4957B}: our baseline mass definition is $\rho_c$-based with $\Delta=500$, as used by \cite{2010A&A...517A..92A}. At each redshift, we translate this into a $\Delta$ value for a $\rho_M$-based definition, which we use to compute the mass function from the parameterisations of \cite{2008ApJ...688..709T,2010ApJ...724..878T}. We also re-derive the concentration-mass relation of \cite{2008MNRAS.390L..64D} for a $\rho_c$-based $\Delta=500$ from their $\Delta=200$ parameterisation by integrating the NFW profile to the corresponding halo radius. Within the redshifts covered by our analysis we find that this is well fit by:
      \begin{equation}
        c_{500c}(M,z)= A\,(M/M_{\rm pivot})^B\,(1+z)^C,
      \end{equation}
      with $M_{\rm pivot}=2.7\times10^{12}\,M_\odot$ and $(A,B,C)=(3.67,\,-0.0903,\,-0.51)$.

\section{Data}\label{sec:data}
  \subsection{The Compton-$y$ map}\label{ssec:data.y}
    \begin{figure}
      \centering
      \includegraphics[width=0.5\textwidth]{mask_y.pdf}
      \includegraphics[width=0.5\textwidth]{mask_g.pdf}
      \caption{{\sl Top panel:} sky mask used for the Compton-$y$ map, corresponding to a sky fraction $f_{\rm sky}=0.59$. {\sl Bottom panel:} mask used for the 2MPZ and \wisc~ galaxy surveys, corresponding to a sky fraction $f_{\rm sky}=0.68$. The product of both masks leaves a usable sky fraction $f_{\rm sky}\simeq0.58$.
      %The top panel shows, in turquoise, the regions masked additionally when removing sky patches around the position of the tSZ sources detected by \planck\ above 6$\sigma$.
      }
      \label{fig:msk}
    \end{figure}
    We make use of the maps of the Compton-$y$ parameter made public by the Planck collaboration \citep{2016A&A...594A..22P}. These maps were generated using different flavours of the Internal Linear Combination method \citep{2004ApJ...612..633E,2008arXiv0811.4277V}. In a simplified description, the ILC technique selects the linear combination of all frequency channels that preserves the spectrum of the source one wishes to map minimising the map-level variance. The refined versions of the ILC method used by \planck\ further optimise the linear weights on different scales and different regions of the map, and project out sources with known spectra that are likely to cause significant contamination. In particular, the Planck collaboration has released two $y$ maps, extracted using the MILCA \citep{2013A&A...558A.118H} and NILC \citep{2011MNRAS.410.2481R} variations of the ILC technique. Both methods deproject CMB contamination through its well-known spectrum, but differ on the methods used to calculate the optimal scale-dependent and spatially-varying linear weights.

    The MILCA and NILC maps have been found to be in good agreement in different studies, although the NILC map has a higher noise level on large scales \citep{2016A&A...594A..22P}. We thus use the MILCA map as our fiducial Compton-$y$ map, but will repeat our analysis on the NILC map as part of our systematics analysis. We use a fiducial mask for the $y$ maps based on a combination of the \planck\ 60\% Galactic mask and the union of the HFI and LFI point source masks (see top panel of Fig.\!~\ref{fig:msk}).
    %As part of our study of the mass dependence of the signal on halo mass, we additionally mask out all tSZ sources detected by \planck\ above 6$\sigma$, based on the Union catalogue of \cite{2016A&A...594A..27P}.

    Finally, in order to evaluate the level of contamination from extragalactic dust in the $\delta_g$-$y$ correlation, we make use of the HFI 545 GHz map, as described in Section \ref{sssec:results.syst.y}.

  \subsection{2MPZ and \wisc}\label{ssec:data.g1}
    \begin{figure}
      \centering
      \includegraphics[width=0.5\textwidth]{nzs.pdf}
      \caption{Fiducial redshift distributions of the different galaxy samples used in this analysis. See Table \ref{tab:z_bins} for further details.}
      \label{fig:dndz}
    \end{figure}
    \begin{table}
      \begin{center}
        \begin{tabular}{l|cccc}
          \hline
          Sample & $[z_{{\rm ph},i},z_{{\rm ph},f}]$ & $\bar{z}$ & $\bar{n}_g\,[{\rm deg}^{-2^{\phantom{2}}}]$ & $\ell_{\rm max}$\\[1ex]
          \hline
          2MPZ    & N.A.         & 0.07 &  25.5 &  280 \\
          \wisc-1 & $[0.1,0.15]$ & 0.13 & 106   &  540 \\
          \wisc-2 & $[0.15,0.2]$ & 0.18 & 126   &  745 \\
          \wisc-3 & $[0.2,0.25]$ & 0.23 & 136   &  945 \\
          \wisc-4 & $[0.25,0.3]$ & 0.27 & 118   & 1130 \\
          \wisc-5 & $[0.3,0.35]$ & 0.32 & 41    & 1310 \\
          \hline
        \end{tabular}
        \caption{Galaxy samples used in this analysis, corresponding to the full 2MPZ survey and five tomographic redshift bins of the \wisc~ survey. The second, third and fourth columns list the photometric redshift interval defining the sample, its mean redshift and its number density respectively. The largest multipole used in the analysis of each sample (corresponding to a comoving scale of $k_{\rm max}\sim 1\,{\rm Mpc}^{-1}$) is shown in the last column.}\label{tab:z_bins}
      \end{center}
    \end{table} 
    We make use of two low-redshift photometric redshift catalogues, the 2MASS Photometric Redshift dataset \citep[2MPZ,][]{2014ApJS..210....9B} and the WISE $\times$ SuperCOSMOS catalogue \citep[\wisc,][]{2016ApJS..225....5B}. Both samples were created by cross-matching full-sky imaging surveys, and photo-$z$s were subsequently computed for all the included sources. Their broad photometric coverage, together with adequate spectroscopic calibration data allowed for obtaining well-constrained photo-$z$s, with minimal mean bias, relatively low scatter and a small number of outliers.

    2MPZ was constructed by cross-matching the extended-source catalogue from the 2 Micron All-Sky Survey \citep[2MASS,][]{2006AJ....131.1163S,2000AJ....119.2498J} with the photographic plates of SuperCOSMOS \citep{2001MNRAS.326.1295H,2016MNRAS.462.2085P} and the photometry of the Wide-field Infrared Survey Explorer (WISE: \citejap{2010AJ....140.1868W}). After applying an apparent magnitude cut $K_s<13.9$ to achieve uniformity, 2MPZ includes over 940,000 sources observed in 8 bands: SuperCOSMOS's optical $(B,R,I)$, 2MASS's near-infrared $(J,H,K_s)$ and WISE's mid-infrared $(W1,W2)$. Photometric redshifts (photo-$z$s) were extracted using the neural network code ANNz \citep{2004PASP..116..345C} trained on a large spectroscopic sample from overlapping surveys. The resulting photo-$z$'s have a typical error $\sigma_z\simeq0.015$, and the sample has a median redshift $z\simeq0.08$ (see also \citealt{2018MNRAS.476.1050B} for a more detailed analysis of 2MPZ photo-$z$ properties). As we will see, due to the low redshift of this sample, the cross-correlation with the $y$ map is dominated by the 1-halo term for 2MPZ, and little is gained by sub-dividing it into narrower redshift bins. Therefore we use 2MPZ as a single tomographic sample.

    A deeper sample is obtained by dropping the 2MASS data and cross-matching WISE and SuperCOSMOS only. After removing the sources already contained in 2MPZ, the resulting catalogue, \wisc, is $\sim3$ times deeper, contains $\sim20$ million sources and reaches up to redshift $z\sim0.4$, with a median redshift of $\sim0.2$. The photometric redshifts are less accurate, given the poorer photometric coverage $(B,\,R,\,W1,\,W2)$, with a mean error $\sigma_z/(1+z)\simeq0.035$. We divide the \wisc~ sample into 5 redshift bins, corresponding to photo-$z$ intervals of equal width $\delta z_{\rm photo}=0.05$ in the range $0.1<z_{\rm photo}<0.35$. Details regarding each of these redshift bins are given in Table \ref{tab:z_bins}, and the corresponding redshift distributions are shown in Fig.\!~\ref{fig:dndz}. We estimate fiducial redshift distributions for each tomographic sample as described in \cite{2018MNRAS.481.1133P}, and we discuss the marginalisation over uncertainties in these distributions in Section \ref{sssec:methods.syst.photoz}.

    Both 2MPZ and WISC suffer from contamination from Galactic and observational systematics in different levels. The most relevant Galactic systematic is star contamination, particularly for \wisc~ \citep{2018arXiv181208182X}. Besides avoiding regions of high dust and star contamination using the sky mask described in \cite{2018MNRAS.481.1133P} (see bottom panel of Fig.\!~\ref{fig:msk}), we correct for the effects of stellar contamination by correcting for a smooth non-linear relation between galaxy and star density (also described in \citejap{2018MNRAS.481.1133P}). After doing so, three potential sources of systematic uncertainty remain: residual stellar contamination, modulation of the galaxy density due to Galactic dust reddening and modulation due to zero-point fluctuations in the photographic plates used by SuperCOSMOS. We address the first two (dust and stars) by deprojecting them at the map level as described in Section \ref{sssec:methods.syst.deproj}. We address the contamination from fluctuations in the SuperCOSMOS plates by modelling it at the power spectrum level, which we describe in Section \ref{sssec:methods.syst.plates}.

\section{Methods}\label{sec:methods}
  \subsection{Estimating power spectra}\label{ssec:methods.cls}
    We measure all auto- and cross-power spectra between the different redshift bins and the $y$ maps using the pseudo-$C_\ell$ estimator \citep[e.g.][]{2002ApJ...567....2H} as implemented in the {\tt NaMaster} code\footnote{\url{https://github.com/LSSTDESC/NaMaster}.} \citep{2019MNRAS.484.4127A}. Details about the method can be found in these references, but we provide a brief description here for completeness. For an incomplete sky coverage, a given field observed on the sphere, $\tilde{u}(\nv)$, can be modelled as a product of the true underlying field $u$, and a sky mask $w$
    \begin{equation}
      \tilde{u}^{\rm obs}(\nv) = w(\nv)\,u(\nv).
    \end{equation}
    In the simplest scenario, the mask $w$ is simply a binary map ($w=0$ or 1) selecting the pixels in the sky that have been observed. More generally, $w$ can be designed to optimally up- or downweight different regions in an inverse-variance manner. Through the convolution theorem, the spherical harmonic transform of the observed field is a product of the harmonic transforms of the true field and the mask. Provided the mask and true field are uncorrelated, this then translates into a similar result for the ensemble average of the observed power spectra $\tilde{C}^{uv}_\ell$:
    \begin{equation}
      \tilde{C}^{uv}_\ell = \sum_{\ell'}\,M^{uv}_{\ell \ell'}\, C^{uv}_{\ell'},
    \end{equation}
    where $C^{uv}_\ell$ is the true underlying power spectrum. $M^{uv}_{\ell \ell'}$ is the so-called mode-coupling matrix, which depends solely on the masks of both fields, and which can be computed analytically. Roughly speaking, the pseudo-$C_\ell$ approach is then based on estimating $M^{uv}$ and inverting it to yield an unbiased estimate of the power spectrum.

    For the galaxy auto-correlation, the pseudo-$C_\ell$ method requires an additional step of subtracting the shot noise bias. We do so analytically following the approach described in Section 2.4.2 of \cite{2019MNRAS.484.4127A} with a local noise variance given by $\sigma_n^2=1/\bar{n}_\Omega$, where $\bar{n}_\Omega$ is the mean surface number density in units of inverse steradians.

    All maps were generated and operated on using the {\tt HEALPix} pixelisation scheme \citep{2005ApJ...622..759G} with resolution parameter $N_{\rm side}=512$, corresponding to a pixel size $\theta_{\rm pix}\sim7'$.

  \subsection{Covariance matrices}\label{ssec:methods.cov}
    We combine two different methods to estimate the power spectrum covariance matrix.

    We make a first estimate of the covariance using the jackknife resampling method. We divide the common footprint covered by the masks of both the galaxy overdensity and Compton-$y$ maps into $N_{\rm JK}$ regions of roughly equal area. We mask each region in turn and compute the power spectrum  using the remaining available footprint. The covariance matrix is then estimated as:
    \begin{equation}\label{eq:cov_jk}
      {\rm Cov}\left(C^{uv}_\ell,C^{wz}_{\ell'}\right)=\frac{N_{\rm JK}-1}{N_{\rm JK}}\sum_{n=1}^{N_{\rm JK}}\Delta C^{uv,(n)}_\ell\,\Delta C^{wz,(n)}_{\ell'},
    \end{equation}
    where $\Delta C^{uv,(n)}_\ell$ is the difference between the power spectrum estimated when removing the $n$-th jackknife region and the power spectrum averaged over all jackknife regions. We use $N_{\rm JK}=461$ jackknife regions defined as {\tt HEALPix} pixels with resolution $N_{\rm side}=8$.

    Although the jackknife method is able to provide an estimate of the size of the power spectrum uncertainties in a model independent way, it also has some drawbacks. There are only so many jackknife regions that can be selected with a reasonable size, and therefore the estimated covariance is noisy at some level. Furthermore, since the footprint associated with the removal of each jackknife region is different from the overall footprint, the method is also not able to recover the mode-coupling associated with the map geometry by construction. In order to verify and improve our estimate of the covariance matrix, we make use of a second analytical estimator.

    We compute the analytical covariance matrix following the methods outlined in \cite{2017MNRAS.470.2100K}. The covariance receives two main additive contributions, from the so-called {\sl disconnected} and {\sl connected} trispectra. The disconnected part is essentially the covariance matrix estimated under the assumption that all fields are Gaussian. In the absence of sky masks, it is given by
    \begin{equation}
      {\rm Cov}^{\rm G}\left(C^{uv}_\ell,C^{wz}_{\ell'}\right)=\delta_{\ell\ell'}\frac{C^{uw}_\ell C^{vz}_\ell+C^{uz}_\ell C^{vw}_\ell}{2\ell+1}.
    \end{equation}
    A sky mask introduces non-zero coupling between different $\ell$ modes. To account for these, we use the  method introduced in \cite{2004MNRAS.349..603E} and implemented in {\tt NaMaster}, which has been shown to be an excellent approximation for large-scale structure data \citep{2019arXiv190611765G}.

    We compute the connected (i.e. non-Gaussian) contribution to the covariance matrix using the halo model as the 1-halo trispectrum \citep{2002MNRAS.336.1256K}, given by:
    \begin{align}\nonumber
      {\rm Cov}^{\rm NG}\left(C^{uv}_\ell,C^{wz}_{\ell'}\right)=\int &d\chi\,\frac{W_u(\chi)W_v(\chi)W_w(\chi)W_z(\chi)}{4\pi f_{\rm sky}\,\chi^6}\times\\\label{eq:cov_ng}
      &T^{1h}_{uvwz}\left(k=\frac{\ell+1/2}{\chi}\right),
    \end{align}
    where
    \begin{equation}\nonumber
      T^{1h}_{uvwz}(k)\equiv\int dM\frac{dn}{dM}\langle U(k|M) V(k|M) W(k|M) Z(k|M)\rangle.
    \end{equation}
    Here we have used the notation introduced in Section \ref{ssec:theory.cls} for the radial kernels ($W_u(\chi)$) and Fourier-space halo profiles ($U(k|M)$) of the different projected fields. The total covariance matrix is simply given by ${\rm Cov}={\rm Cov}^{\rm G}+{\rm Cov}^{\rm NG}$. Note that estimating the connected term requires the use of the best-fit halo model parameters which we do not know a priori. In order to circumvent this issue we proceed as in \cite{2018MNRAS.473.4318A} and estimate the covariance matrix in a two-step process, where we first obtain best-fit parameters by minimising a $\chi^2$ that uses only the Gaussian covariance with power spectra computed directly from the data, and we then use those parameters to calculate the non-Gaussian contribution (as well as to recalculate the Gaussian part using the best-fit prediction for the power spectra).
    \begin{figure}
      \centering
      \includegraphics[width=0.5\textwidth]{cov_diag_wisc2.pdf}
      \caption{Diagonals of the covariance matrix for the $\delta_g\times y$ cross-correlation in the second \wisc~redshift bin. Black and red lines show the analytic and jackknife covariances respectively. The solid and dashed lines show the zeroth-order ($i=j$) and first-order ($i=j+1$) diagonals respectively. We find compatible results from both methods.}
      \label{fig:covdiag}
    \end{figure}

    Fig.\!~\ref{fig:covdiag} shows the diagonal of the covariance matrix for one of the tSZ-galaxy power spectra estimated using these two methods. We find that both estimators are in good agreement with each other. We construct our final fiducial covariance matrix as a hybrid of both estimators: in order to ensure that we recover realistic error bar sizes, we use the variance estimated from the jackknives. We then combine this with the correlation matrix estimated with our analytical method. This ensures that our estimator accounts for the coupling between different modes caused by survey geometry and non-Gaussianities while avoiding the the statistical noise in the jackknife estimator. The final covariance is therefore:
    \begin{equation}
      {\rm Cov}_{ij} = {\rm Cov}^{\rm ana}_{ij} \sqrt{\frac{{\rm Cov}^{\rm JK}_{ii}\,{\rm Cov}^{\rm JK}_{jj}}{{\rm Cov}^{\rm ana}_{ii}\,{\rm Cov}^{\rm ana}_{jj}}},
    \end{equation}
    where ${\rm Cov}^{\rm JK}$ and ${\rm Cov}^{\rm ana}$ are the jackknife and analytical covariance matrices respectively.

  \subsection{Systematics treatment}\label{ssec:methods.syst}
    \subsubsection{Map-level deprojection}\label{sssec:methods.syst.deproj}
      For small levels of contamination, the impact of a given systematic on an observed sky map can be modelled at the linear level:
      \begin{equation}
        {\bf m}_{\rm obs}={\bf m}_{\rm true} + \epsilon\,{\bf t}.
      \end{equation}
      Here ${\bf m}_{\rm obs}$ and ${\bf m}_{\rm true}$ are vectors corresponding to the observed sky map and the true underlying quantity we wish to map respectively, ${\bf t}$ is a template map describing the contaminant (e.g. a map of the Galactic dust fluctuations), and $\epsilon$ is an unknown amplitude. In order to fully account for the effects of this contaminant one would build a likelihood for ${\bf m}_{\rm obs}$ using the equation above as a model (together with a model for ${\rm m}_{\rm true}$) and marginalise over $\epsilon$. As shown in \cite{2017MNRAS.465.1847E} and \cite{2019MNRAS.484.4127A}, within the pseudo-$C_\ell$ framework, this can be done exactly by projecting ${\bf m}_{\rm obs}$ onto the subspace perpendicular to ${\bf t}$ or, in other words, by `deprojecting' ${\bf t}$. The loss of modes due to deprojection then needs to be taken into account when estimating the power spectrum, which can be done analytically.

      For our analysis, we deproject two systematic templates from the galaxy and $y$ maps. We create a reddening template using the dust map of \cite{1998ApJ...500..525S}, and remove its associated contamination from the $y$ maps and from all the galaxy overdensity maps. We also generate a star density template from the WISE data, and remove its associated fluctuations from all the galaxy overdensity maps. The effects of this deprojection are illustrated in Fig.\!~\ref{fig:clsyst}.

      \begin{figure}
        \centering
        \includegraphics[width=0.48\textwidth]{cl_syst_summary.pdf}
        \caption{Summary of the different sources of systematic contamination affecting the galaxy auto-correlations for the particular case of the third \wisc~bin. The red and blue points show the measurements before and after deprojecting a dust and a star template, while the grey dashed line shows the best-fit contamination from SuperCOSMOS plate fluctuations assuming no intrinsic clustering. The solid black line shows the best-fit theory model. The light grey bands indicate the data points removed due to scale cuts.}
        \label{fig:clsyst}
      \end{figure}

  \begin{figure*}
    \centering
    \includegraphics[width=0.8\textwidth]{fits.pdf}
    \caption{Measured galaxy auto-spectra (left column) and $\delta_g$-$y$ cross-spectra (right column) for the 6 galaxy redshift bins shown in Fig.\!~\ref{fig:dndz} in ascending order. Each panel shows the measurements (red points with error bars) and best-fit predictions (solid black lines) decomposed into their 1-halo and 2-halo contributions (green and blue lines). The right column additionally shows the estimated contamination from extragalactic dust (yellow squares with error bars), which is found to be negligible. The grey bands indicate the scales removed from the analysis. The bottom part of each panel shows the difference between data and theory normalised by the 1$\sigma$ uncertainties.}
    \label{fig:cls}
  \end{figure*}

  \begin{figure*}
    \centering
    \includegraphics[width=0.27\textwidth]{cov_2mpz.pdf}
    \includegraphics[width=0.27\textwidth]{cov_wisc1.pdf}
    \includegraphics[width=0.27\textwidth]{cov_wisc2.pdf}
    \includegraphics[width=0.27\textwidth]{cov_wisc3.pdf}
    \includegraphics[width=0.27\textwidth]{cov_wisc4.pdf}
    \includegraphics[width=0.27\textwidth]{cov_wisc5.pdf}
    \caption{Correlation matrices for the 6 redshift bins used in the analysis. Each covariance matrix consists of 4 sub-matrices, corresponding to the covariances of $C^{gg}_\ell$ and $C^{gy}_\ell$ (block diagonals), as well as their cross-covariance.}
    \label{fig:covs}
  \end{figure*}

    \subsubsection{$C_\ell$-level deprojection}\label{sssec:methods.syst.plates}
      We model the systematic fluctuations in the number density of sources in the \wisc~ sample caused by variations in the zero-point of the SuperCOSMOS photographic plate exposures as Gaussian random variations within the footprint of each exposure with a variance $\sigma^2_{\rm plate}$:
      \begin{equation}
        \delta_{\rm plate}(\nv) = \sum_p \delta_p\,S_{\rm plate}\,W(\nv-\nv_p),
      \end{equation}
      where the sum runs over all exposures, $\delta_p$ is the fluctuation in exposure $p$ (with $\langle\delta_p^2\rangle=\sigma^2_{\rm plate}$), $S_{\rm plate}$ is the footprint area of each exposure and $W(\nv)$ is the plate window function. Assuming a roughly homogeneous coverage of the sky, the power spectrum of these fluctuations is given by
      \begin{equation}
        C_\ell^{\rm plate}=S_{\rm plate}\sigma_{\rm plate}^2\left|W_\ell\right|^2,
      \end{equation}
      where $W_\ell$ is the harmonic transform of the plate window function. SuperCOSMOS used photographic plates covering an area of $5^\circ\times5^\circ$. The corresponding window function can be roughly approximated as $|W_\ell|^2=\exp[-(\ell\,\theta_{\rm plate})^2/12]$, where $\theta_{\rm plate}=5\pi/180$ for 5-degree plates.

      The contamination from plate fluctuations can therefore be accounted for as an additive contribution to the model describing the galaxy auto-spectrum, proportional to a template $T_\ell\equiv|W_\ell|^2$ with a free amplitude $A\equiv S_{\rm plate}\sigma_{\rm plate}^2$ that is marginalised over. Since $A$ is a linear parameter, this can be done analytically in a pre-processing step by modifying the inverse covariance matrix of the galaxy auto-spectra as follows \citep{1992ApJ...398..169R}:
      \begin{equation}
        {\sf Cov}^{-1}\hspace{6pt}\rightarrow\hspace{6pt} {\sf Cov}^{-1}-\frac{{\sf Cov}^{-1}{\bf T}\cdot{\bf T}^T{\sf Cov}^{-1}}{{\bf T}^T{\sf Cov}^{-1}{\bf T}},
      \end{equation}
      where ${\bf T}$ is a vector containing the template $T_\ell$ for all the scales used in the analysis. Fig.\!~\ref{fig:clsyst} shows the shape of the plate template $T_\ell$ normalised by the best-fit value of the parameter $A$.

    \subsubsection{Scale cuts}\label{sssec:methods.syst.scales}
      After deprojecting dust and stars at the map level, and the imprint of the SuperCOSMOS plates at the power spectrum level, we still observe an unacceptably large amount of power on scales $\ell<10$ in all galaxy auto-correlations involving \wisc. These may be due to residual star contamination that is not simply removed with a linear template \citep{2018arXiv181208182X}, or inaccuracies in our treatment of the SuperCOSMOS fluctuations. To avoid biasing our results we therefore remove the lowest bandpower from all galaxy auto-correlations involving \wisc.

      On small scales, the simple halo model prescription used to describe the non-linear power spectra and covariance matrices may not be sufficiently accurate. Therefore we impose a cut on angular multipoles $\ell$ larger than the typical physical scale of a halo, $\ell_{\rm max}=k_{\rm max}\bar{\chi}-1/2$, where $k_{\rm max}=1\,{\rm Mpc}^{-1}$, and $\bar{\chi}$ is the mean comoving radial distance in each redshift bin. The corresponding values of $\ell_{\rm max}$ in each bin are given in Table \ref{tab:z_bins}.

    \subsubsection{Redshift distribution uncertainties}\label{sssec:methods.syst.photoz}
      For each redshift bin we estimate fiducial redshift distributions using the method described in \cite{2018MNRAS.481.1133P}. In short, a true-redshift distribution is estimated from the distribution of photometric redshifts for a given bin using a model for the conditional photo-$z$ distribution:
      \begin{equation}\label{eq:nz_calc}
        p(z)=\int dz_{\rm photo}\,p(z|z_{\rm photo})\,p(z_{\rm photo}),
      \end{equation}
      where the model for $p(z|z_{\rm photo})$ was calibrated using overlapping spectroscopic data. Although the spectroscopic coverage of 2MPZ and \wisc~ is high compared to other photometric redshift surveys, the resulting redshift distributions are not infinitely precise, and therefore we need to account for any uncertainty in them that could affect our measurement.

      In particular, our interpretation of the $y\times \delta_g$ cross-correlation is especially sensitive to the width of the redshift distributions. This is because, while the amplitude to the galaxy auto-correlation is strongly affected by the width of the distribution (wider $p(z)$ reduce the clustering amplitude), the cross-correlation with $y$ is almost insensitive to it. We therefore introduce an additional parameter $w_z$ that stretches the support of the redshift distribution while preserving unit total probability. Concretely, given a fiducial distribution $p_{\rm fid}(z)$ with mean redshift $\bar{z}$, $w_z$ is implemented as
      \begin{equation}
        p(z)\propto p_{\rm fid}\left(\bar{z}+\frac{z-\bar{z}}{w_z}\right),
      \end{equation}
      where the proportionality constant is fixed by making sure that $p(z)$ integrates to unity. We make $w_z$ a free parameter that we marginalise over with a top-hat prior $0.8<w_z<1.2$. This prior is significantly larger than the actual expected uncertainty in the width of the redshift distributions. To be precise, we estimate that the parameters (e.g. Gaussian mean and variance) of the conditional photo-$z$ distribution $p(z|z_{\rm photo})$ used to calculate the true redshift distributions (Eq.\!~\ref{eq:nz_calc}), are known to the level of $1\%$. When propagated into an uncertainty on the width $w_z$ of $p(z)$, this corresponds to an uncertainty of the same order ($\sim0.9\%$). Thus, the margins of the assumed top-hat priors are wide enough to encompass any lack of precision in the number density distribution.

  \subsection{Likelihood}\label{ssec:methods.like}
    \begin{table}
      \begin{center}
        \begin{tabular}{lll|lll}
          $b$ & $\ell^b_{\rm ini}$ & $\ell^b_{\rm end}$ & $b$ & $\ell^b_{\rm ini}$ & $\ell^b_{\rm end}$ \\[1ex]
          \hline
           1 &   2 &  12 &  13 &  180 &  216\\
           2 &  12 &  22 &  14 &  216 &  258\\
           3 &  22 &  32 &  15 &  258 &  308\\
           4 &  32 &  42 &  16 &  308 &  369\\
           5 &  42 &  52 &  17 &  369 &  441\\
           6 &  52 &  62 &  18 &  441 &  527\\
           7 &  62 &  74 &  19 &  527 &  629\\
           8 &  74 &  88 &  20 &  629 &  752\\
           9 &  88 & 106 &  21 &  752 &  899\\
          10 & 106 & 126 &  22 &  899 & 1074\\
          11 & 126 & 151 &  23 & 1074 & 1284\\
          12 & 151 & 180 &  24 & 1284 & 1535\\
          \hline
        \end{tabular}
        \caption{Power spectrum bandpowers used in this work. The $b$-th bandpower includes all integer multipoles $\ell^b_{\rm ini}<\ell<\ell^b_{\rm end}$. The bandpower edges listed here correspond roughly to linearly-spaced bands between $\ell=2$ and $\ell=52$, and logarithmic bands afterwards.}\label{tab:bpws}
      \end{center}
    \end{table} 
    In order to connect our measurements with the posterior distribution of the model parameters $\vec{\theta}$, we assume that the measured power spectra follow a Gaussian likelihood:
    \begin{equation}
      -2\ln p({\bf d}|\vec{\theta}) = \chi^2\equiv ({\bf d}-{\bf t}(\vec{\theta}))^T {\sf C}^{-1} ({\bf d}-{\bf t}(\vec{\theta})),
    \end{equation}
    where ${\bf d}$ is a vector of power spectrum measurements, ${\bf t}(\vec{\theta})$ is the theory prediction for ${\bf d}$ with parameters $\vec{\theta}$ and ${\sf Cov}$ is the covariance matrix described in the previous sections.

    We explore the likelihood of each redshift bin separately. For each bin, our data vector ${\bf d}$ includes two sets of power spectrum measurements, corresponding to the auto-correlation of the galaxy overdensity and to its cross-correlation with the Compton-$y$ map, ${\bf d}=(C^{gg}_\ell,C^{gy}_\ell)$. We compute all power spectra in the range of multipoles $2<\ell<1535$, binned into the bandpowers described in Table \ref{tab:bpws}. For a given redshift bin, we only include those bandpowers that satisfy the scale cuts described in Section \ref{sssec:methods.syst.scales}.

    For each redshift bin, our theory model has five free parameters: $\log_{10}M_{\rm min}/M_\odot$, $\log_{10}M_1'/M_\odot$, $1-b_{\rm H}$, $\rho_{yg}$, and a nuisance width parameter $w_z$. The first two parameters effectively fit the galaxy bias and small-scale amplitude in the galaxy auto-correlation, while $1-b_{\rm H}$ and $\rho_{yg}$ are then constrained by including the tSZ cross-correlation. We fix all cosmological parameters to the best-fit values in \cite{2018arXiv180706209P}: $(\Omega_c h^2,\Omega_bh^2,h,\sigma_8,n_s)=(0.119,0.0224,0.6766,0.8102,0.9665)$. We impose the following top-hat priors on the free parameters:
    \begin{align}
      &10\le\log_{10}M_{\rm min}/M_\odot\le16,\\
      &10\le\log_{10}M_1'/M_\odot\le16,\\
      &0\le(1-\bH)\le0.99,\\
      &-1\le\rho_{yg}\le1,\\
      &0.8\le w_z\le1.2.
    \end{align}
    We sample the resulting posterior distributions using the Markov chain Monte Carlo method (MCMC) as implemented in the {\tt emcee} software package \citep{2013PASP..125..306F}\footnote{\url{https://emcee.readthedocs.io/en/v2.2.1/}.}.

      \begin{figure*}
        \centering
        \includegraphics[width=0.55\textwidth]{fiducial_wisc3.pdf}
        \caption{68\% and 95\% contours for the model parameters in the third WI$\times$SC redshift bin.}
        \label{fig:triangle}
      \end{figure*}

      \begin{figure*}
        \centering
        \includegraphics[width=0.7\textwidth]{bhydro.pdf}
        \caption{Summary figure showing our constraints on the tSZ mass bias $1-\bH$. Our fiducial constrains are shown as black circles with error bars, and are centred at the mean redshift of each sample. The upward-pointing green triangles show the same constraints found using the NILC $y$ map, which are in good agreement with our fiducial results. The light-orange downward-pointing triangles show the constraints found fixing the photo-$z$ width parameter $w_z$. They are in good agreement with our fiducial measurements, with $\sim20\%$ smaller error bars. The burgundy squares show the results found using the 2010 Tinker mass function, which are systematically biased low. The red diamond shows our combined, redshift-independent constraint on $1-\bH$. For comparison, the grey and turquoise bands show the constraints on the mass bias found by combining cluster counts and CMB primary \citep{2016A&A...594A..24P} as well as the constraints using CMB lensing to calibrate cluster masses \citep{2019arXiv190407887Z}, respectively. The top panel shows the normalised redshift distributions for the six redshift bins, for reference.}
        \label{fig:bh}
      \end{figure*}

\section{Results}\label{sec:results}
  \subsection{Power spectra and covariances}\label{ssec:results.cls}
    We estimate the galaxy auto-power spectrum, the galaxy-tSZ cross-spectrum, and their covariance matrix for each of the redshift bins shown in Fig.\!~\ref{fig:dndz} using the methods described in Section \ref{sec:methods}. The resulting measured power spectra and errors are shown in red in Fig.\!~\ref{fig:cls}, together with their best-fit halo model prediction in black, decomposed into its 1-halo and 2-halo contributions (green and blue respectively). The bottom part of each panel shows the residuals with respect to the best-fit prediction normalised by the 1$\sigma$ errors. The grey bands cover the data points not used in the analysis due to scale cuts.

    Fig.\!~\ref{fig:covs} shows the correlation matrix of the combined data vector $(C^{gg}_\ell,C^{gy}_\ell)$ for each redshift bin (where the correlation matrix $r_{ij}$ is related to the covariance $C_{ij}$ as $r_{ij}=C_{ij}/\sqrt{C_{ii}C_{jj}}$). At low redshifts, 2MPZ shows strong correlations between different scales, mostly caused by the non-Gaussian contribution to the covariance matrix (Eq.\!~\ref{eq:cov_ng}). These become less relevant at higher redshifts, where non-linear effects are weaker, and where the radial projection pushes the non-linear scale into larger multipole values.

    Overall, we find a good agreement between theory and data over the scales used in this analysis. We discuss this agreement and the associated scientific results in the following sections.

  \subsection{Fiducial results}\label{ssec:results.fid}

    \subsubsection{Tomographic measurement of the mass bias}\label{ssec:results.fid.1mb}

      \begin{figure*}
        \centering
        \includegraphics[width=0.7\textwidth]{by.pdf}
        \caption{Summary figure showing our constraints on the bias-weighted thermal pressure $\langle bP_e\rangle$. Our measurements are shown as blue circles with error bars and a `violin' background. The circle and error bars show the peak value and 68\% confidence interval, while the violins show the full 1D posterior distribution. The grey lines show the predictions of the shock-heating model of \citet{2012ApJ...758...75B} for different values of the $r_{\rm max}$ threshold cluster radius (see legend). For comparison, the figure also shows the constraints on the same parameter found by \citet{2017MNRAS.467.2315V} (black) and \citet{2019arXiv190413347P} (red and green).}
        \label{fig:by}
      \end{figure*}

      \begin{table*}
        \begin{center}
          \begin{tabular}{l|cccccc}
            \hline
            Sample & $\bar{z}$ & $1-\bH\,\,({\rm best\,\,fit})$ & $1-\bH\,\,(68\%\,{\rm C.L.})$ & $\langle bP_e\rangle\,[{\rm eV}\,\,{\rm cm}^{-3^{\phantom{2}}}]$ & $\chi^2/{\rm d.o.f.}$ & ${\rm PTE}(\chi^2)$\\[1ex]
            \hline
            2MPZ    & 0.07     & 0.33                         & $0.21^{+0.31}_{-0.05}$      & $0.087^{+0.052^{\phantom{A}}}_{-0.031}$                          & 0.92                  & 0.57               \\
            \wisc-1 & 0.13     & 0.71                         & $0.62^{+0.14}_{-0.08}$      & $0.176^{+0.020^{\phantom{A}}}_{-0.025}$                          & 1.35                  & 0.09               \\
            \wisc-2 & 0.18     & 0.73                         & $0.62^{+0.10}_{-0.07}$      & $0.188^{+0.013^{\phantom{A}}}_{-0.024}$                          & 0.87                  & 0.69               \\
            \wisc-3 & 0.23     & 0.64                         & $0.64^{+0.07}_{-0.08}$      & $0.203^{+0.018^{\phantom{A}}}_{-0.023}$                          & 1.17                  & 0.22               \\
            \wisc-4 & 0.27     & 0.55                         & $0.58^{+0.07}_{-0.07}$      & $0.197^{+0.020^{\phantom{A}}}_{-0.016}$                          & 1.04                  & 0.40               \\
            \wisc-5 & 0.32     & 0.58                         & $0.61^{+0.09}_{-0.07}$      & $0.210^{+0.033^{\phantom{A}}}_{-0.010_{\phantom{A}}}$                          & 1.26                  & 0.12               \\
            \hline
          \end{tabular}
          \caption{Summary table presenting our main results. The first two columns list our 6 tomographic bins and their mean redshift. Columns 3 and 4 show the best-fit value of the mass bias $1-\bH$ and their 1D peak value and 68\% confidence interval respectively. Column 5 shows the peak value and 68\% confidence interval of the bias-averaged thermal pressure (Eq.\!~\ref{eq:by}) in each bin. Finally, columns 6 and 7 show the reduced $\chi^2$ and associated probability to exceed, indicating that we find a good fit in all cases.}\label{tab:results}
        \end{center}
      \end{table*}
      We use the measured power spectra to constrain the free parameters of the model described in Section \ref{sec:theory}, with the main aim of providing an alternative measurement of the mass bias $(1-\bH)$ as a function of redshift. Fig.\!~\ref{fig:triangle} shows an example of the posterior parameter contours for our 5 free parameters, $\{M_{\rm min},M_1,\bH,\rho_{gy},w_z\}$, in the \wisc-3 sample ($z\sim0.23$). As the figure shows, there are strong degeneracies between $M_{\rm min}$, $M_1$ and $w_z$. This is easy to understand, given that all of these parameters affect the overall amplitude of the galaxy auto-correlation, but we do not probe to scales where the 1-halo term is fully resolved.  The lack of such resolution means that we do not break the degeneracy between $M_{\rm min}$ and $M_1$, which regulate the abundance of centrals and satellites, and therefore the constraint on these parameters mostly comes from the 2-halo amplitude (i.e. the galaxy bias), and the 1-halo shot-noise level. On the other hand, the width of the redshift distribution also has a strong impact on the amplitude of the angular power spectrum at all scales due to projection effects. Since a measurement of the galaxy bias from the galaxy auto-correlation is effectively used to constrain $\bH$ from the galaxy-$y$ cross-correlation, the mass bias also shows some degeneracy with the HOD parameters and $w_z$, albeit at a more moderate level. More interestingly, the mass-bias parameter $\bH$ shows a visible degeneracy with $\rho_{gy}$. This is also expected: the effects of $\rho_{gy}$ and $\bH$ on the 1-halo term of the galaxy-$y$ power spectrum are completely degenerate, and thus a free $\rho_{gy}$ ensures that any information obtained on $\bH$ comes entirely from the 2-halo contribution.

      The corresponding constraints on $1-\bH$ for all redshift bins are shown in the bottom panel of Fig.\!~\ref{fig:bh} as black circles with error bars. The values shown in the figure and given explicitly in column 4 of Table \ref{tab:results} correspond to the peak of the 1-dimensional distribution of $1-\bH$ and to the equal-probability values encompassing a total probability of 0.68. The overall best-fit value of $1-\bH$ is provided in column 3 of the same Table. Columns 6 and 7 of the same table list the reduced $\chi^2$ values for each sample and their associated probability-to-exceed (PTE), respectively. In all cases we find that the model described in Section \ref{sec:theory} is able to describe the data with no evidence for a significant statistical tension. The top panel of Fig.\!~\ref{fig:bh} shows the normalised redshift distributions of the different bins used in this analysis, and can be used to visually assess the level of correlation between the different measurements.

      We see that, while we are able to measure $1-\bH$ to a reasonable accuracy ($\sim12\%$) in all of the \wisc~ redshift bins, the sensitivity for the 2MPZ sample is much poorer. This is not entirely unexpected: even though the cross-correlation between the Compton-$y$ map and the 2MPZ catalogue yields the highest signal-to-noise of all the samples used here, the low-redshift range covered by this sample implies that the signal is strongly dominated by the one-halo term. This can be seen in the top right panel of Fig.\!~\ref{fig:cls}. This degrades the constraining power of the 2MPZ cross-correlation significantly since, as we have described above, we can only obtain reliable constraints on $1-\bH$ from the two-halo contribution.

      Our results are in broad agreement with the estimate of a redshift-independent $1-\bH$ found by \cite{2019arXiv190407887Z} by calibrating cluster masses with CMB lensing ($1-\bH=0.71\pm0.1$), shown in Fig.\!~\ref{fig:bh} as a turquoise semi-transparent band. In turn, the grey band in the same figure shows the constraints on $1-\bH$ found by combining tSZ cluster counts and the $TT$ CMB power spectrum measured by \planck\ \cite{2016A&A...594A..24P} ($1-\bH=0.58\pm0.04$). This is the value of $1-\bH$ needed to explain the amplitude of density perturbations predicted by the CMB in comparison with the abundance of massive clusters. Our measurements are visually in agreement with both of these estimates, which themselves are not in significant tension with one another.

      We can however use our results to quantify whether approximating $1-\bH$ to be constant with redshift is supported by the data. To do so, we combine our six measurements under the assumption that they correspond to the same redshift-independent quantity. We do so by finding the quantity $\bar{b}_H$ that minimises the $\chi^2$:
      \begin{equation}
        \chi^2=\sum_{i,j=1}^6 (b_{H,i}-\bar{b}_H){\sf Cov}^{-1}_{b,ij}(b_{H,j}-\bar{b}_H),
      \end{equation}
      where $b_{H,i}$ is the mass bias measured in the $i$-th redshift bin, and ${\sf Cov}_b$ is the covariance matrix of these measurements. Since the galaxy samples used in this analysis have significant redshift overlap, the off-diagonal elements of ${\sf Cov}_b$ cannot be ignored. We estimate ${\sf Cov}_b$ through jackknife resampling: we use the power spectra measured in each jackknife region described in Section \ref{ssec:methods.cov} to estimate the best-fit value of $b_{H,i}$ for each of them, and then calculate the covariance through Eq.\!~\ref{eq:cov_jk}. Since $\bar{b}_H$ is a linear parameter, its best-fit and standard deviation can be found analytically as:
      \begin{equation}
        \bar{b}_H=\frac{\sum_{ij}{\sf Cov}_{b,ij}^{-1}b_i}{\sum_{ij}{\sf Cov}^{-1}_{b,ij}},
        \hspace{12pt}
        \sigma(\bar{b}_H)=\left(\sum_{ij}{\sf Cov}^{-1}_{b,ij}\right)^{-1/2}.
      \end{equation}
      At this point it is worth acknowledging that this estimate $\bar{b}_H$ is only strictly consistent if the posterior distribution of the $b_{H,i}$ is Gaussian. We find that, with the exception of the 2MPZ sample, which has a comparatively small statistical power, the marginalised distributions in all redshift bins are sufficiently well-behaved that this is a reasonable approximation (e.g. see 1-dimensional distribution for $\bH$ in Fig.\!~\ref{fig:triangle}). Our combined constraint on $\bar{b}_H$ following this procedure is:
      \begin{equation}
        1-\bar{b}_H=0.59\pm0.03.
      \end{equation}
      More interestingly, the $\chi^2$ value associated with this measurement is $\chi^2=2.1$, which has an associated PTE$\simeq0.8$. We therefore find that the assumption of a constant mass bias with redshift is compatible with our measurements. This agrees with the results of \cite{2019A&A...626A..27S}, found using tSZ-selected clusters. The preferred value of $1-\bar{b}_H$ found also agrees with the results of \cite{2018MNRAS.480.3928M} in cross-correlation with galaxies at very low redshift, and those of \cite{2019arXiv190707870M} using weak-lensing cross-correlations at higher $z$.

    \subsubsection{Tomographic measurement of thermal gas pressure}\label{ssec:results.fid.bpe}
      So far we have presented our constraints in terms of a the mass-bias parameter $1-\bH$, since this is the main source of systematic uncertainty in the cosmological analysis of cluster number counts carried out by Planck. However, the physical interpretation of this parameter (the fraction of missing mass estimated from X-ray measurements under the assumption of hydrostatic equilibrium) is not directly related to the physical process that allows us to constrain it through the cross-correlation of $y$ and $\delta_g$: the fact that galaxy density and pressure trace the same underlying dark-matter fluctuations. In this sense, a more direct observable is the bias-weighted pressure $\langle bP_e\rangle$. This quantity can be interpreted both as the relation between large-scale matter and pressure fluctuations and as the halo-bias-weighted thermal energy density of all haloes at a given redshift \citep{2017JCAP...11..040B}. This quantity has been measured at low  redshifts by \cite{2017MNRAS.467.2315V} making use of galaxy groups, and at higher redshifts by the Dark Energy Science Collaboration \citep{2019arXiv190413347P}. The redshift range $0.1\lesssim z\lesssim0.4$, containing a large fraction of the tSZ sources detected by \planck\ \citep{2016A&A...594A..27P}, is fairly unconstrained tomographically through this type of measurements.

      We derive constraints on $\langle bP_e\rangle$ from our data by reprocessing our Monte-Carlo chains, computing $\langle bP_e\rangle$ at each sample to find its marginalised posterior distribution. The results are shown in Fig.\!~\ref{fig:by}, together with the measurements of \cite{2017MNRAS.467.2315V} and \cite{2019arXiv190413347P}. Our results are in good qualitative agreement with the trend of these previous measurements, as well as with the predictions of the shock heating models of \cite{2012ApJ...758...75B}. In these models, the thermal energy entering Eq.\!~\ref{eq:by} is estimated by integrating the pressure profile of \cite{2012ApJ...758...75B} up to a radius $r_{\rm max}=N\,r_{200c}$. As a visual aid to evaluate the agreement of our results with these models, the predictions for $N=2,\,3,\,5$ and $\infty$ are shown as solid, dashed, dot-dashed and dotted grey lines respectively in Fig.\!~\ref{fig:by}.

  \subsection{Systematics analysis}\label{ssec:results.syst}
    \subsubsection{tSZ systematics}\label{sssec:results.syst.y}
      No component separation method is perfect, and the MILCA Compton-$y$ map used in our fiducial analysis is known to suffer from small levels of contamination from various other astrophysical components. The most relevant for this analysis is the presence of Galactic and extragalactic dust. As described in Section \ref{sssec:methods.syst.deproj}, we remove contamination from Galactic dust at the map level in both $y$ and $\delta_g$. The extragalactic component, the so-called Cosmic Infrared Background (CIB), is however a more relevant concern, given that it traces the large-scale structure, and is therefore statistically correlated with both of our observables ($\delta_g$ and $y$). Since the CIB is most relevant near the peak of star formation ($z\sim2$), we expect this contamination to be small, but it must however be quantified carefully.

      To do so, we follow the same method used in \cite{2017MNRAS.467.2315V}. We model the CIB contamination in the $y$ map as:
      \begin{equation}
        y_{\rm obs}(\nv)=y_{\rm true}(\nv)+\epsilon_{\rm CIB}\,c(\nv),
      \end{equation}
      where $y_{\rm obs}$ and $y_{\rm true}$ are the observed and true Compton-$y$ maps, $\epsilon_{\rm CIB}$ is a free parameter, and $c(\nv)$ is a template for the CIB emission. For our analysis we used the 545 GHz map released by \planck\ as a proxy for CIB emission. The different cross-correlation between $y_{\rm obs}$ and both $\delta_g$ and $c$ are then given by:
      \begin{align}\label{eq:cl_yc}
        &C^{yc,{\rm obs}}_\ell= C^{yc}_\ell+\epsilon_{\rm CIB}\,C^{cc}_\ell,\\
        &C^{yg,{\rm obs}}_\ell= C^{yg}_\ell+\epsilon_{\rm CIB}\,C^{gc}_\ell,
      \end{align}
      where $C^{cc}_\ell$, $C^{yc}_\ell$,  and  $C^{gc}_\ell$ are the auto-correlation of the CIB, and its intrinsic cross-correlations with $y$ and $\delta_g$ respectively. Since $C^{gc}_\ell$ can be estimated directly by cross-correlating our galaxy overdensity maps with the 545 GHz map, the only remaining step to quantify the contamination to the $y$-$\delta_g$ correlation is to estimate $\epsilon_{\rm CIB}$. To do so, we measure the cross-correlation between the MILCA $y$ map and the 545 GHz map and fit a model of the form of Eq.\!~\ref{eq:cl_yc}, with a single free parameter $\epsilon_{\rm CIB}$, and $C^{yc}_\ell$ and $C^{cc}_\ell$ given by the best-fit models for the CIB auto- and cross-correlation provided by \cite{2014A&A...571A..30P,2016A&A...594A..23P}. As reported in \cite{2018PhRvD..97f3514A}, this procedure yields an estimate of the CIB contamination
      \begin{equation}
        \epsilon_{\rm CIB}=(2.3\pm6.6)\times10^{-7}\,({\rm MJy}/{\rm sr})^{-1}.
      \end{equation}
      For this exercise, in order to reduce the noise variance from the Galactic component of the 545 GHz map, the cross-correlations $C^{yc,{\rm obs}}_\ell$ and $C^{gc}_\ell$ were estimated using Planck's 20\% Galactic mask. Additionally, all uncertainties were estimated using the jackknife method described in Section \ref{ssec:methods.cov}.

      Using this measurement of $\epsilon_{\rm CIB}$ and the estimate of $C^{gc}_\ell$ from the cross-correlation with the 545 GHz map, Fig.\!~\ref{fig:cls} shows, in the right panels, the estimated level of contamination from the CIB in our $y$-$\delta_g$ cross-correlation. In all cases the contamination is small, at the level of $\sim1\%$ of the signal, and therefore can be neglected in our analysis.

      As an additional test for systematics, we have also repeated our full analysis replacing the MILCA $y$ map with the NILC map released by Planck. Different component-separation methods are sensitive to different types of contamination, and this exercise is therefore both a necessary consistency check and a way to reinforce our conclusion that the level of CIB contamination is negligible. The resulting measurements of $1-\bH$ are shown in Fig.\!~\ref{fig:bh} as red triangles with error bars. The results are in very good agreement with our fiducial analysis.

      \subsubsection{Photometric redshift uncertainties}\label{sssec:results.syst.pz}
      We have quantified the impact on our results of the uncertainties on the redshift distributions of the different samples used here by introducing the free width parameter $w_z$ with a 20\% top-hat prior. In order to study the impact of these uncertainties on our results, we have recomputed the constraints on $1-\bH$ fixing $w_z$ to its fiducial value of 1. The results are shown in Fig. \ref{fig:bh} as yellow down-pointing triangles. We observe that the only effect of allowing $w_z$ to vary is to increase the final uncertainties on $1-\bH$ by about $20\%$. The final best-fit value of $1-\bH$ does not change significantly, and the posterior distribution of $w_z$ is always peaked around the fiducial value of $1$ (see e.g. bottom right panel of Fig. \ref{fig:triangle}).

      \subsubsection{Mass function parameterisation}\label{sssec:results.syst.mf}
      \begin{figure}
        \centering
        \includegraphics[width=0.49\textwidth]{mf_ratio.pdf}
        \caption{Ratio between the mass function parametrizations of \citet{2008ApJ...688..709T} and \citet{2010ApJ...724..878T} in the range of redshifts relevant to this analysis. A systematic offset of about $10$-$20\%$ between them can be observed, which causes the lower value of $1-b_{\rm H}$ found using the latter mass function (see Fig.\!~\ref{fig:bh}). }
        \label{fig:mf_ratio}
      \end{figure}
      Another possible source of systematics in our measurement is the uncertainty on the mass function used in our halo model. Our fiducial mass function is the parameterisation of \cite{2008ApJ...688..709T}, which we use in order to be able to make a direct comparison with the results of \cite{2016A&A...594A..24P}. To explore the dependence on the choice of the mass function, we redo our analysis using the updated parameterisation of \cite{2010ApJ...724..878T}. Fig.\!~\ref{fig:bh} shows the final constraints on $1-\bH$ in this case as burgundy squares, which are consistently lower by $\sim 1\sigma$. We find that this is caused by a redshift-dependent systematic offset between both mass function parameterisations which reaches the level of $10$-$20\%$ in the range $0<z<0.4$. This is shown explicitly in Fig. \ref{fig:mf_ratio}. Since the aim of this paper is not to characterise the theoretical uncertainties on the halo mass function, we leave the study of this issue for future work, and limit ourselves to using the parameterisation of \cite{2008ApJ...688..709T} in order to match previous analyses \citep[e.g.][]{2016A&A...594A..24P,2018MNRAS.477.4957B,2018MNRAS.473.4318A,2019arXiv190407887Z,2019arXiv190707870M}.

\section{Conclusion}\label{sec:conclusion}
  Cross-correlating maps of the tSZ Compton-$y$ parameter with tomographic measurements of the projected galaxy distribution allows us to study the redshift evolution of the thermal gas pressure, since we expect both pressure and galaxies to trace the same underlying matter inhomogeneities. We have measured the $\delta_g$-$y$ cross-correlation to very high significance using the public $y$ maps made available by the Planck collaboration \citep{2016A&A...594A..22P} and the 2MPZ and \wisc~ galaxy catalogues \citep{2014ApJS..210....9B,2016ApJS..225....5B} in six photometric redshift bins covering the redshift range $z\lesssim0.4$.

  Combining this measurement with a measurement of the galaxy auto-correlation allows us to break the degeneracy between the two parameters that relate $\delta_g$ and $y$ to the matter fluctuations: the galaxy bias, which we model effectively using a 2-parameter HOD prescription, and the mass bias parameter $1-\bH$, thus enabling us to make a redshift-dependent measurement of $1-\bH$. The results, shown in Table \ref{tab:results} and Fig.\!~\ref{fig:bh}, agree well with the measurements of $1-\bH$ made by \planck\ through the combination of cluster number counts and CMB primary anisotropies \citep{2016A&A...594A..24P}, as well as with the calibration of tSZ cluster masses with CMB lensing measurements \citep{2019arXiv190407887Z}, and with similar measurements of $1-\bH$ made by \cite{2018MNRAS.480.3928M} through the same type of cross-correlation but at much lower redshifts. More importantly, our tomographic measurement allows us to study the possible redshift dependence of the mass bias, an important ingredient in cosmological analysis of cluster abundances. Given our uncertainties, we do not find any statistical evidence for a redshift dependence of $1-\bH$, in agreement with previous analyses \citep{2019A&A...626A..27S}.

  Perhaps more interestingly, our measurements can be interpreted as constraints on the bias-weighted mean gas pressure $\langle bP_e\rangle$, the equivalent of the large-scale galaxy bias for the $y$ parameter. This quantity is directly related to the energetics of gas in haloes, and can be used to constrain different heating models. Our results, shown in Table \ref{tab:results} and Fig.\!~\ref{fig:by}, agree well with previous measurements of the same quantity \citep{2017MNRAS.467.2315V,2019arXiv190413347P}, as well as with shock-heating models \citep{2012ApJ...758...75B}. These results are also the most precise measurement of the large-scale correlation between $\delta_g$ and $y$ to date.

  The main sources of systematic uncertainty in our analysis are contamination of the galaxy clustering auto-correlation by stars, Galactic dust and other observing conditions, the contamination from CIB emission in the $y$ map, and uncertainties in the galaxy redshift distribution due to the use of photometric redshifts. We address the galaxy clustering systematics by deprojecting templates for dust and star contamination at the map level, by deprojecting the expected contamination from zero-point fluctuations in the SuperCOSMOS photographic plates at the power spectrum level, and by masking out the largest scales ($\ell<10$) in the galaxy clustering auto-correlation. We use the 545 GHz \planck\ map as a tracer of CIB to quantify the level of contamination in the $y$-$\delta_g$ cross-correlation, and find it to be negligible (as could be expected given the relatively low redshift of our sample compared with the peak of star formation, $z\sim2$). Finally, we determine that the most relevant form of systematic associated with uncertainties in the redshift distributions is that associated with the width of $p(z)$. To address this, we add a new parameter to our model, $w_z$, parameterising the distribution widths. We marginalize over $w_z$ with a 20\% prior, which we have determined to be significantly larger than the expected uncertainty on the true width. This has the effect of degrading our constraints on $1-\bH$ and $\langle bP_e\rangle$ by $\sim20\%$ without modifying the best-fit value of either quantity significantly.

  We must also note that our parameter constraints have been derived for a fixed cosmological model, corresponding to the best-fit parameters found by \planck\ \citep{2018arXiv180706209P}. The most significant consequence of this is the fact that our constraints are strongly degenerate with the amplitude of matter fluctuations, parameterised by $\sigma_8$. Therefore, the agreement between our constraints on $1-\bH$ and those found by \planck\ \citep{2016A&A...594A..24P} can therefore be thought of as a proof of the consistency between the properties of the galaxy distribution in 2MPZ and \wisc~ and the CMB anisotropies. However, our results regarding the redshift evolution of $1-\bH$ (or lack thereof), and the agreement of $\langle bP_e\rangle$ with existing heating models, are only possible thanks to the tomographic cross-correlation with the galaxy density fluctuations. Robust joint constraints on cosmological and astrophysical parameters could be achieved by a combined analysis of galaxy clustering, Compton-$y$ maps and gravitational lensing data (either from cosmic shear or CMB lensing observations).

  The scientific yield of these types of observations will increase significantly with data from current and near-future experiments, such the Advanced Atacama Cosmology Telescope \citep{2016SPIE.9910E..14D} or the Simons Observatory \citep{2019JCAP...02..056A} on the CMB side, and the Large Synoptic Survey Telescope \citep{2009arXiv0912.0201L} or the Euclid satellite \citep{2011arXiv1110.3193L} in terms of galaxy clustering and cosmic shear. The main advances will come in the form of lower-noise and higher-resolution $y$ and CMB lensing maps, as well as a dense ($\sim30\,{\rm arcmin}^{-2}$) sampling of the galaxy distribution to much higher redshifts ($z\lesssim2$). This increase in sensitivity, however, will have to be accompanied by a much better control of systematics such as contamination from CIB and other sources, galaxy clustering systematics or photo-$z$ uncertainties.

\section*{Acknowledgements}
  NK is funded by the Science and Technology Facilities Council (STFC). DA acknowledges support from the Beecroft trust and from STFC through an Ernest Rutherford Fellowship, grant reference ST/P004474/1. MB is supported by the Polish Ministry of Science and Higher Education through grant DIR/WK/2018/12. JAP was supported by the European Research Council under grant no. 670193.

\setlength{\bibhang}{2.0em}
\setlength\labelwidth{0.0em}
\bibliography{paper}

\end{document}

### 2019-09-11 plot_mf.py

@@ -42,7 +42,7 @@ mfr = np.array(mfr)
 cmap = truncate_colormap(cm.Reds, 0.2, 1.0)
 col = [cmap(i) for i in np.linspace(0, 1, len(a))]
 
-fig, ax = plt.subplots(figsize=(9, 7))
+fig, ax = plt.subplots()
 ax.set_xlim(M.min(), M.max())
 ax.axhline(y=1, ls="--", color="k")
 [ax.loglog(M, R, c=c, label="%s" % red) for R, c, red in zip(mfr, col, z)]
@@ -58,8 +58,8 @@ ticks = cbar.get_ticks()
 cbar.ax.invert_yaxis()
 cbar.set_ticks(ticks[::-1])
 
-ax.set_xlabel(r"$M \mathrm{/ M_{\odot}}$", fontsize=17)
-ax.set_ylabel(r"$\xi_{\mathrm{T}08} / \xi_{\mathrm{T}10}$", fontsize=17)
+ax.set_xlabel(r"$M_{500c} \mathrm{/ M_{\odot}}$", fontsize=17)
+ax.set_ylabel(r"$n_{\mathrm{T}08}(M) / n_{\mathrm{T}10}(M)$", fontsize=17)
 ax.tick_params(which="both", labelsize="large")
 
 cbar.set_label("$z$", rotation=0, labelpad=15, fontsize=17)

### 2019-09-11 notes/paper/paper.tex
synced latest version

@@
 \newcommand{\MB}[1]{\textcolor{red}{#1}}
-\newcommand{\DA}[1]{\textcolor{green}{#1}}
+\newcommand{\DA}[1]{\textcolor{blue}{#1}}
 
@@
       \begin{equation}
-        \langle N_s(M)\rangle=\Theta(M-M_0)\,\left(\frac{M-M_0}{M_1'}\right)^{\alpha_s}.
+        \langle N_s(M)\rangle=N_c(M)\,\Theta(M-M_0)\,\left(\frac{M-M_0}{M_1'}\right)^{\alpha_s}.
       \end{equation}
@@
 
-      Putting everything together, the moments of the galaxy overdensity Fourier profile are \citep{2013MNRAS.430..725V}:
+      Putting everything together, the moments of the galaxy overdensity Fourier profile are \citep[e.g. see section 2.2 of][]{2013MNRAS.430..725V}:
       \begin{align}
-        &\langle u_g(k)\rangle=\bar{n}_g^{-1}\langle N_c\rangle\left[1+\langle N_s\rangle\,u_s(k)\right],\\
-        &\langle |u_g(k)|^2\rangle=\bar{n}_g^{-2}\langle N_c\rangle\left[\langle N_s\rangle^2u_s^2(k)+2\langle N_s\rangle u_s(k)\right],
+        &\langle u_g(k)\rangle=\bar{n}_g^{-1}\left[\langle N_c\rangle	+\langle N_s\rangle\,u_s(k)\right],\\
+        &\langle |u_g(k)|^2\rangle=\bar{n}_g^{-2}\left[\langle N_s\rangle^2u_s^2(k)+2\langle N_s\rangle u_s(k)\right],
       \end{align}
@@
       \begin{equation}
-        \bar{n}_g\equiv\int dM\,\frac{dn}{dM}\langle N_c\rangle\left[1+\langle N_s\rangle\right],
+        \bar{n}_g\equiv\int dM\,\frac{dn}{dM}\left(\langle N_c\rangle+\langle N_s\rangle\right),
       \end{equation} 
@@
 There are only so many jackknife regions that can be selected with a reasonable size, and therefore the estimated covariance is noisy at some level.
-Furthermore, since the footprint associated with the removal of each jackknife region is different from the overall footprint, the method is also not able to recover the mode-coupling associated with the map geometry by construction.
+\DA{Typically the number of independent realizations used to estimate a sample covariance matrix should be at least one order of magnitude larger than the size of the data vector (up to 50 elements in our case).} Furthermore, since the footprint associated with the removal of each jackknife region is different from the overall footprint, the method is also not able to recover the mode-coupling associated with the map geometry by construction.
 In order to verify and improve our estimate of the covariance matrix, we make use of a second analytical estimator.
@@
     where ${\rm Cov}^{\rm JK}$ and ${\rm Cov}^{\rm ana}$ are the jackknife and analytical covariance matrices respectively.
+\DA{We have verified that the resulting covariance matrices are well behaved (i.e.
+they are invertible, and their eigenvalues have a reasonable dynamical range).}
 
@@
 Thus, the margins of the assumed top-hat priors are wide enough to encompass any lack of precision in the number density distribution.
+
+      \DA{Another possible source of systematic uncertainty is the effect of biased photometric redshifts (i.e.
+where $\langle z|z_{\rm photo}\rangle\neq z_{\rm photo}$).
+The ANNz method used in \cite{2018MNRAS.481.1133P} should guarantee unbiased photo-$z$s, but this can never be achieved exactly in practice.
+It would be possible to account for this form of uncertainty by treating $\bar{z}$ as a free parameter, as is usually done in photometric cosmic shear analyses.
+Our results, however, are more sensitive to the distribution widths, and we find that this simple parametrization is able to describe our data sufficiently well.
+We leave a more detailed analysis of the associated photometric redshift systematics for future work.}
 
@@
 As the figure shows, there are strong degeneracies between $M_{\rm min}$, $M_1$ and $w_z$.
-This is easy to understand, given that all of these parameters affect the overall amplitude of the galaxy auto-correlation, but we do not probe to scales where the 1-halo term is fully resolved.
-The lack of such resolution means that we do not break the degeneracy between $M_{\rm min}$ and $M_1$, which regulate the abundance of centrals and satellites, and therefore the constraint on these parameters mostly comes from the 2-halo amplitude (i.e.
+This is easy to understand, given that all of these parameters affect the overall amplitude of the galaxy auto-correlation.
+Since we do not probe scales where the 1-halo term is fully resolved, we do not break the degeneracy between $M_{\rm min}$ and $M_1$, which regulate the abundance of centrals and satellites, and therefore the constraint on these parameters mostly comes from the 2-halo amplitude (i.e.
 the galaxy bias), and the 1-halo shot-noise level.
@@
       Our results are in broad agreement with the estimate of a redshift-independent $1-\bH$ found by \cite{2019arXiv190407887Z} by calibrating cluster masses with CMB lensing ($1-\bH=0.71\pm0.1$), shown in Fig.\!~\ref{fig:bh} as a turquoise semi-transparent band.
-In turn, the grey band in the same figure shows the constraints on $1-\bH$ found by combining tSZ cluster counts and the $TT$ CMB power spectrum measured by \planck\ \cite{2016A&A...594A..24P} ($1-\bH=0.58\pm0.04$).
+In turn, the grey band in the same figure shows the constraints on $1-\bH$ found by combining tSZ cluster counts and the $TT$ CMB power spectrum measured by \planck\ \citep{2016A&A...594A..24P} ($1-\bH=0.58\pm0.04$).
 This is the value of $1-\bH$ needed to explain the amplitude of density perturbations predicted by the CMB in comparison with the abundance of massive clusters.
@@
 To do so, we combine our six measurements under the assumption that they correspond to the same redshift-independent quantity.
-We do so by finding the quantity $\bar{b}_H$ that minimises the $\chi^2$:
+We do so by finding the quantity $\bar{b}_{\rm H}$ that minimises the $\chi^2$:
       \begin{equation}
-        \chi^2=\sum_{i,j=1}^6 (b_{H,i}-\bar{b}_H){\sf Cov}^{-1}_{b,ij}(b_{H,j}-\bar{b}_H),
+        \chi^2=\sum_{i,j=1}^6 (b_{{\rm H},i}-\bar{b}_{\rm H}){\sf Cov}^{-1}_{b,ij}(b_{{\rm H},j}-\bar{b}_{\rm H}),
       \end{equation}
-      where $b_{H,i}$ is the mass bias measured in the $i$-th redshift bin, and ${\sf Cov}_b$ is the covariance matrix of these measurements.
+      where $b_{{\rm H},i}$ is the mass bias measured in the $i$-th redshift bin, and ${\sf Cov}_b$ is the covariance matrix of these measurements.
 Since the galaxy samples used in this analysis have significant redshift overlap, the off-diagonal elements of ${\sf Cov}_b$ cannot be ignored.
-We estimate ${\sf Cov}_b$ through jackknife resampling: we use the power spectra measured in each jackknife region described in Section \ref{ssec:methods.cov} to estimate the best-fit value of $b_{H,i}$ for each of them, and then calculate the covariance through Eq.\!~\ref{eq:cov_jk}.
-Since $\bar{b}_H$ is a linear parameter, its best-fit and standard deviation can be found analytically as:
+We estimate ${\sf Cov}_b$ through jackknife resampling: we use the power spectra measured in each jackknife region described in Section \ref{ssec:methods.cov} to estimate the best-fit value of $b_{{\rm H},i}$ for each of them, and then calculate the covariance through Eq.\!~\ref{eq:cov_jk}.
+Since $\bar{b}_{\rm H}$ is a linear parameter, its best-fit and standard deviation can be found analytically as:
       \begin{equation}
-        \bar{b}_H=\frac{\sum_{ij}{\sf Cov}_{b,ij}^{-1}b_i}{\sum_{ij}{\sf Cov}^{-1}_{b,ij}},
+        \bar{b}_{\rm H}=\frac{\sum_{ij}{\sf Cov}_{b,ij}^{-1}b_{{\rm H},i}}{\sum_{ij}{\sf Cov}^{-1}_{b,ij}},
         \hspace{12pt}
-        \sigma(\bar{b}_H)=\left(\sum_{ij}{\sf Cov}^{-1}_{b,ij}\right)^{-1/2}.
+        \sigma(\bar{b}_{\rm H})=\left(\sum_{ij}{\sf Cov}^{-1}_{b,ij}\right)^{-1/2}.
       \end{equation}
-      At this point it is worth acknowledging that this estimate $\bar{b}_H$ is only strictly consistent if the posterior distribution of the $b_{H,i}$ is Gaussian.
+      At this point it is worth acknowledging that this estimate $\bar{b}_{\rm H}$ is only strictly consistent if the posterior distribution of the $b_{{\rm H},i}$ is Gaussian.
 We find that, with the exception of the 2MPZ sample, which has a comparatively small statistical power, the marginalised distributions in all redshift bins are sufficiently well-behaved that this is a reasonable approximation (e.g.
 see 1-dimensional distribution for $\bH$ in Fig.\!~\ref{fig:triangle}).
-Our combined constraint on $\bar{b}_H$ following this procedure is:
+Our combined constraint on $\bar{b}_{\rm H}$ following this procedure is:
       \begin{equation}
-        1-\bar{b}_H=0.59\pm0.03.
+        1-\bar{b}_{\rm H}=0.59\pm0.03.
       \end{equation}
@@
 This agrees with the results of \cite{2019A&A...626A..27S}, found using tSZ-selected clusters.
-The preferred value of $1-\bar{b}_H$ found also agrees with the results of \cite{2018MNRAS.480.3928M} in cross-correlation with galaxies at very low redshift, and those of \cite{2019arXiv190707870M} using weak-lensing cross-correlations at higher $z$.
+The preferred value of $1-\bar{b}_{\rm H}$ found also agrees with the results of \cite{2018MNRAS.480.3928M} in cross-correlation with galaxies at very low redshift, and those of \cite{2019arXiv190707870M} using weak-lensing cross-correlations at higher $z$.
+
+      \DA{Since the amplitudes of the galaxy auto-correlation and the galaxy-$y$ cross-correlation are both affected by the value of $\sigma_8$, which we have fixed to the best-fit value found by \planck\, the fact that the value of $1-\bH$ we find is compatible with that found by \cite{2016A&A...594A..24P} is not surprising.
+In other words, this agreement can be understood as a evidence of the compatibility between the best-fit \planck\ cosmology and the clustering properties of galaxies and thermal pressure in the datasets used here.
+The corresponding best-fit value of $1-\bH\simeq0.6$ is at odds with the expectation from hydrodynamical simulations \citep{2016ApJ...827..112B} and some direct calibration efforts \citep[e.g.][]{2016MNRAS.456L..74S,2019A&A...621A..40E}, which seem to prefer smaller missing mass fractions ($1-\bH\simeq0.8$).
+A possible resolution of the mild tension between tSZ cluster count and CMB data could be the presence of new physics that modify the late-time expansion and structure growth.
+However, most of these modifications (e.g.
+a one-parameter excursion where the dark energy equation of state takes a larger value $w\sim-0.7$) would make the existing tension in the value of the local expansion rate between CMB and local measurements \citep{2019ApJ...876...85R} worse.
+A careful study of all possibilities, invoking both non-standard physics and more sophisticated astrophysical models, together with improved datasets, will therefore be necessary before this tension can be fully resolved.}
 
@@
 As a visual aid to evaluate the agreement of our results with these models, the predictions for $N=2,\,3,\,5$ and $\infty$ are shown as solid, dashed, dot-dashed and dotted grey lines respectively in Fig.\!~\ref{fig:by}.
+\DA{These results are the most precise measurement to date of this quantity.
+The main factors that contribute to this constraining power are the larger amplitude of the tSZ signal towards low redshifts and the high density of tracers in the 2MPZ and \wisc\ samples.}
 
@@
 
-      As an additional test for systematics, we have also repeated our full analysis replacing the MILCA $y$ map with the NILC map released by Planck.
+      As an additional test for systematics, we have also repeated our full analysis replacing the MILCA $y$ map with the NILC map released by \planck.
 Different component-separation methods are sensitive to different types of contamination, and this exercise is therefore both a necessary consistency check and a way to reinforce our conclusion that the level of CIB contamination is negligible.
@@
 Our fiducial mass function is the parameterisation of \cite{2008ApJ...688..709T}, which we use in order to be able to make a direct comparison with the results of \cite{2016A&A...594A..24P}.
-To explore the dependence on the choice of the mass function, we redo our analysis using the updated parameterisation of \cite{2010ApJ...724..878T}.
+To explore the dependence on the choice of mass function parametrisation, we redo our analysis using the updated parameterisation of \cite{2010ApJ...724..878T}.
 Fig.\!~\ref{fig:bh} shows the final constraints on $1-\bH$ in this case as burgundy squares, which are consistently lower by $\sim 1\sigma$.
@@
 The results, shown in Table \ref{tab:results} and Fig.\!~\ref{fig:bh}, agree well with the measurements of $1-\bH$ made by \planck\ through the combination of cluster number counts and CMB primary anisotropies \citep{2016A&A...594A..24P}, as well as with the calibration of tSZ cluster masses with CMB lensing measurements \citep{2019arXiv190407887Z}, and with similar measurements of $1-\bH$ made by \cite{2018MNRAS.480.3928M} through the same type of cross-correlation but at much lower redshifts.
-More importantly, our tomographic measurement allows us to study the possible redshift dependence of the mass bias, an important ingredient in cosmological analysis of cluster abundances.
+More importantly, our tomographic measurement allows us to study the possible redshift dependence of the mass bias, an important ingredient in the cosmological analysis of cluster abundances.
 Given our uncertainties, we do not find any statistical evidence for a redshift dependence of $1-\bH$, in agreement with previous analyses \citep{2019A&A...626A..27S}.
+\DA{A reliable interpretation of the low value of this parameter ($1-\bH\simeq0.6$) when compared with direct calibration studies and numerical simulations, will require a more careful study of different possible model as well as other datasets.}
 
@@
 Finally, we determine that the most relevant form of systematic associated with uncertainties in the redshift distributions is that associated with the width of $p(z)$.
-To address this, we add a new parameter to our model, $w_z$, parameterising the distribution widths.
+To address this, we add a new parameter to our model, $w_z$, which describes the distribution widths.
 We marginalize over $w_z$ with a 20\% prior, which we have determined to be significantly larger than the expected uncertainty on the true width.
@@
 The most significant consequence of this is the fact that our constraints are strongly degenerate with the amplitude of matter fluctuations, parameterised by $\sigma_8$.
-Therefore, the agreement between our constraints on $1-\bH$ and those found by \planck\ \citep{2016A&A...594A..24P} can therefore be thought of as a proof of the consistency between the properties of the galaxy distribution in 2MPZ and \wisc~ and the CMB anisotropies.
+Therefore, the agreement between our constraints on $1-\bH$ and those found by \planck\ \citep{2016A&A...594A..24P} can be thought of as a proof of the consistency between the properties of the galaxy distribution in 2MPZ and \wisc~ and the CMB anisotropies.
 However, our results regarding the redshift evolution of $1-\bH$ (or lack thereof), and the agreement of $\langle bP_e\rangle$ with existing heating models, are only possible thanks to the tomographic cross-correlation with the galaxy density fluctuations.
 Robust joint constraints on cosmological and astrophysical parameters could be achieved by a combined analysis of galaxy clustering, Compton-$y$ maps and gravitational lensing data (either from cosmic shear or CMB lensing observations).
+We leave this analysis for future work.
 

### 2019-09-12 notes/paper/paper.tex
ns_independent

@@
 More generally, $w$ can be designed to optimally up- or downweight different regions in an inverse-variance manner.
-Through the convolution theorem, the spherical harmonic transform of the observed field is a product of the harmonic transforms of the true field and the mask.
+Through the convolution theorem, the spherical harmonic transform of the observed field is a convolution of the harmonic transforms of the true field and the mask.
 Provided the mask and true field are uncorrelated, this then translates into a similar result for the ensemble average of the observed power spectra $\tilde{C}^{uv}_\ell$:

### 2019-09-12 model/data.py

@@ -20,7 +20,8 @@ def get_profile(m):
     if m['type'] == 'y':
         return Arnaud(name=m['name'])
     elif m['type'] == 'g':
-        return HOD(name=m['name'], nz_file=m['dndz'])
+        return HOD(name=m['name'], nz_file=m['dndz'],
+                   ns_indepent=m.get('ns_independent'))
 
 
 class Tracer(object):

### 2019-09-12 model/profile2D.py

@@ -189,7 +189,7 @@ class NFW(object):
 
 class HOD(object):
     """Calculates a Halo Occupation Distribution profile quantity of a halo."""
-    def __init__(self, name='HOD', nz_file=None):
+    def __init__(self, name='HOD', nz_file=None, ns_independent=False):
 
         self.Delta = 500  # reference overdensity (Arnaud et al.)
         self.z, nz = np.loadtxt(nz_file, unpack=True)
@@ -197,6 +197,7 @@ class HOD(object):
                             bounds_error=False, fill_value=0)
         self.z_avg = np.average(self.z, weights=nz)
         self.name = name
+        self.ns_independent = ns_independent
 
     def kernel(self, cosmo, a, **kwargs):
         """The galaxy number overdensity window function."""
@@ -249,7 +250,10 @@ class HOD(object):
         Nc = self.n_cent(M, **kwargs)   # centrals
         Ns = self.n_sat(M, **kwargs)    # satellites
 
-        dng = mfunc*Nc*(fc+Ns)  # integrand
+        if self.ns_independent:
+            dng = mfunc*(Nc*fc+Ns)  # integrand
+        else:
+            dng = mfunc*Nc*(fc+Ns)  # integrand
 
         ng = simps(dng, x=np.log10(M))
         return ng.squeeze() if squeeze else ng
@@ -272,5 +276,8 @@ class HOD(object):
         H, _ = NFW().fourier_profiles(cosmo, k, M, a, squeeze=False,
                                       **kwargs)
 
-        F, F2 = Nc*(fc + Ns*H), Nc*(2*fc*Ns*H + (Ns*H)**2)
+        if self.ns_independent:
+            F, F2 = (Nc*fc + Ns*H), (2*Nc*fc*Ns*H + (Ns*H)**2)
+        else:
+            F, F2 = Nc*(fc + Ns*H), Nc*(2*fc*Ns*H + (Ns*H)**2)
         return (F.squeeze(), F2.squeeze()) if squeeze else F, F2

### 2019-09-13 plot_bhydro.py
uncoupled Ns from Nc, freed up sigma_lnM, runs & results

@@ -26,13 +26,23 @@ class AnyObjectHandler(HandlerBase):
         return [l1, l2]
 
 
+class constantfit(HandlerBase):
+# Adapted from:
+# https://matplotlib.org/users/legend_guide.html#legend-handlers
+    def create_artists(self, legend, orig_handle,
+                       x0, y0, width, height, fontsize, trans):
+        ll = plt.Line2D([x0,y0+width], [0.7*height,0.7*height],
+                        lw=3, linestyle="-", color="limegreen")
+        return ll
+
+
 def plotfunc(ax, zz, dd, inverted=False,
              fmt=None, color=None, label=None, offset=0):
     """Plots b_hydro data with error bars."""
     yerr = dd[1:] if not inverted else np.flip(dd[1:], axis=0)
     bh = dd[0] if not inverted else 1-dd[0]
 
-    ax.errorbar(zz+0.004*offset, bh, yerr=yerr, fmt=fmt, c=color, label=label)
+    ax.errorbar(zz+0.004*offset, bh, yerr=yerr, fmt=fmt, ms=7, c=color, label=label)
 
 
 
@@ -52,6 +62,7 @@ param_yml = ["params_dam_wnarrow.yml",
              "params_dam_tinker10.yml",
              "params_dam_wfixed.yml",
              "params_dam_ynilc.yml",
+             "params_dam_wnarrow_ns.yml",
 #             "params_dam_masked.yml"
 ]
 
@@ -61,11 +72,12 @@ lbls = ["Fiducial",
         "Tinker 2010",
         "Fixed $w_z$",
         "NILC",
-        "tSZ-masked"]
-#lbls = ["$w = 1$", r"$w \in [0.8, 1.2]$", r"$w \in [0.2, 2.0]$"]
-colours = ["k", "brown", "darkorange", "#009900", "y"]
+        r"$\langle N_s \rangle$ independent"
+#        "tSZ-masked"
+]
+colours = ["k", "brown", "r", "orange", "y"]
 col = [copper(i) for i in np.linspace(0, 1, len(sci))]
-fmts = ["o","s","v","^","x","d"]
+fmts = ["o","s","v","^","*","d"]
 
 
 
@@ -107,24 +119,32 @@ ax.tick_params(labelsize="large")
 hist.set_ylim(0, np.ceil(np.max(dN)))
[…]

### 2019-09-13 notes/paper/paper.tex
NK edits

@@
     analysis in terms of the so-called `hydrostatic bias' parameter
-    $1-\bH$. These resultsts can also be interpreted as measurements
+    $1-\bH$. These results can also be interpreted as measurements
     of the bias-weighted average gas
@@
     theoretical expectations from shock-heating
-    models. \todo{Something we do not discuss at all, but should, is
-      the fact that all our constraints assume (and depend on) the
-      value of $\sigma_8$ found by Planck18 primary CMB. Our
-      measurement of $1-\bH$ will depend on whatever prior on
-      $\sigma_8$ we use, and therefore it shouldn't be completely
-      surprising that we find something that agrees with \planck. It
-      is however a good consistency check that we do, and what is
-      definitely new is the measurement of the redshift
-      dependence. I'd add words about this in Sections
-      \ref{sec:results} and \ref{sec:conclusion}.}
+    models.
 \end{abstract}
@@
 
-  In this work we will focus on the cross-correlation between galaxy clustering data and maps of the tSZ Compton-$y$ parameter, making use of existing data from the Planck collaboration \citep{2016A&A...594A..22P} and a set of photometric galaxy surveys \citep{2014ApJS..210....9B,2016ApJS..225....5B}.
+  In this work we focus on the cross-correlation between galaxy clustering data and maps of the tSZ Compton-$y$ parameter, making use of existing data from the Planck collaboration \citep{2016A&A...594A..22P} and a set of photometric galaxy surveys \citep{2014ApJS..210....9B,2016ApJS..225....5B}.
 The availability of redshift information will allow us to place constraints on the cosmic evolution of the thermal gas pressure and the thermal energy in haloes, as well as to examine any redshift dependence of the mass bias for tSZ cluster studies.
 This is a relevant topic given the current mild tensions between SZ cluster number counts and CMB primary anisotropies \citep{2016A&A...594A..24P,2016ApJ...832...95D,2019ApJ...878...55B,2019arXiv190407887Z}, which could be caused by the assumptions made to model the $y$-mass relation.
-Conversely, under the assumption that the relation between mass and gas pressure is well understood, the tSZ effect can be thought of as a mass tracer, which can be used to break degeneracies with the galaxy bias parameter -- we will however leave this analysis for future work.
+Conversely, under the assumption that the relation between mass and gas pressure is well understood, the tSZ effect can be thought of as a mass tracer, which can be used to break degeneracies with the galaxy bias parameter -- we however leave this analysis for future work.
 
@@
 \section{Theory}\label{sec:theory}
-  Our work focuses on the cross-correlation of the projected galaxy overdensity in consecutive redshift bins $\delta_g$ and maps of the tSZ Compton-$y$ parameter.
+  Our work focuses on the cross-correlation of the projected galaxy overdensity in consecutive redshift bins, $\delta_g$, and maps of the tSZ Compton-$y$ parameter.
 
-  Here $\delta_g$ is simply the overdensity in the number of galaxies integrated over a redshift bin:
+  Here, $\delta_g$ is simply the overdensity in the number of galaxies integrated over a redshift bin:
   \begin{equation}
@@
     \subsubsection{Galaxies and the halo occupation distribution}\label{sssec:theory.hm.hod}
-      To model the galaxy overdensity $\Delta_g$ we will use a Halo Occupation Distribution (HOD) model \citep{2002ApJ...575..587B,2005ApJ...633..791Z,2013MNRAS.430..725V}, as prescribed by \cite{2011ApJ...736...59Z}.
+      To model the galaxy overdensity, $\Delta_g$, we use a Halo Occupation Distribution (HOD) model \citep{2002ApJ...575..587B,2005ApJ...633..791Z,2013MNRAS.430..725V}, as prescribed by \cite{2011ApJ...736...59Z}.
 The HOD models the galaxy content of dark matter haloes as being made up of central and satellite galaxies.
@@
       \end{equation}
-      For simplicity, we will fix $M_0$ to $M_{\rm min}$, $\sigma_{\rm lnM}=0.15$ and $\alpha_s$=1, as in \cite{2018MNRAS.473.4318A}, leaving only two free parameters: $M_{\rm min}$ and $M_1'$.
+      For simplicity, we fix $M_0$ to $M_{\rm min}$, $\sigma_{\rm lnM}=0.15$ and $\alpha_s$=1, as in \cite{2018MNRAS.473.4318A}, leaving only two free parameters: $M_{\rm min}$ and $M_1'$.
 
@@
       \end{equation}
-      where $r_{500c}$ is the cluster radius enclosing an overdensity of 500 times the critical density (see Section \ref{sssec:theory.hm.cm}). The normalization $P_*$ is given by
+      where $r_{500c}$ is the cluster radius enclosing an overdensity of 500 times the critical density (see Section \ref{sssec:theory.hm.cm}). The normalisation $P_*$ is given by
       \begin{equation}\label{eq:arnaud_norm}
@@
 This factor is also commonly referred to as the `hydrostatic bias', since it was originally defined to account for the fraction of halo mass not in hydrostatic equilibrium missed by X-ray observations.
-Since this parameter also encapsulates other sources of bias in the X-ray-based mass estimates, we will instead refer to it as the \emph{mass bias}.
+Since this parameter also encapsulates other sources of bias in the X-ray-based mass estimates, we instead refer to it as the \emph{mass bias}.
 Numerical simulations have constrained the mass deficit to be around 20\% (i.e.
@@
       where $P_e(k)$ is the Fourier transform of the GNFW profile and $\sigma_{\ln Y}=0.173\pm0.023$ is the intrinsic logarithmic scatter in the $y$-mass relation \cite{2016A&A...594A..24P}.
-Note that, since we do not make use of the tSZ auto-correlation, we will not use the second order cumulant of the pressure profile in our analysis.
+Note that, since we do not make use of the tSZ auto-correlation, we do not use the second order cumulant of the pressure profile in our analysis.
 However, since we analyse the galaxy-tSZ correlation, we need to model the covariance between the galaxy overdensity and pressure profiles.
@@
 \ref{eq:compty}.]}.
-We will also express our measurements in terms of this parameter in Section \ref{sec:results}.
+We also express our measurements in terms of this parameter in Section \ref{sec:results}.
 
@@
       \end{equation}
-      Common choices for $\rho_*$ are the critical density $\rho_c=3H^2(z)/4\pi G$ or the matter density $\rho_M(z)$ \MB{[which one do we use?]}\DA{[We state this in the next paragraph.]}.
+      Common choices for $\rho_*$ are the critical density, $\rho_c=3H^2(z)/4\pi G$, or the matter density, $\rho_M(z)$ \MB{[which one do we use?]}\DA{[We state this in the next paragraph.]}.
 The spherical overdensity parameter $\Delta$ is usually chosen within the range $\sim(200,500)$ and sometimes defined as the quantity yielding the virial radius in the spherical top-hat collapse model $\Delta_v$ \citep{1998ApJ...495...80B}.
@@
       \includegraphics[width=0.5\textwidth]{mask_g.pdf}
-      \caption{{\sl Top panel:} sky mask used for the Compton-$y$ map, corresponding to a sky fraction $f_{\rm sky}=0.59$.
-{\sl Bottom panel:} mask used for the 2MPZ and \wisc~ galaxy surveys, corresponding to a sky fraction $f_{\rm sky}=0.68$.
+      \caption{{\sl Top:} sky mask used for the Compton-$y$ map, corresponding to a sky fraction $f_{\rm sky}=0.59$.
+{\sl Bottom:} mask used for the 2MPZ and \wisc~ galaxy surveys, corresponding to a sky fraction $f_{\rm sky}=0.68$.
 The product of both masks leaves a usable sky fraction $f_{\rm sky}\simeq0.58$.
@@
     \end{table} 
-    We make use of two low-redshift photometric redshift catalogues, the 2MASS Photometric Redshift dataset \citep[2MPZ,][]{2014ApJS..210....9B} and the WISE $\times$ SuperCOSMOS catalogue \citep[\wisc,][]{2016ApJS..225....5B}.
+    We make use of two low-redshift photometric redshift catalogues, the 2MASS Photometric Redshift data set \citep[2MPZ,][]{2014ApJS..210....9B} and the WISE $\times$ SuperCOSMOS catalogue \citep[\wisc,][]{2016ApJS..225....5B}.
 Both samples were created by cross-matching full-sky imaging surveys, and photo-$z$s were subsequently computed for all the included sources.
@@
 The resulting photo-$z$'s have a typical error $\sigma_z\simeq0.015$, and the sample has a median redshift $z\simeq0.08$ (see also \citealt{2018MNRAS.476.1050B} for a more detailed analysis of 2MPZ photo-$z$ properties).
-As we will see, due to the low redshift of this sample, the cross-correlation with the $y$ map is dominated by the 1-halo term for 2MPZ, and little is gained by sub-dividing it into narrower redshift bins.
+As demonstrated in Section \ref{sec:results}, due to the low redshift of this sample, the cross-correlation with the $y$ map is dominated by the 1-halo term for 2MPZ, and little is gained by sub-dividing it into narrower redshift bins.
 Therefore we use 2MPZ as a single tomographic sample.
 
-    A deeper sample is obtained by dropping the 2MASS data and cross-matching WISE and SuperCOSMOS only.
+    A deeper sample is obtained by ignoring the 2MASS data and cross-matching WISE and SuperCOSMOS only.
 After removing the sources already contained in 2MPZ, the resulting catalogue, \wisc, is $\sim3$ times deeper, contains $\sim20$ million sources and reaches up to redshift $z\sim0.4$, with a median redshift of $\sim0.2$.
@@
 There are only so many jackknife regions that can be selected with a reasonable size, and therefore the estimated covariance is noisy at some level.
-\DA{Typically the number of independent realizations used to estimate a sample covariance matrix should be at least one order of magnitude larger than the size of the data vector (up to 50 elements in our case).} Furthermore, since the footprint associated with the removal of each jackknife region is different from the overall footprint, the method is also not able to recover the mode-coupling associated with the map geometry by construction.
+\DA{Typically the number of independent realisations used to estimate a sample covariance matrix should be at least one order of magnitude larger than the size of the data vector (up to 50 elements in our case).} Furthermore, since the footprint associated with the removal of each jackknife region is different from the overall footprint, the method is also not able to recover the mode-coupling associated with the map geometry by construction.
 In order to verify and improve our estimate of the covariance matrix, we make use of a second analytical estimator.
@@
 It would be possible to account for this form of uncertainty by treating $\bar{z}$ as a free parameter, as is usually done in photometric cosmic shear analyses.
-Our results, however, are more sensitive to the distribution widths, and we find that this simple parametrization is able to describe our data sufficiently well.
+Our results, however, are more sensitive to the distribution widths, and we find that this simple parametrisation is able to describe our data sufficiently well.
 We leave a more detailed analysis of the associated photometric redshift systematics for future work.}
@@
 Our fiducial constrains are shown as black circles with error bars, and are centred at the mean redshift of each sample.
-The upward-pointing green triangles show the same constraints found using the NILC $y$ map, which are in good agreement with our fiducial results.
-The light-orange downward-pointing triangles show the constraints found fixing the photo-$z$ width parameter $w_z$.
+The grey circles show the same constraints found using the NILC $y$ map, which are in good agreement with our fiducial results.
+The red downward-pointing triangles show the constraints found fixing the photo-$z$ width parameter $w_z$.
 They are in good agreement with our fiducial measurements, with $\sim20\%$ smaller error bars.
 The burgundy squares show the results found using the 2010 Tinker mass function, which are systematically biased low.
-The red diamond shows our combined, redshift-independent constraint on $1-\bH$.
+The orange diamond and the mesh show our combined, redshift-independent constraint on $1-\bH$.
 For comparison, the grey and turquoise bands show the constraints on the mass bias found by combining cluster counts and CMB primary \citep{2016A&A...594A..24P} as well as the constraints using CMB lensing to calibrate cluster masses \citep{2019arXiv190407887Z}, respectively.
@@
 a one-parameter excursion where the dark energy equation of state takes a larger value $w\sim-0.7$) would make the existing tension in the value of the local expansion rate between CMB and local measurements \citep{2019ApJ...876...85R} worse.
-A careful study of all possibilities, invoking both non-standard physics and more sophisticated astrophysical models, together with improved datasets, will therefore be necessary before this tension can be fully resolved.}
+A careful study of all possibilities, invoking both non-standard physics and more sophisticated astrophysical models, together with improved datasets, is therefore necessary before this tension can be fully resolved.}
 
@@
 As a visual aid to evaluate the agreement of our results with these models, the predictions for $N=2,\,3,\,5$ and $\infty$ are shown as solid, dashed, dot-dashed and dotted grey lines respectively in Fig.\!~\ref{fig:by}.
-\DA{These results are the most precise measurement to date of this quantity.
+\DA{These results demonstrate the most precise measurement of this quantity to date.
 The main factors that contribute to this constraining power are the larger amplitude of the tSZ signal towards low redshifts and the high density of tracers in the 2MPZ and \wisc\ samples.}
@@
 Different component-separation methods are sensitive to different types of contamination, and this exercise is therefore both a necessary consistency check and a way to reinforce our conclusion that the level of CIB contamination is negligible.
-The resulting measurements of $1-\bH$ are shown in Fig.\!~\ref{fig:bh} as red triangles with error bars.
+The resulting measurements of $1-\bH$ are shown in Fig.\!~\ref{fig:bh} next to the fiducial measurements, as grey circles with error bars.
 The results are in very good agreement with our fiducial analysis.
@@
 The results are shown in Fig.
-\ref{fig:bh} as yellow down-pointing triangles.
+\ref{fig:bh} as red down-pointing triangles.
 We observe that the only effect of allowing $w_z$ to vary is to increase the final uncertainties on $1-\bH$ by about $20\%$.
@@
         \includegraphics[width=0.49\textwidth]{mf_ratio.pdf}
-        \caption{Ratio between the mass function parametrizations of \citet{2008ApJ...688..709T} and \citet{2010ApJ...724..878T} in the range of redshifts relevant to this analysis.
+        \caption{Ratio between the mass function parametrisations of \citet{2008ApJ...688..709T} and \citet{2010ApJ...724..878T} in the range of redshifts relevant to this analysis.
 A systematic offset of about $10$-$20\%$ between them can be observed, which causes the lower value of $1-b_{\rm H}$ found using the latter mass function (see Fig.\!~\ref{fig:bh}).
@@
 To explore the dependence on the choice of mass function parametrisation, we redo our analysis using the updated parameterisation of \cite{2010ApJ...724..878T}.
-Fig.\!~\ref{fig:bh} shows the final constraints on $1-\bH$ in this case as burgundy squares, which are consistently lower by $\sim 1\sigma$.
+Fig.\!~\ref{fig:bh} shows the final constraints on $1-\bH$ in this case as burgundy squares, which are consistently lower by $\sim 2\sigma$.
 We find that this is caused by a redshift-dependent systematic offset between both mass function parameterisations which reaches the level of $10$-$20\%$ in the range $0<z<0.4$.
@@
 Given our uncertainties, we do not find any statistical evidence for a redshift dependence of $1-\bH$, in agreement with previous analyses \citep{2019A&A...626A..27S}.
-\DA{A reliable interpretation of the low value of this parameter ($1-\bH\simeq0.6$) when compared with direct calibration studies and numerical simulations, will require a more careful study of different possible model as well as other datasets.}
+\DA{A reliable interpretation of the low value of this parameter ($1-\bH\simeq0.6$) when compared with direct calibration studies and numerical simulations, requires a more careful study of different possible model as well as other datasets.}
 
@@
 To address this, we add a new parameter to our model, $w_z$, which describes the distribution widths.
-We marginalize over $w_z$ with a 20\% prior, which we have determined to be significantly larger than the expected uncertainty on the true width.
+We marginalise over $w_z$ with a 20\% prior, which we have determined to be significantly larger than the expected uncertainty on the true width.
 This has the effect of degrading our constraints on $1-\bH$ and $\langle bP_e\rangle$ by $\sim20\%$ without modifying the best-fit value of either quantity significantly.

### 2019-09-13 plot_bhydro.py

@@ -59,25 +59,25 @@ def get_dndz(fname, width):
 
 
 param_yml = ["params_dam_wnarrow.yml",
-             "params_dam_tinker10.yml",
-             "params_dam_wfixed.yml",
              "params_dam_ynilc.yml",
-             "params_dam_wnarrow_ns.yml",
+             "params_dam_wfixed.yml",
+             "params_dam_tinker10.yml",
+#             "params_dam_wnarrow_ns.yml",
 #             "params_dam_masked.yml"
 ]
 
 sci = [r"$\mathrm{2MPZ}$"] + \
       [r"$\mathrm{WI \times SC}$ - $\mathrm{%d}$" % i for i in range(1, 6)]
 lbls = ["Fiducial",
-        "Tinker 2010",
-        "Fixed $w_z$",
         "NILC",
+        "Fixed $w_z$",
+        "Tinker 2010",
         r"$\langle N_s \rangle$ independent"
-#        "tSZ-masked"
+        "tSZ-masked"
 ]
-colours = ["k", "brown", "r", "orange", "y"]
+colours = ["k", "grey", "r", "brown", "orange"]
 col = [copper(i) for i in np.linspace(0, 1, len(sci))]
-fmts = ["o","s","v","^","*","d"]
+fmts = ["o","o", "v","s","*","d"]
 
 
 
@@ -124,8 +124,8 @@ ax.axhspan(0.72-0.10, 0.72+0.10, color="cadetblue", alpha=0.3)
 ax.axhline(0.58, ls=":", color="grey")
 ax.axhspan(0.58-0.04, 0.58+0.06, color="grey", alpha=0.3)
 # OUR DATA
-#ax.axhline(0.59, ls=":", color="limegreen")
-#ax.axhspan(0.59-0.03, 0.59+0.03, color="limegreen", alpha=0.15, hatch="/")
+ax.axhline(0.59, ls=":", color="orange")
+ax.axhspan(0.59-0.03, 0.59+0.03, color="orange", alpha=0.15, fill=False, hatch="xxx")
 
 props = dict(boxstyle="round", facecolor="w", alpha=0.5)
 ax.text(0.005, 0.595, "CMB + N.C.",
@@ -143,7 +143,7 @@ hist.set_ylabel(r"$\mathrm{d} n \mathrm{/d} z$", fontsize=17)
 for i, (dd, cc, fmt, lbl) in enumerate(zip(data, colours, fmts, lbls)):
[…]

### 2019-09-14 notes/paper/paper.tex
added parameter talk

@@
 
-\title[Tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations]{Wide-angle tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations}
+\title[Tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations]{Wide-angle tomographic measurement of the intergalactic gas pressure through galaxy-tSZ Fcross-correlations}
 \author[David Alonso]{Nick Koukoufilippas$^1$, David Alonso$^1$, Maciej Bilicki$^2$, John A. Peacock$^3$\\
@@
       \end{equation}
-      We then assume that satellites can only be formed if a halo has a central and has a mass larger than some threshold $M_0$.
+      In our fiducial scenario we assume that satellites can only be formed if a halo has a central and has a mass larger than some threshold $M_0$.
 In that case, the average number of satellites follows a power law of the form:
@@
       For simplicity, we fix $M_0$ to $M_{\rm min}$, $\sigma_{\rm lnM}=0.15$ and $\alpha_s$=1, as in \cite{2018MNRAS.473.4318A}, leaving only two free parameters: $M_{\rm min}$ and $M_1'$.
+
+      Coupling $M_0$ and $M_{\rm min}$ allows for all haloes containing a central to also contain satellites, and conversely, for all haloes containing satellites to necessarily contain a central.
+This assumption breaks down in cases such as mergers, where centrals have not been established yet.
+Nevertheless, we have confirmed that decoupling $M_0$ and $M_{\rm min}$, and allowing haloes to contain solely satellites, does not yield any statistically significant offset from our fiducial scenario.
+We have also tested the effect of freeing-up $\sigma_{\rm lnM}$, and confirmed that the measurements we obtain are almost identical to our fiducial results.
 

### 2019-09-14 notes/paper/paper.tex
added parameter talk

@@
 
-\title[Tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations]{Wide-angle tomographic measurement of the intergalactic gas pressure through galaxy-tSZ Fcross-correlations}
+\title[Tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations]{Wide-angle tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations}
 \author[David Alonso]{Nick Koukoufilippas$^1$, David Alonso$^1$, Maciej Bilicki$^2$, John A. Peacock$^3$\\

### 2019-09-14 notes/paper/paper.tex
revised up to section 3

@@
 
-\title[Tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations]{Wide-angle tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations}
+\title[Tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations]{Tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations}
 \author[David Alonso]{Nick Koukoufilippas$^1$, David Alonso$^1$, Maciej Bilicki$^2$, John A. Peacock$^3$\\
@@
 \begin{abstract}
-    We cross-correlate maps of the thermal Sunyaev-Zeldovich (tSZ)
-    Compton-$y$ parameter published by \planck\ with the projected
-    distribution of galaxies in a set of low-redshift tomographic
-    bins. We use the nearly full-sky 2MASS Photometric Redshift and
-    WISE $\times$ SuperCOSMOS public
-    catalogues, covering the redshift range $z\lesssim0.4$. Our
-    measurements allow us to place constraints on the redshift
-    dependence of the mass-observable relation for tSZ cluster count
-    analysis in terms of the so-called `hydrostatic bias' parameter
-    $1-\bH$. These results can also be interpreted as measurements
-    of the bias-weighted average gas
-    pressure $\langle bP_e\rangle$ as a function of redshift, a
-    quantity that can be related to the thermodynamics of gas inside
-    haloes and used to constrain energy injection processes. We
-    measure $1-\bH$ with $\sim13\%$ precision in 6 equispaced
-    redshift bins, and find no evidence for a redshift-dependent mass
-    bias parameter, in agreement with previous analyses. Our mean value of
-    $1-\bH = 0.59\pm0.03$ is also in good agreement with that estimated by
-    the joint analysis of \planck\ cluster counts and CMB
-    anisotropies. Our measurements of $\langle bP_e\rangle$, at the
-    level of $\sim10\%$ in each bin, are the most stringent
-    constraints on the redshift dependence of this parameter to date,
-    and agree well both with previous measurements and with
-    theoretical expectations from shock-heating
-    models.
+    We cross-correlate maps of the thermal Sunyaev-Zeldovich (tSZ) Compton-$y$ parameter published by \planck\ with the projected distribution of galaxies in a set of low-redshift tomographic bins.
+We use the nearly full-sky 2MASS Photometric Redshift and WISE $\times$ SuperCOSMOS public catalogues, covering the redshift range $z\lesssim0.4$.
+Our measurements allow us to place constraints on the redshift dependence of the mass-observable relation for tSZ cluster count analysis in terms of the so-called `hydrostatic bias' parameter $1-\bH$.
+These results can also be interpreted as measurements of the bias-weighted average gas pressure $\langle bP_e\rangle$ as a function of redshift, a quantity that can be related to the thermodynamics of gas inside haloes and used to constrain energy injection processes.
+We measure $1-\bH$ with $\sim13\%$ precision in 6 equispaced redshift bins, and find no evidence for a redshift-dependent mass bias parameter, in agreement with previous analyses.
+Our mean value of $1-\bH = 0.59\pm0.03$ is also in good agreement with that estimated by the joint analysis of \planck\ cluster counts and CMB anisotropies.
+Our measurements of $\langle bP_e\rangle$, at the level of $\sim10\%$ in each bin, are the most stringent constraints on the redshift dependence of this parameter to date, and agree well both with previous measurements and with theoretical expectations from shock-heating models.
 \end{abstract}
@@
 The limiting factor for cosmological constraints from cluster number counts is the uncertainty in the mass-observable relation \citep{2009ApJ...692.1060V,2010ApJ...722.1180V,2011ApJ...732...44S,2013JCAP...07..008H,2014MNRAS.440.2077M,2014A&A...571A..20P,2015MNRAS.446.2205M,2016A&A...594A..24P,2016ApJ...832...95D,2019ApJ...878...55B}.
-\MB{[why is this relevant here?]} \DA{[It's another example of where gastrophysics limits cosmology.]} Cosmic shear measurements are strongly affected by sub-grid baryonic physics, and by uncertainties in the processes by which galaxies acquire correlated intrinsic alignments \citep[e.g.][]{2001MNRAS.320L...7C,2002MNRAS.332..788M,2004PhRvD..70f3526H,2017MNRAS.465.2033J,2018PhRvD..98d3528T,2018arXiv181206076H,2018ARA&A..56..393M,2018arXiv181106989S}.
+Cosmic shear measurements are strongly affected by sub-grid baryonic physics, and by uncertainties in the processes by which galaxies acquire correlated intrinsic alignments \citep[e.g.][]{2001MNRAS.320L...7C,2002MNRAS.332..788M,2004PhRvD..70f3526H,2017MNRAS.465.2033J,2018PhRvD..98d3528T,2018arXiv181206076H,2018ARA&A..56..393M,2018arXiv181106989S}.
+Understanding the impact of baryons in the matter power spectrum will require a better understanding of the distribution of gas in halos.
 Finally, even though the clustering pattern of galaxies is one of the cosmological observables with the highest signal-to-noise ratio, the cosmological constraints that can be extracted from it are severely limited by our incomplete understanding of the galaxy-dark matter connection \citep[see e.g.][and references therein]{2018ARA&A..56..435W}.
@@
 
-  The CMB secondary anisotropies, in particular the thermal and kinetic Sunyaev-Zeldovich effects \citep[tSZ and kSZ respectively,][]{1972CoASP...4..173S}, as well as the gravitational lensing of the CMB photons, have gained popularity as a means to address this issue \citep{2017JCAP...11..040B,2019BAAS...51c.297B}.
+  The CMB secondary anisotropies, in particular the thermal and kinetic Sunyaev-Zeldovich effects \citep[tSZ and kSZ respectively,][]{1972CoASP...4..173S}, as well as the gravitational lensing of the CMB photons, have gained popularity as a means to address these issues \citep{2017JCAP...11..040B,2019BAAS...51c.297B}.
 These effects are relatively clean probes of some of the physical quantities that need to be understood in order to mitigate the impact of astrophysical uncertainties: the matter and gas densities, the gas pressure and the velocity field.
 Since these observables are also sensitive to cosmology, their combination with large-scale structure data can be extremely powerful at disentangling astrophysical and cosmological parameters.
-This has been explored by a large number of groups: CMB lensing data have been used to constrain the bias of different tracers of the matter distribution \citep[e.g.][]{2019MNRAS.485.1720H,2018JCAP...04..053A,2018arXiv181002322A,2018MNRAS.481.1133P}, as well as to calibrate the measurement of galaxy shapes in cosmic shear analyses \citep{2017PhRvD..95l3512S}.
+This has been explored by a large number of groups: CMB lensing data have been used to constrain the bias of different tracers of the matter distribution \citep[e.g.][]{2019MNRAS.485.1720H,2018JCAP...04..053A,2018arXiv181002322A,2018MNRAS.481.1133P}, as well as to calibrate the measurement of galaxy shapes in cosmic shear analyses \citep{2019PhRvD.100b3541A}.
 The tSZ effect has been used in cross-correlation with galaxy clustering and weak lensing data to determine the physical properties of the diffuse gas, as well as to potentially improve constraints on the amplitude of matter fluctuations \citep{2014PhRvD..89b3508V,2014JCAP...02..030H,2015JCAP...09..046M,2017MNRAS.471.1565H,2017ApJ...845...71A,2018PhRvD..97f3514A,2018MNRAS.480.3928M,2019A&A...624A..48D,2019MNRAS.483..223T,2019arXiv190306654T,2019arXiv190413347P,2019arXiv190707870M}.
@@
 
-  In this work we focus on the cross-correlation between galaxy clustering data and maps of the tSZ Compton-$y$ parameter, making use of existing data from the Planck collaboration \citep{2016A&A...594A..22P} and a set of photometric galaxy surveys \citep{2014ApJS..210....9B,2016ApJS..225....5B}.
+  In this work we focus on the cross-correlation between galaxy clustering data and maps of the tSZ Compton-$y$ parameter, making use of existing data from the \planck\ collaboration \citep{2016A&A...594A..22P} and a set of photometric galaxy surveys \citep{2014ApJS..210....9B,2016ApJS..225....5B}.
 The availability of redshift information will allow us to place constraints on the cosmic evolution of the thermal gas pressure and the thermal energy in haloes, as well as to examine any redshift dependence of the mass bias for tSZ cluster studies.
@@
       For simplicity, we fix $M_0$ to $M_{\rm min}$, $\sigma_{\rm lnM}=0.15$ and $\alpha_s$=1, as in \cite{2018MNRAS.473.4318A}, leaving only two free parameters: $M_{\rm min}$ and $M_1'$.
-
 Coupling $M_0$ and $M_{\rm min}$ allows for all haloes containing a central to also contain satellites, and conversely, for all haloes containing satellites to necessarily contain a central.
 This assumption breaks down in cases such as mergers, where centrals have not been established yet.
-Nevertheless, we have confirmed that decoupling $M_0$ and $M_{\rm min}$, and allowing haloes to contain solely satellites, does not yield any statistically significant offset from our fiducial scenario.
-We have also tested the effect of freeing-up $\sigma_{\rm lnM}$, and confirmed that the measurements we obtain are almost identical to our fiducial results.
+We will however explore departures from this fiducial model.
 
       Besides their mean values, we also need to specify the statistics of $N_c$ and $N_s$.
-Following the standard practice \citep{2013MNRAS.430..725V}, we assume $N_c$ to have a binomial distribution with probability $p=\langle N_c\rangle$, and $N_s$ to be Poisson-distributed.
+Following the standard practice \citep{2013MNRAS.430..725V}, we assume $N_c$ to have a Bernoulli distribution with probability $p=\langle N_c\rangle$, and $N_s$ to be Poisson-distributed.
 
@@
     \subsubsection{tSZ and pressure profiles}\label{sssec:theory.hm.pe}
-      In order to describe the electron pressure in a halo, we use the generalised NFW profile (GNFW) described in \cite{2010A&A...517A..92A} and used in the \planck\ tSZ cluster analysis \cite{2016A&A...594A..24P}.
+      In order to describe the electron pressure in a halo, we use the generalised NFW profile (GNFW) described in \cite{2010A&A...517A..92A} and used in the \planck\ tSZ cluster analysis \citep{2016A&A...594A..24P}.
 This profile takes the form:
@@
 This factor is also commonly referred to as the `hydrostatic bias', since it was originally defined to account for the fraction of halo mass not in hydrostatic equilibrium missed by X-ray observations.
-Since this parameter also encapsulates other sources of bias in the X-ray-based mass estimates, we instead refer to it as the \emph{mass bias}.
+Since this parameter also encapsulates other sources of bias in the X-ray-based mass estimates, we instead refer to it as the {\sl mass bias}.
 Numerical simulations have constrained the mass deficit to be around 20\% (i.e.
@@
 However, since we analyse the galaxy-tSZ correlation, we need to model the covariance between the galaxy overdensity and pressure profiles.
-For simplicity, we adopt a simple parameterisation:
+For simplicity, we adopt a one-parameter model:
       \begin{equation}
@@
       \end{equation}
-      where $\rho_{yg}$ is a free parameter that determines the sign of the correlation between galaxy abundance and pressure.
+      where the free parameter $\rho_{yg}$ determines the sign of the correlation between galaxy abundance and pressure.
 Marginalising over this parameter has the added advantage of removing any sensitivity of our final constraints to $1-\bH$ on the details of the cross-spectrum model in the 1-halo regime, where both parameters are completely degenerate.
@@
       where $E_T(M)$ is the thermal energy in a halo of mass $M$ \citep{2017MNRAS.467.2315V,2019arXiv190413347P}.
-A measurement of $\langle bP_e\rangle$ can therefore be related to the thermodynamics of gas inside haloes \MB{[more about this relation?
-and, this is electron pressure - how it connects to gas pressure?]} \DA{[Eq.
-\ref{eq:by} is the equation linking to thermal energy.
-Note that electron and total pressure are just proportional to each other, I've now noted this below Eq.
-\ref{eq:compty}.]}.
+A measurement of $\langle bP_e\rangle$ can therefore be related to the thermodynamics of gas inside haloes.
 We also express our measurements in terms of this parameter in Section \ref{sec:results}.
@@
       \end{equation}
-      Common choices for $\rho_*$ are the critical density, $\rho_c=3H^2(z)/4\pi G$, or the matter density, $\rho_M(z)$ \MB{[which one do we use?]}\DA{[We state this in the next paragraph.]}.
+      Common choices for $\rho_*$ are the critical density, $\rho_c=3H^2(z)/4\pi G$, or the matter density, $\rho_M(z)$.
 The spherical overdensity parameter $\Delta$ is usually chosen within the range $\sim(200,500)$ and sometimes defined as the quantity yielding the virial radius in the spherical top-hat collapse model $\Delta_v$ \citep{1998ApJ...495...80B}.
@@
 
+  \todo{ Nevertheless, we have confirmed that decoupling $M_0$ and $M_{\rm min}$, and allowing haloes to contain solely satellites, does not yield any statistically significant offset from our fiducial scenario.
+We have also tested the effect of freeing-up $\sigma_{\rm lnM}$, and confirmed that the measurements we obtain are almost identical to our fiducial results.}
+
 \section*{Acknowledgements}

### 2019-09-14 notes/paper/paper.tex
revised up to section 4.4

@@
     Here, $P_L(k)$ is the linear matter power spectrum, $dn/dM$ is the halo mass function (comoving density of haloes per unit halo mass) and $b_h(M)$ is the halo bias.
-    %Further details are discussed in Appendix \ref{app:hm}.
 
@@
       \end{equation} 
-      and we have suppressed the mass dependence of all quantities for simplicity.
+      and we have suppressed the mass dependence of all quantities for brevity.
 
@@
     \end{figure}
-    We make use of the maps of the Compton-$y$ parameter made public by the Planck collaboration \citep{2016A&A...594A..22P}.
+    We make use of of the Compton-$y$ parameter maps made public by the \planck\ collaboration \citep{2016A&A...594A..22P}.
 These maps were generated using different flavours of the Internal Linear Combination method \citep{2004ApJ...612..633E,2008arXiv0811.4277V}.
@@
 The refined versions of the ILC method used by \planck\ further optimise the linear weights on different scales and different regions of the map, and project out sources with known spectra that are likely to cause significant contamination.
-In particular, the Planck collaboration has released two $y$ maps, extracted using the MILCA \citep{2013A&A...558A.118H} and NILC \citep{2011MNRAS.410.2481R} variations of the ILC technique.
+In particular, \planck\ has released two $y$ maps, extracted using the MILCA \citep{2013A&A...558A.118H} and NILC \citep{2011MNRAS.410.2481R} variations of the ILC technique.
 Both methods deproject CMB contamination through its well-known spectrum, but differ on the methods used to calculate the optimal scale-dependent and spatially-varying linear weights.
@@
     \end{table} 
-    We make use of two low-redshift photometric redshift catalogues, the 2MASS Photometric Redshift data set \citep[2MPZ,][]{2014ApJS..210....9B} and the WISE $\times$ SuperCOSMOS catalogue \citep[\wisc,][]{2016ApJS..225....5B}.
+    We make use of two low-redshift photometric redshift (photo-$z$) catalogues, the 2MASS Photometric Redshift catalogue \citep[2MPZ,][]{2014ApJS..210....9B} and the WISE $\times$ SuperCOSMOS catalogue \citep[\wisc,][]{2016ApJS..225....5B}.
 Both samples were created by cross-matching full-sky imaging surveys, and photo-$z$s were subsequently computed for all the included sources.
-Their broad photometric coverage, together with adequate spectroscopic calibration data allowed for obtaining well-constrained photo-$z$s, with minimal mean bias, relatively low scatter and a small number of outliers.
+Their broad photometric coverage, together with adequate spectroscopic calibration data allowed for well-constrained photo-$z$s, with minimal mean bias, relatively low scatter and a small number of outliers.
 
@@
 Photometric redshifts (photo-$z$s) were extracted using the neural network code ANNz \citep{2004PASP..116..345C} trained on a large spectroscopic sample from overlapping surveys.
-The resulting photo-$z$'s have a typical error $\sigma_z\simeq0.015$, and the sample has a median redshift $z\simeq0.08$ (see also \citealt{2018MNRAS.476.1050B} for a more detailed analysis of 2MPZ photo-$z$ properties).
+The resulting photo-$z$'s have a typical error $\sigma_z\simeq0.015$, and the sample has a median redshift $z\simeq0.08$ (see also \citealt{2018MNRAS.476.1050B} for a more detailed analysis of the 2MPZ photo-$z$ properties).
 As demonstrated in Section \ref{sec:results}, due to the low redshift of this sample, the cross-correlation with the $y$ map is dominated by the 1-halo term for 2MPZ, and little is gained by sub-dividing it into narrower redshift bins.
@@
 
-    Both 2MPZ and WISC suffer from contamination from Galactic and observational systematics in different levels.
+    Both 2MPZ and WISC suffer from different levels of contamination from Galactic and observational systematics.
 The most relevant Galactic systematic is star contamination, particularly for \wisc~ \citep{2018arXiv181208182X}.
@@
 There are only so many jackknife regions that can be selected with a reasonable size, and therefore the estimated covariance is noisy at some level.
-\DA{Typically the number of independent realisations used to estimate a sample covariance matrix should be at least one order of magnitude larger than the size of the data vector (up to 50 elements in our case).} Furthermore, since the footprint associated with the removal of each jackknife region is different from the overall footprint, the method is also not able to recover the mode-coupling associated with the map geometry by construction.
+Typically, the number of independent realisations used to estimate a sample covariance matrix should be at least one order of magnitude larger than the size of the data vector (up to 50 elements in our case).
+Furthermore, since the footprint associated with the removal of each jackknife region is different from the overall footprint, the method is also not able to recover the mode-coupling associated with the map geometry by construction.
 In order to verify and improve our estimate of the covariance matrix, we make use of a second analytical estimator.
@@
     where ${\rm Cov}^{\rm JK}$ and ${\rm Cov}^{\rm ana}$ are the jackknife and analytical covariance matrices respectively.
-\DA{We have verified that the resulting covariance matrices are well behaved (i.e.
-they are invertible, and their eigenvalues have a reasonable dynamical range).}
+We have verified that the resulting covariance matrices are well behaved (i.e.
+they are invertible, and their eigenvalues have a reasonable dynamical range).
 
@@
       where ${\bf T}$ is a vector containing the template $T_\ell$ for all the scales used in the analysis.
-Fig.\!~\ref{fig:clsyst} shows the shape of the plate template $T_\ell$ normalised by the best-fit value of the parameter $A$.
+Fig.\!~\ref{fig:clsyst} shows the shape of the plate template $T_\ell$ normalised by the best-fit value of the parameter $A$ assuming no intrinsic clustering.
 
@@
 
-      In particular, our interpretation of the $y\times \delta_g$ cross-correlation is especially sensitive to the width of the redshift distributions.
-This is because, while the amplitude to the galaxy auto-correlation is strongly affected by the width of the distribution (wider $p(z)$ reduce the clustering amplitude), the cross-correlation with $y$ is almost insensitive to it.
+      In particular, our model of the $y\times \delta_g$ cross-correlation is especially sensitive to the width of the redshift distributions.
+This is because, while the amplitude to the galaxy auto-correlation is strongly affected by the width of the distribution (wider $p(z)$s reduce the clustering amplitude), the cross-correlation with $y$ is almost insensitive to it.
 We therefore introduce an additional parameter $w_z$ that stretches the support of the redshift distribution while preserving unit total probability.
@@
 
-      \DA{Another possible source of systematic uncertainty is the effect of biased photometric redshifts (i.e.
+      Another possible source of systematic uncertainty is the effect of biased photometric redshifts (i.e.
 where $\langle z|z_{\rm photo}\rangle\neq z_{\rm photo}$).
@@
 Our results, however, are more sensitive to the distribution widths, and we find that this simple parametrisation is able to describe our data sufficiently well.
-We leave a more detailed analysis of the associated photometric redshift systematics for future work.}
+We leave a more detailed analysis of the associated photometric redshift systematics for future work.
 

### 2019-09-15 notes/paper/paper.tex
finished revision

@@
 Cosmic shear measurements are strongly affected by sub-grid baryonic physics, and by uncertainties in the processes by which galaxies acquire correlated intrinsic alignments \citep[e.g.][]{2001MNRAS.320L...7C,2002MNRAS.332..788M,2004PhRvD..70f3526H,2017MNRAS.465.2033J,2018PhRvD..98d3528T,2018arXiv181206076H,2018ARA&A..56..393M,2018arXiv181106989S}.
-Understanding the impact of baryons in the matter power spectrum will require a better understanding of the distribution of gas in halos.
+Understanding the impact of baryons in the matter power spectrum will require a better understanding of the distribution of gas in haloes.
 Finally, even though the clustering pattern of galaxies is one of the cosmological observables with the highest signal-to-noise ratio, the cosmological constraints that can be extracted from it are severely limited by our incomplete understanding of the galaxy-dark matter connection \citep[see e.g.][and references therein]{2018ARA&A..56..435W}.
@@
 In that case, the average number of satellites follows a power law of the form:
-      \begin{equation}
+      \begin{equation}\label{eq:hod1}
         \langle N_s(M)\rangle=N_c(M)\,\Theta(M-M_0)\,\left(\frac{M-M_0}{M_1'}\right)^{\alpha_s}.
@@
 
-  \begin{figure*}
-    \centering
-    \includegraphics[width=0.8\textwidth]{fits.pdf}
-    \caption{Measured galaxy auto-spectra (left column) and $\delta_g$-$y$ cross-spectra (right column) for the 6 galaxy redshift bins shown in Fig.\!~\ref{fig:dndz} in ascending order.
-Each panel shows the measurements (red points with error bars) and best-fit predictions (solid black lines) decomposed into their 1-halo and 2-halo contributions (green and blue lines).
-The right column additionally shows the estimated contamination from extragalactic dust (yellow squares with error bars), which is found to be negligible.
-The grey bands indicate the scales removed from the analysis.
-The bottom part of each panel shows the difference between data and theory normalised by the 1$\sigma$ uncertainties.}
-    \label{fig:cls}
-  \end{figure*}
-
-  \begin{figure*}
-    \centering
-    \includegraphics[width=0.27\textwidth]{cov_2mpz.pdf}
-    \includegraphics[width=0.27\textwidth]{cov_wisc1.pdf}
-    \includegraphics[width=0.27\textwidth]{cov_wisc2.pdf}
-    \includegraphics[width=0.27\textwidth]{cov_wisc3.pdf}
-    \includegraphics[width=0.27\textwidth]{cov_wisc4.pdf}
-    \includegraphics[width=0.27\textwidth]{cov_wisc5.pdf}
-    \caption{Correlation matrices for the 6 redshift bins used in the analysis.
-Each covariance matrix consists of 4 sub-matrices, corresponding to the covariances of $C^{gg}_\ell$ and $C^{gy}_\ell$ (block diagonals), as well as their cross-covariance.}
-    \label{fig:covs}
-  \end{figure*}
-
     \subsubsection{$C_\ell$-level deprojection}\label{sssec:methods.syst.plates}
@@
   \subsection{Likelihood}\label{ssec:methods.like} 
+  \begin{figure*}
+    \centering
+    \includegraphics[width=0.8\textwidth]{fits.pdf}
+    \caption{Measured galaxy auto-spectra (left column) and $\delta_g$-$y$ cross-spectra (right column) for the 6 galaxy redshift bins shown in Fig.\!~\ref{fig:dndz} in ascending order.
+Each panel shows the measurements (red points with error bars) and best-fit predictions (solid black lines) decomposed into their 1-halo and 2-halo contributions (green and blue lines).
+The right column additionally shows the estimated contamination from extragalactic dust (yellow squares with error bars), which is found to be negligible.
+The grey bands indicate the scales removed from the analysis.
+The bottom part of each panel shows the difference between data and theory normalised by the 1$\sigma$ uncertainties.}
+    \label{fig:cls}
+  \end{figure*}
+  \begin{figure*}
+    \centering
+    \includegraphics[width=0.27\textwidth]{cov_2mpz.pdf}
+    \includegraphics[width=0.27\textwidth]{cov_wisc1.pdf}
+    \includegraphics[width=0.27\textwidth]{cov_wisc2.pdf}
+    \includegraphics[width=0.27\textwidth]{cov_wisc3.pdf}
+    \includegraphics[width=0.27\textwidth]{cov_wisc4.pdf}
+    \includegraphics[width=0.27\textwidth]{cov_wisc5.pdf}
+    \caption{Correlation matrices for the 6 redshift bins used in the analysis.
+Each covariance matrix consists of 4 sub-matrices, corresponding to the covariances of $C^{gg}_\ell$ and $C^{gy}_\ell$ (block diagonals), as well as their cross-covariance.}
+    \label{fig:covs}
+  \end{figure*}
   \begin{table}
@@
 
-      \begin{figure*}
-        \centering
-        \includegraphics[width=0.55\textwidth]{fiducial_wisc3.pdf}
-        \caption{68\% and 95\% contours for the model parameters in the third WI$\times$SC redshift bin.}
-        \label{fig:triangle}
-      \end{figure*}
-
-      \begin{figure*}
-        \centering
-        \includegraphics[width=0.7\textwidth]{bhydro.pdf}
-        \caption{Summary figure showing our constraints on the tSZ mass bias $1-\bH$.
-Our fiducial constrains are shown as black circles with error bars, and are centred at the mean redshift of each sample.
-The grey circles show the same constraints found using the NILC $y$ map, which are in good agreement with our fiducial results.
-The red downward-pointing triangles show the constraints found fixing the photo-$z$ width parameter $w_z$.
-They are in good agreement with our fiducial measurements, with $\sim20\%$ smaller error bars.
-The burgundy squares show the results found using the 2010 Tinker mass function, which are systematically biased low.
-The orange diamond and the mesh show our combined, redshift-independent constraint on $1-\bH$.
-For comparison, the grey and turquoise bands show the constraints on the mass bias found by combining cluster counts and CMB primary \citep{2016A&A...594A..24P} as well as the constraints using CMB lensing to calibrate cluster masses \citep{2019arXiv190407887Z}, respectively.
-The top panel shows the normalised redshift distributions for the six redshift bins, for reference.}
-        \label{fig:bh}
-      \end{figure*}
-
 \section{Results}\label{sec:results}
@@
         \centering
-        \includegraphics[width=0.7\textwidth]{by.pdf}
-        \caption{Summary figure showing our constraints on the bias-weighted thermal pressure $\langle bP_e\rangle$.
-Our measurements are shown as blue circles with error bars and a `violin' background.
-The circle and error bars show the peak value and 68\% confidence interval, while the violins show the full 1D posterior distribution.
-The grey lines show the predictions of the shock-heating model of \citet{2012ApJ...758...75B} for different values of the $r_{\rm max}$ threshold cluster radius (see legend).
-For comparison, the figure also shows the constraints on the same parameter found by \citet{2017MNRAS.467.2315V} (black) and \citet{2019arXiv190413347P} (red and green).}
-        \label{fig:by}
+        \includegraphics[width=0.6\textwidth]{fiducial_wisc3.pdf}
+        \caption{68\% and 95\% contours for the model parameters in the third WI$\times$SC redshift bin.}
+        \label{fig:triangle}
+      \end{figure*}
+
+      \begin{figure*}
+        \centering
+        \includegraphics[width=0.7\textwidth]{bhydro.pdf}
+        \caption{Summary figure showing our constraints on the tSZ mass bias $1-\bH$.
+Our fiducial constrains are shown as black circles with error bars, and are centred at the mean redshift of each sample.
+The grey circles show the same constraints found using the NILC $y$ map, which are in good agreement with our fiducial results.
+The red downward-pointing triangles show the constraints found fixing the photo-$z$ width parameter $w_z$.
+They are in good agreement with our fiducial measurements, with $\sim20\%$ smaller error bars.
+The burgundy squares show the results found using the 2010 Tinker mass function, which are systematically biased low.
+The orange diamond and the mesh show our combined, redshift-independent constraint on $1-\bH$.
+For comparison, the grey and turquoise bands show the constraints on the mass bias found by combining cluster counts and CMB primary \citep{2016A&A...594A..24P} as well as the constraints using CMB lensing to calibrate cluster masses \citep{2019arXiv190407887Z}, respectively.
+The top panel shows the normalised redshift distributions for the six redshift bins, for reference.}
+        \label{fig:bh}
       \end{figure*}
@@
 The overall best-fit value of $1-\bH$ is provided in column 3 of the same Table.
-Columns 6 and 7 of the same table list the reduced $\chi^2$ values for each sample and their associated probability-to-exceed (PTE), respectively.
+Columns 6 and 7 list the reduced $\chi^2$ values for each sample and their associated probability-to-exceed (PTE), respectively.
 In all cases we find that the model described in Section \ref{sec:theory} is able to describe the data with no evidence for a significant statistical tension.
@@
       We see that, while we are able to measure $1-\bH$ to a reasonable accuracy ($\sim12\%$) in all of the \wisc~ redshift bins, the sensitivity for the 2MPZ sample is much poorer.
-This is not entirely unexpected: even though the cross-correlation between the Compton-$y$ map and the 2MPZ catalogue yields the highest signal-to-noise of all the samples used here, the low-redshift range covered by this sample implies that the signal is strongly dominated by the one-halo term.
+This is not entirely unexpected: even though the cross-correlation between the Compton-$y$ map and the 2MPZ catalogue yields the highest signal-to-noise ratio of all the samples used here, the low-redshift range covered by this sample implies that the signal is strongly dominated by the one-halo term.
 This can be seen in the top right panel of Fig.\!~\ref{fig:cls}.
@@
 In turn, the grey band in the same figure shows the constraints on $1-\bH$ found by combining tSZ cluster counts and the $TT$ CMB power spectrum measured by \planck\ \citep{2016A&A...594A..24P} ($1-\bH=0.58\pm0.04$).
-This is the value of $1-\bH$ needed to explain the amplitude of density perturbations predicted by the CMB in comparison with the abundance of massive clusters.
+This is the value of $1-\bH$ needed to simultaneously explain the amplitude of density perturbations predicted by the CMB and the abundance of massive clusters.
 Our measurements are visually in agreement with both of these estimates, which themselves are not in significant tension with one another.
@@
       \end{equation}
-      At this point it is worth acknowledging that this estimate $\bar{b}_{\rm H}$ is only strictly consistent if the posterior distribution of the $b_{{\rm H},i}$ is Gaussian.
+      At this point it is worth acknowledging that this estimate of $\bar{b}_{\rm H}$ is only strictly consistent if the posterior distribution of the $b_{{\rm H},i}$ is Gaussian.
 We find that, with the exception of the 2MPZ sample, which has a comparatively small statistical power, the marginalised distributions in all redshift bins are sufficiently well-behaved that this is a reasonable approximation (e.g.
@@
 The preferred value of $1-\bar{b}_{\rm H}$ found also agrees with the results of \cite{2018MNRAS.480.3928M} in cross-correlation with galaxies at very low redshift, and those of \cite{2019arXiv190707870M} using weak-lensing cross-correlations at higher $z$.
+      \begin{figure*}
+        \centering
+        \includegraphics[width=0.7\textwidth]{by.pdf}
+        \caption{Summary figure showing our constraints on the bias-weighted thermal pressure $\langle bP_e\rangle$.
+Our measurements are shown as blue circles with error bars and a `violin' background.
+The circle and error bars show the peak value and 68\% confidence interval, while the violins show the full 1D posterior distribution.
+The grey lines show the predictions of the shock-heating model of \citet{2012ApJ...758...75B} for different values of the $r_{\rm max}$ threshold cluster radius (see legend).
+For comparison, the figure also shows the constraints on the same parameter found by \citet{2017MNRAS.467.2315V} (black) and \citet{2019arXiv190413347P} (red and green).}
+        \label{fig:by}
+      \end{figure*}
 
-      \DA{Since the amplitudes of the galaxy auto-correlation and the galaxy-$y$ cross-correlation are both affected by the value of $\sigma_8$, which we have fixed to the best-fit value found by \planck\, the fact that the value of $1-\bH$ we find is compatible with that found by \cite{2016A&A...594A..24P} is not surprising.
+      Since the amplitudes of the galaxy auto-correlation and the galaxy-$y$ cross-correlation are both affected by the value of $\sigma_8$, which we have fixed to the best-fit value found by \planck, the fact that the value of $1-\bH$ we find is compatible with that found by \cite{2016A&A...594A..24P} is not surprising.
 In other words, this agreement can be understood as a evidence of the compatibility between the best-fit \planck\ cosmology and the clustering properties of galaxies and thermal pressure in the datasets used here.
 The corresponding best-fit value of $1-\bH\simeq0.6$ is at odds with the expectation from hydrodynamical simulations \citep{2016ApJ...827..112B} and some direct calibration efforts \citep[e.g.][]{2016MNRAS.456L..74S,2019A&A...621A..40E}, which seem to prefer smaller missing mass fractions ($1-\bH\simeq0.8$).
-A possible resolution of the mild tension between tSZ cluster count and CMB data could be the presence of new physics that modify the late-time expansion and structure growth.
+A possible resolution of the mild tension between tSZ cluster counts and CMB data could be the presence of new physics that modify the late-time expansion and structure growth.
 However, most of these modifications (e.g.
 a one-parameter excursion where the dark energy equation of state takes a larger value $w\sim-0.7$) would make the existing tension in the value of the local expansion rate between CMB and local measurements \citep{2019ApJ...876...85R} worse.
-A careful study of all possibilities, invoking both non-standard physics and more sophisticated astrophysical models, together with improved datasets, is therefore necessary before this tension can be fully resolved.}
+A careful study of all possibilities, invoking both non-standard physics and more sophisticated astrophysical models, together with improved datasets, is therefore necessary before this tension can be fully resolved.
 
     \subsubsection{Tomographic measurement of thermal gas pressure}\label{ssec:results.fid.bpe}
-      So far we have presented our constraints in terms of a the mass-bias parameter $1-\bH$, since this is the main source of systematic uncertainty in the cosmological analysis of cluster number counts carried out by Planck.
+      So far we have presented our constraints in terms of a the mass-bias parameter $1-\bH$, since this is the main source of systematic uncertainty in the cosmological analysis of cluster number counts carried out by \planck.
 However, the physical interpretation of this parameter (the fraction of missing mass estimated from X-ray measurements under the assumption of hydrostatic equilibrium) is not directly related to the physical process that allows us to constrain it through the cross-correlation of $y$ and $\delta_g$: the fact that galaxy density and pressure trace the same underlying dark-matter fluctuations.
@@
 
-      We derive constraints on $\langle bP_e\rangle$ from our data by reprocessing our Monte-Carlo chains, computing $\langle bP_e\rangle$ at each sample to find its marginalised posterior distribution.
+      We derive constraints on $\langle bP_e\rangle$ from our data by reprocessing our Monte-Carlo chains, computing $\langle bP_e\rangle$ at each sample to find its 1D posterior distribution.
 The results are shown in Fig.\!~\ref{fig:by}, together with the measurements of \cite{2017MNRAS.467.2315V} and \cite{2019arXiv190413347P}.
@@
 As a visual aid to evaluate the agreement of our results with these models, the predictions for $N=2,\,3,\,5$ and $\infty$ are shown as solid, dashed, dot-dashed and dotted grey lines respectively in Fig.\!~\ref{fig:by}.
-\DA{These results demonstrate the most precise measurement of this quantity to date.
-The main factors that contribute to this constraining power are the larger amplitude of the tSZ signal towards low redshifts and the high density of tracers in the 2MPZ and \wisc\ samples.}
+These results are the most precise measurement of this quantity to date.
+The main factors that contribute to the improved constraining power are the larger amplitude of the tSZ signal towards low redshifts and the high density of tracers in the 2MPZ and \wisc\ samples.
 
@@
 The extragalactic component, the so-called Cosmic Infrared Background (CIB), is however a more relevant concern, given that it traces the large-scale structure, and is therefore statistically correlated with both of our observables ($\delta_g$ and $y$).
-Since the CIB is most relevant near the peak of star formation ($z\sim2$), we expect this contamination to be small, but it must however be quantified carefully.
+Since the CIB is most relevant near the peak of star formation ($z\sim2$), we expect this contamination to be small, but it must be quantified carefully.
 
@@
       \end{equation}
-      For this exercise, in order to reduce the noise variance from the Galactic component of the 545 GHz map, the cross-correlations $C^{yc,{\rm obs}}_\ell$ and $C^{gc}_\ell$ were estimated using Planck's 20\% Galactic mask.
+      For this exercise, in order to reduce the noise variance from the Galactic component of the 545 GHz map, the cross-correlations $C^{yc,{\rm obs}}_\ell$ and $C^{gc}_\ell$ were estimated using \planck's 20\% Galactic mask.
 Additionally, all uncertainties were estimated using the jackknife method described in Section \ref{ssec:methods.cov}.
@@
 The results are shown in Fig.
-\ref{fig:bh} as red down-pointing triangles.
+\ref{fig:bh} as red downward-pointing triangles.
 We observe that the only effect of allowing $w_z$ to vary is to increase the final uncertainties on $1-\bH$ by about $20\%$.
@@
 
+    \subsubsection{Galaxy clustering model}\label{sssec:results.syst.gc}
+      To verify that our results are robust against the details of the HOD model used to parametrise the galaxy-matter connection, we have repeated the analysis for extended versions of our baseline model.
+We explore two such extensions:
+      \begin{itemize}
+        \item We include the threshold width for centrals $\sigma_{\rm lnM}$ as an additional free parameter with a broad top-hat prior, instead of fixing it to the value used by \cite{2018MNRAS.473.4318A}.
+        \item We decouple central and satellite galaxies, allowing for haloes without a central galaxy to contain satellites.
+This implies removing the factor $N_c(M)$ in Eq.
+\ref{eq:hod1} and introducing $M_0$ (the mass threshold to have satellites) as a new free parameter that is not linked to $M_{\rm min}$.
+      \end{itemize}
+      In both cases we have confirmed that the constraints derived on $1-\bH$ do not deviate significantly from our fiducial results, and that our data are not able to constrain the new free HOD parameters introduced by each extension ($\sigma_{\rm lnM}$ and $M_0$ respectively).
+We therefore conclude that our results are insensitive to the specifics of the model used to characterise the clustering of galaxies, which is well described in the range of scales studied here by our fiducial 2-parameter HOD model .
+
 \section{Conclusion}\label{sec:conclusion}
   Cross-correlating maps of the tSZ Compton-$y$ parameter with tomographic measurements of the projected galaxy distribution allows us to study the redshift evolution of the thermal gas pressure, since we expect both pressure and galaxies to trace the same underlying matter inhomogeneities.
-We have measured the $\delta_g$-$y$ cross-correlation to very high significance using the public $y$ maps made available by the Planck collaboration \citep{2016A&A...594A..22P} and the 2MPZ and \wisc~ galaxy catalogues \citep{2014ApJS..210....9B,2016ApJS..225....5B} in six photometric redshift bins covering the redshift range $z\lesssim0.4$.
+We have measured the $\delta_g$-$y$ cross-correlation to very high significance using the public $y$ maps made available by the \planck\ collaboration \citep{2016A&A...594A..22P} and the 2MPZ and \wisc~ galaxy catalogues \citep{2014ApJS..210....9B,2016ApJS..225....5B} in six photometric redshift bins covering the redshift range $z\lesssim0.4$.
 
   Combining this measurement with a measurement of the galaxy auto-correlation allows us to break the degeneracy between the two parameters that relate $\delta_g$ and $y$ to the matter fluctuations: the galaxy bias, which we model effectively using a 2-parameter HOD prescription, and the mass bias parameter $1-\bH$, thus enabling us to make a redshift-dependent measurement of $1-\bH$.
-The results, shown in Table \ref{tab:results} and Fig.\!~\ref{fig:bh}, agree well with the measurements of $1-\bH$ made by \planck\ through the combination of cluster number counts and CMB primary anisotropies \citep{2016A&A...594A..24P}, as well as with the calibration of tSZ cluster masses with CMB lensing measurements \citep{2019arXiv190407887Z}, and with similar measurements of $1-\bH$ made by \cite{2018MNRAS.480.3928M} through the same type of cross-correlation but at much lower redshifts.
+The results, shown in Table \ref{tab:results} and Fig.\!~\ref{fig:bh}, agree well with the measurements of $1-\bH$ made by \planck\ through the combination of cluster number counts and CMB primary anisotropies \citep{2016A&A...594A..24P}, as well as with the calibration of tSZ cluster masses with CMB lensing measurements \citep{2019arXiv190407887Z}, and with similar measurements of $1-\bH$ made by \cite{2018MNRAS.480.3928M} through the same type of cross-correlation at lower redshifts.
 More importantly, our tomographic measurement allows us to study the possible redshift dependence of the mass bias, an important ingredient in the cosmological analysis of cluster abundances.
-Given our uncertainties, we do not find any statistical evidence for a redshift dependence of $1-\bH$, in agreement with previous analyses \citep{2019A&A...626A..27S}.
-\DA{A reliable interpretation of the low value of this parameter ($1-\bH\simeq0.6$) when compared with direct calibration studies and numerical simulations, requires a more careful study of different possible model as well as other datasets.}
+Within our uncertainties, we do not find any statistical evidence for a redshift dependence of $1-\bH$, in agreement with previous analyses \citep{2019A&A...626A..27S}.
+A reliable interpretation of the low value of this parameter ($1-\bH\simeq0.6$) when compared with direct calibration studies and numerical simulations, requires a more careful study of different possible models as well as other datasets.
 
@@
 
-  \todo{ Nevertheless, we have confirmed that decoupling $M_0$ and $M_{\rm min}$, and allowing haloes to contain solely satellites, does not yield any statistically significant offset from our fiducial scenario.
-We have also tested the effect of freeing-up $\sigma_{\rm lnM}$, and confirmed that the measurements we obtain are almost identical to our fiducial results.}
-
 \section*{Acknowledgements}

### 2019-09-15 notes/paper/paper.tex
few changes

@@
   \date{\today}
-  \pagerange{1--18} \pubyear{2018}
+  \pagerange{1--18} \pubyear{2019}
   \maketitle
@@
 Cosmic shear measurements are strongly affected by sub-grid baryonic physics, and by uncertainties in the processes by which galaxies acquire correlated intrinsic alignments \citep[e.g.][]{2001MNRAS.320L...7C,2002MNRAS.332..788M,2004PhRvD..70f3526H,2017MNRAS.465.2033J,2018PhRvD..98d3528T,2018arXiv181206076H,2018ARA&A..56..393M,2018arXiv181106989S}.
-Understanding the impact of baryons in the matter power spectrum will require a better understanding of the distribution of gas in haloes.
+Understanding the impact of baryons in the matter power spectrum requires a better understanding of the distribution of gas in haloes.
 Finally, even though the clustering pattern of galaxies is one of the cosmological observables with the highest signal-to-noise ratio, the cosmological constraints that can be extracted from it are severely limited by our incomplete understanding of the galaxy-dark matter connection \citep[see e.g.][and references therein]{2018ARA&A..56..435W}.
@@
   In this work we focus on the cross-correlation between galaxy clustering data and maps of the tSZ Compton-$y$ parameter, making use of existing data from the \planck\ collaboration \citep{2016A&A...594A..22P} and a set of photometric galaxy surveys \citep{2014ApJS..210....9B,2016ApJS..225....5B}.
-The availability of redshift information will allow us to place constraints on the cosmic evolution of the thermal gas pressure and the thermal energy in haloes, as well as to examine any redshift dependence of the mass bias for tSZ cluster studies.
+The availability of redshift information allows us to place constraints on the cosmic evolution of the thermal gas pressure and the thermal energy in haloes, as well as to examine any redshift dependence of the mass bias for tSZ cluster studies.
 This is a relevant topic given the current mild tensions between SZ cluster number counts and CMB primary anisotropies \citep{2016A&A...594A..24P,2016ApJ...832...95D,2019ApJ...878...55B,2019arXiv190407887Z}, which could be caused by the assumptions made to model the $y$-mass relation.
@@
 This assumption breaks down in cases such as mergers, where centrals have not been established yet.
-We will however explore departures from this fiducial model.
+We however explore departures from this fiducial model.
 
@@
 $1-\bH\simeq0.8$: \citejap{2012ApJ...758...74B}; \citejap{2014ApJ...782..107N}), although it is known that a smaller value is needed in order to fully reconcile CMB primary constraints and SZ cluster counts \citep{2016A&A...594A..24P}.
-This will be a central point of our discussion in Sections \ref{sec:results} and \ref{sec:conclusion}.
+This is a central point of our discussion in Sections \ref{sec:results} and \ref{sec:conclusion}.
 
@@
     \end{figure}
-    We make use of of the Compton-$y$ parameter maps made public by the \planck\ collaboration \citep{2016A&A...594A..22P}.
+    We make use of the Compton-$y$ parameter maps made public by the \planck\ collaboration \citep{2016A&A...594A..22P}.
 These maps were generated using different flavours of the Internal Linear Combination method \citep{2004ApJ...612..633E,2008arXiv0811.4277V}.
@@
     The MILCA and NILC maps have been found to be in good agreement in different studies, although the NILC map has a higher noise level on large scales \citep{2016A&A...594A..22P}.
-We thus use the MILCA map as our fiducial Compton-$y$ map, but will repeat our analysis on the NILC map as part of our systematics analysis.
+We thus use the MILCA map as our fiducial Compton-$y$ map, but repeat our analysis on the NILC map as part of our systematics analysis.
 We use a fiducial mask for the $y$ maps based on a combination of the \planck\ 60\% Galactic mask and the union of the HFI and LFI point source masks (see top panel of Fig.\!~\ref{fig:msk}).
@@
 We then combine this with the correlation matrix estimated with our analytical method.
-This ensures that our estimator accounts for the coupling between different modes caused by survey geometry and non-Gaussianities while avoiding the the statistical noise in the jackknife estimator.
+This ensures that our estimator accounts for the coupling between different modes caused by survey geometry and non-Gaussianities while avoiding the statistical noise in the jackknife estimator.
 The final covariance is therefore:

### 2019-09-17 plot_fits.py
figure cosmetics

@@ -183,6 +183,7 @@ for s, v in enumerate(p.get("data_vectors")):
         ax1.set_xlim(lsg[i][0]/1.1, lsg[i][-1]*1.1)
         ax2.set_xlim(ax1.get_xlim())
         ax2.set_ylim(res[mask].min()-1, res[mask].max()+1)
+        ax2.set_ylim(-2.7, 2.7)        
 
         # flip one data point start & end to draw line
         if not mask[0]: mask[np.where(mask == True)[0][0]] = False
@@ -219,7 +220,7 @@ for s, v in enumerate(p.get("data_vectors")):
         ax2.axvspan(lmax, ax1.get_xlim()[1], color="grey", alpha=0.2)
 
         if i == 0:
-            ax1.text(0.02, 0.06, sci[s]+"\n"+"$\\chi^2/N_{d}=%.2lf/%d$" %
+            ax1.text(0.02, 0.06, sci[s]+"\n"+"$\\chi^2/N_{\\rm{d}}=%.2lf/%d$" %
                      (chi2, dof), transform=ax1.transAxes)
 
             ax1.set_ylabel('$C_\\ell$', fontsize=15)
@@ -232,7 +233,8 @@ for s, v in enumerate(p.get("data_vectors")):
             if i == 1:
                 ax1.text(0.45, 1.1, r"$y \times g$", fontsize=15,
                          transform=ax1.transAxes)
-                ax1.legend(loc="lower center", ncol=4, fontsize=8)
+                ax1.legend(loc="lower center", ncol=4, fontsize=8,
+                           borderaxespad=0.1, columnspacing=1.9)
 
         if s != len(surveys)-1:
             ax2.get_xaxis().set_visible(False)

### 2019-09-17 notes/paper/paper.tex
minor corr + final fits fig

@@
 We use the nearly full-sky 2MASS Photometric Redshift and WISE $\times$ SuperCOSMOS public catalogues, covering the redshift range $z\lesssim0.4$.
-Our measurements allow us to place constraints on the redshift dependence of the mass-observable relation for tSZ cluster count analysis in terms of the so-called `hydrostatic bias' parameter $1-\bH$.
+Our measurements allow us to place constraints on the redshift dependence of the mass-observable relation for tSZ cluster count analyses in terms of the so-called `hydrostatic mass bias' parameter $1-\bH$.
 These results can also be interpreted as measurements of the bias-weighted average gas pressure $\langle bP_e\rangle$ as a function of redshift, a quantity that can be related to the thermodynamics of gas inside haloes and used to constrain energy injection processes.
 We measure $1-\bH$ with $\sim13\%$ precision in 6 equispaced redshift bins, and find no evidence for a redshift-dependent mass bias parameter, in agreement with previous analyses.
-Our mean value of $1-\bH = 0.59\pm0.03$ is also in good agreement with that estimated by the joint analysis of \planck\ cluster counts and CMB anisotropies.
+Our mean value of $1-\bH = 0.59\pm0.03$ is also in good agreement with the one estimated by the joint analysis of \planck\ cluster counts and CMB anisotropies.
 Our measurements of $\langle bP_e\rangle$, at the level of $\sim10\%$ in each bin, are the most stringent constraints on the redshift dependence of this parameter to date, and agree well both with previous measurements and with theoretical expectations from shock-heating models.
@@
 Cosmic shear measurements are strongly affected by sub-grid baryonic physics, and by uncertainties in the processes by which galaxies acquire correlated intrinsic alignments \citep[e.g.][]{2001MNRAS.320L...7C,2002MNRAS.332..788M,2004PhRvD..70f3526H,2017MNRAS.465.2033J,2018PhRvD..98d3528T,2018arXiv181206076H,2018ARA&A..56..393M,2018arXiv181106989S}.
-Understanding the impact of baryons in the matter power spectrum requires a better understanding of the distribution of gas in haloes.
+Understanding the impact of baryons on the matter power spectrum requires better knowledge of the distribution of gas in haloes.
 Finally, even though the clustering pattern of galaxies is one of the cosmological observables with the highest signal-to-noise ratio, the cosmological constraints that can be extracted from it are severely limited by our incomplete understanding of the galaxy-dark matter connection \citep[see e.g.][and references therein]{2018ARA&A..56..435W}.
@@
 
-  The CMB secondary anisotropies, in particular the thermal and kinetic Sunyaev-Zeldovich effects \citep[tSZ and kSZ respectively,][]{1972CoASP...4..173S}, as well as the gravitational lensing of the CMB photons, have gained popularity as a means to address these issues \citep{2017JCAP...11..040B,2019BAAS...51c.297B}.
-These effects are relatively clean probes of some of the physical quantities that need to be understood in order to mitigate the impact of astrophysical uncertainties: the matter and gas densities, the gas pressure and the velocity field.
+  The CMB secondary anisotropies, in particular the thermal and kinetic Sunyaev-Zeldovich effects \citep[tSZ and kSZ respectively,][]{1972CoASP...4..173S}, as well as the gravitational lensing of CMB photons, have gained popularity as a means to address these issues \citep{2017JCAP...11..040B,2019BAAS...51c.297B}.
+These effects are relatively clean probes of some of the physical quantities that need to be understood in order to mitigate the impact of astrophysical uncertainties: the matter and gas densities, the gas pressure, and the velocity field.
 Since these observables are also sensitive to cosmology, their combination with large-scale structure data can be extremely powerful at disentangling astrophysical and cosmological parameters.
@@
 
-    The angular power spectrum can be related to the 3D power spectrum of the associated 3D fields $P_{UV}$ as\footnote{Note that Eq.\!~\ref{eq:cllimber} is only valid in the {\sl Limber approximation} \citep{1953ApJ...117..134L,1992ApJ...388..272K}, which is accurate for broad radial kernels.
+    The angular power spectrum can be related to the 3D power spectrum of the associated 3D fields $P_{UV}$ via\footnote{Note that Eq.\!~\ref{eq:cllimber} is only valid in the {\sl Limber approximation} \citep{1953ApJ...117..134L,1992ApJ...388..272K}, which is accurate for broad radial kernels.
 This approximation is adequate for the redshift distributions and scales used here.}:
@@
     \end{equation}
-    The halo model prediction for the cross-power spectrum $P_{UV}$ then consists of two contributions, from the so-called 1-halo term and 2-halo term:
+    The halo model prediction for the cross-power spectrum $P_{UV}$ then consists of two contributions, the so-called 1-halo term and 2-halo term:
     \begin{equation}
@@
     It is important to note that the halo model is inaccurate in the range of scales corresponding to the transition between the 1-halo and 2-halo-dominated regimes.
-This is a well-known effect \citep{2015MNRAS.454.1958M}, and we correct for it here simply by multiplying all halo-model power spectra by a universal scale-dependent factor, given by the ratio between the revised {\sl halofit} prediction for the matter power spectrum of \cite{2012ApJ...761..152T} and the pure halo-model prediction for the same quantity
+This is a well-known effect \citep{2015MNRAS.454.1958M}, and we correct for it here simply by multiplying all halo-model power spectra by a universal scale-dependent factor, given by the ratio between the revised {\sl Halofit} prediction for the matter power spectrum of \cite{2012ApJ...761..152T} and the pure halo-model prediction for the same quantity
     \begin{equation}
@@
 This assumption breaks down in cases such as mergers, where centrals have not been established yet.
-We however explore departures from this fiducial model.
+We however explore departures from the fiducial model.
 
       Besides their mean values, we also need to specify the statistics of $N_c$ and $N_s$.
-Following the standard practice \citep{2013MNRAS.430..725V}, we assume $N_c$ to have a Bernoulli distribution with probability $p=\langle N_c\rangle$, and $N_s$ to be Poisson-distributed.
+Following standard practice \citep{2013MNRAS.430..725V}, we assume $N_c$ to have a Bernoulli distribution with probability $p=\langle N_c\rangle$, and $N_s$ to be Poisson-distributed.
 
@@
       \end{equation} 
-      and we have suppressed the mass dependence of all quantities for brevity.
+      where we have suppressed the mass dependence of all quantities for brevity.
 
-      Finally, we assume that the satellites follow the matter distribution, and therefore $u_s(k|M)$ is given by a truncated Navarro, Frenk and White profile \citep{1996ApJ...462..563N}:
+      Finally, we assume that the satellites follow the matter distribution, and therefore $u_s(k|M)$ is given by a truncated Navarro, Frenk \& White profile \citep{1996ApJ...462..563N}:
       \begin{align}
@@
         P_*=6.41\,\left(1.65\,\, {\rm eV}\,{\rm cm}^{-3}\right)h_{70}^{8/3}
-        \left(\frac{h_{70}(1-\bH)M_{500c}}{3\times10^{14}M_\odot}\right)^{0.79},
+        \left(\frac{h_{70}(1-\bH)M_{500c}}{3\times10^{14}{\rm M_\odot}}\right)^{0.79},
       \end{equation}
@@
       \end{equation}
-      Common choices for $\rho_*$ are the critical density, $\rho_c=3H^2(z)/4\pi G$, or the matter density, $\rho_M(z)$.
-The spherical overdensity parameter $\Delta$ is usually chosen within the range $\sim(200,500)$ and sometimes defined as the quantity yielding the virial radius in the spherical top-hat collapse model $\Delta_v$ \citep{1998ApJ...495...80B}.
+      Common choices for $\rho_*$ are the critical density, $\rho_c=3H^2(z)/8\pi G$, or the matter density, $\rho_M(z)$.
+The spherical overdensity parameter, $\Delta$, is usually chosen within the range $\sim(200,500)$ and sometimes defined as the quantity yielding the virial radius in the spherical top-hat collapse model, $\Delta_v$ \citep{1998ApJ...495...80B}.
 
@@
       \end{equation}
-      with $M_{\rm pivot}=2.7\times10^{12}\,M_\odot$ and $(A,B,C)=(3.67,\,-0.0903,\,-0.51)$.
+      with $M_{\rm pivot}=2.7\times10^{12}\,{\rm M_\odot}$ and $(A,B,C)=(3.67,\,-0.0903,\,-0.51)$.
 
@@
 These maps were generated using different flavours of the Internal Linear Combination method \citep{2004ApJ...612..633E,2008arXiv0811.4277V}.
-In a simplified description, the ILC technique selects the linear combination of all frequency channels that preserves the spectrum of the source one wishes to map minimising the map-level variance.
+In a simplified description, the ILC technique selects the linear combination of all frequency channels that preserves the spectrum of the source one wishes to map, minimising the map-level variance.
 The refined versions of the ILC method used by \planck\ further optimise the linear weights on different scales and different regions of the map, and project out sources with known spectra that are likely to cause significant contamination.
@@
     We make use of two low-redshift photometric redshift (photo-$z$) catalogues, the 2MASS Photometric Redshift catalogue \citep[2MPZ,][]{2014ApJS..210....9B} and the WISE $\times$ SuperCOSMOS catalogue \citep[\wisc,][]{2016ApJS..225....5B}.
-Both samples were created by cross-matching full-sky imaging surveys, and photo-$z$s were subsequently computed for all the included sources.
-Their broad photometric coverage, together with adequate spectroscopic calibration data allowed for well-constrained photo-$z$s, with minimal mean bias, relatively low scatter and a small number of outliers.
+Both samples were created by cross-matching full-sky imaging surveys, and photo-$z$'s were subsequently computed for all the included sources.
+Their broad photometric coverage, together with adequate spectroscopic calibration data allows for well-constrained photo-$z$'s, with minimal mean bias, relatively low scatter and a small number of outliers.
 
@@
 After applying an apparent magnitude cut $K_s<13.9$ to achieve uniformity, 2MPZ includes over 940,000 sources observed in 8 bands: SuperCOSMOS's optical $(B,R,I)$, 2MASS's near-infrared $(J,H,K_s)$ and WISE's mid-infrared $(W1,W2)$.
-Photometric redshifts (photo-$z$s) were extracted using the neural network code ANNz \citep{2004PASP..116..345C} trained on a large spectroscopic sample from overlapping surveys.
+Photometric redshifts were extracted using the neural network code {\tt ANNz} \citep{2004PASP..116..345C} trained on a large spectroscopic sample from overlapping surveys.
 The resulting photo-$z$'s have a typical error $\sigma_z\simeq0.015$, and the sample has a median redshift $z\simeq0.08$ (see also \citealt{2018MNRAS.476.1050B} for a more detailed analysis of the 2MPZ photo-$z$ properties).
@@
 The photometric redshifts are less accurate, given the poorer photometric coverage $(B,\,R,\,W1,\,W2)$, with a mean error $\sigma_z/(1+z)\simeq0.035$.
-We divide the \wisc~ sample into 5 redshift bins, corresponding to photo-$z$ intervals of equal width $\delta z_{\rm photo}=0.05$ in the range $0.1<z_{\rm photo}<0.35$.
+We divide the \wisc~ sample into 5 redshift bins, corresponding to photo-$z$ intervals of equal width $\delta z_{\rm photo}=0.05$ in the range $0.10<z_{\rm photo}<0.35$.
 Details regarding each of these redshift bins are given in Table \ref{tab:z_bins}, and the corresponding redshift distributions are shown in Fig.\!~\ref{fig:dndz}.
@@
 
-    Although the jackknife method is able to provide an estimate of the size of the power spectrum uncertainties in a model independent way, it also has some drawbacks.
-There are only so many jackknife regions that can be selected with a reasonable size, and therefore the estimated covariance is noisy at some level.
+    Although the jackknife method is able to provide an estimate of the size of the power spectrum uncertainties in a model independent way, it has some drawbacks.
+There are only so many jackknife regions of reasonable size that can be selected; therefore the estimated covariance is noisy at some level.
 Typically, the number of independent realisations used to estimate a sample covariance matrix should be at least one order of magnitude larger than the size of the data vector (up to 50 elements in our case).
@@
       \caption{Diagonals of the covariance matrix for the $\delta_g\times y$ cross-correlation in the second \wisc~redshift bin.
-Black and red lines show the analytic and jackknife covariances respectively.
+Black and red lines show the analytical and jackknife covariances respectively.
 The solid and dashed lines show the zeroth-order ($i=j$) and first-order ($i=j+1$) diagonals respectively.
@@
 
-    Fig.\!~\ref{fig:covdiag} shows the diagonal of the covariance matrix for one of the tSZ-galaxy power spectra estimated using these two methods.
+    Fig.\!~\ref{fig:covdiag} shows the diagonal of the covariance matrix for one of the galaxy-tSZ power spectra estimated using these two methods.
 We find that both estimators are in good agreement with each other.
-We construct our final fiducial covariance matrix as a hybrid of both estimators: in order to ensure that we recover realistic error bar sizes, we use the variance estimated from the jackknives.
-We then combine this with the correlation matrix estimated with our analytical method.
+We construct our final fiducial covariance matrix using both estimators: in order to ensure that we recover realistic error bar sizes, we use the variance estimated from the jackknives, and then combine it with the correlation matrix estimated analytically.
 This ensures that our estimator accounts for the coupling between different modes caused by survey geometry and non-Gaussianities while avoiding the statistical noise in the jackknife estimator.
@@
         {\bf m}_{\rm obs}={\bf m}_{\rm true} + \epsilon\,{\bf t}.
-      \end{equation}
+      \end{equation}\label{eq:deproj}
       Here ${\bf m}_{\rm obs}$ and ${\bf m}_{\rm true}$ are vectors corresponding to the observed sky map and the true underlying quantity we wish to map respectively, ${\bf t}$ is a template map describing the contaminant (e.g.
 a map of the Galactic dust fluctuations), and $\epsilon$ is an unknown amplitude.
-In order to fully account for the effects of this contaminant one would build a likelihood for ${\bf m}_{\rm obs}$ using the equation above as a model (together with a model for ${\rm m}_{\rm true}$) and marginalise over $\epsilon$.
+In order to fully account for the effects of this contaminant one has to build a likelihood for ${\bf m}_{\rm obs}$ using the Eq.
+\ref{eq:deproj} as a model (together with a model for ${\rm m}_{\rm true}$) and marginalise over $\epsilon$.
 As shown in \cite{2017MNRAS.465.1847E} and \cite{2019MNRAS.484.4127A}, within the pseudo-$C_\ell$ framework, this can be done exactly by projecting ${\bf m}_{\rm obs}$ onto the subspace perpendicular to ${\bf t}$ or, in other words, by `deprojecting' ${\bf t}$.
@@
 
-      In particular, our model of the $y\times \delta_g$ cross-correlation is especially sensitive to the width of the redshift distributions.
-This is because, while the amplitude to the galaxy auto-correlation is strongly affected by the width of the distribution (wider $p(z)$s reduce the clustering amplitude), the cross-correlation with $y$ is almost insensitive to it.
-We therefore introduce an additional parameter $w_z$ that stretches the support of the redshift distribution while preserving unit total probability.
+      In particular, our model of the $y\times \delta_g$ cross-correlation is particularly sensitive to the width of the redshift distributions.
+This is because, while the amplitude to the galaxy auto-correlation is strongly affected by the width of the distribution (wider $p(z)$'s reduce the clustering amplitude), the cross-correlation with $y$ is almost insensitive to it.
+We therefore introduce an additional parameter, $w_z$, that stretches the support of the redshift distribution while preserving unit total probability.
 Concretely, given a fiducial distribution $p_{\rm fid}(z)$ with mean redshift $\bar{z}$, $w_z$ is implemented as
@@
 where $\langle z|z_{\rm photo}\rangle\neq z_{\rm photo}$).
-The ANNz method used in \cite{2018MNRAS.481.1133P} should guarantee unbiased photo-$z$s, but this can never be achieved exactly in practice.
+The {\tt ANNz} method used in \cite{2018MNRAS.481.1133P} should guarantee unbiased photo-$z$'s, but this can never be achieved exactly in practice.
 It would be possible to account for this form of uncertainty by treating $\bar{z}$ as a free parameter, as is usually done in photometric cosmic shear analyses.
@@
 
-    For each redshift bin, our theory model has five free parameters: $\log_{10}M_{\rm min}/M_\odot$, $\log_{10}M_1'/M_\odot$, $1-b_{\rm H}$, $\rho_{yg}$, and a nuisance width parameter $w_z$.
+    For each redshift bin, our theoretical model has five free parameters: $\log_{10}M_{\rm min}/{\rm M_\odot}$, $\log_{10}M_1'/{\rm M_\odot}$, $1-b_{\rm H}$, $\rho_{yg}$, and a nuisance width parameter $w_z$.
 The first two parameters effectively fit the galaxy bias and small-scale amplitude in the galaxy auto-correlation, while $1-b_{\rm H}$ and $\rho_{yg}$ are then constrained by including the tSZ cross-correlation.
@@
     \begin{align}
-      &10\le\log_{10}M_{\rm min}/M_\odot\le16,\\
-      &10\le\log_{10}M_1'/M_\odot\le16,\\
+      &10\le\log_{10}M_{\rm min}/{\rm M_\odot}\le16,\\
+      &10\le\log_{10}M_1'/{\rm M_\odot}\le16,\\
       &0\le(1-\bH)\le0.99,\\
@@
 The grey circles show the same constraints found using the NILC $y$ map, which are in good agreement with our fiducial results.
-The red downward-pointing triangles show the constraints found fixing the photo-$z$ width parameter $w_z$.
+The red downward-pointing triangles show the constraints found fixing the photo-$z$ width parameter, $w_z$.
 They are in good agreement with our fiducial measurements, with $\sim20\%$ smaller error bars.
@@
             \hline
-            Sample & $\bar{z}$ & $1-\bH\,\,({\rm best\,\,fit})$ & $1-\bH\,\,(68\%\,{\rm C.L.})$ & $\langle bP_e\rangle\,[{\rm eV}\,\,{\rm cm}^{-3^{\phantom{2}}}]$ & $\chi^2/{\rm d.o.f.}$ & ${\rm PTE}(\chi^2)$\\[1ex]
+            Sample & $\bar{z}$ & $1-\bH\,\,({\rm best\,\,fit})$ & $1-\bH\,\,(68\%\,{\rm C.L.})$ & $\langle bP_e\rangle\,[{\rm meV}\,\,{\rm cm}^{-3^{\phantom{2}}}]$ & $\chi^2/{\rm d.o.f.}$ & ${\rm PTE}(\chi^2)$\\[1ex]
             \hline
@@
 On the other hand, the width of the redshift distribution also has a strong impact on the amplitude of the angular power spectrum at all scales due to projection effects.
-Since a measurement of the galaxy bias from the galaxy auto-correlation is effectively used to constrain $\bH$ from the galaxy-$y$ cross-correlation, the mass bias also shows some degeneracy with the HOD parameters and $w_z$, albeit at a more moderate level.
-More interestingly, the mass-bias parameter $\bH$ shows a visible degeneracy with $\rho_{gy}$.
-This is also expected: the effects of $\rho_{gy}$ and $\bH$ on the 1-halo term of the galaxy-$y$ power spectrum are completely degenerate, and thus a free $\rho_{gy}$ ensures that any information obtained on $\bH$ comes entirely from the 2-halo contribution.
+Since a measurement of the galaxy bias from the galaxy auto-correlation is effectively used to constrain $\bH$ from the galaxy-tSZ cross-correlation, the mass bias also shows some degeneracy with the HOD parameters and $w_z$, albeit at a more moderate level.
+More interestingly, the mass bias parameter, $\bH$, shows a visible degeneracy with $\rho_{gy}$.
+This is also expected: the effects of $\rho_{gy}$ and $\bH$ on the 1-halo term of the galaxy-tSZ power spectrum are completely degenerate, and thus a free $\rho_{gy}$ ensures that any information obtained on $\bH$ comes entirely from the 2-halo contribution.
 
-      The corresponding constraints on $1-\bH$ for all redshift bins are shown in the bottom panel of Fig.\!~\ref{fig:bh} as black circles with error bars.
-The values shown in the figure and given explicitly in column 4 of Table \ref{tab:results} correspond to the peak of the 1-dimensional distribution of $1-\bH$ and to the equal-probability values encompassing a total probability of 0.68.
-The overall best-fit value of $1-\bH$ is provided in column 3 of the same Table.
+      The corresponding constraints on $1-\bH$ for all redshift bins are shown in the main panel of Fig.\!~\ref{fig:bh} as black circles with error bars.
+The values shown in the figure and given explicitly in column 4 of Table \ref{tab:results} correspond to the mode of the 1-dimensional distribution of $1-\bH$ and to the equal-probability values encompassing a total probability of 0.68 (1$\sigma$).
+The overall best-fit value (mean of 1-dimensional posterior) of $1-\bH$ is provided in column 3 of the same Table.
 Columns 6 and 7 list the reduced $\chi^2$ values for each sample and their associated probability-to-exceed (PTE), respectively.
@@
       We see that, while we are able to measure $1-\bH$ to a reasonable accuracy ($\sim12\%$) in all of the \wisc~ redshift bins, the sensitivity for the 2MPZ sample is much poorer.
-This is not entirely unexpected: even though the cross-correlation between the Compton-$y$ map and the 2MPZ catalogue yields the highest signal-to-noise ratio of all the samples used here, the low-redshift range covered by this sample implies that the signal is strongly dominated by the one-halo term.
+This is not entirely unexpected: even though the cross-correlation between the Compton-$y$ map and the 2MPZ catalogue yields the highest signal-to-noise ratio of all the samples used here, the low-redshift range covered by this sample implies that the signal is strongly dominated by the 1-halo term.
 This can be seen in the top right panel of Fig.\!~\ref{fig:cls}.
-This degrades the constraining power of the 2MPZ cross-correlation significantly since, as we have described above, we can only obtain reliable constraints on $1-\bH$ from the two-halo contribution.
+The constraining power of the 2MPZ cross-correlation degrades significantly since, as we have already described, we can only obtain reliable constraints on $1-\bH$ from the 2-halo contribution.
 
@@
 
-      Since the amplitudes of the galaxy auto-correlation and the galaxy-$y$ cross-correlation are both affected by the value of $\sigma_8$, which we have fixed to the best-fit value found by \planck, the fact that the value of $1-\bH$ we find is compatible with that found by \cite{2016A&A...594A..24P} is not surprising.
-In other words, this agreement can be understood as a evidence of the compatibility between the best-fit \planck\ cosmology and the clustering properties of galaxies and thermal pressure in the datasets used here.
+      Since the amplitudes of the galaxy auto-correlation and the galaxy-tSZ cross-correlation are both affected by the value of $\sigma_8$, which we have fixed to the best-fit value found by \planck, the fact that the value of $1-\bH$ we find is compatible with the one measured by \cite{2016A&A...594A..24P} is not surprising.
+In other words, this agreement can be understood as evidence of the compatibility between the best-fit \planck\ cosmology and the clustering properties of galaxies and thermal pressure in the datasets used here.
 The corresponding best-fit value of $1-\bH\simeq0.6$ is at odds with the expectation from hydrodynamical simulations \citep{2016ApJ...827..112B} and some direct calibration efforts \citep[e.g.][]{2016MNRAS.456L..74S,2019A&A...621A..40E}, which seem to prefer smaller missing mass fractions ($1-\bH\simeq0.8$).
-A possible resolution of the mild tension between tSZ cluster counts and CMB data could be the presence of new physics that modify the late-time expansion and structure growth.
+A possible resolution of the mild tension between tSZ cluster counts and CMB data could be the existence of new physics modifying the late-time expansion and structure growth.
 However, most of these modifications (e.g.
@@
     \subsubsection{Tomographic measurement of thermal gas pressure}\label{ssec:results.fid.bpe}
-      So far we have presented our constraints in terms of a the mass-bias parameter $1-\bH$, since this is the main source of systematic uncertainty in the cosmological analysis of cluster number counts carried out by \planck.
+      So far we have presented our constraints in terms of a the mass bias parameter $1-\bH$, since this is the main source of systematic uncertainty in the cosmological analysis of cluster number counts carried out by \planck.
 However, the physical interpretation of this parameter (the fraction of missing mass estimated from X-ray measurements under the assumption of hydrostatic equilibrium) is not directly related to the physical process that allows us to constrain it through the cross-correlation of $y$ and $\delta_g$: the fact that galaxy density and pressure trace the same underlying dark-matter fluctuations.
@@
 This quantity can be interpreted both as the relation between large-scale matter and pressure fluctuations and as the halo-bias-weighted thermal energy density of all haloes at a given redshift \citep{2017JCAP...11..040B}.
-This quantity has been measured at low  redshifts by \cite{2017MNRAS.467.2315V} making use of galaxy groups, and at higher redshifts by the Dark Energy Science Collaboration \citep{2019arXiv190413347P}.
-The redshift range $0.1\lesssim z\lesssim0.4$, containing a large fraction of the tSZ sources detected by \planck\ \citep{2016A&A...594A..27P}, is fairly unconstrained tomographically through this type of measurements.
+It has been measured at low  redshifts by \cite{2017MNRAS.467.2315V} making use of galaxy groups, and at higher redshifts by the Dark Energy Science Collaboration \citep{2019arXiv190413347P}.
+The redshift range $0.1\lesssim z\lesssim0.4$, containing a large fraction of the tSZ sources detected by \planck\ \citep{2016A&A...594A..27P}, has been so far fairly unconstrained tomographically through this type of measurements.
 
-      We derive constraints on $\langle bP_e\rangle$ from our data by reprocessing our Monte-Carlo chains, computing $\langle bP_e\rangle$ at each sample to find its 1D posterior distribution.
+      We derive constraints on $\langle bP_e\rangle$ from our data by reprocessing our Monte-Carlo chains, computing $\langle bP_e\rangle$ at each sample to find its 1-dimensional posterior distribution.
 The results are shown in Fig.\!~\ref{fig:by}, together with the measurements of \cite{2017MNRAS.467.2315V} and \cite{2019arXiv190413347P}.
@@
 Fig.\!~\ref{fig:bh} shows the final constraints on $1-\bH$ in this case as burgundy squares, which are consistently lower by $\sim 2\sigma$.
-We find that this is caused by a redshift-dependent systematic offset between both mass function parameterisations which reaches the level of $10$-$20\%$ in the range $0<z<0.4$.
+We find that this is caused by a redshift-dependent systematic offset between the two mass function parameterisations which reaches the level of $10$-$20\%$ in the range $0<z<0.4$.
 This is shown explicitly in Fig.
@@
   Cross-correlating maps of the tSZ Compton-$y$ parameter with tomographic measurements of the projected galaxy distribution allows us to study the redshift evolution of the thermal gas pressure, since we expect both pressure and galaxies to trace the same underlying matter inhomogeneities.
-We have measured the $\delta_g$-$y$ cross-correlation to very high significance using the public $y$ maps made available by the \planck\ collaboration \citep{2016A&A...594A..22P} and the 2MPZ and \wisc~ galaxy catalogues \citep{2014ApJS..210....9B,2016ApJS..225....5B} in six photometric redshift bins covering the redshift range $z\lesssim0.4$.
+We have measured the $\delta_g$-$y$ cross-correlation to very high significance using public $y$ maps made available by the \planck\ collaboration \citep{2016A&A...594A..22P} and the 2MPZ and \wisc~ galaxy catalogues \citep{2014ApJS..210....9B,2016ApJS..225....5B} in six photometric redshift bins covering the redshift range $z\lesssim0.4$.
 
-  Combining this measurement with a measurement of the galaxy auto-correlation allows us to break the degeneracy between the two parameters that relate $\delta_g$ and $y$ to the matter fluctuations: the galaxy bias, which we model effectively using a 2-parameter HOD prescription, and the mass bias parameter $1-\bH$, thus enabling us to make a redshift-dependent measurement of $1-\bH$.
+  Combining this measurement with a measurement of the galaxy auto-correlation allows us to break the degeneracy between the two parameters that relate $\delta_g$ and $y$ to the matter fluctuations: the galaxy bias, which we model effectively using a 2-parameter HOD prescription, and the mass bias parameter $1-\bH$; and thus enables us to make a redshift-dependent measurement of $1-\bH$.
 The results, shown in Table \ref{tab:results} and Fig.\!~\ref{fig:bh}, agree well with the measurements of $1-\bH$ made by \planck\ through the combination of cluster number counts and CMB primary anisotropies \citep{2016A&A...594A..24P}, as well as with the calibration of tSZ cluster masses with CMB lensing measurements \citep{2019arXiv190407887Z}, and with similar measurements of $1-\bH$ made by \cite{2018MNRAS.480.3928M} through the same type of cross-correlation at lower redshifts.
@@
 Our results, shown in Table \ref{tab:results} and Fig.\!~\ref{fig:by}, agree well with previous measurements of the same quantity \citep{2017MNRAS.467.2315V,2019arXiv190413347P}, as well as with shock-heating models \citep{2012ApJ...758...75B}.
-These results are also the most precise measurement of the large-scale correlation between $\delta_g$ and $y$ to date.
+This result is also the most precise measurement of the large-scale correlation between $\delta_g$ and $y$ to date.
 
@@
   We must also note that our parameter constraints have been derived for a fixed cosmological model, corresponding to the best-fit parameters found by \planck\ \citep{2018arXiv180706209P}.
-The most significant consequence of this is the fact that our constraints are strongly degenerate with the amplitude of matter fluctuations, parameterised by $\sigma_8$.
+The most significant consequence is the fact that our constraints are strongly degenerate with the amplitude of matter fluctuations, parameterised by $\sigma_8$.
 Therefore, the agreement between our constraints on $1-\bH$ and those found by \planck\ \citep{2016A&A...594A..24P} can be thought of as a proof of the consistency between the properties of the galaxy distribution in 2MPZ and \wisc~ and the CMB anisotropies.

### 2019-09-17 notes/paper/paper.tex
table script

@@
 Numerical simulations have constrained the mass deficit to be around 20\% (i.e.
-$1-\bH\simeq0.8$: \citejap{2012ApJ...758...74B}; \citejap{2014ApJ...782..107N}), although it is known that a smaller value is needed in order to fully reconcile CMB primary constraints and SZ cluster counts \citep{2016A&A...594A..24P}.
+$1-\bH\simeq0.8$: \citejap{2012ApJ...758...74B}; \citejap{2014ApJ...782..107N}), although it is known that a smaller value is necessary in order to fully reconcile CMB primary constraints and SZ cluster counts \citep{2016A&A...594A..24P}.
 This is a central point of our discussion in Sections \ref{sec:results} and \ref{sec:conclusion}.
@@
       The corresponding constraints on $1-\bH$ for all redshift bins are shown in the main panel of Fig.\!~\ref{fig:bh} as black circles with error bars.
-The values shown in the figure and given explicitly in column 4 of Table \ref{tab:results} correspond to the mode of the 1-dimensional distribution of $1-\bH$ and to the equal-probability values encompassing a total probability of 0.68 (1$\sigma$).
-The overall best-fit value (mean of 1-dimensional posterior) of $1-\bH$ is provided in column 3 of the same Table.
+The values shown in the figure and given explicitly in column 4 of Table \ref{tab:results} correspond to the peak of the 1-dimensional distribution of $1-\bH$ and to the equal-probability values encompassing a total probability of 0.68 (1$\sigma$).
+The maximum-likelihood value of $1-\bH$ is provided in column 3 of the same Table.
 Columns 6 and 7 list the reduced $\chi^2$ values for each sample and their associated probability-to-exceed (PTE), respectively.

### 2019-09-17 table.py

@@ -1,0 +1,54 @@
+import os
+import numpy as np
+from likelihood.chanal import chan
+import matplotlib.pyplot as plt
+from matplotlib import rc
+from scipy.stats import chi2
+rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+rc('text', usetex=True)
+plt.rcParams['text.latex.preamble']=[r"\usepackage{amsmath}"]
+
+fname_params = "params_dam_wnarrow.yml"
+pars, (chi2s,ndofs,bfs), chains = chan(fname_params, diff=True, error_type="hpercentile",
+                                   by_subsample=10)
+ns=len(chains[0][0])
+ns_sub=len(chains[1][0])
+print(ns,ns_sub)
+for i,s in enumerate(['2MPZ_bin1','WISC_bin1','WISC_bin2',
+                      'WISC_bin3','WISC_bin4','WISC_bin5']):
+    ch_mb=1-chains[0][i][ns//4:,2]
+    ch_by=(chains[1][i]*1e3)[ns_sub//4:]
+    def get_summary_numbers(chain):
+        from scipy.stats import gaussian_kde
+        from scipy.optimize import minimize_scalar, root_scalar
+        from scipy.integrate import quad, simps
+        x_min=np.amin(chain)
+        x_max=np.amax(chain)
+        d = gaussian_kde(chain)
+        def minfunc(x):
+            return -d(x)
+        x_bf = minimize_scalar(minfunc,bracket=[x_min,x_max]).x[0]
+        p_bf = d(x_bf)[0]
+        def limfunc(x,thr):
+            return d(x)[0]-thr
+        def get_prob(a,b):
+            xr=np.linspace(a,b,128)
+            return simps(d(xr),x=xr)
+        def cutfunc(pthr):
+            r_lo=root_scalar(limfunc,args=(pthr),bracket=(x_min,x_bf)).root
+            r_hi=root_scalar(limfunc,args=(pthr),bracket=(x_bf,x_max)).root
+            pr=get_prob(r_lo,r_hi)
+            return pr-0.68
+        p_thr=root_scalar(cutfunc,bracket=(0.05*p_bf,0.95*p_bf)).root
+        x_lo=root_scalar(limfunc,args=(p_thr),bracket=(x_min,x_bf)).root
[…]

### 2019-09-20 likelihood/chanal.py
new chain analysis pipeline, automated, user friendly

@@ -3,6 +3,8 @@ sys.path.append("../../")
 import numpy as np
 from scipy.integrate import simps
 from scipy.interpolate import interp1d
+from scipy.stats import gaussian_kde
+from scipy.optimize import minimize_scalar, root_scalar
 from analysis.params import ParamRun
 from model.data import DataManager
 from likelihood.like import Likelihood
@@ -12,93 +14,79 @@ from model.power_spectrum import HalomodCorrection, hm_bias
 from model.utils import selection_planck_erf, selection_planck_tophat
 
 
-def halmodcor(p, cosmo):
-    # Include halo model correction if needed
-    if p.get('mcmc').get('hm_correct'):
-        hm_correction = HalomodCorrection(cosmo)
-    else:
-        hm_correction = None
-    return hm_correction
 
-def selfunc(p):
-    # Include selection function if needed
-    sel = p.get('mcmc').get('selection_function')
-    if sel is not None:
-        if sel == 'erf':
-            sel = selection_planck_erf
-        elif sel == 'tophat':
-            sel = selection_planck_tophat
-        elif sel == 'none':
-            sel = None
-    return sel
+def vpercentile(chain):
+    """Best fit and errors using manual watershed method."""
+    percentile = 68
+    pdf, x = np.histogram(chain, bins=100, density=True)
+    x = (x[:-1] + x[1:])/2
 
-
-def get_dndz(fname, width):
-    """Get the modified galaxy number counts."""
-    zd, Nd = np.loadtxt(fname, unpack=True)
-    Nd /= simps(Nd, x=zd)
-    zavg = np.average(zd, weights=Nd)
-    nzf = interp1d(zd, Nd, kind="cubic", bounds_error=False, fill_value=0)
-
-    Nd_new = nzf(zavg + (1/width)*(zd-zavg))
-    return zd, Nd_new
-
-
-def vpercentile(chain, percentile=68, bins=100, eps=0.005):
-    """Finds the parameter errors using a Markov chain."""
-    pdf, x = np.histogram(chain, bins, density=True)
-
-    cut = pdf.max()*np.flip(np.arange(eps, 1, eps))
+    par_bf = x[np.argmax(pdf)]
+    eps = 0.005
+    cut = pdf.max()*np.arange(1-eps, 0, -eps)
     for cc in cut:
 
         bb = np.where(pdf-cc > 0)[0]
-        if bb.size < 2: continue
+        if bb.size < 2:
+            continue
         par_min, par_max = x[bb[0]], x[bb[-1]]
[…]

### 2019-09-20 notes/paper/paper.tex
most recent versions of stuff

@@
       The corresponding constraints on $1-\bH$ for all redshift bins are shown in the main panel of Fig.\!~\ref{fig:bh} as black circles with error bars.
-The values shown in the figure and given explicitly in column 4 of Table \ref{tab:results} correspond to the peak of the 1-dimensional distribution of $1-\bH$ and to the equal-probability values encompassing a total probability of 0.68 (1$\sigma$).
+The values quoted in column 4 of Table \ref{tab:results} correspond to the peak of the 1-dimensional distribution of $1-\bH$ and to the equal-probability values encompassing a total probability of 0.68 (1$\sigma$).
+The values in Fig.
+\ref{fig:bh} are the medians of the 1-dimensional distributions in each redshift bin.
 The maximum-likelihood value of $1-\bH$ is provided in column 3 of the same Table.
@@
 
+  In data analysis the {\tt python} packages {\tt numpy}, {\tt scipy} were used. For our plots, we used {\tt matplotlib}.
+
 \setlength{\bibhang}{2.0em}

### 2019-09-20 notes/notes.tex
updated after paper on arXiv

--- 2019-04-02 notes/notes.tex
@@
 
-\section{Results}
-  Results for 2MPZ and the 5 WISC redshift bins in Figures \ref{fig:res_2mpz}, \ref{fig:res_wisc1}, \ref{fig:res_wisc2}, \ref{fig:res_wisc3}, \ref{fig:res_wisc4} and \ref{fig:res_wisc5} respectively.
-Results are summarized in Fig.
-\ref{fig:oneminusb}.
-  \begin{figure*}
-    \centering
-    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_2mpz_cls_2mpz_2mpz}
-    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_2mpz_cls_2mpz_y_milca}
-    \includegraphics[width = 0.90\textwidth]{../output_test/sampler_minimal_hmc_2mpz_triangle}
-    \caption{{\sl Upper left:} galaxy-galaxy power spectrum. {\sl Upper right:} galaxy-tSZ power spectrum. {\sl Lower:} parameter constraints. All for the 2MPZ sample.}\label{fig:res_2mpz}
-  \end{figure*}
-  \begin{figure*}
-    \centering
-    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_wisc1_cls_wisc1_wisc1}
-    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_wisc1_cls_wisc1_y_milca}
-    \includegraphics[width = 0.90\textwidth]{../output_test/sampler_minimal_hmc_wisc1_triangle}
-    \caption{Same as Fig. \ref{fig:res_2mpz} for the first WISC bin.}\label{fig:res_wisc1}
-  \end{figure*}
-  \begin{figure*}
-    \centering
-    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_wisc2_cls_wisc2_wisc2}
-    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_wisc2_cls_wisc2_y_milca}
-    \includegraphics[width = 0.90\textwidth]{../output_test/sampler_minimal_hmc_wisc2_triangle}
-    \caption{Same as Fig. \ref{fig:res_2mpz} for the second WISC bin.}\label{fig:res_wisc2}
-  \end{figure*}
-  \begin{figure*}
-    \centering
-    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_wisc3_cls_wisc3_wisc3}
-    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_wisc3_cls_wisc3_y_milca}
-    \includegraphics[width = 0.90\textwidth]{../output_test/sampler_minimal_hmc_wisc3_triangle}
-    \caption{Same as Fig. \ref{fig:res_2mpz} for the third WISC bin.}\label{fig:res_wisc3}
-  \end{figure*}
-  \begin{figure*}
-    \centering
-    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_wisc4_cls_wisc4_wisc4}
-    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_wisc4_cls_wisc4_y_milca}
-    \includegraphics[width = 0.90\textwidth]{../output_test/sampler_minimal_hmc_wisc4_triangle}
-    \caption{Same as Fig. \ref{fig:res_2mpz} for the fourth WISC bin.}\label{fig:res_wisc4}
-  \end{figure*}
-  \begin{figure*}
-    \centering
-    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_wisc5_cls_wisc5_wisc5}
-    \includegraphics[width = 0.49\textwidth]{../output_test/sampler_minimal_hmc_wisc5_cls_wisc5_y_milca}
-    \includegraphics[width = 0.90\textwidth]{../output_test/sampler_minimal_hmc_wisc5_triangle}
-    \caption{Same as Fig. \ref{fig:res_2mpz} for the fifth WISC bin.}\label{fig:res_wisc5}
-  \end{figure*}
-
-  \begin{figure}
-   \centering
-   \includegraphics[width = 0.7\textwidth]{../output_test/sampler_minimal_hmc_b_hydro_all}
-   \caption{Summary plot.}\label{fig:oneminusb}
-  \end{figure}
-
 \bibliography{notes}

### 2019-09-20 notes/paper/paper.tex
updated after paper on arXiv

--- 2019-09-17 notes/paper/paper.tex
@@
 
-%\usepackage{widetext}
 \usepackage{graphicx}
@@
 \newcommand{\wisc}{WI$\times$SC}
-\newcommand{\cites}{{\bf CITES}}
-\newcommand{\todo}[1]{{\bf TODO:} #1}
 \newcommand{\kalo}{Karhunen-Lo\`{e}ve\,}
@@
 \newcommand{\araa}{Annual Review of Astron and Astrophys}
-
-\newcommand{\MB}[1]{\textcolor{red}{#1}}
-\newcommand{\DA}[1]{\textcolor{blue}{#1}}
 
@@
 The limiting factor for cosmological constraints from cluster number counts is the uncertainty in the mass-observable relation \citep{2009ApJ...692.1060V,2010ApJ...722.1180V,2011ApJ...732...44S,2013JCAP...07..008H,2014MNRAS.440.2077M,2014A&A...571A..20P,2015MNRAS.446.2205M,2016A&A...594A..24P,2016ApJ...832...95D,2019ApJ...878...55B}.
-Cosmic shear measurements are strongly affected by sub-grid baryonic physics, and by uncertainties in the processes by which galaxies acquire correlated intrinsic alignments \citep[e.g.][]{2001MNRAS.320L...7C,2002MNRAS.332..788M,2004PhRvD..70f3526H,2017MNRAS.465.2033J,2018PhRvD..98d3528T,2018arXiv181206076H,2018ARA&A..56..393M,2018arXiv181106989S}.
+Cosmic shear measurements are strongly affected by sub-grid baryonic physics, and by uncertainties in the processes by which galaxies acquire correlated intrinsic alignments \citep[e.g.][]{2001MNRAS.320L...7C,2002MNRAS.332..788M,2004PhRvD..70f3526H,2017MNRAS.465.2033J,2018PhRvD..98d3528T,2018arXiv181206076H,2018ARA&A..56..393M,2019MNRAS.tmp.2187S}.
 Understanding the impact of baryons on the matter power spectrum requires better knowledge of the distribution of gas in haloes.
@@
 Since these observables are also sensitive to cosmology, their combination with large-scale structure data can be extremely powerful at disentangling astrophysical and cosmological parameters.
-This has been explored by a large number of groups: CMB lensing data have been used to constrain the bias of different tracers of the matter distribution \citep[e.g.][]{2019MNRAS.485.1720H,2018JCAP...04..053A,2018arXiv181002322A,2018MNRAS.481.1133P}, as well as to calibrate the measurement of galaxy shapes in cosmic shear analyses \citep{2019PhRvD.100b3541A}.
+This has been explored by a large number of groups: CMB lensing data have been used to constrain the bias of different tracers of the matter distribution \citep[e.g.][]{2019MNRAS.485.1720H,2018JCAP...04..053A,2019PhRvD.100b3541A,2018MNRAS.481.1133P}, as well as to calibrate the measurement of galaxy shapes in cosmic shear analyses \citep{2019PhRvD.100b3541A}.
 The tSZ effect has been used in cross-correlation with galaxy clustering and weak lensing data to determine the physical properties of the diffuse gas, as well as to potentially improve constraints on the amplitude of matter fluctuations \citep{2014PhRvD..89b3508V,2014JCAP...02..030H,2015JCAP...09..046M,2017MNRAS.471.1565H,2017ApJ...845...71A,2018PhRvD..97f3514A,2018MNRAS.480.3928M,2019A&A...624A..48D,2019MNRAS.483..223T,2019arXiv190306654T,2019arXiv190413347P,2019arXiv190707870M}.
@@
 The availability of redshift information allows us to place constraints on the cosmic evolution of the thermal gas pressure and the thermal energy in haloes, as well as to examine any redshift dependence of the mass bias for tSZ cluster studies.
-This is a relevant topic given the current mild tensions between SZ cluster number counts and CMB primary anisotropies \citep{2016A&A...594A..24P,2016ApJ...832...95D,2019ApJ...878...55B,2019arXiv190407887Z}, which could be caused by the assumptions made to model the $y$-mass relation.
+This is a relevant topic given the current mild tensions between SZ cluster number counts and CMB primary anisotropies \citep{2016A&A...594A..24P,2016ApJ...832...95D,2019ApJ...878...55B,2019MNRAS.489..401Z}, which could be caused by the assumptions made to model the $y$-mass relation.
 Conversely, under the assumption that the relation between mass and gas pressure is well understood, the tSZ effect can be thought of as a mass tracer, which can be used to break degeneracies with the galaxy bias parameter -- we however leave this analysis for future work.
@@
 Coupling $M_0$ and $M_{\rm min}$ allows for all haloes containing a central to also contain satellites, and conversely, for all haloes containing satellites to necessarily contain a central.
-This assumption breaks down in cases such as mergers, where centrals have not been established yet.
-We however explore departures from the fiducial model.
+This assumption breaks down in cases such as recent major mergers, where centrals may not immediately be established.
 
@@
 The product of both masks leaves a usable sky fraction $f_{\rm sky}\simeq0.58$.
-      %The top panel shows, in turquoise, the regions masked additionally when removing sky patches around the position of the tSZ sources detected by \planck\ above 6$\sigma$.
       }
@@
 We use a fiducial mask for the $y$ maps based on a combination of the \planck\ 60\% Galactic mask and the union of the HFI and LFI point source masks (see top panel of Fig.\!~\ref{fig:msk}).
-    %As part of our study of the mass dependence of the signal on halo mass, we additionally mask out all tSZ sources detected by \planck\ above 6$\sigma$, based on the Union catalogue of \cite{2016A&A...594A..27P}.
 
@@
     Both 2MPZ and WISC suffer from different levels of contamination from Galactic and observational systematics.
-The most relevant Galactic systematic is star contamination, particularly for \wisc~ \citep{2018arXiv181208182X}.
+The most relevant Galactic systematic is star contamination, particularly for \wisc~ \citep{2019JCAP...08..037X}.
 Besides avoiding regions of high dust and star contamination using the sky mask described in \cite{2018MNRAS.481.1133P} (see bottom panel of Fig.\!~\ref{fig:msk}), we correct for the effects of stellar contamination by correcting for a smooth non-linear relation between galaxy and star density (also described in \citejap{2018MNRAS.481.1133P}).
@@
         \caption{Summary of the different sources of systematic contamination affecting the galaxy auto-correlations for the particular case of the third \wisc~bin.
-The red and blue points show the measurements before and after deprojecting a dust and a star template, while the grey dashed line shows the best-fit contamination from SuperCOSMOS plate fluctuations assuming no intrinsic clustering.
-The solid black line shows the best-fit theory model.
-The light grey bands indicate the data points removed due to scale cuts.}
+The red and blue points show the measurements before and after deprojecting a dust and a star template.
+The dot-dashed line shows the best-fit contamination from SuperCOSMOS plate fluctuations that explains the residuals of the data with respect to the best-fit HOD-only model (dashed line).
+The total combined prediction is shown as the solid line.
+The light grey bands show our scale cuts.}
         \label{fig:clsyst}
@@
       where ${\bf T}$ is a vector containing the template $T_\ell$ for all the scales used in the analysis.
-Fig.\!~\ref{fig:clsyst} shows the shape of the plate template $T_\ell$ normalised by the best-fit value of the parameter $A$ assuming no intrinsic clustering.
+The dot-dashed line in Fig.\!~\ref{fig:clsyst} shows the shape of the plate template $T_\ell$ normalised by the best-fit value of the parameter $A$ that explains the residuals of the data with respect to the best-fit HOD-only model (shown as a dashed line).
+The plate fluctuations contribute to $\sim10\%$ of the signal on scales $\ell\lesssim 30$.
 
@@
       After deprojecting dust and stars at the map level, and the imprint of the SuperCOSMOS plates at the power spectrum level, we still observe an unacceptably large amount of power on scales $\ell<10$ in all galaxy auto-correlations involving \wisc.
-These may be due to residual star contamination that is not simply removed with a linear template \citep{2018arXiv181208182X}, or inaccuracies in our treatment of the SuperCOSMOS fluctuations.
+These may be due to residual star contamination that is not simply removed with a linear template \citep{2019JCAP...08..037X}, or inaccuracies in our treatment of the SuperCOSMOS fluctuations.
 To avoid biasing our results we therefore remove the lowest bandpower from all galaxy auto-correlations involving \wisc.
@@
 It would be possible to account for this form of uncertainty by treating $\bar{z}$ as a free parameter, as is usually done in photometric cosmic shear analyses.
-Our results, however, are more sensitive to the distribution widths, and we find that this simple parametrisation is able to describe our data sufficiently well.
+Our results, however, are more sensitive to the distribution widths, and we find that this simple parameterisation is able to describe our data sufficiently well.
 We leave a more detailed analysis of the associated photometric redshift systematics for future work.
@@
         \centering
-        \includegraphics[width=0.6\textwidth]{fiducial_wisc3.pdf}
+        \includegraphics[width=0.7\textwidth]{fiducial_wisc3.pdf}
         \caption{68\% and 95\% contours for the model parameters in the third WI$\times$SC redshift bin.}
@@
 The orange diamond and the mesh show our combined, redshift-independent constraint on $1-\bH$.
-For comparison, the grey and turquoise bands show the constraints on the mass bias found by combining cluster counts and CMB primary \citep{2016A&A...594A..24P} as well as the constraints using CMB lensing to calibrate cluster masses \citep{2019arXiv190407887Z}, respectively.
+For comparison, the grey and turquoise bands show the constraints on the mass bias found by combining cluster counts and CMB primary \citep{2016A&A...594A..24P} as well as the constraints using CMB lensing to calibrate cluster masses \citep{2019MNRAS.489..401Z}, respectively.
 The top panel shows the normalised redshift distributions for the six redshift bins, for reference.}
@@
 
-      The corresponding constraints on $1-\bH$ for all redshift bins are shown in the main panel of Fig.\!~\ref{fig:bh} as black circles with error bars.
-The values shown in the figure and given explicitly in column 4 of Table \ref{tab:results} correspond to the peak of the 1-dimensional distribution of $1-\bH$ and to the equal-probability values encompassing a total probability of 0.68 (1$\sigma$).
-The maximum-likelihood value of $1-\bH$ is provided in column 3 of the same Table.
-Columns 6 and 7 list the reduced $\chi^2$ values for each sample and their associated probability-to-exceed (PTE), respectively.
+      The corresponding constraints on $1-\bH$ for all redshift bins are shown in the main panel of Fig.\!~\ref{fig:bh} as black circles with error bars (corresponding to the median and 68\% confidence interval).
+These results are summarized in Table \ref{tab:results}, where column 3 shows the maximum-likelihood value of $1-\bH$, while column 4 lists the peak of the marginalized 1-dimensional distribution and the confidence interval corresponding to the equal-probability values encompassing a total probability of 0.68.
+Columns 6 and 7 of the same table list the reduced $\chi^2$ values for each sample and their associated probability-to-exceed (PTE), respectively.
 In all cases we find that the model described in Section \ref{sec:theory} is able to describe the data with no evidence for a significant statistical tension.
@@
 
-      Our results are in broad agreement with the estimate of a redshift-independent $1-\bH$ found by \cite{2019arXiv190407887Z} by calibrating cluster masses with CMB lensing ($1-\bH=0.71\pm0.1$), shown in Fig.\!~\ref{fig:bh} as a turquoise semi-transparent band.
+      Our results are in broad agreement with the estimate of a redshift-independent $1-\bH$ found by \cite{2019MNRAS.489..401Z} by calibrating cluster masses with CMB lensing ($1-\bH=0.71\pm0.1$), shown in Fig.\!~\ref{fig:bh} as a turquoise semi-transparent band.
 In turn, the grey band in the same figure shows the constraints on $1-\bH$ found by combining tSZ cluster counts and the $TT$ CMB power spectrum measured by \planck\ \citep{2016A&A...594A..24P} ($1-\bH=0.58\pm0.04$).
@@
 Our measurements are shown as blue circles with error bars and a `violin' background.
-The circle and error bars show the peak value and 68\% confidence interval, while the violins show the full 1D posterior distribution.
+The circle and error bars show the median and 68\% confidence interval, while the violins show the full 1D posterior distribution.
 The grey lines show the predictions of the shock-heating model of \citet{2012ApJ...758...75B} for different values of the $r_{\rm max}$ threshold cluster radius (see legend).
@@
       We derive constraints on $\langle bP_e\rangle$ from our data by reprocessing our Monte-Carlo chains, computing $\langle bP_e\rangle$ at each sample to find its 1-dimensional posterior distribution.
-The results are shown in Fig.\!~\ref{fig:by}, together with the measurements of \cite{2017MNRAS.467.2315V} and \cite{2019arXiv190413347P}.
+The results are listed in Table \ref{tab:results} and shown in Fig.\!~\ref{fig:by}, together with the measurements of \cite{2017MNRAS.467.2315V} and \cite{2019arXiv190413347P}.
 Our results are in good qualitative agreement with the trend of these previous measurements, as well as with the predictions of the shock heating models of \cite{2012ApJ...758...75B}.
@@
         \includegraphics[width=0.49\textwidth]{mf_ratio.pdf}
-        \caption{Ratio between the mass function parametrisations of \citet{2008ApJ...688..709T} and \citet{2010ApJ...724..878T} in the range of redshifts relevant to this analysis.
+        \caption{Ratio between the mass function parameterisations of \citet{2008ApJ...688..709T} and \citet{2010ApJ...724..878T} in the range of redshifts relevant to this analysis.
 A systematic offset of about $10$-$20\%$ between them can be observed, which causes the lower value of $1-b_{\rm H}$ found using the latter mass function (see Fig.\!~\ref{fig:bh}).
@@
 Our fiducial mass function is the parameterisation of \cite{2008ApJ...688..709T}, which we use in order to be able to make a direct comparison with the results of \cite{2016A&A...594A..24P}.
-To explore the dependence on the choice of mass function parametrisation, we redo our analysis using the updated parameterisation of \cite{2010ApJ...724..878T}.
+To explore the dependence on the choice of mass function parameterisation, we redo our analysis using the updated parameterisation of \cite{2010ApJ...724..878T}.
 Fig.\!~\ref{fig:bh} shows the final constraints on $1-\bH$ in this case as burgundy squares, which are consistently lower by $\sim 2\sigma$.
@@
 \ref{fig:mf_ratio}.
-Since the aim of this paper is not to characterise the theoretical uncertainties on the halo mass function, we leave the study of this issue for future work, and limit ourselves to using the parameterisation of \cite{2008ApJ...688..709T} in order to match previous analyses \citep[e.g.][]{2016A&A...594A..24P,2018MNRAS.477.4957B,2018MNRAS.473.4318A,2019arXiv190407887Z,2019arXiv190707870M}.
+Since the aim of this paper is not to characterise the theoretical uncertainties on the halo mass function, we leave the study of this issue for future work, and limit ourselves to using the parameterisation of \cite{2008ApJ...688..709T} in order to match previous analyses \citep[e.g.][]{2016A&A...594A..24P,2018MNRAS.477.4957B,2018MNRAS.473.4318A,2019MNRAS.489..401Z,2019arXiv190707870M}.
 
     \subsubsection{Galaxy clustering model}\label{sssec:results.syst.gc}
-      To verify that our results are robust against the details of the HOD model used to parametrise the galaxy-matter connection, we have repeated the analysis for extended versions of our baseline model.
+      To verify that our results are robust against the details of the HOD model used to parameterise the galaxy-matter connection, we have repeated the analysis for extended versions of our baseline model.
 We explore two such extensions:
@@
   Combining this measurement with a measurement of the galaxy auto-correlation allows us to break the degeneracy between the two parameters that relate $\delta_g$ and $y$ to the matter fluctuations: the galaxy bias, which we model effectively using a 2-parameter HOD prescription, and the mass bias parameter $1-\bH$; and thus enables us to make a redshift-dependent measurement of $1-\bH$.
-The results, shown in Table \ref{tab:results} and Fig.\!~\ref{fig:bh}, agree well with the measurements of $1-\bH$ made by \planck\ through the combination of cluster number counts and CMB primary anisotropies \citep{2016A&A...594A..24P}, as well as with the calibration of tSZ cluster masses with CMB lensing measurements \citep{2019arXiv190407887Z}, and with similar measurements of $1-\bH$ made by \cite{2018MNRAS.480.3928M} through the same type of cross-correlation at lower redshifts.
+The results, shown in Table \ref{tab:results} and Fig.\!~\ref{fig:bh}, agree well with the measurements of $1-\bH$ made by \planck\ through the combination of cluster number counts and CMB primary anisotropies \citep{2016A&A...594A..24P}, as well as with the calibration of tSZ cluster masses with CMB lensing measurements \citep{2019MNRAS.489..401Z}, and with similar measurements of $1-\bH$ made by \cite{2018MNRAS.480.3928M} through the same type of cross-correlation at lower redshifts.
 More importantly, our tomographic measurement allows us to study the possible redshift dependence of the mass bias, an important ingredient in the cosmological analysis of cluster abundances.
@@
 \section*{Acknowledgements}
+  We would like to thank Boris Bolliet and Eiichiro Komatsu for useful comments and discussions.
 NK is funded by the Science and Technology Facilities Council (STFC).
@@
 
+  The {\tt python} packages {\tt healpy}, {\tt numpy} and {\tt scipy} were used for data analysis, and {\tt matplotlib} was used to plot our results.
+
 \setlength{\bibhang}{2.0em}

### 2019-09-20 likelihood/chanal.py
added PTE

@@ -3,7 +3,7 @@ sys.path.append("../../")
 import numpy as np
 from scipy.integrate import simps
 from scipy.interpolate import interp1d
-from scipy.stats import gaussian_kde
+from scipy.stats import gaussian_kde, chi2
 from scipy.optimize import minimize_scalar, root_scalar
 from analysis.params import ParamRun
 from model.data import DataManager
@@ -264,9 +264,10 @@ class chan(object):
             all_pars = self.p.p.get("params")
             dof = np.sum([param["vary"] for param in all_pars if "vary" in param])
             kwargs["dof"] = len(lik.dv) - dof
+            kwargs["PTE"] = 1 - chi2.cdf(kwargs["chi2"], kwargs["dof"])
 
             if s == 0:
-                keys = ["z", "chi2", "dof"] + pars
+                keys = ["z", "chi2", "dof", "PTE"] + pars
                 OV_BF = {k: kwargs[k] for k in keys}
             else:
                 for k in keys:

### 2019-09-20 likelihood/chanal.py
added multiprocessing potential/tidied up HM biases

@@ -154,6 +154,24 @@ class chan(object):
 
     def get_chains(self, pars, **specargs):
         """Returns a dictionary containing the chains of `pars`. """
+        def bias_one(p0, num):
+            """Calculates the halo model bias for a set of parameters."""
+            bb = hm_bias(self.cosmo, 1/(1+zarr),
+                         d.tracers[num][1].profile,
+                         **lik.build_kwargs(p0))
+            return bb
+
+
+        def bias_avg(num):
+            """Calculates the halo model bias of a profile, from a chain."""
+            import pathos.multiprocessing as mpc
+            pool = mpc.ProcessingPool(mpc.cpu_count())
+            bb = list(map(lambda p0: bias_one(p0, num), sam.chain[::by_skip]))
+#            bb = pool.map(lambda p0: bias_one(p0, num), sam.chain[::by_skip])
+            bb = np.mean(np.array(bb), axis=1)
+            return bb
+
+
         if type(pars) == str: pars = [pars]
 
         if "by" in pars:
@@ -191,18 +209,11 @@ class chan(object):
             if "by" or "bg" in pars:
                 sigz = np.sqrt(np.sum(NN * (zz - zmean)**2) / np.sum(NN))
                 zarr = np.linspace(zmean-sigz, zmean+sigz, 10)
-                if "by" in pars:
-                    bys = np.mean(np.array([hm_bias(self.cosmo, 1/(1 + zarr),
-                                                    d.tracers[1][1].profile,
-                                                    **(lik.build_kwargs(p0)))
-                                    for p0 in sam.chain[::by_skip]]), axis=1)
-                    chains["by"] = bys
                 if "bg" in pars:
-                    bgs = np.mean(np.array([hm_bias(self.cosmo, 1/(1 + zarr),
-                                                    d.tracers[0][1].profile,
-                                                    **(lik.build_kwargs(p0)))
-                                    for p0 in sam.chain[::by_skip]]), axis=1)
-                    chains["bg"] = bgs
+                    chains["bg"] = bias_avg(num=0)
+                if "by" in pars:
+                    chains["by"] = bias_avg(num=1)
+
 
             # Construct tomographic dictionary
             if s == 0:
@@ -215,11 +226,14 @@ class chan(object):
         return CHAINS
 
 
-    def get_best_fit(self, pars, diff=True, **specargs):
+    def get_best_fit(self, pars, diff=True, chains=None, **specargs):
[…]

### 2019-09-20 plot_bhydro.py
dam chains + gaussian KDE implemented in chan, replotted

@@ -45,7 +45,6 @@ def plotfunc(ax, zz, dd, inverted=False,
     ax.errorbar(zz+0.004*offset, bh, yerr=yerr, fmt=fmt, ms=7, c=color, label=label)
 
 
-
 def get_dndz(fname, width):
     """Get the modified galaxy number counts."""
     zd, Nd = np.loadtxt(fname, unpack=True)
@@ -82,29 +81,32 @@ fmts = ["o","o", "v","s","*","d"]
 
 
 p = ParamRun(param_yml[0])
-temp = [chan(paryml, diff=True, error_type="hpercentile", chains=False, b_hydro=0.5*np.ones([1,6]))
-        for paryml in param_yml]
-pars = [t[0] for t in temp]
-data = np.array([[p["b_hydro"] for p in par] for par in pars])
-data = [d.T for d in data]
-data = [[[0.21, 0.62, 0.62, 0.64, 0.58, 0.61],
-         [0.05, 0.08, 0.07, 0.08, 0.07, 0.07],
-         [0.31, 0.14, 0.10, 0.07, 0.07, 0.09]],
+#temp = [chan(paryml, diff=True, error_type="hpercentile", chains=False, b_hydro=0.5*np.ones([1,6]))
+#        for paryml in param_yml]
+#pars = [t[0] for t in temp]
+#data = np.array([[p["b_hydro"] for p in par] for par in pars])
+#data = [d.T for d in data]
+
+BF = [chan(fname).get_best_fit("b_hydro") for fname in param_yml]
 
 
 
+
+widths = chan(param_yml[0]).get_best_fit("width")
+widths = np.hstack((widths["width"][:, 0]))
 dz, dN = [[] for i in range(2)]
 i = 0
 for g in p.get("maps"):
     if g["type"] == "g":
-        w = pars[0][i]["width"]  # [default][z-bins]["width"]
-        w = w if type(w) is float else w[0]  # for fixed w
+        w = widths[i]
+        w = w if type(w) is np.float64 else w[0]  # for fixed w
         zz, NN = get_dndz(g["dndz"], w)
         dz.append(zz)
         dN.append(NN)
         i += 1  # g-counter
 
-z = np.array([np.average(zz, weights=NN) for zz, NN in zip(dz, dN)])
+z = np.hstack((BF[0]["z"]))
[…]

### 2019-09-20 plot_by.py

@@ -11,32 +11,10 @@ rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
 rc('text', usetex=True)
 plt.rcParams['text.latex.preamble']=[r"\usepackage{amsmath}"]
 
-fname_params = "params_dam_wnarrow.yml"
-p = ParamRun(fname_params)
-cosmo=p.get_cosmo()
-pars, _, chains = chan(fname_params, diff=True, error_type="hpercentile", by_subsample=10)
-bys = [bb for bb in 1e3*np.array(chains[1])]
-
-z = np.array([par["z"] for par in pars])
-by = np.array([par["by"] for par in pars]).T
-
-DESx = np.array([0.15, 0.24, 0.2495, 0.383, 0.393, 0.526, 0.536, 0.678, 0.688])
-DESy = 1e-1*np.array([1.5, 1.51, 0.91, 2.46, 2.55, 3.85, 3.08, 2.61, 2.25])
-DESsy_min = 1e-1*np.array([1.275, 0.940, 0.2587, 1.88, 2.092, 2.961, 2.377, 1.442, 1.284])
-DESsy_max = 1e-1*np.array([1.726, 2.029, 1.593, 3.039, 2.991, 4.628, 3.620, 3.971, 2.994])
-
-DESsy = np.vstack((DESy-DESsy_min, DESsy_max-DESy))
-
-DES = np.vstack((DESx, DESy, DESsy))
-
-black = DES[:, 0]
-green = DES[:, 1::2]
-orang = DES[:, 2::2]
 
 # Theory predictions
 def get_battaglia(m,z,delta) :
-    """Sets all parameters needed to compute the Battaglia et al. profile
-    """
+    """Sets all parameters needed to compute the Battaglia et al. profile."""
     fb=cosmo.cosmo.params.Omega_b/cosmo.cosmo.params.Omega_m
     ez2=(ccl.h_over_h0(cosmo,1/(1+z)))**2
     h=cosmo.cosmo.params.h
@@ -49,40 +27,64 @@ def get_battaglia(m,z,delta) :
          'beta':4.35*(mr**0.0393)*((1+z)**0.415)}
     return dic
 
-def ups_battaglia(x,bp) :
-    """Battaglia pressure profile in units of pressure
-    x = r/rDelta
-    """
-    xr=x/bp['xc']
+
+def ups_battaglia(x, bp) :
[…]

### 2019-09-20 plot_covdiag.py
fixed legend

@@ -1,14 +1,27 @@
 import numpy as np
 import matplotlib.pyplot as plt
 from matplotlib import rc
+from matplotlib.legend_handler import HandlerBase
 rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
 rc('text', usetex=True)
 
+
+class AnyObjectHandler(HandlerBase):
+    def create_artists(self, legend, orig_handle,
+                       x0, y0, width, height, fontsize, trans):
+        l1 = plt.Line2D([x0,y0+width], [0.7*height,0.7*height],
+                           linestyle=orig_handle[1], color=orig_handle[0])
+        l2 = plt.Line2D([x0,y0+width], [0.3*height,0.3*height],
+                           linestyle=orig_handle[3], color=orig_handle[2])
+        return [l1, l2]
+
+
+
 gsample='wisc2'
-ls=np.load("output_dam/cls_y_milca_"+gsample+".npz")['ls']
-c1=np.load("output_dam/cov_model_"+gsample+"_y_milca_"+gsample+"_y_milca.npz")['cov']
-d1=np.load("output_dam/dcov_1h4pt_"+gsample+"_y_milca_"+gsample+"_y_milca.npz")['cov']
-c2=np.load("output_dam/cov_jk_"+gsample+"_y_milca_"+gsample+"_y_milca.npz")['cov']
+ls=np.load("output_default/cls_y_milca_"+gsample+".npz")['ls']
+c1=np.load("output_default/cov_model_"+gsample+"_y_milca_"+gsample+"_y_milca.npz")['cov']
+d1=np.load("output_default/dcov_1h4pt_"+gsample+"_y_milca_"+gsample+"_y_milca.npz")['cov']
+c2=np.load("output_default/cov_jk_"+gsample+"_y_milca_"+gsample+"_y_milca.npz")['cov']
 c1+=d1
 plt.figure()
 ax=plt.gca()
@@ -23,9 +36,16 @@ ax.plot([-1,-1],[-1,-1],'k-',label='$i=j$')
 ax.plot([-1,-1],[-1,-1],'k--',label='$i=j+1$')
 ax.set_xscale('log')
 ax.set_yscale('log')
-ax.legend(loc='lower left',ncol=2,fontsize=15,frameon=False)
 ax.set_xlabel('$(\\ell_i+\\ell_j)/2$',fontsize=15)
 ax.set_ylabel('$|{\\rm Cov}(\\ell_i,\\ell_j)|$',fontsize=15)
[…]

### 2019-09-20 notes/paper/paper.tex
gaussian KDE for bH & by, minor improvements

@@
 \title[Tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations]{Tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations}
-\author[David Alonso]{Nick Koukoufilippas$^1$, David Alonso$^1$, Maciej Bilicki$^2$, John A. Peacock$^3$\\
-                      $^{1}$Department of Physics, University of Oxford, Keble Road, Oxford, OX1 3RH, UK\\
+\author[Koukoufilippas et al.]{Nick Koukoufilippas$^1$, David Alonso$^1$, Maciej Bilicki$^2$, John A. Peacock$^3$\\
+                      $^{1}$Department of Physics, University of Oxford, Keble Road, Oxford, OX1 3RH, United Kingdom\\
                       $^{2}$Center for Theoretical Physics, Polish Academy of Sciences, al. Lotnik\'ow 32/46, 02-668, Warsaw, Poland\\
@@
             \hline
-            2MPZ    & 0.07     & 0.33                         & $0.21^{+0.31}_{-0.05}$      & $0.087^{+0.052^{\phantom{A}}}_{-0.031}$                          & 0.92                  & 0.57               \\
-            \wisc-1 & 0.13     & 0.71                         & $0.62^{+0.14}_{-0.08}$      & $0.176^{+0.020^{\phantom{A}}}_{-0.025}$                          & 1.35                  & 0.09               \\
-            \wisc-2 & 0.18     & 0.73                         & $0.62^{+0.10}_{-0.07}$      & $0.188^{+0.013^{\phantom{A}}}_{-0.024}$                          & 0.87                  & 0.69               \\
-            \wisc-3 & 0.23     & 0.64                         & $0.64^{+0.07}_{-0.08}$      & $0.203^{+0.018^{\phantom{A}}}_{-0.023}$                          & 1.17                  & 0.22               \\
-            \wisc-4 & 0.27     & 0.55                         & $0.58^{+0.07}_{-0.07}$      & $0.197^{+0.020^{\phantom{A}}}_{-0.016}$                          & 1.04                  & 0.40               \\
-            \wisc-5 & 0.32     & 0.58                         & $0.61^{+0.09}_{-0.07}$      & $0.210^{+0.033^{\phantom{A}}}_{-0.010_{\phantom{A}}}$                          & 1.26                  & 0.12               \\
+            2MPZ    & 0.07     & 0.33                         & $0.24^{+0.26}_{-0.09}$      & $0.087^{+0.052^{\phantom{A}}}_{-0.031}$                          & 0.92                  & 0.57               \\
+            \wisc-1 & 0.13     & 0.71                         & $0.61^{+0.14}_{-0.07}$      & $0.176^{+0.020^{\phantom{A}}}_{-0.025}$                          & 1.35                  & 0.09               \\
+            \wisc-2 & 0.18     & 0.72                         & $0.64^{+0.09}_{-0.08}$      & $0.188^{+0.013^{\phantom{A}}}_{-0.024}$                          & 0.87                  & 0.69               \\
+            \wisc-3 & 0.23     & 0.66                         & $0.61^{+0.09}_{-0.06}$      & $0.203^{+0.018^{\phantom{A}}}_{-0.023}$                          & 1.17                  & 0.22               \\
+            \wisc-4 & 0.27     & 0.53                         & $0.55^{+0.10}_{-0.04}$      & $0.197^{+0.020^{\phantom{A}}}_{-0.016}$                          & 1.04                  & 0.40               \\
+            \wisc-5 & 0.32     & 0.56                         & $0.63^{+0.07}_{-0.09}$      & $0.210^{+0.033^{\phantom{A}}}_{-0.010_{\phantom{A}}}$                          & 1.26                  & 0.12               \\
             \hline
@@
 
-      The corresponding constraints on $1-\bH$ for all redshift bins are shown in the main panel of Fig.\!~\ref{fig:bh} as black circles with error bars (corresponding to the median and 68\% confidence interval).
-These results are summarized in Table \ref{tab:results}, where column 3 shows the maximum-likelihood value of $1-\bH$, while column 4 lists the peak of the marginalized 1-dimensional distribution and the confidence interval corresponding to the equal-probability values encompassing a total probability of 0.68.
+      The corresponding constraints on $1-\bH$ for all redshift bins are shown in the main panel of Fig.\!~\ref{fig:bh} as black circles with error bars.
+These values, which are also given explicitly in column 4 of Table \ref{tab:results}, correspond to the peak of the 1-dimensional distribution of $1-\bH$ and to the equal-probability values encompassing a total probability of 0.68.
+In Table \ref{tab:results}, column 3 shows the maximum-likelihood value of $1-\bH$.
 Columns 6 and 7 of the same table list the reduced $\chi^2$ values for each sample and their associated probability-to-exceed (PTE), respectively.

### 2019-09-20 plots/plot_bhydro.py
all plotting scripts in one place

@@ -1,5 +1,7 @@
 import os
-#os.chdir("../../")
+import sys
+sys.path.insert(0, os.getcwd())
+#os.chdir("../")
 import numpy as np
 from scipy.integrate import simps
 from scipy.interpolate import interp1d

### 2019-09-20 plots/plot_by.py

@@ -1,4 +1,7 @@
 import os
+import sys
+sys.path.insert(0, os.getcwd())
+#os.chdir("../")
 import numpy as np
 import pyccl as ccl
 from analysis.params import ParamRun

### 2019-09-20 plots/plot_clsyst.py

@@ -1,3 +1,7 @@
+import os
+import sys
+sys.path.insert(0, os.getcwd())
+#os.chdir("../")
 import pyccl as ccl
 import numpy as np
 import matplotlib.pyplot as plt
@@ -15,9 +19,9 @@ rc('text', usetex=True)
 
 sample='wisc3'
 
-dgg_wdpj=np.load("output_dam/cls_"+sample+"_"+sample+".npz")
-dgg_wodpj=np.load("output_dam_nodpj/cls_"+sample+"_"+sample+".npz")
-cov_gg=np.load("output_dam/cov_comb_m_"+sample+"_"+sample+
+dgg_wdpj=np.load("output_default/cls_"+sample+"_"+sample+".npz")
+dgg_wodpj=np.load("output_default_nodpj/cls_"+sample+"_"+sample+".npz")
+cov_gg=np.load("output_default/cov_comb_m_"+sample+"_"+sample+
                "_"+sample+"_"+sample+".npz")['cov']
 ls=dgg_wdpj['ls']
 

### 2019-09-20 plots/plot_covdiag.py

@@ -1,3 +1,7 @@
+import os
+import sys
+sys.path.insert(0, os.getcwd())
+#os.chdir("../")
 import numpy as np
 import matplotlib.pyplot as plt
 from matplotlib import rc

### 2019-09-20 plots/plot_fits.py

@@ -1,5 +1,7 @@
 import os
-#os.chdir("../..")
+import sys
+sys.path.insert(0, os.getcwd())
+#os.chdir("../")
 import numpy as np
 import pyccl as ccl
 from analysis.params import ParamRun
@@ -183,7 +185,7 @@ for s, v in enumerate(p.get("data_vectors")):
         ax1.set_xlim(lsg[i][0]/1.1, lsg[i][-1]*1.1)
         ax2.set_xlim(ax1.get_xlim())
         ax2.set_ylim(res[mask].min()-1, res[mask].max()+1)
-        ax2.set_ylim(-2.7, 2.7)        
+        ax2.set_ylim(-2.7, 2.7)
 
         # flip one data point start & end to draw line
         if not mask[0]: mask[np.where(mask == True)[0][0]] = False

### 2019-09-20 plots/plot_jks.py

@@ -1,3 +1,7 @@
+import os
+import sys
+sys.path.insert(0, os.getcwd())
+#os.chdir("../")
 import numpy as np
 import matplotlib.pyplot as plt
 
@@ -10,11 +14,11 @@ exps=['2mpz']+['wisc%d'%(n+1) for n in range(5)]
 nexp=len(exps)
 npars=len(pars)
 njk=461
-ds=[np.load("output_dam/sampler_lmin10_"+kmax+"_tinker08_ymilca_wnarrow_"+x+"_jkall.npz") for x in exps]
-ps=[np.load("output_dam/sampler_lmin10_"+kmax+"_tinker08_ymilca_wnarrow_"+x+"_properties.npz") for x in exps]
+ds=[np.load("output_default/sampler_lmin10_"+kmax+"_tinker08_ymilca_wnarrow_"+x+"_jkall.npz") for x in exps]
+ps=[np.load("output_default/sampler_lmin10_"+kmax+"_tinker08_ymilca_wnarrow_"+x+"_properties.npz") for x in exps]
 ms=[]
 for x in exps:
-    reader = emcee.backends.HDFBackend("output_dam/sampler_lmin10_"+kmax+"_tinker08_ymilca_wnarrow_"+x+"_chain.h5", read_only=True)
+    reader = emcee.backends.HDFBackend("output_default/sampler_lmin10_"+kmax+"_tinker08_ymilca_wnarrow_"+x+"_chain.h5", read_only=True)
     chain = reader.get_chain(flat=True)
     ms.append(np.mean(chain,axis=0))
 

### 2019-09-20 plots/plot_masked.py

@@ -1,0 +1,30 @@
+import os
+import sys
+#sys.path.insert(0, os.getcwd())
+os.chdir("../")
+import numpy as np
+import pyccl as ccl
+import matplotlib.pyplot as plt
+
+for sample in ['2mpz']+['wisc%d'%(i+1) for i in range(5)]:
+    d_gy_f=np.load("output_default/cls_y_milca_"+sample+".npz")
+    d_gy_m=np.load("output_mask/cls_y_milca_"+sample+".npz")
+    cv_gy_f=np.load("output_default/cov_comb_m_"+sample+"_y_milca_"+sample+"_y_milca.npz")['cov']
+    cv_gy_m=np.load("output_default_mask/cov_comb_m_"+sample+"_y_milca_"+sample+"_y_milca.npz")['cov']
+
+    d_gg_f=np.load("output_default/cls_"+sample+"_"+sample+".npz")
+    d_gg_m=np.load("output_mask/cls_"+sample+"_"+sample+".npz")
+    cv_gg_f=np.load("output_default/cov_comb_m_"+sample+"_"+sample+"_"+sample+"_"+sample+".npz")['cov']
+    cv_gg_m=np.load("output_default_mask/cov_comb_m_"+sample+"_"+sample+"_"+sample+"_"+sample+".npz")['cov']
+
+    plt.figure()
+    plt.title(sample+" gg")
+    plt.errorbar(d_gg_f['ls'],d_gg_f['cls']-d_gg_f['nls'],yerr=np.sqrt(np.diag(cv_gg_f)),fmt='r-')
+    plt.errorbar(d_gg_m['ls'],d_gg_m['cls']-d_gg_m['nls'],yerr=np.sqrt(np.diag(cv_gg_m)),fmt='k-')
+    plt.loglog()
+    plt.figure()
+    plt.title(sample+" gy")
+    plt.errorbar(d_gy_f['ls'],d_gy_f['cls']-d_gy_f['nls'],yerr=np.sqrt(np.diag(cv_gy_f)),fmt='r-')
+    plt.errorbar(d_gy_m['ls'],d_gy_m['cls']-d_gy_m['nls'],yerr=np.sqrt(np.diag(cv_gy_m)),fmt='k-')
+    plt.loglog()
+    plt.show()

### 2019-09-20 plots/plot_masks.py

@@ -1,3 +1,7 @@
+import os
+import sys
+sys.path.insert(0, os.getcwd())
+#os.chdir("../")
 import numpy as np
 import matplotlib.pyplot as plt
 from matplotlib import cm
@@ -17,5 +21,5 @@ plt.savefig('notes/paper/mask_g.pdf',bbox_inches='tight')
 hp.mollview(msk_y,cbar=False,title='')
 #hp.mollview(msk_y+msk_y_m,cbar=False,title='')
 hp.graticule()
-plt.savefig('notes/paper/mask_y.pdf',bbox_inches='tight')
+#plt.savefig('notes/paper/mask_y.pdf',bbox_inches='tight')
 plt.show()

### 2019-09-20 plots/plot_mf.py

@@ -1,3 +1,7 @@
+import os
+import sys
+sys.path.insert(0, os.getcwd())
+#os.chdir("../")
 import pyccl as ccl
 import numpy as np
 import matplotlib.pyplot as plt

### 2019-09-20 plots/plot_nzs.py

@@ -1,3 +1,7 @@
+import os
+import sys
+sys.path.insert(0, os.getcwd())
+#os.chdir("../")
 import numpy as np
 import matplotlib.pyplot as plt
 import healpy as hp
@@ -27,7 +31,7 @@ cols=['r']
 cm_wisc=cm.get_cmap('Blues')
 for i in np.arange(5) :
     cols.append(cm_wisc(0.2+((i+1.)/5.)*0.8))
-                        
+
 nzs=[]
 nzs.append(Nz("data/dndz/2MPZ_bin1.txt","data/maps/2mpz_05_01_512.fits","data/maps/mask_v3.fits","2MPZ"))
 nzs.append(Nz("data/dndz/WISC_bin1.txt","data/maps/2dstarsub_WISC_cleaned_public.bin_0.1_z_0.15.Pix512.fits","data/maps/mask_v3.fits","WI$\\times$SC-1"))

### 2019-09-29 paper.tex
Update on Overleaf.

--- 2019-09-20 notes/paper/paper.tex
@@
                       $^{2}$Center for Theoretical Physics, Polish Academy of Sciences, al. Lotnik\'ow 32/46, 02-668, Warsaw, Poland\\
-                      $^{3}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ, United Kingdom
+                      $^{3}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh, EH9 3HJ, United Kingdom
                       }

### 2019-10-15 model/power_spectrum.py
fixed interpolation bug

@@ -30,7 +30,7 @@ class HalomodCorrection(object):
                           for a in 1. / (1 + zarr)])
         ratio = pk_hf / pk_hm
 
-        self.rk_func = interp2d(lkarr, zarr, ratio,
+        self.rk_func = interp2d(lkarr, 1/(1+zarr), ratio,
                                 bounds_error=False, fill_value=1)
 
     def rk_interp(self, k, a):

### 2019-10-15 plots/plot_bhydro.py
changed to reflect current directory structure and new param filenames

@@ -1,7 +1,9 @@
+# move to parent dir
 import os
-import sys
-sys.path.insert(0, os.getcwd())
-#os.chdir("../")
+THIS_PATH = os.path.dirname(os.path.realpath(__file__))
+NEW_PATH = "/".join(THIS_PATH.split("/")[:-1])
+os.chdir("NEW_PATH")
+####
 import numpy as np
 from scipy.integrate import simps
 from scipy.interpolate import interp1d
@@ -59,12 +61,12 @@ def get_dndz(fname, width):
     return zd, Nd_new
 
 
-param_yml = ["params_dam_wnarrow.yml",
-             "params_dam_ynilc.yml",
-             "params_dam_wfixed.yml",
-             "params_dam_tinker10.yml",
-#             "params_dam_wnarrow_ns.yml",
-#             "params_dam_masked.yml"
+param_yml = ["params_wnarrow.yml",
+             "params_ynilc.yml",
+             "params_wfixed.yml",
+             "params_tinker10.yml",
+#             "params_wnarrow_ns.yml",
+#             "params_masked.yml"
 ]
 
 sci = [r"$\mathrm{2MPZ}$"] + \
@@ -169,4 +171,3 @@ hist.legend(loc="lower center", bbox_to_anchor=[0.5, -0.15],
 
 plt.savefig("notes/paper/bhydro.pdf", bbox_inches="tight")
 plt.show()
-#os.chdir("images/b_hydro/")

### 2019-10-15 plots/plot_by.py

@@ -1,7 +1,9 @@
+# move to parent dir
 import os
-import sys
-sys.path.insert(0, os.getcwd())
-#os.chdir("../")
+THIS_PATH = os.path.dirname(os.path.realpath(__file__))
+NEW_PATH = "/".join(THIS_PATH.split("/")[:-1])
+os.chdir("NEW_PATH")
+####
 import numpy as np
 import pyccl as ccl
 from analysis.params import ParamRun
@@ -55,7 +57,7 @@ def get_bpe(z, n_r, delta, nmass=256):
     return itg.simps(et*bh*mfunc,x=lmarr)
 
 
-fname_params = "params_dam_wnarrow.yml"
+fname_params = "params_wnarrow.yml"
 p = ParamRun(fname_params)
 cosmo = p.get_cosmo()
 

### 2019-10-15 plots/plot_clsyst.py

@@ -1,7 +1,9 @@
+# move to parent dir
 import os
-import sys
-sys.path.insert(0, os.getcwd())
-#os.chdir("../")
+THIS_PATH = os.path.dirname(os.path.realpath(__file__))
+NEW_PATH = "/".join(THIS_PATH.split("/")[:-1])
+os.chdir("NEW_PATH")
+####
 import pyccl as ccl
 import numpy as np
 import matplotlib.pyplot as plt
@@ -25,7 +27,7 @@ cov_gg=np.load("output_default/cov_comb_m_"+sample+"_"+sample+
                "_"+sample+"_"+sample+".npz")['cov']
 ls=dgg_wdpj['ls']
 
-fname_params = "params_dam_wnarrow.yml"
+fname_params = "params_wnarrow.yml"
 p = ParamRun(fname_params)
 cosmo = p.get_cosmo()
 hm_correction = HalomodCorrection(cosmo)

### 2019-10-15 plots/plot_covdiag.py

@@ -1,7 +1,9 @@
+# move to parent dir
 import os
-import sys
-sys.path.insert(0, os.getcwd())
-#os.chdir("../")
+THIS_PATH = os.path.dirname(os.path.realpath(__file__))
+NEW_PATH = "/".join(THIS_PATH.split("/")[:-1])
+os.chdir("NEW_PATH")
+####
 import numpy as np
 import matplotlib.pyplot as plt
 from matplotlib import rc

### 2019-10-15 plots/plot_dndz.py

@@ -1,7 +1,9 @@
+# move to parent dir
 import os
-import sys
-sys.path.insert(0, os.getcwd())
-#os.chdir("../")
+THIS_PATH = os.path.dirname(os.path.realpath(__file__))
+NEW_PATH = "/".join(THIS_PATH.split("/")[:-1])
+os.chdir("NEW_PATH")
+####
 import numpy as np
 import matplotlib.pyplot as plt
 from matplotlib import cm

### 2019-10-15 plots/plot_fits.py

@@ -1,7 +1,9 @@
+# move to parent dir
 import os
-import sys
-sys.path.insert(0, os.getcwd())
-#os.chdir("../")
+THIS_PATH = os.path.dirname(os.path.realpath(__file__))
+NEW_PATH = "/".join(THIS_PATH.split("/")[:-1])
+os.chdir("NEW_PATH")
+####
 import numpy as np
 import pyccl as ccl
 from analysis.params import ParamRun
@@ -37,7 +39,7 @@ class thr(object):
                           **pars)
 
 
-fname_params = "params_dam_wnarrow.yml"
+fname_params = "params_wnarrow.yml"
 p = ParamRun(fname_params)
 cosmo = p.get_cosmo()
 

### 2019-10-15 plots/plot_jks.py

@@ -1,7 +1,9 @@
+# move to parent dir
 import os
-import sys
-sys.path.insert(0, os.getcwd())
-#os.chdir("../")
+THIS_PATH = os.path.dirname(os.path.realpath(__file__))
+NEW_PATH = "/".join(THIS_PATH.split("/")[:-1])
+os.chdir("NEW_PATH")
+####
 import numpy as np
 import matplotlib.pyplot as plt
 

### 2019-10-15 plots/plot_masked.py

@@ -1,7 +1,9 @@
+# move to parent dir
 import os
-import sys
-#sys.path.insert(0, os.getcwd())
-os.chdir("../")
+THIS_PATH = os.path.dirname(os.path.realpath(__file__))
+NEW_PATH = "/".join(THIS_PATH.split("/")[:-1])
+os.chdir("NEW_PATH")
+####
 import numpy as np
 import pyccl as ccl
 import matplotlib.pyplot as plt

### 2019-10-15 plots/plot_masks.py

@@ -1,14 +1,16 @@
+# move to parent dir
 import os
-import sys
-sys.path.insert(0, os.getcwd())
-#os.chdir("../")
+THIS_PATH = os.path.dirname(os.path.realpath(__file__))
+NEW_PATH = "/".join(THIS_PATH.split("/")[:-1])
+os.chdir("NEW_PATH")
+####
 import numpy as np
 import matplotlib.pyplot as plt
 from matplotlib import cm
 import healpy as hp
 import yaml
 
-with open('params_dam_wnarrow.yml') as f:
+with open('params_wnarrow.yml') as f:
     p = yaml.safe_load(f)
 
 msk_g=hp.read_map(p['masks']['mask_lowz'],verbose=False)

### 2019-10-15 plots/plot_mf.py

@@ -1,7 +1,9 @@
+# move to parent dir
 import os
-import sys
-sys.path.insert(0, os.getcwd())
-#os.chdir("../")
+THIS_PATH = os.path.dirname(os.path.realpath(__file__))
+NEW_PATH = "/".join(THIS_PATH.split("/")[:-1])
+os.chdir("NEW_PATH")
+####
 import pyccl as ccl
 import numpy as np
 import matplotlib.pyplot as plt

### 2019-10-15 plots/plot_nzs.py

@@ -1,7 +1,9 @@
+# move to parent dir
 import os
-import sys
-sys.path.insert(0, os.getcwd())
-#os.chdir("../")
+THIS_PATH = os.path.dirname(os.path.realpath(__file__))
+NEW_PATH = "/".join(THIS_PATH.split("/")[:-1])
+os.chdir("NEW_PATH")
+####
 import numpy as np
 import matplotlib.pyplot as plt
 import healpy as hp

### 2019-10-15 paper.tex
Update on Overleaf.

@@
   \date{\today}
-  \pagerange{1--18} \pubyear{2019}
+  \pagerange{1--19} \pubyear{2019}
   \maketitle
@@
 
-    All maps were generated and operated on using the {\tt HEALPix} pixelisation scheme \citep{2005ApJ...622..759G} with resolution parameter $N_{\rm side}=512$, corresponding to a pixel size $\theta_{\rm pix}\sim7'$.
+    All maps were generated and operated on using the {\tt HEALPix} pixelisation scheme \citep{2005ApJ...622..759G} with resolution parameter $N_{\rm side}=512$, corresponding to a pixel size $\theta_{\rm pix}\sim7'$ ($\ell \sim 1570$).
 
@@
       For small levels of contamination, the impact of a given systematic on an observed sky map can be modelled at the linear level:
-      \begin{equation}
+      \begin{equation}\label{eq:deproj}
         {\bf m}_{\rm obs}={\bf m}_{\rm true} + \epsilon\,{\bf t}.
-      \end{equation}\label{eq:deproj}
+      \end{equation}
       Here ${\bf m}_{\rm obs}$ and ${\bf m}_{\rm true}$ are vectors corresponding to the observed sky map and the true underlying quantity we wish to map respectively, ${\bf t}$ is a template map describing the contaminant (e.g.
@@
 
-      In particular, our model of the $y\times \delta_g$ cross-correlation is particularly sensitive to the width of the redshift distributions.
-This is because, while the amplitude to the galaxy auto-correlation is strongly affected by the width of the distribution (wider $p(z)$'s reduce the clustering amplitude), the cross-correlation with $y$ is almost insensitive to it.
-We therefore introduce an additional parameter, $w_z$, that stretches the support of the redshift distribution while preserving unit total probability.
+      In particular, our model of the $y\times \delta_g$ cross-correlation is very sensitive to the width of the redshift distributions.
+This is because wider redshift distributions, which imply lower clustering amplitude, affect the amplitude of the galaxy auto-correlation, $\delta_g\times \delta_g$.
+At the same time, the $y$ auto-spectrum is almost insensitive to clustering; therefore the width only affects the $y\ times \delta_g$ cross-correlation in our analysis.
+We introduce an additional parameter, $w_z$, that stretches the support of the redshift distribution while preserving unit total probability.
 Concretely, given a fiducial distribution $p_{\rm fid}(z)$ with mean redshift $\bar{z}$, $w_z$ is implemented as

### 2019-10-16 notes/paper/paper.tex
sensitivity comment

@@
 
-      In particular, our model of the $y\times \delta_g$ cross-correlation is very sensitive to the width of the redshift distributions.
-This is because wider redshift distributions, which imply lower clustering amplitude, affect the amplitude of the galaxy auto-correlation, $\delta_g\times \delta_g$.
-At the same time, the $y$ auto-spectrum is almost insensitive to clustering; therefore the width only affects the $y\ times \delta_g$ cross-correlation in our analysis.
+      In particular, our constraints on $1-\bH$ are very sensitive to the width of the redshift distributions.
+This is because wider redshift distributions, which lead to lower projected clustering amplitudes, affect the galaxy auto-correlation, $\delta_g\times \delta_g$, while the $y\times\delta_g$ cross-correlation is almost insensitive to the width.
 We introduce an additional parameter, $w_z$, that stretches the support of the redshift distribution while preserving unit total probability.

### 2019-10-19 likelihood/chanal.py
gaussian-KDE can extend; at exception vpercentile smoothes

@@ -12,14 +12,21 @@ from likelihood.sampler import Sampler
 from model.theory import get_theory
 from model.power_spectrum import HalomodCorrection, hm_bias
 from model.utils import selection_planck_erf, selection_planck_tophat
+from scipy.stats import norm
+_PP = norm.sf(-1)-norm.sf(1)
 
 
 
 def vpercentile(chain):
-    """Best fit and errors using manual watershed method."""
-    percentile = 68
+    """Best fit and errors using manual watershed."""
+    from scipy.signal import savgol_filter
+    percentile = 100*_PP
     pdf, x = np.histogram(chain, bins=100, density=True)
     x = (x[:-1] + x[1:])/2
+
+    # smooth posterior
+    window = int(np.ceil(np.sqrt(pdf.size)) // 2 * 2 + 1)
+    pdf = savgol_filter(pdf, window, 3)
 
     par_bf = x[np.argmax(pdf)]
     eps = 0.005
@@ -39,37 +46,55 @@ def vpercentile(chain):
 
 
 def gauss_kde(chain):
-    """Best fit and erros using Gaussian-KDE."""
-    def get_prob(a,b):
+    """Best fit and erros using Gaussian-KDE watershed."""
+    def get_prob(a, b, f):
         xr=np.linspace(a, b, 128)
-        return simps(d(xr), x=xr)
+        return simps(f(xr), x=xr)
 
-    def cutfunc(pthr):
-        r_lo = root_scalar(limfunc, args=(pthr), bracket=(x_min,x_bf)).root
-        r_hi = root_scalar(limfunc, args=(pthr), bracket=(x_bf,x_max)).root
-        pr = get_prob(r_lo, r_hi)
-        return pr-0.68
+    def cutfunc(pthr, f, x_lim=None):
+        if x_lim is None:
+            x1, x2 = x_min, x_max
+        else:
+            x1, x2 = x_lim
+        r_lo = root_scalar(limfunc, args=(pthr, f), bracket=(x1, x_bf)).root
+        r_hi = root_scalar(limfunc, args=(pthr, f), bracket=(x_bf, x2)).root
+        pr = get_prob(r_lo, r_hi, f)
+        return pr-_PP
 
-    minfunc = lambda x: -d(x)
-    limfunc = lambda x, thr: d(x)[0]-thr
+    def extend_kde(f, X=20):
+        """Extend kde boundaries by X% in case of boundary inconsistency."""
+        import warnings
[…]

### 2019-10-19 plots/plot_by.py
new by plot, has MILCA+NILC

@@ -75,7 +75,7 @@ def by_pts(filename):
 
 zm, bym, chainsm = by_pts(fname_params[0])  # m for y_milca
 zn, byn, chainsn = by_pts(fname_params[1])  # n for y_nilc
-zn += 0.1
+zn += 0.01
 
 # DES data
 DESx = np.array([0.15, 0.24, 0.2495, 0.383, 0.393, 0.526, 0.536, 0.678, 0.688])
@@ -98,9 +98,9 @@ etinf = np.array([get_bpe(z, 20, 200) for z in zarr])*1e6
 fig, ax = plt.subplots(figsize=(9,7))
 ax.violinplot(chainsm.T, zm, widths=0.03, showextrema=False)
 ax.errorbar(zm, bym[0], bym[1:],
-            fmt="o", c="navy", elinewidth=2, label="This work, $y$ MILCA map")
+            fmt="o", c="royalblue", elinewidth=2, label="This work, Planck MILCA $y$ map")
 ax.errorbar(zn, byn[0], byn[1:],
-            fmt="o", c="royalblue", elinewidth=2, label="This work, $y$ NILC map")
+            fmt="o", c="mediumorchid", elinewidth=2, label="This work, Planck NILC $y$ map")
 
 ax.errorbar(black[0], black[1], black[2], fmt="ko", elinewidth=2,
             label="V17")
@@ -119,7 +119,10 @@ ax.plot(zarr,etinf,':',label='$r_{\\rm max}=\\infty$',c='#AAAAAA')
 ax.tick_params(labelsize="large")
 ax.set_xlabel("$z$", fontsize=17)
 ax.set_ylabel(r"$\mathrm{\langle bP_e \rangle \ \big[ meV \ cm^{-3} \big] }$", fontsize=17)
-ax.legend(loc="upper left", frameon=False, ncol=2, fontsize=14)
+
+handles, labels = ax.get_legend_handles_labels()
+handles, labels = map(lambda x: list(np.roll(x, 5)), [handles, labels])
+ax.legend(handles, labels, loc="upper left", frameon=False, ncol=2, fontsize=13)
 
 fig.savefig("notes/paper/by.pdf", bbox_inches="tight")
 plt.show()

### 2019-10-19 plots/plot_fits.py
re-coloured 1h-term

@@ -199,8 +199,8 @@ for s, v in enumerate(p.get("data_vectors")):
 
 
         # plot data & theory
-        ax1.plot(ll, t1, ls=":", c="darkgreen", alpha=0.3)
-        ax1.plot(lsd[i], tv1hd[i], ls="-", c="darkgreen", alpha=0.3,
+        ax1.plot(ll, t1, ls=":", c="darkred", alpha=0.3)
+        ax1.plot(lsd[i], tv1hd[i], ls="-", c="darkred", alpha=0.3,
                  label=r"$\mathrm{1}$-$\mathrm{halo}$")
 
         ax1.plot(ll, t2, ls=":", c="navy", alpha=0.3)

### 2019-10-19 notes/paper/paper.tex

@@
     2MPZ was constructed by cross-matching the extended-source catalogue from the 2 Micron All-Sky Survey \citep[2MASS,][]{2006AJ....131.1163S,2000AJ....119.2498J} with the photographic plates of SuperCOSMOS \citep{2001MNRAS.326.1295H,2016MNRAS.462.2085P} and the photometry of the Wide-field Infrared Survey Explorer (WISE: \citejap{2010AJ....140.1868W}).
-After applying an apparent magnitude cut $K_s<13.9$ to achieve uniformity, 2MPZ includes over 940,000 sources observed in 8 bands: SuperCOSMOS's optical $(B,R,I)$, 2MASS's near-infrared $(J,H,K_s)$ and WISE's mid-infrared $(W1,W2)$.
+After applying an apparent magnitude cut $K_s<13.9$ (in Vega system) to achieve uniformity, 2MPZ includes over 940,000 sources observed in 8 bands: SuperCOSMOS's optical $(B,R,I)$, 2MASS's near-infrared $(J,H,K_s)$ and WISE's mid-infrared $(W1,W2)$.
 Photometric redshifts were extracted using the neural network code {\tt ANNz} \citep{2004PASP..116..345C} trained on a large spectroscopic sample from overlapping surveys.
